### 2006-07-17 prince/samples/TestPlotsExtended.tex
Initial revision

\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}

%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Wednesday, January 11, 2006 13:01:05}
%TCIDATA{LastRevised=Wednesday, January 18, 2006 15:41:47}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Standard LaTeX\Blank - Standard LaTeX Article">}
%TCIDATA{CSTFile=40 LaTeX article.cst}
%TCIDATA{ComputeDefs=
%$f(x)=e^{-x^{2}}$
%$g(x)=f^{\prime }(x)$
%$\rho (\phi ,\theta )=(1.2)^{\phi }\sin (\theta )$
%$h(a,b)=a^{2}+b^{3}$
%}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\input{tcilatex}
\begin{document}

\section{Simple Function tests:}

\subsection{\qquad 2D}

\subsubsection{Plot 2D, Rectangular}

$x\sin \dfrac{5}{x}$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-1.0852558745991";yviewmax
"4.2078841327291";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$x\sin \dfrac{5}{x}$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AJ00.xvz';valid_file "T";tempfilename
'ITB8AJ00.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 2D, Implicit}

$\left( x-2\right) ^{2}+\left( y-3\right) ^{2}=25$\FRAME{dtbpFX}{4.5in}{3in}{%
0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5.001";xviewmax "5.001";yviewmin "-5.001";yviewmax
"5.001";plottype 12;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 24;num-y-gridlines
24;plotstyle "patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};yis
\TEXUX{y};var1name \TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$\left(
x-2\right) ^{2}+\left( y-3\right) ^{2}=25$};linecolor "black";linestyle
1;pointstyle "point";linethickness 1;lineAttributes "Solid";var1range
"-5,5";var2range "-5,5";num-x-gridlines 24;num-y-gridlines 24;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AJ01.xvz';valid_file "T";tempfilename
'ITB8AJ01.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 2D, Inequality}

\subsubsection{$x+y^{2}<5$\protect\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin
"-5.001";xviewmax "5.001";yviewmin "-5.001";yviewmax "5.001";plottype
25;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 120;num-y-gridlines
120;plotstyle "patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};yis
\TEXUX{y};var1name \TEXUX{$x$};var2name \TEXUX{$y$};function
\TEXUX{$x+y^{2}<5$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";num-x-gridlines 120;num-y-gridlines 120;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";fillColor
"[flat::RGB:0x00ffcd99]";fillColor2 "[flat::RGB:0x00ffffff]";fillStyle
"Solid";VCamFile 'ITB8AN02.xvz';valid_file "T";tempfilename
'ITB8AN03.wmf';tempfile-properties "XPR";}}Fill color blue, background
magenta\protect\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5.001";xviewmax
"5.001";yviewmin "-5.001";yviewmax "5.001";plottype 25;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 120;num-y-gridlines
120;plotstyle "patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};yis
\TEXUX{y};var1name \TEXUX{$x$};var2name \TEXUX{$y$};function
\TEXUX{$x+y^{2}<5$};linecolor "magenta";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";num-x-gridlines 120;num-y-gridlines 120;curveColor
"[flat::RGB:0x00ff00ff]";curveStyle "Line";fillColor
"[flat::RGB:0x00ff0000]";fillColor2 "[flat::RGB:0x00ff00ff]";fillStyle
"Solid";VCamFile 'ITB8AQ03.xvz';valid_file "T";tempfilename
'ITB8AQ05.wmf';tempfile-properties "XPR";}}}

\subsubsection{Plot 2D, Parametric}

$\left( \sin 2t,\cos 3t\right) $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin "-1";xviewmax
"1";yviewmin "-1";yviewmax "1.00015585770157";plottype 19;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{t};var1name
\TEXUX{$t$};function \TEXUX{$\left( \sin 2t,\cos 3t\right) $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AR04.xvz';valid_file "T";tempfilename
'ITB8AR06.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 2D, Polar}

$1-\sin \theta +2\sin 3\theta \qquad $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{%
Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-3.1416";xmax
"3.1416";xviewmin "-2.27272652935265";xviewmax "2.28071430316265";yviewmin
"-4";yviewmax "1.3624997567594";plottype 8;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{v58130};var1name
\TEXUX{$\theta $};function \TEXUX{$1-\sin \theta +2\sin 3\theta $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";coordinateSystem "polar";var1range "-3.1416,3.1416";num-x-gridlines
100;curveColor "[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AR05.xvz';valid_file "T";tempfilename
'ITB8AR07.wmf';tempfile-properties "XPR";}}

This one uses equal scaling on axes: $1-\sin \theta +2\sin 3\theta $\FRAME{%
dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific
Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-3.1416";xmax "3.1416";xviewmin "-2.27272652935265";xviewmax
"2.28071430316265";yviewmin "-4";yviewmax "1.3624997567594";plottype
8;axesFont "Times New Roman,12,0000000000,useDefault,normal";constrained
TRUE;numpoints 100;plotstyle "patch";axesstyle "normal";axestips FALSE;xis
\TEXUX{v58130};var1name \TEXUX{$\theta $};function \TEXUX{$1-\sin \theta
+2\sin 3\theta $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";coordinateSystem
"polar";var1range "-3.1416,3.1416";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AS06.xvz';valid_file "T";tempfilename
'ITB8AS08.wmf';tempfile-properties "XPR";}}

\bigskip Plot as parametric, then edit plot and change Items Plotted/Plot
type to polar This one uses 400 points: $\left( r,r^{2}\right) $\FRAME{dtbpFX%
}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific Word";type
"MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";xviewmin "-5";xviewmax "5";yviewmin
"-4.84609122932098";yviewmax "4.84609122932098";plottype 22;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{t};var1name
\TEXUX{$t$};function \TEXUX{$\left( r,r^{2}\right) $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";coordinateSystem "polar";var1range "-5,5";num-x-gridlines
400;curveColor "[flat::RGB:0000000000]";curveStyle
"Line";rangeset"X";VCamFile 'ITB8AS07.xvz';valid_file "T";tempfilename
'ITB8AS09.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 2D, Conformal}

$\dfrac{z-1}{z+1}$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "0";xmax "1";ymin "0";ymax "1";xviewmin
"-1.00012000010001";xviewmax "0.200120000020012";yviewmin
"-0.00010000010002";yviewmax "1.00010000010002";plottype 9;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpts-xgridline
15;numpts-ygridline 15;num-x-gridlines 11;num-y-gridlines 11;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{z};var1name
\TEXUX{$z$};function \TEXUX{$\dfrac{z-1}{z+1}$};linecolor "black";linestyle
1;pointstyle "point";linethickness 1;lineAttributes "Solid";var1range
"0,1";var2range "0,1";num-x-gridlines 11;num-y-gridlines 11;numpts-xgridline
15;numpts-ygridline 15;curveColor "[flat::RGB:0000000000]";curveStyle
"Line";curveColor2 "[flat::RGB:0x00000080]";VCamFile
'ITB8AS08.xvz';valid_file "T";tempfilename
'ITB8AS0A.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 2D, Gradient}

(plot 3d rectangular, 2d gradient) $x^{2}+2y^{2}$\FRAME{dtbpFX}{4.5in}{3in}{%
0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5.001";xviewmax "5.001";yviewmin "-5.001";yviewmax
"5.001";plottype 10;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 10;num-y-gridlines
10;plotstyle "patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};yis
\TEXUX{y};var1name \TEXUX{$x$};var2name \TEXUX{$y$};function
\TEXUX{$x^{2}+2y^{2}$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";num-x-gridlines 10;num-y-gridlines 10;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AU09.xvz';valid_file "T";tempfilename
'ITB8AU0B.wmf';tempfile-properties "XPR";}}\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{%
}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"0";zviewmax "75";phi 45;theta 45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$x^{2}+2y^{2}$};linestyle 1;pointstyle
"point";lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";VCamFile 'ITB8AV0A.xvz';valid_file "T";tempfilename
'ITB8AV0C.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 2D, Vector Field}

$\left( \dfrac{1}{\sqrt{\left( 1+\left\vert y^{2}-t^{2}\right\vert
^{2}\right) }},\dfrac{y^{2}-t^{2}}{\sqrt{\left( 1+\left\vert
y^{2}-t^{2}\right\vert ^{2}\right) }}\right) $\FRAME{dtbpFX}{4.5in}{3in}{0pt%
}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5.001";xviewmax "5.001";yviewmin "-5.001";yviewmax
"5.001";plottype 11;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 10;num-y-gridlines
10;plotstyle "patch";axesstyle "normal";axestips FALSE;xis \TEXUX{t};yis
\TEXUX{y};var1name \TEXUX{$t$};var2name \TEXUX{$y$};function \TEXUX{$\left(
\dfrac{1}{\sqrt{\left( 1+\left\vert y^{2}-t^{2}\right\vert ^{2}\right)
}},\dfrac{y^{2}-t^{2}}{\sqrt{\left( 1+\left\vert y^{2}-t^{2}\right\vert
^{2}\right) }}\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";num-x-gridlines 10;num-y-gridlines 10;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8AW0B.xvz';valid_file "T";tempfilename
'ITB8AW0D.wmf';tempfile-properties "XPR";}}

\bigskip

\section{\qquad 3D}

\subsubsection{plotting curves in space}

$\left[ 
\begin{array}{ccc}
t & 2\sin t & t^{2}%
\end{array}%
\right] $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5.000000001";xviewmax
"5.000000001";yviewmin "-1.9908159159";yviewmax "1.9908159159";zviewmin
"-2.5E-9";zviewmax "25.0000000025";phi 45;theta 45;plottype 5;axesFont
"Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{t};yis \TEXUX{y};var1name \TEXUX{$t$};var2name
\TEXUX{$y$};function \TEXUX{$\left[
\MATRIX{3,1}{c}\VR{,,c,,,}{,,c,,,}{,,c,,,}{,,,,,}\HR{,}\CELL{t}\CELL{2\sin
t}\CELL{t^{2}}\right] $};linestyle 1;pointstyle "point";lineAttributes
"Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";num-x-gridlines 25;num-y-gridlines
25;VCamFile 'ITB8AW0C.xvz';valid_file "T";tempfilename
'ITB8AW0E.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 3D, Rectangular}

$\sin x+\cos y$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin
"-5";yviewmax "5";zviewmin "-1.97708196246";zviewmax "1.99540795775";phi
45;theta 45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$\sin x+\cos y$};linestyle 1;pointstyle
"point";lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";VCamFile 'ITB8AX0D.xvz';valid_file "T";tempfilename
'ITB8AX0F.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 3D, Cylindrical}

X, y, z axis labels with grid lines, rotated with vcam $\left[ r,\theta
,\theta \right] $\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-3.1416";xmax "3.1416";ymin "0";ymax "5";xviewmin
"-4.99999999987";xviewmax "5";yviewmin "-4.99999999997";yviewmax
"4.99999999997";zviewmin "-3.1416";zviewmax "3.1416";phi 45;theta
45;cameraOrientation "[0,0,0.106103]";cameraOrientationFixed TRUE;plottype
14;labeloverrides 7;x-label "X axis";y-label "Y axis";z-label "Z axis
label";axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips TRUE;gridLines
TRUE;plotshading "XYZ";lighting 0;xis \TEXUX{v58130};yis \TEXUX{r};var1name
\TEXUX{$\theta $};var2name \TEXUX{$r$};function \TEXUX{$\left[ r,\theta
,\theta \right] $};linestyle 1;pointstyle "point";lineAttributes
"Solid";coordinateSystem "cylindrical";var1range "-3.1416,3.1416";var2range
"0,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";VCamFile 'ITB8AY0E.xvz';valid_file "T";tempfilename
'ITB8AY0G.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 3D, Gradient}

\bigskip $xz+xy+yz$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";zmin "-5";zmax "5";xviewmin
"-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin "-5";zviewmax "5";phi
45;theta 45;plottype 16;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 6;num-y-gridlines
6;num-z-gridlines 6;plotstyle "line";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};zis
\TEXUX{z};var1name \TEXUX{$x$};var2name \TEXUX{$y$};var3name
\TEXUX{$z$};function \TEXUX{$xz+xy+yz$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";var3range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";num-x-gridlines 6;num-y-gridlines
6;num-z-gridlines 6;VCamFile 'ITB8AZ0F.xvz';valid_file "T";tempfilename
'ITB8AZ0H.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 3D, Implicit}

\bigskip $xz+xy+yz=-1$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";zmin "-5";zmax "5";xviewmin
"-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin "-5";zviewmax "5";phi
45;theta 45;plottype 18;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 10;num-y-gridlines
10;num-z-gridlines 10;plotstyle "patch";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};zis
\TEXUX{z};var1name \TEXUX{$x$};var2name \TEXUX{$y$};var3name
\TEXUX{$z$};function \TEXUX{$xz+xy+yz=-1$};linestyle 1;pointstyle
"point";lineAttributes "Solid";var1range "-5,5";var2range "-5,5";var3range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 10;num-y-gridlines 10;num-z-gridlines
10;surfaceMesh "Mesh";VCamFile 'ITB8B00G.xvz';valid_file "T";tempfilename
'ITB8B00I.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 3D, Rectangular (parametric plots)}

$\left[ s\sin s\cos t,s\cos s\cos t,s\sin t\right] $\FRAME{dtbpFX}{4.5in}{3in%
}{0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-4.79462137332";xviewmax "4.70675516462";yviewmin
"-3.27224668237";yviewmax "3.27224668237";zviewmin "-4.97703978876";zviewmax
"4.97703978876";phi 45;theta 45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{s};yis \TEXUX{t};var1name \TEXUX{$s$};var2name
\TEXUX{$t$};function \TEXUX{$\left[ s\sin s\cos t,s\cos s\cos t,s\sin
t\right] $};linestyle 1;pointstyle "point";lineAttributes "Solid";var1range
"-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8B50H.xvz';valid_file "T";tempfilename
'ITB8B50J.wmf';tempfile-properties "XPR";}}

\subsubsection{Plot 3D, Spherical}

\bigskip $2$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-3.1416";xmax "3.1416";ymin "0";ymax "3.1416";xviewmin
"-1.99999999993";xviewmax "1.99999999999";yviewmin "-1.99999999997";yviewmax
"1.99999999997";zviewmin "-1.99999999995";zviewmax "2";phi 45;theta
45;plottype 15;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{v58130};yis \TEXUX{v58144};var1name
\TEXUX{$\theta $};var2name \TEXUX{$\phi $};function \TEXUX{$2$};linestyle
1;pointstyle "point";lineAttributes "Solid";coordinateSystem
"spherical";var1range "-3.1416,3.1416";var2range "0,3.1416";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8B60I.xvz';valid_file "T";tempfilename
'ITB8B60K.wmf';tempfile-properties "XPR";}}Equal scaling, wireframe,
gridlines\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-3.1416";xmax "3.1416";ymin "0";ymax "3.1416";xviewmin
"-1.99999999993";xviewmax "1.99999999999";yviewmin "-1.99999999997";yviewmax
"1.99999999997";zviewmin "-1.99999999995";zviewmax "2";phi 45;theta
45;plottype 15;axesFont "Times New
Roman,12,0000000000,useDefault,normal";constrained TRUE;num-x-gridlines
25;num-y-gridlines 25;plotstyle "wireframe";axesstyle "normal";axestips
FALSE;gridLines TRUE;plotshading "XYZ";lighting 0;xis \TEXUX{v58130};yis
\TEXUX{v58144};var1name \TEXUX{$\theta $};var2name \TEXUX{$\phi $};function
\TEXUX{$2$};linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";coordinateSystem "spherical";var1range "-3.1416,3.1416";var2range
"0,3.1416";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Wire
Frame";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8B70J.xvz';valid_file "T";tempfilename
'ITB8B70L.wmf';tempfile-properties "XPR";}}

\bigskip

\bigskip Use the ranges $-1\leq \theta \leq 2\pi $ and $0\leq \phi \leq \pi $
and define $\rho (\phi ,\theta )=(1.2)^{\phi }\sin (\theta )$ and plot the
expression $\rho (\theta ,\phi )$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot%
}{\special{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";animated TRUE;animationStartTime "0";
animationEndTime "10"; animationFramesPerSecond "5";xmin "-1.0";xmax
"6.28";ymin "0";ymax "3.14";animationParamMin "0";animationParamMax
"10";xviewmin "-1.79751692243";xviewmax "3.14235861566";yviewmin
"-2.38014042841";yviewmax "1.35349326697";zviewmin "-1.57118379138";zviewmax
"1.57118777677";phi 45;theta 45;plottype 15;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{v58130};yis \TEXUX{v58144};animationParam
\TEXUX{t};var1name \TEXUX{$\theta $};var2name \TEXUX{$\phi
$};animationParamList \TEXUX{$t$};function \TEXUX{$\rho (\theta ,\phi
)$};linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";coordinateSystem "spherical";var1range "-1.0,6.28";var2range
"0,3.14";animationParamRange "0,10";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";rangeset"XYA";VCamFile 'ITB8B70K.xvz';valid_file "T";tempfilename
'ITB8B70M.wmf';tempfile-properties "XPR";}}

\bigskip

More examples needed here:eg define f(x,y) and try to plot a plane tangent
to f at some point. Ron will send some examples.

\bigskip

\subsubsection{Plot 3D, Tube}

$\left[ 
\begin{array}{c}
-10\cos t-2\cos (5t)+15\sin (2t) \\ 
-15\cos (2t)+10\sin t-2\sin (5t) \\ 
10\cos (3t)%
\end{array}%
\right] $ \QTR{MenuDialog}{Radius} is set to $1$, the \QTR{MenuDialog}{Plot
Interval} is set to $0\leq t\leq 6.28$ ($\approx 2\pi $) and 
\QTR{MenuDialog}{Surface Style} is set to \QTR{MenuDialog}{Hidden }\FRAME{%
dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific
Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"0";xmax "6.28";xviewmin "-21.6482506908";xviewmax "21.6198260833";yviewmin
"-15.991880473";yviewmax "23.9800884112";zviewmin "-10.9651308421";zviewmax
"10.9779288173";phi 45;theta 45;plottype 13;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 50;num-y-gridlines
10;plotstyle "hidden";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{t};var1name \TEXUX{$t$};var2name
\TEXUX{{}};function \TEXUX{$\left[
\MATRIX{1,3}{c}\VR{,,c,,,}{,,,,,}\HR{,,,}\CELL{-10\cos t-2\cos (5t)+15\sin
(2t)}\CELL{-15\cos (2t)+10\sin t-2\sin (5t)}\CELL{10\cos (3t)}\right]
$};linestyle 1;radius \TEXUX{$1$};pointstyle "point";lineAttributes
"Solid";var1range "0,6.28";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Hidden
Line";num-x-gridlines 50;num-y-gridlines 10;surfaceMesh
"Mesh";rangeset"X";VCamFile 'ITB8BQ0L.xvz';valid_file "T";tempfilename
'ITB8BQ0N.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot 3D, Vector field}

\bigskip $\left[ -y/z,x/z,z\right] $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot%
}{\special{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";zmin
"-5";zmax "5";xviewmin "-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-5";zviewmax "5";phi 54;theta 26;cameraDistance "8.45973";cameraOrientation
"[0,0,0.0666667]";cameraOrientationFixed TRUE;plottype 17;axesFont "Times
New Roman,12,0000000000,useDefault,normal";num-x-gridlines 6;num-y-gridlines
6;num-z-gridlines 6;plotstyle "line";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};zis
\TEXUX{z};var1name \TEXUX{$x$};var2name \TEXUX{$y$};var3name
\TEXUX{$z$};function \TEXUX{$\left[ -y/z,x/z,z\right] $};linestyle
1;pointstyle "point";linethickness 1;lineAttributes "Solid";var1range
"-5,5";var2range "-5,5";var3range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";num-x-gridlines 6;num-y-gridlines
6;num-z-gridlines 6;VCamFile 'ITB8BR0M.xvz';valid_file "T";tempfilename
'ITB8BR0O.wmf';tempfile-properties "XPR";}}

\section{Multiple function Tests}

\subsection{Bar chart.}

Drag each group into the plot to create the bar chart

$\left( 2,0,2,0.24\right) $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";xviewmin "1.9995";xviewmax "7.0005";yviewmin
"-0.000028";yviewmax "0.280028";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\left( 2,0,2,0.24\right) $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";curveColor "[flat::RGB:0000000000]";curveStyle "Line";function
\TEXUX{$\left( 3,0,3,0.28\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
4,0,4,0.21\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
5,0,5,0.1\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
6,0,6,0.031\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
2,0,2,0.24,3,0.24\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
3,0,3,0.28,4,0.28,4,0\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function
\TEXUX{$(4,0.21,5,0.21,5,0)$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
5,0\allowbreak .1,6,0.1,6,0\right) $};linecolor "black";linestyle
1;pointstyle "point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
6,0.031,7,0.031,7,0\right) .$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$\left(
2,0,2,0.24\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8BS0N.xvz';valid_file "T";tempfilename
'ITB8BS0P.wmf';tempfile-properties "XPR";}}, $\left( 3,0,3,0.28\right) $, $%
\left( 4,0,4,0.21\right) $, $\left( 5,0,5,0.1\right) $, $\left(
6,0,6,0.031\right) $

\bigskip $\left( 2,0,2,0.24,3,0.24\right) $\quad $\left(
3,0,3,0.28,4,0.28,4,0\right) $\quad $(4,0.21,5,0.21,5,0),$ $\ \left(
5,0\allowbreak .1,6,0.1,6,0\right) $\quad $\left( 6,0.031,7,0.031,7,0\right)
.$

\subsection{Multiple 3D expressions}

\bigskip $\sin x+\cos y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special%
{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5";xviewmax
"5";yviewmin "-5";yviewmax "5";zviewmin "-10";zviewmax "10";phi 45;theta
45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "wireframe";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$\sin x+\cos y$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Wire Frame";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";function \TEXUX{$x+y$};linestyle 1;pointstyle "point";lineAttributes
"Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8BW0O.xvz';valid_file "T";tempfilename
'ITB8BW0Q.wmf';tempfile-properties "XPR";}}

$x+y$

\bigskip

\subsection{Mixed 2D and 3D expressions}

\section{Input Variations}

\subsection{defined functions}

Define this \ \bigskip $f(x)=e^{-x^{2}}$

Define this $g(x)=f^{\prime }(x)$

\bigskip

Plot $g$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-0.853688639720452";yviewmax "1";plottype
4;axesFont "Times New Roman,12,0000000000,useDefault,normal";numpoints
100;plotstyle "patch";axesstyle "normal";axestips FALSE;xis
\TEXUX{x};var1name \TEXUX{$x$};function \TEXUX{$g$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";function \TEXUX{$f$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8BX0P.xvz';valid_file "T";tempfilename
'ITB8BX0R.wmf';tempfile-properties "XPR";}} and then drag $f$ onto it

\subsection{2D Item List}

Set the view limits from 0 to 3 in x and y: list: \ $\left(
1,1,2,1,2,2,1,2,1,1\right) $\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "0";xmax "3";xviewmin "0";xviewmax
"3";yviewmin "0";yviewmax "3";viewset"XY";rangeset"X";plottype 4;axesFont
"Times New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\left( 1,1,2,1,2,2,1,2,1,1\right) $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";curveColor "[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8BX0Q.xvz';valid_file "T";tempfilename
'ITB8BX0S.wmf';tempfile-properties "XPR";}}

matrix:

\bigskip $\left[ 
\begin{array}{cc}
1 & 1 \\ 
2 & 1 \\ 
2 & 2 \\ 
1 & 2%
\end{array}%
\right] $\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "0";xmax "3";xviewmin "0";xviewmax "3";yviewmin "0";yviewmax
"3";viewset"XY";rangeset"X";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\left[
\MATRIX{2,4}{c}\VR{,,c,,,}{,,c,,,}{,,,,,}\HR{,,,,}\CELL{1}\CELL{1}\CELL{2}%
\CELL{1}\CELL{2}\CELL{2}\CELL{1}\CELL{2}\right] $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";curveColor "[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8BZ0R.xvz';valid_file "T";tempfilename
'ITB8BZ0T.wmf';tempfile-properties "XPR";}}

\bigskip

Set axis scale to be equal here

$\left( 1,0,\cos \frac{2\pi }{5},\sin \frac{2\pi }{5},\cos \frac{4\pi }{5}%
,\sin \frac{4\pi }{5},\cos \frac{6\pi }{5},\sin \frac{6\pi }{5},\cos \frac{%
8\pi }{5},\sin \frac{8\pi }{5},1,0\right) $\FRAME{dtbpFX}{4.4996in}{3in}{0pt%
}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.4996in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-0.809197896074437";xviewmax "1.00018090169944";yviewmin
"-0.951246727598259";yviewmax "0.951246727598259";plottype 4;axesFont "Times
New Roman,12,0000000000,useDefault,normal";constrained TRUE;numpoints
100;plotstyle "patch";axesstyle "normal";axestips FALSE;xis
\TEXUX{x};var1name \TEXUX{$x$};function \TEXUX{$\left( 1,0,\cos \frac{2\pi
}{5},\sin \frac{2\pi }{5},\cos \frac{4\pi }{5},\sin \frac{4\pi }{5},\cos
\frac{6\pi }{5},\sin \frac{6\pi }{5},\cos \frac{8\pi }{5},\sin \frac{8\pi
}{5},1,0\right) $};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8BZ0S.xvz';valid_file "T";tempfilename
'ITB8BZ0U.wmf';tempfile-properties "XPR";}}

\bigskip

\bigskip

\subsection{piecewise-defined functions}

Piecewise defined: $\ \left\{ 
\begin{array}{ccc}
x^{2}-1 & \text{if} & x<-1 \\ 
10-10x^{2} & \text{if} & -1\leq x\leq 1 \\ 
x^{2}-1 & \text{if} & 1<x%
\end{array}%
\right. $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-0.002197327879071";yviewmax
"24.0023999821351";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\ \left\{
\MATRIX{3,3}{c}\VR{,,c,,,}{,,c,,,}{,,c,,,}{,,,,,}\HR{,,,}\CELL{x^{2}-1}%
\CELL{\text{if}}\CELL{x<-1}\CELL{10-10x^{2}}\CELL{\text{if}}\CELL{-1\leq
x\leq 1}\CELL{x^{2}-1}\CELL{\text{if}}\CELL{1<x}\right. $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8C20T.xvz';valid_file "T";tempfilename
'ITB8C10V.wmf';tempfile-properties "XPR";}}

\bigskip

\bigskip Piecewise discontinuous: $\left\{ 
\begin{array}{ccc}
x^{2}-1 & \text{if} & x<-1 \\ 
20-x^{2} & \text{if} & -1\leq x\leq 1 \\ 
x^{2}-1 & \text{if} & 1<x%
\end{array}%
\right. $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.5in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-0.002197327879071";yviewmax
"24.0023999821351";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\left\{
\MATRIX{3,3}{c}\VR{,,c,,,}{,,c,,,}{,,c,,,}{,,,,,}\HR{,,,}\CELL{x^{2}-1}%
\CELL{\text{if}}\CELL{x<-1}\CELL{20-x^{2}}\CELL{\text{if}}\CELL{-1\leq x\leq
1}\CELL{x^{2}-1}\CELL{\text{if}}\CELL{1<x}\right. $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8C20U.xvz';valid_file "T";tempfilename
'ITB8C20W.wmf';tempfile-properties "XPR";}}

\subsection{\protect\bigskip}

\bigskip

\subsection{discontinuous plots}

Adjust for discontinuities on: $\ \dfrac{x+1}{x-1}$\FRAME{dtbpFX}{4.5in}{3in%
}{0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-5.0010000010002";xviewmax "5.0010000010002";yviewmin
"-4.38381953749931";yviewmax "5.58382218528931";plottype 4;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\ \dfrac{x+1}{x-1}$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8C20V.xvz';valid_file "T";tempfilename
'ITB8C20X.wmf';tempfile-properties "XPR";}}

\bigskip

adjust plot for discontinuities off: $\dfrac{x+1}{x-1}$\FRAME{dtbpFX}{%
4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific Word";type
"MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-3.50375000375076";yviewmax
"34.0037500038008";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\dfrac{x+1}{x-1}$};linecolor "black";linestyle
1;discont FALSE;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";discont FALSE;VCamFile
'ITB8C30W.xvz';valid_file "T";tempfilename
'ITB8C30Y.wmf';tempfile-properties "XPR";}}

\subsection{Functions}

\subsubsection{special functions}

2D rectangular Gamma: $\Gamma (x)$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-5.0008999910002";xviewmax "5.0009999910002";yviewmin
"-11.5100945114081";yviewmax "13.6031262095081";plottype 4;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\Gamma (x)$};linecolor "black";linestyle
1;pointstyle "point";linethickness 1;lineAttributes "Solid";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0000000000]";curveStyle
"Line";VCamFile 'ITB8C30X.xvz';valid_file "T";tempfilename
'ITB8C30Z.wmf';tempfile-properties "XPR";}}

\bigskip

\bigskip $\left\lfloor x\right\rfloor $\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{%
Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-5.0008999810002";xviewmax "5.0008999810002";yviewmin
"-5.00090000090018";yviewmax "4.00090000090018";plottype 4;axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\left\lfloor x\right\rfloor $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8C40Y.xvz';valid_file "T";tempfilename
'ITB8C410.wmf';tempfile-properties "XPR";}}

\subsubsection{trigonometric functions of degrees}

Set plot limits from -360 to 360 $\ \ \ \sin 2x\unit{%
%TCIMACRO{\U{b0}}%
%BeginExpansion
{{}^\circ}%
%EndExpansion
}+\cos 3x\unit{%
%TCIMACRO{\U{b0}}%
%BeginExpansion
{{}^\circ}%
%EndExpansion
}$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific
Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-360";xmax "360";xviewmin "-360.072000072014";xviewmax
"360.072000072014";yviewmin "-2";yviewmax "2";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$\sin 2x\unit{\U{b0}}+\cos
3x\unit{\U{b0}}$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range
"-360,360";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";rangeset"X";VCamFile
'ITB8C40Z.xvz';valid_file "T";tempfilename
'ITB8C411.wmf';tempfile-properties "XPR";}}

\bigskip

\subsubsection{Plot Approximate Integral}

The following \QTR{MenuDialog}{Middle Boxes} plot uses $0<x<3$ and 
\QTR{MenuDialog}{Number of Boxes }is 10.

\begin{quote}
$\blacktriangleright $\quad \QTR{MenuDialog}{Calculus + Plot Approximate
Integral}
\end{quote}

$x\sin x$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "0";xmax "5";xviewmin "-0.0005000005001";xviewmax
"5.0005000005001";yviewmin "-4.81510158736084";yviewmax
"1.82014320468084";plottype 3;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};boxtype 4;numboxes 10;function \TEXUX{$x\sin x$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";numboxes 10;approxIntBoxType "middle";approxIntShowInfo
"NoInfo";var1range "0,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";fillColor
"[flat::RGB:0x00ffcd99]";fillStyle "Solid";rangeset"X";VCamFile
'ITB8C510.xvz';valid_file "T";tempfilename
'ITB8C512.wmf';tempfile-properties "XPR";}}

\section{Plot properties Tests}

\subsection{plotting a grid}

Add Grid and Axes Tips, background cyan $\ x$\FRAME{dtbpFX}{4.4996in}{3in}{%
0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.4996in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-5.0010000010002";xviewmax "5.0010000010002";yviewmin
"-5.0010000010002";yviewmax "5.0010000010002";plottype 4;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips TRUE;gridLines TRUE;backgroundColor
"[flat::RGB:0x00ffff80]";xis \TEXUX{x};var1name \TEXUX{$x$};function
\TEXUX{$x$};linecolor "black";linestyle 1;pointstyle "point";linethickness
1;lineAttributes "Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8C511.xvz';valid_file "T";tempfilename
'ITB8C513.wmf';tempfile-properties "XPR";}}

\subsection{Colors}

\subsubsection{Line Styles, Colors, labels}

Solid $x$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";xviewmin "-5.0010000010002";xviewmax
"5.0010000010002";yviewmin "-7.0014000010002";yviewmax
"7.0014000010002";plottype 4;plotticks 1;num-x-ticks 10;num-y-ticks
8;labeloverrides 3;x-label "This is X";y-label "This is Y";axesFont "Times
New Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$x$};linecolor "black";linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0000000000]";curveStyle
"Line";function \TEXUX{$x+1$};linecolor "blue";linestyle 2;pointstyle
"point";linethickness 1;lineAttributes "Dash";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0x00000080]";curveStyle
"Line";function \TEXUX{$x+2$};linecolor "maroon";linestyle 3;pointstyle
"point";linethickness 2;lineAttributes "Dots";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0x00800000]";curveStyle
"Line";function \TEXUX{$x-1$};linecolor "green";linestyle 4;pointstyle
"point";linethickness 3;lineAttributes "DotDash";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0x00008000]";curveStyle
"Line";function \TEXUX{$x-2$};linecolor "yellow";linestyle 1;pointstyle
"point";linethickness 3;lineAttributes "Solid";var1range
"-5,5";num-x-gridlines 100;curveColor "[flat::RGB:0x00ffff80]";curveStyle
"Line";function \TEXUX{$(4,1,3,-1,2,-2)$};linecolor "magenta";linestyle
1;pointplot TRUE;pointstyle "circle";linethickness 1;lineAttributes
"Solid";curveColor "[flat::RGB:0x00800080]";curveStyle "Point";function
\TEXUX{$(-4,4,-3,5,-2,6)$};linecolor "yellow";linestyle 1;pointplot
TRUE;pointstyle "box";linethickness 1;lineAttributes "Solid";curveColor
"[flat::RGB:0x00ffff00]";curveStyle "Point";VCamFile
'ITB8C612.xvz';valid_file "T";tempfilename
'ITB8C614.wmf';tempfile-properties "XPR";}}

Dashed, red $x+1$

Dots, blue, medium $x+2$

dashdot, green, thick $x-1$

cyan, thick $x-2$

points, circles, purple $(4,1,3,-1,2,-2)$

points, boxes, lt green blue $(-4,4,-3,5,-2,6)$

Xaxis label: This is X

Yaxis label:\ This is Y

X axis ticks:\ 10

Y axis ticks:\ 8

\subsubsection{Plot variables}

plot this as 3d cylindrical $\ \ h(a,b)=a^{2}+b^{3}$\FRAME{dtbpFX}{4.5in}{3in%
}{0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.5in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-3.1416";xmax
"3.1416";ymin "0";ymax "5";xviewmin "-134.869650556";xviewmax "125";yviewmin
"-127.467412639";yviewmax "127.467412639";zviewmin "0";zviewmax "5";phi
45;theta 45;plottype 14;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{a};yis \TEXUX{b};var1name \TEXUX{$a$};var2name
\TEXUX{$b$};function \TEXUX{$a^{2}+b^{3}$};linestyle 1;pointstyle
"point";lineAttributes "Solid";coordinateSystem "cylindrical";var1range
"-3.1416,3.1416";var2range "0,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8C713.xvz';valid_file "T";tempfilename
'ITB8C715.wmf';tempfile-properties "XPR";}}

swap variables\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-3.1416";xmax "3.1416";ymin "0";ymax "5";xviewmin
"-56.0064941978";xviewmax "31.0064941985";yviewmin "-21.9816436104";yviewmax
"30.0930421903";zviewmin "0";zviewmax "5";phi 26;theta 1;cameraDistance
"1.44593";cameraOrientation "[0,0,0.133333]";cameraOrientationFixed
TRUE;plottype 14;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{b};yis \TEXUX{a};var1name \TEXUX{$b$};var2name
\TEXUX{$a$};function \TEXUX{$a^{2}+b^{3}$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";coordinateSystem
"cylindrical";var1range "-3.1416,3.1416";var2range "0,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";rangeset"XY";VCamFile 'ITB8C814.xvz';valid_file "T";tempfilename
'ITB8C816.wmf';tempfile-properties "XPR";}}

$h(a,b)$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5";xviewmax
"5";yviewmin "-5";yviewmax "5";zviewmin "-125";zviewmax "150";phi 45;theta
45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{a};yis \TEXUX{b};var1name \TEXUX{$a$};var2name
\TEXUX{$b$};function \TEXUX{$h(a,b)$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";rangeset"XY";VCamFile 'ITB8C915.xvz';valid_file "T";tempfilename
'ITB8C917.wmf';tempfile-properties "XPR";}}

\qquad

\subsection{Plot Layout}

\subsubsection{Height/width}

\subsubsection{Display attributes:}

\paragraph{\qquad In frame}

\paragraph{\qquad Plot only\qquad}

\paragraph{\qquad Frame only}

\paragraph{\qquad Iconified}

\subsubsection{Placement}

\paragraph{\qquad Inline}

\paragraph{\qquad Displayed}

\paragraph{\qquad Floating}

\qquad \qquad Here

\qquad \qquad Separate page

\qquad \qquad Top of page

\qquad \qquad Bottom of page

\subsubsection{Axes scales}

\paragraph{\qquad Log}

Plot log scale and add caption below $5\left( 2^{x}\right) $\FRAME{dtbpFUX}{%
4.4996in}{3in}{0pt}{\Qcb{this is log plot of $5(2^{x})$}}{\Qlb{logplot}}{Plot%
}{\special{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";xviewmin
"-5.0010000010002";xviewmax "5.0010000010002";yviewmin "0.15723";yviewmax
"161.60";plottype 20;axesFont "Times New
Roman,12,0000000000,useDefault,normal";numpoints 100;plotstyle
"patch";axesstyle "normal";axestips FALSE;xis \TEXUX{x};var1name
\TEXUX{$x$};function \TEXUX{$5\left( 2^{x}\right) $};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8CA16.xvz';valid_file "T";tempfilename
'ITB8CA18.wmf';tempfile-properties "XPR";}}

\paragraph{\qquad Log-log}

Plot loglog scale and add caption $5x^{2/3}$\FRAME{dtbpFUX}{4.4996in}{3in}{%
0pt}{\Qcb{This is caption for loglog $5x^{\frac{2}{3}}$}}{\Qlb{loglog}}{%
loglogplot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.4996in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "5E-6";xmax "5";xviewmin
"4.9998E-6";xviewmax "4.9996";yviewmin "1.4081";yviewmax "14.557";plottype
21;axesFont "Times New Roman,12,0000000000,useDefault,normal";numpoints
100;plotstyle "patch";axesstyle "normal";axestips FALSE;xis
\TEXUX{x};var1name \TEXUX{$x$};function \TEXUX{$5x^{2/3}$};linecolor
"black";linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "5E-6,5";num-x-gridlines 100;curveColor
"[flat::RGB:0000000000]";curveStyle "Line";VCamFile
'ITB8CS17.xvz';valid_file "T";tempfilename
'ITB8CS19.wmf';tempfile-properties "XPR";}}

\subsubsection{3D Specific}

\subsubsection{background colors for 3D plots}

\bigskip

\paragraph{3D Lighting}

\paragraph{3D Surface Style}

Defaults $\ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.5in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.5in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin
"-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-11.3600527772";zviewmax "13.0400884979";phi 45;theta 45;plottype
5;axesFont "Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "patch";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointstyle "point";lineAttributes "Solid";var1range
"-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8CT18.xvz';valid_file "T";tempfilename
'ITB8CT1A.wmf';tempfile-properties "XPR";}}

\bigskip

X range: -10..10, y range -7..7, 50 points in each direction $\ x\sin x\cos
y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-10";xmax "10";ymin "-7";ymax "7";xviewmin "-10";xviewmax
"10";yviewmin "-7";yviewmax "7";zviewmin "-21.8113885306";zviewmax
"22.2194305408";phi 45;theta 45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$x\sin x\cos y+x+y$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range "-10,10";var2range
"-7,7";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 50;num-y-gridlines 50;surfaceMesh
"Mesh";rangeset"XY";VCamFile 'ITB8CU19.xvz';valid_file "T";tempfilename
'ITB8CU1B.wmf';tempfile-properties "XPR";}}

\bigskip

Wireframe, contour, -200\TEXTsymbol{<}x\TEXTsymbol{<}200, -300 \TEXTsymbol{<}
y \TEXTsymbol{<} 150, 100 points x, 70 points y $\ \ x\sin x\cos y+x+y$%
\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language "Scientific
Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-199";xmax "200";ymin "-300";ymax "150";xviewmin "-199";xviewmax
"200";yviewmin "-300";yviewmax "150";zviewmin "-585.905853913";zviewmax
"473.234373927";phi 45;theta 45;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "wireframe";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$\ \ x\sin x\cos y+x+y$};linestyle 1;pointstyle
"point";linethickness 1;lineAttributes "Solid";var1range
"-199,200";var2range "-300,150";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Wire
Frame";num-x-gridlines 100;num-y-gridlines 70;surfaceMesh
"Contour";rangeset"XY";VCamFile 'ITB8CV1A.xvz';valid_file "T";tempfilename
'ITB8CV1C.wmf';tempfile-properties "XPR";}}

\bigskip

Directonal shading zhue $\ \ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{%
0pt}{}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.4996in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-11.3600527772";zviewmax "13.0400884979";phi 45;theta 45;plottype
5;axesFont "Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "patch";axesstyle "normal";axestips
FALSE;plotshading "ZHUE";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[rainbow:Z:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "ULines";VCamFile
'ITB8D21B.xvz';valid_file "T";tempfilename
'ITB8D21D.wmf';tempfile-properties "XPR";}}

\bigskip

Surface style point $\ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{%
}{}{Plot}{\special{language "Scientific Word";type "MAPLEPLOT";width
4.4996in;height 3in;depth 0pt;display "USEDEF";plot_snapshots
TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin
"-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-11.3600527772";zviewmax "13.0400884979";phi 45;theta 45;plottype
5;axesFont "Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "point";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointplot TRUE;pointstyle "point";linethickness
1;lineAttributes "Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Point";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8D41C.xvz';valid_file "T";tempfilename
'ITB8D41E.wmf';tempfile-properties "XPR";}}

\bigskip

Axis boxed $\ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin
"-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-11.3600527772";zviewmax "13.0400884979";phi 45;theta 45;plottype
5;axesFont "Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "patch";axesstyle "boxed";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8D41D.xvz';valid_file "T";tempfilename
'ITB8D41F.wmf';tempfile-properties "XPR";}}

\bigskip

Axis Framed $x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{%
\special{language "Scientific Word";type "MAPLEPLOT";width 4.4996in;height
3in;depth 0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute
FALSE;lastEngine "MuPAD";xmin "-5";xmax "5";ymin "-5";ymax "5";xviewmin
"-5";xviewmax "5";yviewmin "-5";yviewmax "5";zviewmin
"-11.3600527772";zviewmax "13.0400884979";phi 45;theta 45;plottype
5;axesFont "Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "patch";axesstyle "frame";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointstyle "point";lineAttributes "Solid";var1range
"-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8D51E.xvz';valid_file "T";tempfilename
'ITB8D51G.wmf';tempfile-properties "XPR";}}

\bigskip

\bigskip

\bigskip

Turn 62, tilt 67, background $\ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{%
3in}{0pt}{}{}{Plot}{\special{language "Scientific Word";type
"MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin
"-5";yviewmax "5";zviewmin "-11.3600527772";zviewmax "13.0400884979";phi
67;theta 62;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;backgroundColor
"[flat::RGB:0x00ffff00]";plotshading "XYZ";lighting 0;xis \TEXUX{x};yis
\TEXUX{y};var1name \TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$\ x\sin
x\cos y+x+y$};linestyle 1;pointstyle "point";linethickness 1;lineAttributes
"Solid";var1range "-5,5";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8D61F.xvz';valid_file "T";tempfilename
'ITB8D61H.wmf';tempfile-properties "XPR";}}

\bigskip

Turn 60, tilt 16, view intervals -10\TEXTsymbol{<}x\TEXTsymbol{<}10 $x\sin
x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{3in}{0pt}{}{}{Plot}{\special{language
"Scientific Word";type "MAPLEPLOT";width 4.4996in;height 3in;depth
0pt;display "USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine
"MuPAD";xmin "-10";xmax "10";ymin "-5";ymax "5";xviewmin "-10";xviewmax
"10";yviewmin "-5";yviewmax "5";zviewmin "-11.36005";zviewmax
"13.04009";viewset"XYZ";rangeset"XYZ";phi 16;theta 59;plottype 5;axesFont
"Times New Roman,12,0000000000,useDefault,normal";num-x-gridlines
25;num-y-gridlines 25;plotstyle "patch";axesstyle "normal";axestips
FALSE;plotshading "XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name
\TEXUX{$x$};var2name \TEXUX{$y$};function \TEXUX{$x\sin x\cos
y+x+y$};linestyle 1;pointstyle "point";lineAttributes "Solid";var1range
"-10,10";var2range "-5,5";surfaceColor
"[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle "Color
Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh "Mesh";VCamFile
'ITB8D61G.xvz';valid_file "T";tempfilename
'ITB8D61I.wmf';tempfile-properties "XPR";}}

\bigskip

Plot labels at 5,5,7 and 0,0,8 $\ x\sin x\cos y+x+y$\FRAME{dtbpFX}{4.4996in}{%
3in}{0pt}{}{}{Plot}{\special{language "Scientific Word";type
"MAPLEPLOT";width 4.4996in;height 3in;depth 0pt;display
"USEDEF";plot_snapshots TRUE;mustRecompute FALSE;lastEngine "MuPAD";xmin
"-5";xmax "5";ymin "-5";ymax "5";xviewmin "-5";xviewmax "5";yviewmin
"-5";yviewmax "5";zviewmin "-11.3600527772";zviewmax "13.0400884979";phi
80;theta 59;cameraDistance "1.08273";cameraOrientation
"[0,0,0.0273222]";cameraOrientationFixed TRUE;plottype 5;axesFont "Times New
Roman,12,0000000000,useDefault,normal";num-x-gridlines 25;num-y-gridlines
25;plotstyle "patch";axesstyle "normal";axestips FALSE;plotshading
"XYZ";lighting 0;xis \TEXUX{x};yis \TEXUX{y};var1name \TEXUX{$x$};var2name
\TEXUX{$y$};function \TEXUX{$x\sin x\cos y+x+y$};linestyle 1;pointstyle
"point";lineAttributes "Solid";var1range "-5,5";var2range
"-5,5";surfaceColor "[linear:XYZ:RGB:0x00ff0000:0x000000ff]";surfaceStyle
"Color Patch";num-x-gridlines 25;num-y-gridlines 25;surfaceMesh
"Mesh";plotText "Some text at 5,5";plotTextFont "Times New
Roman,12,0000000000,normal";plotTextAlign "center,baseline";plotTextPosition
"[5,5,7]";plotText "Some text at the origin";plotTextFont "Times New
Roman,12,0000000000,normal";plotTextAlign "center,baseline";plotTextPosition
"[0,0,8]";VCamFile 'ITB8D71H.xvz';valid_file "T";tempfilename
'ITB8D71J.wmf';tempfile-properties "XPR";}}

\end{document}

### 2006-07-17 prince/samples/SWP2Mozilla.pl

@@ -1,0 +1,10 @@
+# Converts output from SWP for Netscape into form better for editting
+# Usage SWP2Mozilla.pl < output.xml > output.xhtml
+
+while (<>) {
+  s/\<mml:/\</g;
+  s/\<\/mml:/\<\//g;
+  s/\<math/\<math xmlns=\"http:\/\/www.w3.org\/1998\/Math\/MathML\"/g;
+  s/\<link\ href.*\>/\<link href=\"TestComputation.css\" rel=\"stylesheet\" type=\"text\/css\"\/\>/g;
+  print $_;
+}

### 2006-08-02 filters/ptprince/samplearticle.tex
Brought over Jon's pretex files

\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{revsymb}
\usepackage{eurosym}
\usepackage{graphicx}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2606}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{LastRevised=Monday, September 27, 2004 16:26:10}
%TCIDATA{<META NAME="ViewSettings" CONTENT="31">}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{CSTFile=LaTeX article (bright).cst}
%TCIDATA{PageSetup=72,72,72,72,0}
%TCIDATA{EvenPages=
%H=36,\PARA{038<p type="texpara" tag="Body Text" >samplearticle.tex}
%F=36,\PARA{038<p type="texpara" tag="Body Text" >\hfill Page \thepage \hfill }
%}

%TCIDATA{OddPages=
%H=36,\PARA{038<p type="texpara" tag="Body Text" >\hfill samplearticle.tex}
%F=36,\PARA{038<p type="texpara" tag="Body Text" >\hfill Page \thepage \hfill }
%}

%TCIDATA{FirstPage=
%H=36
%F=36
%}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][]{\textbf{Proof.} }{}
\input{tcilatex}
\def\TextSymbolUnavailable#1{\textbf{???}}
\begin{document}

\title{A Sample Article}
\author{Dr. Tane Hunter \\
%EndAName
TCI Software Research}
\maketitle

\begin{abstract}
This article illustrates many features of a mathematics document created
with Scientific Word or Scientific WorkPlace.
\end{abstract}

\tableofcontents
\listoffigures

\section{A Sample Article}

This document illustrates a wide range of the symbols and constructs
available to you. This document is set up to compile with the standard and
multilingual format files. In particular, certain characters from the
Latin-1, Latin Extended-A, and General Punctuation symbol panels will
typeset as \textbf{???} if a multilingual format file such as TrueTeX
MultiLingual is not used.

\subsection{Mathematics and Text}

Let $H$ be a Hilbert space, $C$ be a closed bounded convex subset of $H$, $T$
a nonexpansive self map of $C$. Suppose that as $n\rightarrow \infty $, $%
a_{n,k}\rightarrow 0$ for each $k$, and $\gamma _{n}=\sum_{k=0}^{\infty
}\left( a_{n,k+1}-a_{n,k}\right) ^{+}\rightarrow 0$ Then for each $x$ in $C$%
, $A_{n}x=\sum_{k=0}^{\infty }a_{n,k}T^{k}x$ converges weakly to a fixed
point of $T$ \cite{dunford}.

In this situation. we would also like to cite \cite%
{black,blyth,Chang,condorcet,funkenbusch}, but we do so only to demonstrate
a citation with multiple entries.

\subsection{In-line and Displayed Mathematics}

The equation 
\begin{equation}
u_{tt}-\Delta u+u^{5}+u\left| u\right| ^{p-2}=0\text{ in }\mathbf{R}%
^{3}\times \left[ 0,\infty \right[ .  \tag{1}  \label{wave}
\end{equation}
is numbered and it also has the label ``wave''. You can use this label to
jump to this equation using hypertext links. You can reference this equation
within your document as equation \ref{wave}.

There are two sets of \LaTeX{} parameters governing mathematical displays.
The spacing left above and below a display depends on whether the lines
above or below are short or long.

Short above 
\begin{equation*}
x^2+y^2=z^2
\end{equation*}
short below.

Long above. This may depend on your margins. Avoid wrapping. 
\begin{equation*}
\sin ^{2}\theta +\cos ^{2}\theta =1
\end{equation*}
and long below. You don't have to worry about this line being long enough in
most circumstances because we've tried to ensure that it will wrap no matter
how wide you have your margins set.

\subsection{Multi-Line Displays}

\emph{Scientific Word and WorkPlace} provide a range of alignment options
for multiline mathematical displays. Here is a series of multiline displays. 
\begin{eqnarray}
x &=&17y \\
y &>&a+b+c+d+e+f+g+h+i+j+  \notag \\
&&k+l+m+n+o+p
\end{eqnarray}
\begin{eqnarray*}
x &\ll &y_{1}+\cdots +y_{n} \\
&\leq &z
\end{eqnarray*}
\begin{eqnarray*}
y &=&a+b+c+d+e+f+g+h+i+j \\
&&\,+k+l+m+n+o+p
\end{eqnarray*}
\begin{eqnarray*}
w+x+y+z &=& \\
&&a+b+c+d+e+f+g+h+i+j+ \\
&&k+l+m+n+o+p
\end{eqnarray*}

If $f(x)=x+1,$ then we will have 
\begin{equation*}
f([x+1]/[x+2])=\{[x+1]/[x+2]\}+1=(2x+3)/(x+2)
\end{equation*}
\begin{eqnarray*}
1+2+3+4+5+6+7+8+9+10+11+12 && \\
+13+14+15+16+17+18+19+20 &=&190
\end{eqnarray*}

\begin{eqnarray}
\max (f,g) &=&\frac{f+g+\left| f-g\right| }{2}\text{,} \\
\max (f,-g) &=&\frac{f-g+\left| f+g\right| }{2}\text{.}
\end{eqnarray}
\qquad 
\begin{eqnarray}
(a+b)^{n+1} &=&(a+b)(a+b)^{n}=(a+b)\sum_{j=0}^{n}\binom{n}{j}a^{n-1}b^{j}
\label{JoyA} \\
&=&\sum_{j=0}^{n}\binom{n}{j}a^{n+1-j}b^{j}+\sum_{j=1}^{n}\binom{n}{j-1}%
a^{n-1}b^{j}  \label{JoyB} \\
&=&\sum_{j=0}^{n}\binom{n+1}{j}a^{n+1-j}b^{j}\text{.}  \label{JoyC}
\end{eqnarray}

The equations in the display immediately above are (\ref{JoyA}), (\ref{JoyB}%
), and (\ref{JoyC}).

You can have subequation numbering generated automatically, illustrated in
the following:

\begin{subequations}
\begin{eqnarray}
x &=&a+b \\
y &=&c+d \\
z &=&e+f
\end{eqnarray}
This is text between the two sets of equations. The following set of
equations continues the numbering from the set above.

\begin{eqnarray}
u &=&g+h \\
v &=&i+j \\
w &=&k+l
\end{eqnarray}

Test the overriding of automatic equation labels: 
\end{subequations}
\begin{eqnarray}
x &=&y+z  \TCItag{A--1} \\
&=&k+m  \TCItag{A--2}
\end{eqnarray}
Test the overriding of automatic equation labels, suppressing annotation: 
\begin{eqnarray}
x &=&y+z  \TCItag*{A--1} \\
&=&k+m  \TCItag*{A--2}
\end{eqnarray}
The labels in the first set of equations should be parenthesized, while the
labels in the second set should not be parenthesized.

There is a significant difference between the standard \LaTeX{} equation
array and the AMS align environment. SW/SWP does not show this difference on
screen. To check this difference, look at the Typeset Preview versions of
the following. 
\begin{eqnarray*}
x &=&y \\
&=&z
\end{eqnarray*}
\begin{align*}
x& =y \\
& =z
\end{align*}

The space around the = sign in the first set of equations (the \LaTeX{}
equation array) is much greater than in the second set (the AMS align
environment). The spacing in the second set is preferred, as it agrees with
the spacing in a single-line display:

\begin{equation*}
x=y
\end{equation*}

To convert the \LaTeX{} equation array to the AMS align environment, select
the equations, then from the Edit menu, choose Properties. Select Advanced
and then select Enable Alignment.

\section{Mathematics in section heads $\protect\int_{\protect\alpha }^{%
\protect\beta }\ln tdt$}

You ought to be able to put mathematics in section heads. It might be a
problem in style with running headers and table of contents entries.

\subsection{Theorems, Lemmata, Etc.}

\label{theorems}You can automatically number theorems and other proclamations%
\footnote{%
Such as propositions, lemmas and corollaries. You can create your own
theorem-like environments to extend the basic set provided with \textsl{SW}.
\par
Footnotes, such as this, can have several paragraphs. Each paragraph can be
as large as you want. You can include mathematics, graphics, or anything
else you can enter in main-document paragraphs. It is even possible to
compare the difference between an in-line sum $\sum_{n=1}^{\infty }\frac{1}{%
n^{2}}$ and a displayed sum 
\begin{equation*}
\sum_{n=1}^{\infty }\frac{1}{n^{2}}
\end{equation*}%
}. This is a marginal marginal note.%
\marginpar{
Marginal notes are like call-outs in graphics. You can bring the reader's
attention to a point made in the text.
\par
Marginal notes can have multiple paragraphs.} These theorem-like
environments are available.

\begin{acknowledgement}
This is an acknowledgement
\end{acknowledgement}

\begin{algorithm}
This is an algorithm
\end{algorithm}

\begin{axiom}
All mathematics is fun.
\end{axiom}

\begin{case}
This is a case
\end{case}

\begin{claim}
This is a claim
\end{claim}

\begin{conclusion}
This is a conclusion
\end{conclusion}

\begin{condition}
This is a condition
\end{condition}

\begin{conjecture}
Some people don't like mathematics.
\end{conjecture}

\begin{corollary}
This is a corollary
\end{corollary}

\begin{criterion}
This is a criterion
\end{criterion}

\begin{definition}
This is a definition
\end{definition}

\begin{example}
This is an example
\end{example}

\begin{exercise}
This is an exercise
\end{exercise}

\begin{lemma}
The plural of lemma is lemmata, so they say. Why all these lemmas?
\end{lemma}

\begin{proof}
This is the proof of the lemma.
\end{proof}

\begin{notation}
This is notation
\end{notation}

\begin{problem}
This is a problem
\end{problem}

\begin{proposition}
This is a proposition
\end{proposition}

\begin{remark}
This is a remark
\end{remark}

\begin{summary}
This is a summary
\end{summary}

\begin{theorem}[Main Theorem]
\label{existence}Suppose $u_{0}\in C^{3}\left( \mathbf{R}^{3}\right)
,u_{1}\in C^{2}\left( \mathbf{R}^{3}\right) $ have finite energy 
\begin{equation}
\int_{\mathbf{R}^{3}}\left( \frac{\left| u_{1}\right| ^{2}+\left| \nabla
u_{0}\right| ^{2}}{2}+\frac{\left| u_{0}\right| ^{6}}{6}\right) dx<\infty 
\tag{9}
\end{equation}
and suppose the solution $u^{(0)}$ to the homogeneous wave equation with
initial data $u_{0},u_{1}$ is uniformly bounded. Then there exists $\epsilon
_{0}>0$ such that for $\left| \epsilon \right| <\epsilon _{0}$ the initial
value problem (\ref{wave}) with data $\epsilon u_{0},\epsilon u_{1}$ admits
a global $C^{2}$-solution.
\end{theorem}

\begin{proof}[Proof of the Main Theorem]
This is the proof.
\end{proof}

\section{Section Heading}

This is body text following a section heading. \label{sectA}

\subsection{Subsection Heading}

This is body text following a subsection heading.\label{ssectA}

\subsubsection{Subsubsection Heading}

This is body text following a subsubsection heading.\label{sssectA}

\paragraph{Subsubsubsection Heading}

This is body text following a subsubsubsection heading.\label{ssssectA}

\subparagraph{Subsubsubsubsection Heading}

This is body text following a subsubsubsubsection heading.\label{sssssectA}

\section{Another Section Heading}

If this section is numbered, check that it is numbered correctly.\label%
{sectB}

\subsection{Another Subsection Heading}

If this subsection heading is numbered, check that it is numbered correctly.%
\label{ssectB}

\subsubsection{Another Subsubsection Heading}

If this subsubsection heading is numbered, check that it is numbered
correctly.\label{sssectB}

\paragraph{Another Subsubsubsection Heading}

If this subsubsubsection heading is numbered, check that it is numbered
correctly.\label{ssssectB}

\subparagraph{Another Subsubsubsubsection Heading}

If this subsubsubsubsection heading is numbered, check that it is numbered
correctly.\label{sssssectB}

The sections above are sections \ref{sectA}, \ref{ssectA}, \ref{sssectA}, %
\ref{ssssectA}, \ref{sssssectA}, \ref{sectB}, \ref{ssectB}, \ref{sssectB}, %
\ref{ssssectB}, \ref{sssssectB}.

\section*{Starred Sections}

With version 4, SW/SWP now provides user access to the \verb|\section*|
command. To adjust this on an existing section heading, position the cursor
on the left side of the section. Use edit properties or the context menu
from the right mouse button to bring up the Section Properties dialog.
Starred sections are not numbered and do not appear in the table of contents
when a document is typeset. A better way to handle this is to set the
section numbering counter depth.

\subsection*{Starred Subsection}

\subsubsection*{Starred Subsubsection}

\paragraph*{Starred Subsubsubsection}

\subparagraph*{Starred Subsubsubsubsection}

\section[Short Form]{Sections with Optional Arguments}

Optional arguments to sections are entered by putting them in square
brackets at the start of the heading text. These optional arguments are used
for the short form of a heading in running heads and in the table of contents

\subsection[Short Form]{Subsection}

\subsubsection[Short Form]{Subsubsection}

\paragraph[Short Form]{Subsubsubsection}

\subparagraph[Short Form]{Subsubsubsubsection}

\subsection{Lists}

\subsubsection{Numbered Lists}

\begin{enumerate}
\item First numbered item, level 1.\label{A}

\begin{enumerate}
\item First numbered item, level 2.,\label{AA}

\begin{enumerate}
\item First numbered item, level 3.\label{AAA}

\begin{enumerate}
\item First numbered item, level 4.\label{AAAA}

\item Second numbered item, level 4.\label{AAAB}
\end{enumerate}

\item Second numbered item, leve1 3.\label{AAB}
\end{enumerate}

\item Second numbered item, level 2.\label{AB}
\end{enumerate}

\item Second numbered item, level 1.\label{B}

\begin{enumerate}
\item First numbered item, level 2.\label{BA}

\begin{enumerate}
\item First numbered item, level 3.\label{BAA}

\begin{enumerate}
\item First numbered item, level 4.\label{BAAA}

\item Second numbered item, level 4.\label{BAAB}
\end{enumerate}

\item Second numbered item, leve1 3.\label{BAB}
\end{enumerate}

\item Second numbered item, level 2.\label{BB}
\end{enumerate}
\end{enumerate}

The items above are numbered \ref{A}, \ref{AA}, \ref{AAA}, \ref{AAAA}, \ref%
{AAAB}, \ref{AAB}, \ref{AB}, \ref{B}, \ref{BA}, \ref{BAA}, \ref{BAAA}, \ref%
{BAAB}, \ref{BAB}, \ref{BB} in that order.

Here is a list with multiple levels on one line. There should be five lines,
only. Items should not be split out on separate lines.

\begin{enumerate}
\item First item, normal.

\item 
\begin{enumerate}
\item Second item, both numbers.
\end{enumerate}

\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item Third item, three numbers.
\end{enumerate}
\end{enumerate}

\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item Fourth item, four numbers.
\end{enumerate}
\end{enumerate}
\end{enumerate}

\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item Fifth item. Second, third, and fourth numbers.
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

Here is a list with continuation items.

\begin{enumerate}
\item Level 1, first paragraph.

Level 1, second paragraph.

\begin{enumerate}
\item Level 2, first paragraph.

Level 2, second paragraph.

\begin{enumerate}
\item Level 3, first paragraph.

Level 3, second paragraph.

\begin{enumerate}
\item Level 4, first paragraph.

Level 4, second paragraph.
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\subsubsection{Bulleted Lists}

\begin{itemize}
\item Bullet item, level 1.

\begin{itemize}
\item Bullet item, level 2.

\begin{itemize}
\item Bullet item, level 3.

\begin{itemize}
\item Bullet item, level 4.
\end{itemize}
\end{itemize}
\end{itemize}

\item Bullet item, level 1.

This is a continuation paragraph in a bullet item. The paragraph has been
made long enough to wrap, and so wrap it will. The question is, do you like
wrap? Is it your taste in music?

\begin{itemize}
\item Bullet item, level 2.

This is a continuation paragraph in a bullet item. The paragraph has been
made long enough to wrap, and so wrap it will. The question is, do you like
wrap?

\begin{itemize}
\item Bullet item, level 3.

This is a continuation paragraph in a bullet item. The paragraph has been
made long enough to wrap, and so wrap it will. The question is, do you like
wrap?

\begin{itemize}
\item Bullet item, level 4.

This is a continuation paragraph in a bullet item. The paragraph has been
made long enough to wrap, and so wrap it will. The question is, do you like
wrap?
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Custom Lists}

\begin{description}
\item[gnat] A small animal, found in the North Woods, that causes no end of
trouble.

\item[gnu] A large animal, found in crossword puzzles, that causes no end of
trouble.

\item[armadillo] A medium-sized animal, named after a medium-sized Texas
city. A medium-sized animal, named after a medium-sized Texas city.

\item[A very long custom label here] There should be enough text following
to allow the paragraph to wrap to the next line.

Here is a continuation paragraph of the above custom item.
\end{description}

\subsubsection{Lists with custom lead-ins.}

\paragraph{Numbered lists with custom lead-ins.}

\begin{enumerate}
\item[Number 1:] First numbered item

\item[Number 2:] Second numbered item

\item[Number 3:] Third numbered item

\begin{enumerate}
\item[Number 3.a:] First item under Number 3

\begin{enumerate}
\item[Number 3.a.i:] First item under Number 3.a:

\begin{enumerate}
\item[Number 3.a.i.1:] First item under Number 3.a.i:

\item[Number 3.a.i.2:] Second item under Number 3.a.i:

Continuation paragraph under the second item under Number 3.a.i:
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\paragraph{Bulleted lists with custom lead-ins.}

\begin{itemize}
\item[Bullet:] First item

\item[Bullet:] Second item

\item[Bullet:] Third item

\begin{itemize}
\item[Square:] First item under the third item

\begin{itemize}
\item[Triangle:] First item under the first item under the third item

\begin{itemize}
\item[elgnairT:] First item under the first item under the first item under
the third item

\item[elgnairT:] Second item under the first item under the first item under
the third item

Continuation paragraph under the second item under the first item under the
third item
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

\paragraph{Lists with multiple lead-ins per line.}

\begin{enumerate}
\item First

\item 
\begin{enumerate}
\item Second, First
\end{enumerate}

\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item Third, First, First
\end{enumerate}
\end{enumerate}

\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item 
\begin{enumerate}
\item Fourth, First, First, First
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\begin{enumerate}
\item Reset to First

\item 
\begin{enumerate}
\item Second, First

\item 
\begin{enumerate}
\item None, Second, First

\item 
\begin{enumerate}
\item None, None, Second, First
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\paragraph{Lists with complex custom items.}

\begin{enumerate}
\item[$\protect\int \sin xdx$] Lead-in is $\int \sin xdx$

\item[$\mathfrak{ABC}$] Lead-in is $\mathfrak{ABC}$

%%JCS\item[$\sqrt[3]{3}$]
\item[{$\sqrt[3]{3}$}]If the leadin contains an item with an optional
parameter, that item should be in a group to prevent the closing bracket of
the optional argument from closing the item brackets.

\item[{\protect\FRAME{itbpF}{0.3528in}{0.3105in}{0in}{}{}{swplogo.wmf}{%
\special{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.3528in;height 0.3105in;depth
0in;original-width 0pt;original-height 0pt;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}}] Lead-in is \FRAME{%
itbpF}{0.3528in}{0.3105in}{0in}{}{}{swplogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"PICT";valid_file "F";width 0.3528in;height 0.3105in;depth
0in;original-width 0.3226in;original-height 0.2811in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}
\end{enumerate}

\paragraph{Lists whose items contain notes}

\begin{enumerate}
\item A footnote\footnote{%
This footnote is in a list item}

\item A margin note%
\marginpar{
This marginal note is in a list item}

\begin{enumerate}
\item A footnote with lists. \footnote{%
A list in a footnote:
\par
\begin{enumerate}
\item First item
\par
\item Second item
\par
\begin{enumerate}
\item First item
\par
\item Second item
\end{enumerate}
\end{enumerate}
}

\item A margin note with lists. 
\marginpar{
A list in a margin note:
\par
\begin{enumerate}
\item First item
\par
\item Second item
\par
\begin{enumerate}
\item First item
\par
\item Second item
\end{enumerate}
\end{enumerate}
}
\end{enumerate}
\end{enumerate}

\subsection{Block Quote and Centered}

In addition to Body Text, there are paragraph tags named Block Quote and
Center. Here is a Block Quote paragraph.

\begin{quotation}
Why, there, there, there, there! A diamond gone, cost me two thousand ducats
in Frankfort! The curse never fell upon our nation till now; I never felt it
till now. Two thousand ducats in that, and other precious, precious jewels.
I would my daughter were dead at my foot, and the jewels in her ear! Would
she were hearsed at my foot, and the jewels in her coffin! No news of them?
Why, thou loss upon loss! The thief gone with so much, and so much to find
the thief, and no satisfaction, no revenge! Nor no ill luck stirring but
what lights o' my shedding.
\end{quotation}

Here is a centered paragraph:

\begin{center}
Nay, that's true, that's very true. Go, Tubal, fee me an officer; bespeak
him a fortnight before. I will have the heart of him if he forfeit, for were
he out of Venice I can make what merchandise I will. Go, Tubal, and meet me
at our synagogue; go, good Tubal; at our synagogue, Tubal.
\end{center}

\subsection{Footnotes and Marginal Notes}

In this section, we insert multiple footnotes and multiple marginal notes.
This illustrates the various parameters used to separate multiple footnotes
and marginal paragraphs.\footnote{%
The first in a series of consecutive footnotes.}\footnote{%
The second in a series of consecutive footnotes.}\footnote{%
The third in a series of consecutive footnotes.}\footnote{%
The fourth in a series of consecutive footnotes.}%
\marginpar{
The first in a series of marginal notes.}%
\marginpar{
The second in a series of marginal notes.}%
\marginpar{
The third in a series of marginal notes.}%
\marginpar{
The fourth in a series of marginal notes.}

\section{Cross-References and Their Ilk}

\label{crossrefs}The section on theorems is numbered \ref{theorems} and is
on page \pageref{theorems}. The current section (on cross-references and
their ilk) is numbered \ref{crossrefs} and is on page \pageref{crossrefs}.

\section{Text Tags}

Text tags are the tags you apply to text within a paragraph, to distinguish
phrases. There are tags for physical phrase markup and tags for logical
phrase markup.

This section discusses the differences between some aspects of the \LaTeX{}
coding \textsl{SW\/} uses in \LaTeX{}2.09 and \LaTeX{}2e documents. In \LaTeX%
{}2.09, the commands for what we call \emph{tagged runs}, including
boldface, italics, and emphasis, are switches. In \LaTeX{}2e, the switch
commands are still available, but use of the new macro forms is strongly
encouraged. We at TCI agree with this wholeheartedly---switches are an
abomination and have caused us no end of trouble in the past. The new macro
forms of the tagged runs also have additional capabilities, most of which
are supported in \textsl{SW}.

\subsection{Tagged Runs in Text}

Here is a comparison of the tagged runs in text.

\begin{center}
\begin{tabular}{llll}
\textbf{Name} & \textbf{\LaTeX{}2.09} & \textbf{\LaTeX{}2e} & \textbf{Example%
} \\ \hline
Italic & \{\TEXTsymbol{\backslash}it text\} & \TEXTsymbol{\backslash}%
textit\{text\} & \textit{text} \\ 
Bold & \{\TEXTsymbol{\backslash}bf text\} & \TEXTsymbol{\backslash}%
textbf\{text\} & \textbf{text} \\ 
Small Caps & \{\TEXTsymbol{\backslash}sc text\} & \TEXTsymbol{\backslash}%
textsc\{text\} & \textsc{text} \\ 
Sans Serif & \{\TEXTsymbol{\backslash}sf text\} & \TEXTsymbol{\backslash}%
textsf\{text\} & \textsf{text} \\ 
Slant & \{\TEXTsymbol{\backslash}sl text\} & \TEXTsymbol{\backslash}%
textsl\{text\} & \textsl{text} \\ 
Typewriter & \{\TEXTsymbol{\backslash}tt text\} & \TEXTsymbol{\backslash}%
texttt\{text\} & \texttt{text} \\ 
Emphasis & \{\TEXTsymbol{\backslash}em text\} & \{\TEXTsymbol{\backslash}em
text\} & \emph{text} \\ 
Roman & \{\TEXTsymbol{\backslash}rm text\} & \TEXTsymbol{\backslash}%
textrm\{text\} & \textrm{text}%
\end{tabular}
\end{center}

\subsection{Tagged Runs in Mathematics}

All of the text tagged runs are also valid in mathematics. Since \textsl{SW}
works very hard to provide a minimal nesting level of tags, these must be
shown in an enviroment that forces math. Within that environment (here, a
pair of empty expanding brackets), we select text in addition to the tagged
run.

\begin{center}
\begin{tabular}{llll}
\textbf{Name} & \textbf{\LaTeX{}2.09} & \textbf{\LaTeX{}2e} & \textbf{Example%
} \\ \hline
Italic & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}it text\}\$ & 
\$\TEXTsymbol{\backslash}textit\{text\}\$ & $\left. \text{\textit{text}}%
\right. $ \\ 
Bold & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}bf text\}\$ & \$%
\TEXTsymbol{\backslash}textbf\{text\}\$ & $\left. \text{\textbf{text}}%
\right. $ \\ 
Small Caps & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}sc
text\}\$ & \$\TEXTsymbol{\backslash}textsc\{text\}\$ & $\left. \text{\textsc{%
text}}\right. $ \\ 
Sans Serif & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}sf
text\}\$ & \$\TEXTsymbol{\backslash}textsf\{text\}\$ & $\left. \text{\textsf{%
text}}\right. $ \\ 
Slant & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}sl text\}\$ & 
\$\TEXTsymbol{\backslash}textsl\{text\}\$ & $\left. \text{\textsl{text}}%
\right. $ \\ 
Typewriter & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}tt
text\}\$ & \$\TEXTsymbol{\backslash}texttt\{text\}\$ & $\left. \text{\texttt{%
text}}\right. $ \\ 
Emphasis & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}em text\}\$
& \$\{\TEXTsymbol{\backslash}em text\}\$ & $\left. \text{\emph{text}}\right. 
$ \\ 
Roman & \$\TEXTsymbol{\backslash}text\{\TEXTsymbol{\backslash}rm text\}\$ & 
\$\TEXTsymbol{\backslash}textrm\{text\}\$ & $\left. \text{\textrm{text}}%
\right. $%
\end{tabular}
\end{center}

The coding of the above tagged runs presents a number of problems for the
filter. There is now an option to use \TEXTsymbol{\backslash}textrm or 
\TEXTsymbol{\backslash}mbox in place of the \TEXTsymbol{\backslash}text
command.

\begin{center}
\begin{tabular}{llll}
\textbf{Name} & \textbf{\LaTeX{}2.09} & \textbf{\LaTeX{}2e} & \textbf{Example%
} \\ \hline
Italic & \{\TEXTsymbol{\backslash}it text\} & \TEXTsymbol{\backslash}%
textit\{text\} & $\mathit{text}$ \\ 
Bold & \{\TEXTsymbol{\backslash}bf text\} & \TEXTsymbol{\backslash}%
textbf\{text\} & $\mathbf{text}$ \\ 
Small Caps & \{\TEXTsymbol{\backslash}sc text\} & \TEXTsymbol{\backslash}%
textsc\{text\} & $\QTR{sc}{text}$ \\ 
Sans Serif & \{\TEXTsymbol{\backslash}sf text\} & \TEXTsymbol{\backslash}%
textsf\{text\} & $\mathsf{text}$ \\ 
Slant & \{\TEXTsymbol{\backslash}sl text\} & \TEXTsymbol{\backslash}%
textsl\{text\} & $\QTR{sl}{text}$ \\ 
Typewriter & \{\TEXTsymbol{\backslash}tt text\} & \TEXTsymbol{\backslash}%
texttt\{text\} & $\mathtt{text}$ \\ 
Emphasis & NA & NA & NA \\ 
Roman & \{\TEXTsymbol{\backslash}rm text\} & \TEXTsymbol{\backslash}%
textrm\{text\} & $\mathrm{text}$%
\end{tabular}
\end{center}

\textsc{Small Caps Here!}

\textsl{This sentence is slanted.}

This is math $\left[ x+\mathit{italic}+y+\mathsf{sansserif}+\mathbf{bold}+%
\mathrm{roman}\right] $

Here is a display 
\begin{equation*}
x+\text{text}+y+\mathrm{roman}+\text{\textrm{roman text}}
\end{equation*}
and then we finish off the paragraph with great alacrity.

\textit{Now we use italics. Here is a display} 
\begin{equation*}
x+\text{text}+y+\mathrm{roman}+\text{\textrm{roman text}}
\end{equation*}
\textit{and then we finish off the paragraph with great alacrity.}

\textit{This is a paragraph of italic text with a stretch of \textrm{roman}
in the middle.}

You obtain \TEXTsymbol{\backslash}mathrm by applying roman to a selection in
math, and you obtain \TEXTsymbol{\backslash}textrm by applying text and then
applying roman. $\left[ x+\mathrm{roman}+\text{\textrm{textroman}}\right] $

\subsection{Bold Symbol}

Bold Symbol is a special tag you can apply in math to build italic bold
symbols. For example: $\boldsymbol{m}$. (Compare with $\mathbf{m}$). Another
examples: $\boldsymbol{2\pi i\neq }$ $\boldsymbol{\dot{x}}$.

\subsection{Calligraphic, Fraktur and Blackboard Bold}

These are math--only tags.

$\mathcal{CALLIGRAPHIC}$

$\mathfrak{fraktur}$

$\mathbb{BLACKBOARDBOLD}$

\section{The \texttt{\TEXTsymbol{\backslash}text} Command}

\textsl{SW} writes text in mathematics using the AMS \TEXTsymbol{\backslash}%
text command. This is the only command for text in mathematics that reduces
size appropriately when smaller fonts are called for in \LaTeX{}2.09. The 
\TEXTsymbol{\backslash}rm switch also works in \LaTeX{}2e. Here is text in
mathematics at various sizes: 
\begin{equation*}
X^{x+\text{text}^{x+\text{text}}}+\text{text}
\end{equation*}
and the same, attempted with \TEXTsymbol{\backslash}rm: 
\begin{equation*}
X^{x+\mathrm{text}^{x+\mathrm{text}}}+\mathrm{text}
\end{equation*}
and with \TEXTsymbol{\backslash}mbox: 
\begin{equation*}
X^{x+\mbox{text}^{x+\mbox{text}}}+\mbox{text}
\end{equation*}

\section{Operators}

The following is a list of operators from the \textsc{Insert, Operator}...
menu selection.

\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
$\int $ & $\iint $ & $\iiint $ & $\iiiint $ & $\idotsint $ & $\oint $ & $%
\sum $ & $\prod $ & $\bigcap $ \\ \hline
$\bigwedge $ & $\bigoplus $ & $\bigodot $ & $\bigsqcup $ & $\coprod $ & $%
\bigcup $ & $\bigvee $ & $\bigotimes $ & $\biguplus $ \\ \hline
\end{tabular}

The following is a list of operators from the \textsc{Insert, Operator}...
menu selection. In this example, all operators are set to ``Big,'' while all
limit positions are set ``at right.''

\begin{tabular}{|l|l|l|l|l|}
\hline
$\dint\nolimits_{b}^{a}$ & $\diint\nolimits_{A}^{b}$ & $\diiint\nolimits_{%
\Delta }dV$ & $\diiiint\nolimits_{what?}dT$ & $\didotsint\nolimits_{\ldots
}d\cdots $ \\ \hline
$\dbigwedge\nolimits_{i}x_{i}$ & $\dbigoplus\nolimits^{100}X_{i}$ & $%
\dbigodot\nolimits_{\nu \neq v}\Psi _{\nu }$ & $\dbigsqcup\nolimits_{\xi
=\left( 
\begin{array}{ll}
1 & 2 \\ 
3 & 4%
\end{array}%
\right) }\xi $ & $\dcoprod\nolimits^{\text{A small paragraph}}\Xi _{i}$ \\ 
\hline
\end{tabular}
\vspace{1.019pc}

\begin{tabular}{|l|l|l|l|}
\hline
$\doint\nolimits_{\Gamma }d\gamma $ & $\dsum\nolimits_{x=1}^{5}\frac{1}{x^{2}%
}$ & $\dprod\nolimits_{x=5}^{7}\left( 1-\sqrt{x}\right) $ & $%
\dbigcap\nolimits_{A\in \mathbf{A}}A$ \\ \hline
$\dbigcup\nolimits_{x^{x^{x}}}U_{x}$ & $\dbigvee\nolimits_{\int i}y^{i}$ & $%
\dbigotimes\nolimits_{\mu \in \{1,2,5,7\}}\Phi \mu $ & $\dbiguplus%
\nolimits_{Blow}^{Joe}B$ \\ \hline
\end{tabular}

The following is a list of operators from the \textsc{Insert, Operator}...
menu selection. In this example, all operators are set to ``Small,'' while
all limit positions are set ``at right.''

\begin{tabular}{|l|l|l|l|l|}
\hline
$\tint\nolimits_{b}^{a}xdx$ & $\tiint\nolimits_{A}\frac{dxdy}{xy}$ & $%
\tiiint\nolimits_{\Delta }dV$ & $\tiiiint\nolimits_{what?}dT$ & $%
\tidotsint\nolimits_{\ldots }d\cdots $ \\ \hline
$\tbigwedge\nolimits_{i}x_{i}$ & $\tbigoplus\nolimits^{100}X_{i}$ & $%
\tbigodot\nolimits_{\nu \neq v}\Psi _{\nu }$ & $\tbigsqcup\nolimits_{\xi
=\left( 
\begin{array}{ll}
1 & 2 \\ 
3 & 4%
\end{array}%
\right) }\xi $ & $\tcoprod\nolimits^{\text{A small paragraph}}\Xi _{i}$ \\ 
\hline
\end{tabular}
\vspace{1.019pc}

\begin{tabular}{|l|l|l|l|}
\hline
$\toint\nolimits_{\Gamma }d\gamma $ & $\tsum\nolimits_{x=1}^{5}\frac{1}{x^{2}%
}$ & $\tprod\nolimits_{x=5}^{7}\left( 1-\sqrt{x}\right) $ & $%
\tbigcap\nolimits_{A\in \mathbf{A}}A$ \\ \hline
$\tbigcup\nolimits_{x^{x^{x}}}U_{x}$ & $\tbigvee\nolimits_{\int i}y^{i}$ & $%
\tbigotimes\nolimits_{\mu \in \{1,2,5,7\}}\Phi \mu $ & $\tbiguplus%
\nolimits_{Blow}^{Joe}B$ \\ \hline
\end{tabular}

The following is a list of operators from the \textsc{Insert, Operator}...
menu selection. In this example, all operators are set to ``Big,'' while all
limit positions are set ``Above/below.''

\begin{tabular}{|l|l|l|l|l|}
\hline
$\dint\limits_{b}^{a}xdx$ & $\diint\limits_{A}\frac{dxdy}{xy}$ & $%
\diiint\limits_{\Delta }dV$ & $\diiiint\limits_{what?}dT$ & $%
\didotsint\limits_{\ldots }d\cdots $ \\ \hline
$\dbigwedge\limits_{i}x_{i}$ & $\dbigoplus\limits^{100}X_{i}$ & $%
\dbigodot\limits_{\nu \neq v}\Psi _{\nu }$ & $\dbigsqcup\limits_{\xi =\left( 
\begin{array}{ll}
1 & 2 \\ 
3 & 4%
\end{array}%
\right) }\xi $ & $\dcoprod\limits^{\text{A small paragraph}}\Xi _{i}$ \\ 
\hline
\end{tabular}
\vspace{1.019pc}

\begin{tabular}{|l|l|l|l|}
\hline
$\doint\limits_{\Gamma }d\gamma $ & $\dsum\limits_{x=1}^{5}\frac{1}{x^{2}}$
& $\dprod\limits_{x=5}^{7}\left( 1-\sqrt{x}\right) $ & $\dbigcap\limits_{A%
\in \mathbf{A}}A$ \\ \hline
$\dbigcup\limits_{x^{x^{x}}}U_{x}$ & $\dbigvee\limits_{\int i}y^{i}$ & $%
\dbigotimes\limits_{\mu \in \{1,2,5,7\}}\Phi \mu $ & $\dbiguplus%
\limits_{Blow}^{Joe}B$ \\ \hline
\end{tabular}

\subsection{Multi-Line Subscripts and Superscripts}

$\sum_{\substack{ 1<i<10  \\ 1<j<10}}^{{}}2^{i+j}$ is more reasonable than $%
\Gamma _{1_{\substack{ 2_{\substack{ 3  \\ 4}}  \\ 5^{\substack{ 6  \\ 7}}}}%
}^{1 ^{\substack{ 5^{\substack{ 7  \\ 6}}  \\ 2_{\substack{ 4  \\ 5}}}}}$

\section{Brackets}

The following is a list of the different brackets from the \textsc{Insert,
Brackets}... menu selection.

%%JCS$%
%%JCS\begin{tabular}{|l|l|l|l|l|l|}
%%JCS\hline
%%JCS$\left( \frac{a}{\frac{x}{y}}\right) $ & $\left\lfloor \frac{E}{X}%
%%JCS\right\rfloor $ & $\left/ \frac{\mathbf{I}}{\mathbf{J}}\right/ $ & $%
%%JCS\left\Updownarrow \frac{m}{\frac{m}{m}}\right\Updownarrow $ & $%
%%JCS\left\Downarrow \frac{Q}{\frac{Q}{\frac{Q}{Q}}}\right\Downarrow $ & $\left\} 
%%JCS\mathsf{U}\right\{ $ \\ \hline
%%JCS$\left[ \frac{b}{\frac{x}{y}}\right] $ & $\left\lceil \frac{F}{X}%
%%JCS\right\rceil $ & $\left\backslash \frac{\mathbf{J}}{\mathbf{L}}%
%%JCS\right\backslash $ & $\left\uparrow \frac{n}{\frac{n}{n}}\right\uparrow $ & $%
%%JCS\left\rceil \frac{R}{\frac{R}{\frac{R}{R}}}\right\lceil $ & $\left] \mathsf{V%
%%JCS}\right[ $ \\ \hline
%%JCS$\left\{ \frac{c}{\frac{x}{y}}\right\} $ & $\left\vert \frac{G}{X}%
%%JCS\right\vert $ & $\left\updownarrow \frac{\mathbf{K}}{\mathbf{L}}%
%%JCS\right\updownarrow $ & $\left\Uparrow \frac{o}{\frac{o}{o}}\right\Uparrow $
%%JCS& $\left\rfloor \frac{S}{\frac{S}{\frac{S}{S}}}\right\lfloor $ & $\left) 
%%JCS\mathsf{W}\right( $ \\ \hline
%%JCS$\left\langle \frac{d}{\frac{x}{y}}\right\rangle $ & $\left\Vert \frac{H}{X}%
%%JCS\right\Vert $ & $\left. \frac{\mathbf{L}}{\mathbf{X}}\right. $ & $%
%%JCS\left\downarrow \frac{p}{\frac{p}{p}}\right\downarrow $ & $\left\rangle 
%%JCS\frac{T}{\frac{T}{\frac{T}{T}}}\right\langle $ &  \\ \hline
%%JCS\end{tabular}%
%%JCS\ $

\section{Math Names}

The following is a sample of names from the \textsc{Insert, Math Name}...
menu selection. Some are standard, built-in names: $\ln x$, $\sin ^{2}x$, $%
\arg \tanh \pi $. Or you can make up your own: $\limfunc{above}\limits^{a\in
B}\left( \left\{ a\right\} \right) $, $\limfunc{right}\nolimits_{b\in
A}\left( \left\{ b\right\} \right) $,$\ \func{func}\left( x\right) $.

\section{Binomials}

The following is a list of operators from the \textsc{Insert, Binomials}...
menu selection.

\noindent 
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|}
\hline
$\QOVERD( ) {2}{3}$ & $\QOVERD[ ] {3}{4}$ & $\QOVERD\{ \} {4}{5}$ & $%
\QOVERD\langle \rangle {5}{6}$ & $\QOVERD\lfloor \rfloor {6}{7}$ & $%
\QOVERD\lceil \rceil {7}{8}$ & $\QOVERD\vert \vert {8}{9}$ & $\QOVERD\Vert
\Vert {9}{0}$ & $\QOVERD/ / {0}{1}$ & $\QOVERD\backslash \backslash {1}{2}$
& $\QOVERD\updownarrow \updownarrow {2}{3}$ & $\QOVERD. . {3}{4}$ \\ \hline
$\QOVERD\Updownarrow \Updownarrow {4}{5}$ & $\QOVERD\uparrow \uparrow {5}{6}$
& $\QOVERD\Uparrow \Uparrow {6}{7}$ & $\QOVERD\downarrow \downarrow {7}{8}$
& $\QOVERD\Downarrow \Downarrow {8}{9}$ & $\QOVERD\rceil \lceil {9}{0}$ & $%
\QOVERD\rfloor \lfloor {0}{1}$ & $\QOVERD\rangle \langle {1}{2}$ & $%
\QOVERD\} \{ {2}{3}$ & $\QOVERD] [ {3}{4}$ & $\QOVERD) ( {4}{5}$ &  \\ \hline
\end{tabular}

You can modify the thickness of the line: none $\binom{q}{p}$, normal $%
\QOVERD( ) {q}{p}$, thick $\QABOVED( ) {1pt}{q}{p}$. And the size : auto $%
\binom{q}{p}$, big $\dbinom{q}{p}$, small $\tbinom{q}{p}$. In a display, the
auto should become big:

\begin{equation*}
\text{auto }\binom{q}{p}\text{, big }\dbinom{q}{p}\text{, small }\tbinom{q}{p%
}
\end{equation*}%
And you can make binomials with no delimiters: none $\QATOP{q}{p}$, normal $%
\frac{q}{p}$, thick $\QABOVE{1pt}{q}{p}$.

\section{Labels}

Use \textsc{Insert, Label}... to build labels above or below. $A\overset{%
f\left( x\right) }{\longrightarrow }B$ or $A^{\ast }\underset{f^{-1}}{%
\Longleftarrow }B^{\ast }$.

\section{Decorations}

The following is a list of decorations from the \textsc{Insert, Decorations}%
... menu selection.

%% jcs$%
%% jcs\begin{tabular}{|l|l|l|l|l|l|l|}
%% jcs\hline
%% jcs$\overline{\frac{1}{1+a^{2}}}$ & $\underleftarrow{\frac{1}{1+d^{2}}}$ & $%
%% jcs\overleftrightarrow{\frac{1}{1+g^{2}}}$ & $\underbrace{\frac{1}{1+j^{2}}}$ & 
%% jcs$\widetilde{\frac{1}{1+m^{2}}}$ & $\underline{\frac{1}{1+b^{2}}}$ & $%
%% jcs\overrightarrow{\frac{1}{1+e^{2}}}$ \\ \hline
%% jcs$\frac{1}{1+h^{2}}$ & $\widehat{\frac{1}{1+k^{2}}}$ & $\frame{$\frac{1}{%
%% jcs1+n^{2}}$}$ & $\overleftarrow{\frac{1}{1+c^{2}}}$ & $\underrightarrow{\frac{1%
%% jcs}{1+f^{2}}}$ & $\overbrace{\frac{1}{1+i^{2}}}$ & $\fbox{$\frac{1}{1+l^{2}}$}$
%% jcs\\ \hline
%% jcs\end{tabular}%
%% jcs\ $

\section{The Symbols}

Here are the symbols on the panels.

\textbf{Note: }If you typeset this document and do not use a multilingual
format file such as TrueTeX MultiLingual, several characters in the Latin-1,
Latin Extended-A, and General Punctuation panels will not typeset properly
and will instead appear as \textbf{???} in the typeset document.

\subsection{Lowercase Greek}

\begin{tabular}{llll}
$\alpha $ & $\beta $ & $\gamma $ & $\delta $ \\ 
$\epsilon $ & $\varepsilon $ & $\zeta $ & $\eta $ \\ 
$\theta $ & $\vartheta $ & $\iota $ & $\kappa $ \\ 
$\lambda $ & $\mu $ & $\nu $ & $\xi $ \\ 
$\pi $ & $\varpi $ & $\rho $ & $\sigma $ \\ 
$\varsigma $ & $\tau $ & $\upsilon $ & $\phi $ \\ 
$\varphi $ & $\chi $ & $\psi $ & $\omega $ \\ 
$\varkappa $ & $\varrho $ &  & 
\end{tabular}

\subsection{Uppercase Greek}

\begin{tabular}{ll}
$\Gamma $ & $\Delta $ \\ 
$\Theta $ & $\Lambda $ \\ 
$\Xi $ & $\Pi $ \\ 
$\Sigma $ & $\Upsilon $ \\ 
$\Phi $ & $\Psi $ \\ 
$\Omega $ & $\digamma $%
\end{tabular}

\subsection{Binary Operations}

\begin{tabular}{lllll}
$\pm $ & $\mp $ & $\times $ & $\cdot $ & $\ast $ \\ 
$\cup $ & $\cap $ & $\circ $ & $\bullet $ & $\div $ \\ 
$\sqcup $ & $\sqcap $ & $\bigcirc $ & $\setminus $ & $\smallsetminus $ \\ 
$\oplus $ & $\ominus $ & $\otimes $ & $\odot $ & $\circledast $ \\ 
$\vee $ & $\wedge $ & $\circledcirc $ & $\lhd $ & $\rhd $ \\ 
$\veebar $ & $\barwedge $ & $\wr $ & $\triangleleft $ & $\triangleright $ \\ 
$\uplus $ & $\doublebarwedge $ & $\amalg $ & $\unlhd $ & $\unrhd $ \\ 
$\bigtriangledown $ & $\bigtriangleup $ & $\diamond $ & $\dagger $ & $%
\ddagger $ \\ 
$\boxplus $ & $\boxminus $ & $\boxtimes $ & $\boxdot $ & $\oslash $ \\ 
$\Cup $ & $\Cap $ & $\ltimes $ & $\rtimes $ & $\star $ \\ 
$\curlyvee $ & $\curlywedge $ & $\leftthreetimes $ & $\rightthreetimes $ & $%
\intercal $ \\ 
$\dotplus $ & $\circleddash $ & $\divideontimes $ & $\centerdot $ & $%
\smallint $ \\ 
$\And $ &  &  &  & 
\end{tabular}

\subsection{Binary Relations}

\begin{tabular}{llllll}
$\leq $ & $\prec $ & $\preceq $ & $\ll $ & $\subset $ & $\subseteq $ \\ 
$\sqsubset $ & $\sqsubseteq $ & $\in $ & $\vdash $ & $\smile $ & $\frown $
\\ 
$\equiv $ & $\sim $ & $\simeq $ & $\asymp $ & $\approx $ & $\geq $ \\ 
$\succ $ & $\succeq $ & $\gg $ & $\supset $ & $\supseteq $ & $\sqsupset $ \\ 
$\sqsupseteq $ & $\ni $ & $\dashv $ & $\mid $ & $\parallel $ & $\perp $ \\ 
$\cong $ & $\bowtie $ & $\propto $ & $\models $ & $\doteq $ & $\Join $ \\ 
$\Vdash $ & $\Vvdash $ & $\vDash $ & $\circeq $ & $\succsim $ & $\gtrsim $
\\ 
$\gtrapprox $ & $\therefore $ & $\because $ & $\doteqdot $ & $\triangleq $ & 
$\precsim $ \\ 
$\lesssim $ & $\lessapprox $ & $\eqslantless $ & $\eqslantgtr $ & $%
\curlyeqprec $ & $\curlyeqsucc $ \\ 
$\preccurlyeq $ & $\leqq $ & $\leqslant $ & $\lessgtr $ & $\risingdotseq $ & 
$\fallingdotseq $ \\ 
$\succcurlyeq $ & $\geqq $ & $\geqslant $ & $\gtrless $ & $\vartriangleright 
$ & $\vartriangleleft $ \\ 
$\trianglerighteq $ & $\trianglelefteq $ & $\between $ & $%
\blacktriangleright $ & $\blacktriangleleft $ & $\eqcirc $ \\ 
$\lesseqgtr $ & $\gtreqless $ & $\lesseqqgtr $ & $\gtreqqless $ & $%
\varpropto $ & $\eqcirc $ \\ 
$\smallfrown $ & $\Subset $ & $\Supset $ & $\subseteqq $ & $\supseteqq $ & $%
\bumpeq $ \\ 
$\Bumpeq $ & $\lll $ & $\ggg $ & $\pitchfork $ & $\backsim $ & $\backsimeq $
\\ 
$\eqsim $ & $\lessdot $ & $\gtrdot $ & $\shortmid $ & $\shortparallel $ & $%
\thicksim $ \\ 
$\thickapprox $ & $\approxeq $ & $\succapprox $ & $\precapprox $ & $%
\backepsilon $ & $\vartriangle $%
\end{tabular}

\subsection{Negated Relations}

\begin{tabular}{lllll}
$\neq $ & $\notin $ & $\lvertneqq $ & $\gvertneqq $ & $\nleq $ \\ 
$\ngeq $ & $\nless $ & $\ngtr $ & $\nprec $ & $\nsucc $ \\ 
$\lneqq $ & $\gneqq $ & $\nleqslant $ & $\ngeqslant $ & $\lneq $ \\ 
$\gneq $ & $\npreceq $ & $\nsucceq $ & $\precnsim $ & $\succnsim $ \\ 
$\lnsim $ & $\gnsim $ & $\nleqq $ & $\ngeqq $ & $\precneqq $ \\ 
$\succneqq $ & $\precnapprox $ & $\succnapprox $ & $\lnapprox $ & $\gnapprox 
$ \\ 
$\nsim $ & $\ncong $ & $\varsubsetneq $ & $\varsupsetneq $ & $\nsubseteqq $
\\ 
$\nsupseteqq $ & $\subsetneqq $ & $\supsetneqq $ & $\varsubsetneqq $ & $%
\varsupsetneqq $ \\ 
$\subsetneq $ & $\supsetneq $ & $\nsubseteq $ & $\nsupseteq $ & $\nparallel $
\\ 
$\nmid $ & $\nshortmid $ & $\nshortparallel $ & $\nvdash $ & $\nVdash $ \\ 
$\nvDash $ & $\nVDash $ & $\ntrianglerighteq $ & $\ntrianglelefteq $ & $%
\ntriangleright $ \\ 
$\ntriangleleft $ & $\nleftarrow $ & $\nrightarrow $ & $\nLeftarrow $ & $%
\nRightarrow $ \\ 
$\nLeftrightarrow $ & $\nleftrightarrow $ &  &  & 
\end{tabular}

\subsection{Arrows}

\begin{tabular}{lllll}
$\leftarrow $ & $\Leftarrow $ & $\rightarrow $ & $\Rightarrow $ & $%
\leftrightarrow $ \\ 
$\Leftrightarrow $ & $\mapsto $ & $\hookleftarrow $ & $\leftharpoonup $ & $%
\leftharpoondown $ \\ 
$\uparrow $ & $\Uparrow $ & $\downarrow $ & $\Downarrow $ & $\updownarrow $
\\ 
$\longleftarrow $ & $\Longleftarrow $ & $\longrightarrow $ & $%
\Longrightarrow $ & $\longleftrightarrow $ \\ 
$\Longleftrightarrow $ & $\longmapsto $ & $\hookrightarrow $ & $%
\rightharpoonup $ & $\rightharpoondown $ \\ 
$\leadsto $ & $\Updownarrow $ & $\nearrow $ & $\searrow $ & $\swarrow $ \\ 
$\nwarrow $ & $\circlearrowright $ & $\circlearrowleft $ & $%
\rightleftharpoons $ & $\leftrightharpoons $ \\ 
$\twoheadrightarrow $ & $\twoheadleftarrow $ & $\leftleftarrows $ & $%
\rightrightarrows $ & $\upuparrows $ \\ 
$\downdownarrows $ & $\upharpoonright $ & $\downharpoonright $ & $%
\upharpoonleft $ & $\downharpoonleft $ \\ 
$\rightarrowtail $ & $\leftarrowtail $ & $\leftrightarrows $ & $%
\rightleftarrows $ & $\Lsh $ \\ 
$\Rsh $ & $\rightsquigarrow $ & $\leftrightsquigarrow $ & $\looparrowleft $
& $\looparrowright $ \\ 
$\multimap $ & $\Rrightarrow $ & $\Lleftarrow $ & $\curvearrowleft $ & $%
\curvearrowright $ \\ 
$\dashrightarrow $ & $\dashleftarrow $ & $\implies $ & $\impliedby $ & $\iff 
$%
\end{tabular}

\subsection{Miscellaneous}

\begin{tabular}{llllll}
$\infty $ & $\partial $ & \ldots & $\cdots $ & $\vdots $ & $\ddots $ \\ 
\i & \j & $\ell $ & $\wp $ & $\hbar $ & $\hslash $ \\ 
$\forall $ & $\exists $ & $\nexists $ & $\Re $ & $\Im $ & $\aleph $ \\ 
$\prime $ & $\backprime $ & $\emptyset $ & $\varnothing $ & $\diagup $ & $%
\diagdown $ \\ 
$\nabla $ & $\surd $ & $\top $ & $\bot $ & $\eth $ & $\lambdabar $ \\ 
$\angle $ & $\measuredangle $ & $\sphericalangle $ & $\circledS $ & $%
\tciLaplace $ & $\tciFourier $ \\ 
$\lnot $ & $\complement $ & $\Finv $ & $\Game $ & $\bigstar $ & $\Vert $ \\ 
$\square $ & $\blacksquare $ & $\Diamond $ & $\lozenge $ & $\blacklozenge $
& \TEXTsymbol{\backslash} \\ 
$\triangle $ & $\blacktriangle $ & $\triangledown $ & $\blacktriangledown $
& \dag & \ddag \\ 
$\beth $ & $\gimel $ & $\daleth $ & $\sharp $ & $\flat $ & $\natural $ \\ 
$\clubsuit $ & $\diamondsuit $ & $\heartsuit $ & $\spadesuit $ & $\checkmark 
$ & $\maltese $ \\ 
$\Bbbk $ & $%
%TCIMACRO{\U{2102} }%
%BeginExpansion
\mathbb{C}
%EndExpansion
$ & $%
%TCIMACRO{\U{2115} }%
%BeginExpansion
\mathbb{N}
%EndExpansion
$ & $%
%TCIMACRO{\U{211a} }%
%BeginExpansion
\mathbb{Q}
%EndExpansion
$ & $%
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
$ & $%
%TCIMACRO{\U{2124} }%
%BeginExpansion
\mathbb{Z}
%EndExpansion
$ \\ 
\cents  & \pounds  & \textcurrency  & \yen  & \euro & \textfranc \\ 
\textlira & \textpeseta  & \texttrademark & $\mho $ & $\colon $ & 
\end{tabular}

\subsection{Delimiters}

\begin{tabular}{ll}
$\lfloor $ & $\rfloor $ \\ 
$\lceil $ & $\rceil $ \\ 
$\langle $ & $\rangle $ \\ 
$\ulcorner $ & $\urcorner $ \\ 
$\llcorner $ & $\lrcorner $%
\end{tabular}

\subsection{Latin-1}

\begin{tabular}{llllll}
~ & $%
%TCIMACRO{\U{b0}}%
%BeginExpansion
{{}^\circ}%
%EndExpansion
$ & \`{A} & \DH  & \`{a} & \dh  \\ 
\textexclamdown  & $\pm $ & \'{A} & \~{N} & \'{a} & \~{n} \\ 
\cents  & 
%TCIMACRO{\U{b2} }%
%BeginExpansion
${{}^2}$
%EndExpansion
& \^{A} & \`{O} & \^{a} & \`{o} \\ 
\pounds  & 
%TCIMACRO{\U{b3} }%
%BeginExpansion
${{}^3}$
%EndExpansion
& \~{A} & \'{O} & \~{a} & \'{o} \\ 
\textcurrency  & 
%TCIMACRO{\U{b4} }%
%BeginExpansion
\'{}
%EndExpansion
& \"{A} & \^{O} & \"{a} & \^{o} \\ 
\yen  & 
%TCIMACRO{\U{b5} }%
%BeginExpansion
$\mu$
%EndExpansion
& \AA  & \~{O} & \aa  & \~{o} \\ 
$%
%TCIMACRO{\U{a6}}%
%BeginExpansion
{\vert}%
%EndExpansion
$ & \P  & \AE  & \"{O} & \ae  & \"{o} \\ 
\S  & \textperiodcentered & \c{C} & $\times $ & \c{c} & $\div $ \\ 
%TCIMACRO{\U{a8} }%
%BeginExpansion
\"{}
%EndExpansion
& 
%TCIMACRO{\U{b8} }%
%BeginExpansion
\c{}
%EndExpansion
& \`{E} & \O  & \`{e} & \o  \\ 
\copyright  & 
%TCIMACRO{\U{b9} }%
%BeginExpansion
${{}^1}$
%EndExpansion
& \'{E} & \`{U} & \'{e} & \`{u} \\ 
%TCIMACRO{\U{aa} }%
%BeginExpansion
${{}^a}$
%EndExpansion
& 
%TCIMACRO{\U{ba} }%
%BeginExpansion
${{}^o}$
%EndExpansion
& \^{E} & \'{U} & \^{e} & \'{u} \\ 
\guillemotleft  & \guillemotright  & \"{E} & \^{U} & \"{e} & \^{u} \\ 
$\lnot $ & 
%TCIMACRO{\U{bc} }%
%BeginExpansion
$\frac14$
%EndExpansion
& \`{I} & \"{U} & \`{\i} & \"{u} \\ 
- & 
%TCIMACRO{\U{bd} }%
%BeginExpansion
$\frac12$
%EndExpansion
& \'{I} & \'{Y} & \'{\i} & \'{y} \\ 
\registered  & 
%TCIMACRO{\U{be} }%
%BeginExpansion
$\frac34$
%EndExpansion
& \^{I} & \TH  & \^{\i} & \th  \\ 
%TCIMACRO{\U{af} }%
%BeginExpansion
\={}
%EndExpansion
& \textquestiondown  & \"{I} & \ss  & \"{\i} & \"{y}%
\end{tabular}

\subsection{Latin Extended-A}

\begin{tabular}{llllllll}
\={A} & \DJ  & \.{G} & \.{I} & 
%TCIMACRO{\U{140} }%
%BeginExpansion
l{\hskip.15em}\llap{\raise.25ex\hbox{$\cdot$}}
%EndExpansion
& \H{O} & \v{S} & \H{U} \\ 
\={a} & \dj  & \.{g} & \i & \L  & \H{o} & \v{s} & \H{u} \\ 
\u{A} & \={E} & \c{G} & 
%TCIMACRO{\U{132} }%
%BeginExpansion
\symbol{156}
%EndExpansion
& \l  & \OE  & \c{T} & \k{U} \\ 
\u{a} & \={e} & \c{g} & 
%TCIMACRO{\U{133} }%
%BeginExpansion
\symbol{188}
%EndExpansion
& \'{N} & \oe  & \c{t} & \k{u} \\ 
\k{A} & \u{E} & \^{H} & \^{J} & \'{n} & \'{R} & \v{T} & \^{W} \\ 
\k{a} & \u{e} & \^{h} & \^{\j} & \c{N} & \'{r} & \v{t} & \^{w} \\ 
\'{C} & \.{E} & 
%TCIMACRO{\U{126} }%
%BeginExpansion
H\llap{\protect\rule[1.1ex]{.735em}{.1ex}}
%EndExpansion
& \c{K} & \c{n} & \c{R} & 
%TCIMACRO{\U{166} }%
%BeginExpansion
T{\hskip-.05em}\llap{\protect\rule[.7ex]{.6em}{.1ex}}{\hskip.05em}
%EndExpansion
& \^{Y} \\ 
\'{c} & \.{e} & 
%TCIMACRO{\U{127} }%
%BeginExpansion
h{\hskip-.2em}\llap{\protect\rule[1.1ex]{.325em}{.1ex}}{\hskip.2em}
%EndExpansion
& \c{k} & \v{N} & \c{r} & 
%TCIMACRO{\U{167} }%
%BeginExpansion
t{\hskip-.05em}\llap{\protect\rule[.7ex]{.36em}{.1ex}}{\hskip.05em}
%EndExpansion
& \^{y} \\ 
\^{C} & \k{E} & \~{I} & \U{138} & \v{n} & \v{R} & \~{U} & \"{Y} \\ 
\^{c} & \k{e} & \~{\i} & \'{L} & 
%TCIMACRO{\U{149} }%
%BeginExpansion
n{\hskip-.3em}\llap{\raise1.5ex\hbox{,}}{\hskip.3em}
%EndExpansion
& \v{r} & \~{u} & \'{Z} \\ 
\.{C} & \v{E} & \={I} & \'{l} & \NG  & \'{S} & \={U} & \'{z} \\ 
\.{c} & \v{e} & \={\i} & \c{L} & \ng  & \'{s} & \={u} & \.{Z} \\ 
\v{C} & \^{G} & \u{I} & \c{l} & \={O} & \^{S} & \u{U} & \.{z} \\ 
\v{c} & \^{g} & \u{\i} & \v{L} & \={o} & \^{s} & \u{u} & \v{Z} \\ 
\v{D} & \u{G} & \k{I} & \v{l} & \u{O} & \c{S} & \r{U} & \v{z} \\ 
\v{d} & \u{g} & \k{i} & 
%TCIMACRO{\U{13f} }%
%BeginExpansion
L{\hskip-.05em}\llap{\raise.5ex\hbox{$\cdot$}}{\hskip.05em}
%EndExpansion
& \u{o} & \c{s} & \r{u} & 
\end{tabular}

\subsection{General Punctuation}

\begin{tabular}{ll}
-- & --- \\ 
` & ' \\ 
\quotesinglbase & \quotedblbase \\ 
\textquotedblleft & \textquotedblright \\ 
\guilsinglleft  & \guilsinglright 
\end{tabular}

\begin{center}
\TeX{} converts the following pairs and triples to single characters called
ligatures

ff fi fl ffi ffl -- \textbf{ff fi fl ffi ffl} -- \textit{ff fi fl ffi ffl}

Kerning is the subtle adjustment of certain pairs of characters.

To, Wo, Ro -- \textbf{To, Wo, Ro }\textit{-- To, Wo, Ro}
\end{center}

\section{Type Styles and Kerns}

The text in this section tests the available \LaTeX{} type styles (plain,
bold, italic, and bold italic) for each of the basic fonts (Roman-Times,
Sans Serif-Arial, and Typewriter-Courier).

\subsection{Type Styles for Roman, Sans Serif, and Typewriter}

Roman \textbf{bold}, \textit{italic}, and \textbf{\textit{bold italic}}.

\textsf{Sans Serif \textbf{bold}, \textit{italic}, and \textbf{\textit{bold
italic}}.}

\texttt{Typewriter \textbf{bold,} \textit{italic,} and\textbf{\ \textit{bold
italic}.}}

{\tiny tiny roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{bold
italic}}}

\textsf{{\tiny tiny Sans Serif \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

\texttt{{\tiny tiny Typewriter \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

{\scriptsize scriptsize roman \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}

\textsf{{\scriptsize scriptsize Sans Serif \textbf{bold},\textit{\ italic},
and \textbf{\textit{bold italic}}}}

\texttt{{\scriptsize scriptsize Typewriter \textbf{bold},\textit{\ italic},
and \textbf{\textit{bold italic}}}}

{\footnotesize footnotesize roman \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}

\textsf{{\footnotesize footnotesize Sans Serif \textbf{bold},\textit{\ italic%
}, and \textbf{\textit{bold italic}}}}

\texttt{{\footnotesize footnotesize Typewriter \textbf{bold},\textit{\ italic%
}, and \textbf{\textit{bold italic}}}}

{\small small roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{%
bold italic}}}

\textsf{{\small small Sans Serif \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

\texttt{{\small small Typewriter \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

{\normalsize normalsize roman \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}

\textsf{{\normalsize normalsize Sans Serif \textbf{bold},\textit{\ italic},
and \textbf{\textit{bold italic}}}}

\texttt{{\normalsize normalsize Typewriter \textbf{bold},\textit{\ italic},
and \textbf{\textit{bold italic}}}}

{\large large roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{%
bold italic}}}

\textsf{{\large large Sans Serif \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

\texttt{{\large large Typewriter \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

{\Large Large roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{%
bold italic}}}

\textsf{{\Large Large Sans Serif \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

\texttt{{\Large Large Typewriter \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

{\LARGE LARGE roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{%
bold italic}}}

\textsf{{\LARGE LARGE Sans Serif \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

\texttt{{\LARGE LARGE Typewriter \textbf{bold},\textit{\ italic}, and 
\textbf{\textit{bold italic}}}}

{\huge huge roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{bold
italic}}}

\textsf{{\huge huge Sans Serif \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

\texttt{{\huge huge Typewriter \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

{\Huge Huge roman \textbf{bold},\textit{\ italic}, and \textbf{\textit{bold
italic}}}

\textsf{{\Huge Huge Sans Serif \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

\texttt{{\Huge Huge Typewriter \textbf{bold},\textit{\ italic}, and \textbf{%
\textit{bold italic}}}}

\subsubsection{Bold Greek Letters}

Here are uppercase and lowercase greek letters, normal and bold, together
with nabla, in a variety of positions:

\begin{equation*}
x+\gamma +\mathbf{\alpha }+\mathbf{\Gamma }(\lambda )\Psi ^{\mathbf{\beta }%
^\delta }+\nabla (\mathbf{\kappa }_{\nu ^{\mathbf{\mu }}}\mathbf{)}+\mathbf{%
\nabla }
\end{equation*}

Here is a more comprehensive listing:

$%
\begin{array}{ccccccc}
\alpha ^{\alpha ^\alpha }\mathbf{\alpha }^{\mathbf{\alpha }^{\mathbf{\alpha }%
}} & \beta ^{\beta ^\beta }\mathbf{\beta }^{\mathbf{\beta }^{\mathbf{\beta }%
}} & \gamma ^{\gamma ^\gamma }\mathbf{\gamma }^{\mathbf{\gamma }^{\mathbf{%
\gamma }}} & \delta ^{\delta ^\delta }\mathbf{\delta }^{\mathbf{\delta }^{%
\mathbf{\delta }}} & \epsilon ^{\epsilon ^\epsilon }\mathbf{\epsilon }^{%
\mathbf{\epsilon }^{\mathbf{\epsilon }}} & \varepsilon ^{\varepsilon
^\varepsilon }\mathbf{\varepsilon }^{\mathbf{\varepsilon }^{\mathbf{%
\varepsilon }}} & \zeta ^{\zeta ^\zeta }\mathbf{\zeta }^{\mathbf{\zeta }^{%
\mathbf{\zeta }}} \\ 
\eta ^{\eta ^\eta }\mathbf{\eta }^{\mathbf{\eta }^{\mathbf{\eta }}} & \theta
^{\theta ^\theta }\mathbf{\theta }^{\mathbf{\theta }^{\mathbf{\theta }}} & 
\vartheta ^{\vartheta ^\vartheta }\mathbf{\vartheta }^{\mathbf{\vartheta }^{%
\mathbf{\vartheta }}} & \iota ^{\iota ^\iota }\mathbf{\iota }^{\mathbf{\iota 
}^{\mathbf{\iota }}} & \kappa ^{\kappa ^\kappa }\mathbf{\kappa }^{\mathbf{%
\kappa }^{\mathbf{\kappa }}} & \lambda ^{\lambda ^\lambda }\mathbf{\lambda }%
^{\mathbf{\lambda }^{\mathbf{\lambda }}} & \mu ^{\mu ^\mu }\mathbf{\mu }^{%
\mathbf{\mu }^{\mathbf{\mu }}}%
\end{array}
$

Here are superscript greek letters, normal and bold, following normal and
bold numbers:

$%
\begin{array}{ccccccc}
1^{\alpha ^{\alpha }}1\mathbf{\alpha }^{\mathbf{\alpha }^{\mathbf{\alpha }}}
& 1^{\beta ^{\beta }}\mathbf{1}^{\mathbf{\beta }^{\mathbf{\beta }}} & 
1^{\gamma ^{\gamma }}\mathbf{1}^{\mathbf{\gamma }^{\mathbf{\gamma }}} & 
1^{\delta ^{\delta }}\mathbf{1}^{\mathbf{\delta }^{\mathbf{\delta }}} & 
1^{\epsilon ^{\epsilon }}\mathbf{1}^{\mathbf{\epsilon }^{\mathbf{\epsilon }}}
& 1^{\varepsilon ^{\varepsilon }}\mathbf{1}^{\mathbf{\varepsilon }^{\mathbf{%
\varepsilon }}} & 1^{\zeta ^{\zeta }}\mathbf{1}^{\mathbf{\zeta }^{\mathbf{%
\zeta }}} \\ 
1^{\eta ^{\eta }}\mathbf{1}^{\mathbf{\eta }^{\mathbf{\eta }}} & 1^{\theta
^{\theta }}\mathbf{1}^{\mathbf{\theta }^{\mathbf{\theta }}} & 1^{\vartheta
^{\vartheta }}\mathbf{1}^{\mathbf{\vartheta }^{\mathbf{\vartheta }}} & 
1^{\iota ^{\iota }}\mathbf{1}^{\mathbf{\iota }^{\mathbf{\iota }}} & 
1^{\kappa ^{\kappa }}\mathbf{1}^{\mathbf{\kappa }^{\mathbf{\kappa }}} & 
1^{\lambda ^{\lambda }}\mathbf{1}^{\mathbf{\lambda }^{\mathbf{\lambda }}} & 
1^{\mu ^{\mu }}\mathbf{1}^{\mathbf{\mu }^{\mathbf{\mu }}}%
\end{array}
$

Here are subscript greek letters, normal and bold, following normal and bold
numbers:

$%
\begin{array}{ccccccc}
1_{\alpha _{\alpha }}\mathbf{1}_{\mathbf{\alpha }_{\mathbf{\alpha }}} & 
1_{\beta _{\beta }}\mathbf{1}_{\mathbf{\beta }_{\mathbf{\beta }}} & 
1_{\gamma _{\gamma }}\mathbf{1}_{\mathbf{\gamma }_{\mathbf{\gamma }}} & 
1_{\delta _{\delta }}\mathbf{1}_{\mathbf{\delta }_{\mathbf{\delta }}} & 
1_{\epsilon _{\epsilon }}\mathbf{1}_{\mathbf{\epsilon }_{\epsilon }} & 
1_{\varepsilon _{\varepsilon }}\mathbf{1}_{\mathbf{\varepsilon }_{\mathbf{%
\varepsilon }}} & 1_{\zeta _{\zeta }}\mathbf{1}_{\mathbf{\zeta }_{\mathbf{%
\zeta }}} \\ 
1_{\eta _{\eta }}\mathbf{1}_{\mathbf{\eta }_{\mathbf{\eta }}} & 1_{\theta
_{\theta }}\mathbf{1}_{\mathbf{\theta }_{\mathbf{\theta }}} & 1_{\vartheta
_{\vartheta }}\mathbf{1}_{\mathbf{\vartheta }_{\mathbf{\vartheta }}} & 
1_{\delta _{\delta }}1_{\mathbf{\delta }_{\mathbf{\delta }}} & 1_{\kappa
_{\kappa }}\mathbf{1}_{\mathbf{\kappa }_{\mathbf{\kappa }}} & 1_{\lambda
_{\lambda }}\mathbf{1}_{\mathbf{\lambda }_{\mathbf{\lambda }}} & 1_{\mu
_{\mu }}\mathbf{1}_{\mathbf{\mu }_{\mathbf{\mu }}}%
\end{array}
$

\section{Font Size Commands}

The \LaTeX{} font size switches are not directly supported by \textsl{SW}.
This is deliberate, because we attempt to create objects that encapsulate
such switches. A switch ``in the clear'' causes the filter to turn that
switch on and off for every paragraph. Thus, all such switches should be
encapsulated like this: \{\TEXTsymbol{\backslash}huge huge text\}. We
strongly discourage the use of such switches. Instead, you should create
appropriate tags in a style, giving the size changes content-oriented
meaning. The following table is included here to check the font sizes and
shapes provided by the style.

\begin{center}
\begin{tabular}{lll}
\textbf{\LaTeX{} Command} & \textbf{Style Editor Size} & \textbf{Example} \\ 
\hline
\TEXTsymbol{\backslash}tiny & tiny & {\tiny Gnu} \\ 
\TEXTsymbol{\backslash}scriptsize & script & {\scriptsize Gnu} \\ 
\TEXTsymbol{\backslash}footnotesize & footnote & {\footnotesize Gnu} \\ 
\TEXTsymbol{\backslash}small & small & {\small Gnu} \\ 
\TEXTsymbol{\backslash}normal & normal & {\normalsize Gnu} \\ 
\TEXTsymbol{\backslash}large & large-1 & {\large Gnu} \\ 
\TEXTsymbol{\backslash}Large & large-2 & {\Large Gnu} \\ 
\TEXTsymbol{\backslash}LARGE & large-3 & {\LARGE Gnu} \\ 
\TEXTsymbol{\backslash}huge & large-4 & {\huge Gnu} \\ 
\TEXTsymbol{\backslash}Huge & large-5 & {\Huge Gnu}%
\end{tabular}
\end{center}

\section{Spacing Objects}

\subsection{Horizontal}

Each horizontal spacing object is placed between reversed brackets, where
this makes sense.

Required space \rbrack\ \lbrack

Non-breaking space \rbrack ~\lbrack

Em space (quad) \rbrack \quad \lbrack

2-Em space (double quad) \rbrack \qquad \lbrack

Thin space \rbrack \thinspace \lbrack

Thick space \rbrack \ \lbrack

Italic correction \rbrack \/\lbrack

Negative thin space \rbrack \negthinspace \lbrack

Zero space \rbrack {}\lbrack

\noindent No indent

Custom space (1 inch) \rbrack \hspace{1in}\lbrack

Custom space (stretchy, 1.0) \rbrack \hfill \lbrack

Custom spaces (stretchy, 1.0, 0.5) \rbrack \hfill \lbrack \rbrack \hspace{%
\stretch{0.5000}}\lbrack

Custom space (stretchy, line) \rbrack \hrulefill \lbrack

Custom space (stretchy, dots) \rbrack \dotfill \lbrack

\subsection{Vertical}

Small skip:\smallskip

Medium skip: \medskip

Big skip: \bigskip

Strut \lbrack \strut \rbrack

Math strut $\sqrt{\mathstrut }$ Radical without math strut $\sqrt{}$

Custom (1 inch): \vspace{1in}

\subsection{Rule}

Rule, raised 0.25 inch, 1 inch wide, .25 inch high \rule[0.25in]{1in}{0.25in}

\subsection{Breaks}

Allowbreak \rbrack \allowbreak \lbrack

Discretionary hyphen \rbrack \-\lbrack

No break \rbrack \nolinebreak \lbrack

Page break\rbrack \pagebreak \lbrack

New page \rbrack \newpage

\lbrack

Line break \rbrack \linebreak \lbrack

New line \rbrack \newline
\lbrack

Custom new line, 1 inch\rbrack \\[1in]
\lbrack

\section{Verb and Verbatim}

The \LaTeX{} \TEXTsymbol{\backslash}verb command is available as a fragment.
You enter the fragment, then choose Edit Properties to change the contents.
A \TEXTsymbol{\backslash}verb: \verb"`~!@#$^&*()_+|\{}"

The \LaTeX{} verbatim environment is translated to the Body Verbatim
paragraph enviroment in \textsl{Scientific Word\/}{}. This environment is
valuable for displaying fragments of program code:
\begin{verbatim}
\long\def\@caption#1[#2]#3{%
  \par
   %\edef\@tempa{\csname #1TOCLabel\endcsname}
   \AddContentsLine
   {\csname ext@#1\endcsname}%
   {#1@toc}%
   {\csname #1toclabel\endcsname}%
   {\ignorespaces #2}%
   \begingroup
     \@parboxrestore
     \normalsize
     \csname @makecaption#1\endcsname{\ignorespaces #3}\par
   \endgroup}
\end{verbatim}

Active \LaTeX{} characters can cause problems in verbatim translations:
\begin{verbatim}
  `~!@#$%^&*()_-+=[]{}\|;:'",<.>/?
\end{verbatim}

Another approach to program code is illustrated by the following, which uses
a table.

\begin{center}
\begin{tabular}{l}
\textbf{for $j:=2$ step $1$ until $n$ do} \\ 
\quad \textbf{begin} $\mathit{accum}:=A\lbrack j\rbrack $; $k:=j-1$; $%
A\lbrack 0\rbrack :=\mathit{accum}$; \\ 
\quad \textbf{while $A\lbrack k\rbrack >\mathit{accum}$ do} \\ 
\qquad \textbf{begin} $A\lbrack k+1\rbrack :=A\lbrack k\rbrack $; $k:=k-1$;
\\ 
\qquad \textbf{end}; \\ 
\quad $A\lbrack k+1\rbrack :=\mathit{accum}$; \\ 
\quad \textbf{end}.%
\end{tabular}
\end{center}

\section{Comments}

You enter \LaTeX{} comments using the comment fragment. Enter the fragment,
then choose Edit Properties to change the body of the comment.%
%This comment is the fragment of TeX code from the Body Verbatim example:
%
%\long\def\@caption#1[#2]#3{%
%  \par
%  %\edef\@tempa{\csname #1TOCLabel\endcsname}
%  \AddContentsLine
%     {\csname ext@#1\endcsname}%
%     {#1@toc}%
%     {\csname #1toclabel\endcsname}%
%     {\ignorespaces #2}%
%  \begingroup
%    \@parboxrestore
%    \normalsize
%    \csname @makecaption#1\endcsname{\ignorespaces #3}\par
%  \endgroup}
%

\section{Tables and Arrays}

\subsection{Tables}

There are many different tables that you can create with the table editor.
Some are included here to test

\begin{center}
\begin{tabular}{|lrrrrrr|}
\hline
&  &  &  &  &  & \% Change \\ 
Ethnicity & 1986 & 1987 & 1988 & 1989 & 1990 & 1986-1990 \\ \hline
Amer. Indian & 294 & 277 & 298 & 328 & 361 & 23.0\% \\ 
Black & 192 & 206 & 199 & 183 & 225 & 17.0\% \\ 
Hispanic & 3,108 & 3,131 & 3,433 & 3,637 & 4,038 & 30.0\% \\ 
Oriental & 67 & 65 & 71 & 77 & 96 & 30.0\% \\ 
Other & 10,057 & 10,324 & 10,283 & 10,075 & 10,089 & 0.3\% \\ \hline
\end{tabular}

\begin{tabular}{|l|rrrrr|}
\hline
Course & 1987 & 1988 & 1989 & 1990 & 1991 \\ \hline
MATH 280 & 68 & 61 & 58 & 61 & 84 \\ \hline
MATH 480 & 36 & 26 & 41 & 44 & 53 \\ \hline
\end{tabular}
\end{center}

\subsubsection{From the \LaTeX{} User's Guide and Reference Manual}

\begin{center}
\begin{tabular}{||l|lr||}
\hline
gnats & gram & \$13.65 \\ \cline{2-3}
& each & .01 \\ \hline
gnu & stuffed & 92.50 \\ \cline{1-1}\cline{3-3}
emur &  & 33.33 \\ \hline
armadillo & frozen & 8.99 \\ \hline
\end{tabular}

\begin{tabular}{|l|l|r|}
\hline\hline
\emph{type} & \multicolumn{2}{c|}{\emph{style}} \\ \hline
smart & red & short \\ 
rather silly & puce & tall \\ \hline\hline
\end{tabular}
\end{center}

\subsubsection{From Jane Hahn's \LaTeX{} for Everyone}

\begin{center}
\begin{tabular}{|l|r|c|r|}
\hline
\multicolumn{4}{|c|}{\textbf{Overall Heading of Table}} \\ \hline
\multicolumn{1}{|c|}{Left-justified} & \multicolumn{1}{c|}{Right-justified}
& Centered & \multicolumn{1}{|c|}{Right-justified} \\ \hline\hline
one & two & three & four \\ \cline{2-4}
1 & 2 & 3 & 4 \\ 
i & ii & iii & iv \\ \hline
\end{tabular}

\begin{tabular}{|l|r@{.}l|}
\hline
\multicolumn{3}{|c|}{\textbf{Household Budget}} \\ \hline\hline
& \multicolumn{2}{c|}{\textbf{\% of}} \\ 
\textbf{Item} & \multicolumn{2}{c|}{\textbf{Budget}} \\ \hline
Housing & 50 & 0 \\ 
Food & 25 & 0 \\ 
Toys & 10 & 5 \\ 
Pet Supplies & 7 & 5 \\ 
Clothes & 5 & 25 \\ 
Charity & 1 & 75 \\ \hline
\end{tabular}

\begin{tabular}{|l|cr|}
\hline
\multicolumn{3}{|c|}{\textbf{PORTABLE HOOK-ON CHAIRS}} \\ \hline\hline
\textbf{BRAND} & \textbf{Graco} & \textbf{Strolee} \\ \hline
\textbf{MODEL} & Tot Loc Chair & Meal Mate \\ \hline
\textbf{PRICE} & \$23 & \$32 \\ \hline
\textbf{OVERALL JUDGEMENT} & Satisfactory & Satisfactory \\ \hline
\textbf{WEIGHT} & 7 lb. 9 oz. & 6 lb. 8 oz. \\ \hline
\end{tabular}

\begin{tabular}{|ll|}
\hline
\multicolumn{2}{|c|}{\textbf{THE CATECHISM}} \\ \hline
Q. & What are we by nature? \\ 
A. & We are part of God's creation, made in the image of God. \\[3mm] 
Q. & What does it mean to be created in the image of God? \\ 
A. & It means that we are free to make choices: to love; to create, to
reason, \\[3mm] 
& and to live in harmony with creation and with God. \\ 
Q. & Why then do we live apart from God and out of harmony with creation? \\ 
A. & From the beginning, human beings have misused their freedom and \\ 
& made wrong choices. \\ \hline
\end{tabular}
\end{center}

\subsubsection{The Economist}

Here is a table that is too wide for the page:

\begin{center}
\begin{tabular}{llllcllcl}
&  &  &  & \multicolumn{5}{c}{\textbf{\% change on}} \\ \cline{5-9}
&  & \multicolumn{2}{c}{\textbf{1993/94}} & \textbf{one} & \textbf{one} & 
\textbf{record} & \multicolumn{2}{c}{\textbf{Dec 31st 1992}} \\ \cline{3-4}
& \textbf{Feb 22nd} & \textbf{high} & \textbf{low} & \textbf{week} & \textbf{%
year} & \textbf{high} & \textbf{in local} & \textbf{in \$} \\ 
&  &  &  & \multicolumn{1}{l}{} &  &  & \textbf{currency} & \textbf{terms}
\\ \hline
\textbf{Australia} & \multicolumn{1}{r}{2,202.5} & \multicolumn{1}{r}{2,340.6
} & \multicolumn{1}{r}{1,495.0} & \multicolumn{1}{l}{$-$ 1.4} & $+$ 36.9 & $%
- $ 5.9 & \multicolumn{1}{l}{$+$42.1} & $+$48.6 \\ \hline
\textbf{Austria} & \multicolumn{1}{r}{450.7} & \multicolumn{1}{r}{460.7} & 
\multicolumn{1}{r}{300.3} & \multicolumn{1}{l}{$+$ 0.1} & $+$ 29.8 & $-$35.9
& \multicolumn{1}{l}{$+$44.0} & $+$35.0 \\ \hline
\textbf{Belgium} & \multicolumn{1}{r}{1,504.5} & \multicolumn{1}{r}{1,542.7}
& \multicolumn{1}{r}{1,125.5} & \multicolumn{1}{l}{$-$ 1.2} & $+$ 24.3 & $-$
2.5 & \multicolumn{1}{l}{$+$33.5} & $+$24.8 \\ \hline
\textbf{Britain} & \multicolumn{1}{r}{3,333.7} & \multicolumn{1}{r}{3,520.3}
& \multicolumn{1}{r}{2,737.6} & \multicolumn{1}{l}{$-$ 1.8} & $+$ 18.3 & $-$
5.3 & \multicolumn{1}{l}{$+$17.1} & $+$14.4 \\ \hline
\textbf{Canada} & \multicolumn{1}{r}{4,371.1} & \multicolumn{1}{r}{4,591.3}
& \multicolumn{1}{r}{3,275.8} & \multicolumn{1}{l}{$-$ 1.0} & $+$ 26.6 & $-$
4.8 & \multicolumn{1}{l}{$+$30.5} & $+$23.5 \\ \hline
\textbf{Denmark} & \multicolumn{1}{r}{407.4} & \multicolumn{1}{r}{415.8} & 
\multicolumn{1}{r}{261.9} & \multicolumn{1}{l}{$+$ 0.3} & $+$ 44.4 & $-$ 2.0
& \multicolumn{1}{l}{$+$55.7} & $+$45.0 \\ \hline
\textbf{France *} & \multicolumn{1}{r}{1,506.6} & \multicolumn{1}{r}{1,585.2}
& \multicolumn{1}{r}{1,114.2} & \multicolumn{1}{l}{$-$ 1.0} & $+$ 23.1 & $-$
5.0 & \multicolumn{1}{l}{$+$32.1} & $+$24.4 \\ \hline
\textbf{Germany} & \multicolumn{1}{r}{2,107.6} & \multicolumn{1}{r}{2,268.0}
& \multicolumn{1}{r}{1,516.5} & \multicolumn{1}{l}{$-$ 0.4} & $+$ 26.8 & $-$
7.1 & \multicolumn{1}{l}{$+$36.4} & $+$27.9 \\ \hline
\textbf{Holland} & \multicolumn{1}{r}{285.6} & \multicolumn{1}{r}{294.8} & 
\multicolumn{1}{r}{198.6} & \multicolumn{1}{l}{$-$ 1.4} & $+$ 35.7 & $-$ 3.1
& \multicolumn{1}{l}{$+$44.2} & $+$35.4 \\ \hline
\textbf{Italy} & \multicolumn{1}{r}{672.2} & \multicolumn{1}{r}{689.0} & 
\multicolumn{1}{r}{446.3} & \multicolumn{1}{l}{$-$ 0.6} & $+$ 33.7 & $-$26.0
& \multicolumn{1}{l}{$+$50.6} & $+$32.0 \\ \hline
\textbf{Japan} & \multicolumn{1}{r}{19,342.6} & \multicolumn{1}{r}{21,148.1}
& \multicolumn{1}{r}{16,078.7} & \multicolumn{1}{l}{$+$ 1.9} & $+$ 14.7 & $-$%
50.3 & \multicolumn{1}{l}{$+$14.3} & $+$35.3 \\ \hline
\textbf{Spain} & \multicolumn{1}{r}{339.6} & \multicolumn{1}{r}{358.3} & 
\multicolumn{1}{r}{215.6} & \multicolumn{1}{l}{$-$ 2.0} & $+$ 49.0 & $-$ 5.2
& \multicolumn{1}{l}{$+$58.5} & $+$29.2 \\ \hline
\textbf{Sweden} & \multicolumn{1}{r}{1,565.8} & \multicolumn{1}{r}{1,603.9}
& \multicolumn{1}{r}{879.1} & \multicolumn{1}{l}{$+$ 2.1} & $+$ 58.5 & $-$
2.4 & \multicolumn{1}{l}{$+$71.6} & $+$53.0 \\ \hline
\textbf{Switzerland} & \multicolumn{1}{r}{2,982.8} & \multicolumn{1}{r}{
3,178.4} & \multicolumn{1}{r}{2,049.5} & \multicolumn{1}{l}{$-$ 0.3} & $+$
45.5 & $-$ 6.2 & \multicolumn{1}{l}{$+$41.6} & $+$43.1 \\ \hline
\textbf{United States} & \multicolumn{1}{r}{3,911.7} & \multicolumn{1}{r}{
3,978.4} & \multicolumn{1}{r}{3,242.0} & \multicolumn{1}{l}{$-$ 0.4} & $+$
17.7 & $-$ 1.7 & \multicolumn{1}{l}{$+$18.5} & $+$18.5 \\ \hline
\textbf{World }$\dagger $ & \multicolumn{1}{r}{621.2} & \multicolumn{1}{r}{
641.0} & \multicolumn{1}{r}{488.6} & \multicolumn{1}{l}{$-$ 0.7} & $+$ 23.1
& $-$ 3.1 & \multicolumn{1}{l}{$+$25.0} & $+$25.0 \\ \hline
\end{tabular}
\end{center}

\section{Matrices}

Matrices have similar behavior to tables, but are in math mode.

Inline matrix: $%
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
$. Generally, these are hard to read without surrounding fences, like $%
\left( 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right) $ or $\left[ 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right] $.

Displayed matrix:

\begin{equation*}
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\text{or }\left( 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right) \text{ or }\left[ 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right]
\end{equation*}

Try various column alignment options: $\ $left$%
\begin{array}{ll}
1 & \frac{1}{4}+\frac{1}{4} \\ 
\frac{1}{4}+\frac{1}{4} & \frac{1}{3}%
\end{array}%
$, center$%
\begin{array}{cc}
1 & \frac{1}{4}+\frac{1}{4} \\ 
\frac{1}{4}+\frac{1}{4} & \frac{1}{3}%
\end{array}%
$, right $%
\begin{array}{rr}
1 & \frac{1}{4}+\frac{1}{4} \\ 
\frac{1}{4}+\frac{1}{4} & \frac{1}{3}%
\end{array}%
$.

Try various baseline alignment options: $\ $top row$%
\begin{array}[t]{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
$, center$%
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
$, bottom row $%
\begin{array}[b]{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
$.

Finally, you can use built-in delimiters which may look better in certain
situations. brackets $%
\begin{bmatrix}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{bmatrix}%
$ vs. $\left[ 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right] $ (standard matrix with fence -- the screen appearance is the same
in SWP). braces $%
\begin{Bmatrix}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{Bmatrix}%
$ vs. $\left\{ 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right\} $. vertical bar $%
\begin{vmatrix}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{vmatrix}%
$ vs. $\left\vert 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right\vert $. double vertical bar $%
\begin{Vmatrix}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{Vmatrix}%
$ vs. $\left\Vert 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right\Vert $. parentheses $%
\begin{pmatrix}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{pmatrix}%
$ vs. $\left( 
\begin{array}{cc}
1 & \frac{1}{2} \\ 
\frac{1}{2} & \frac{1}{3}%
\end{array}%
\right) $.

\section{Graphics}

Here is a displayed graphic.\FRAME{dhFU}{2.3298in}{1.5489in}{0pt}{\Qcb{%
Triangle}}{\Qlb{triangle}}{triangle.wmf}{\special{language "Scientific
Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "FULL";valid_file
"F";width 2.3298in;height 1.5489in;depth 0pt;original-width
166.9375pt;original-height 110.3125pt;cropleft "0";croptop
"1.0004";cropright "0.9981";cropbottom "0";filename
'../Graphics/triangle.wmf';file-properties "XNPEU";}}Displayed graphic.%
\FRAME{dtbpF}{0.3494in}{0.2992in}{0pt}{}{}{swplogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"FULL";valid_file "F";width 0.3494in;height 0.2992in;depth
0pt;original-width 23.3125pt;original-height 20.3125pt;cropleft "0";croptop
"0.9851";cropright "1.0129";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}

In-line graphic in a centered paragraph.

\begin{center}
\FRAME{itbpF}{0.3494in}{0.2992in}{0in}{}{}{swplogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"FULL";valid_file "F";width 0.3494in;height 0.2992in;depth 0in;cropleft
"0";croptop "0.9851";cropright "1.0129";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}
\end{center}

Various inline graphics. On baseline\FRAME{itbpF}{0.3494in}{0.2992in}{0in}{}{%
}{swplogo.wmf}{\special{language "Scientific Word";type
"GRAPHIC";maintain-aspect-ratio TRUE;display "FULL";valid_file "F";width
0.3494in;height 0.2992in;depth 0in;original-width 0.3226in;original-height
0.2811in;cropleft "0";croptop "0.9851";cropright "1.0129";cropbottom
"0";filename '../Graphics/swplogo.wmf';file-properties "XNPEU";}}, raised%
\FRAME{itbpF}{0.3494in}{0.2992in}{-0.3122in}{}{}{swplogo.wmf}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "FULL";valid_file "F";width 0.3494in;height 0.2992in;depth
-0.3122in;original-width 0.3226in;original-height 0.2811in;cropleft
"0";croptop "0.9851";cropright "1.0129";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}, lowered\FRAME{itbpF}{%
0.3494in}{0.2992in}{0.2811in}{}{}{swplogo.wmf}{\special{language "Scientific
Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "FULL";valid_file
"F";width 0.3494in;height 0.2992in;depth 0.2811in;original-width
0.3226in;original-height 0.2811in;cropleft "0";croptop "0.9851";cropright
"1.0129";cropbottom "0";filename '../Graphics/swplogo.wmf';file-properties
"XNPEU";}}, with caption\FRAME{itbpFU}{0.3494in}{0.2992in}{0in}{\Qcb{%
Butterfly}}{}{swplogo.wmf}{\special{language "Scientific Word";type
"GRAPHIC";maintain-aspect-ratio TRUE;display "FULL";valid_file "F";width
0.3494in;height 0.2992in;depth 0in;original-width 23.3125pt;original-height
20.3125pt;cropleft "0";croptop "0.9875";cropright "1.0150";cropbottom
"0";filename '../Graphics/swplogo.wmf';file-properties "XNPEU";}}, without
frame\FRAME{itbpF}{0.3494in}{0.2992in}{0in}{}{}{swplogo.wmf}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.3494in;height 0.2992in;depth
0in;original-width 23.3125pt;original-height 20.3125pt;cropleft "0";croptop
"0.9875";cropright "1.0150";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}, frame only\FRAME{itbpF%
}{0.3494in}{0.2992in}{0in}{}{}{swplogo.wmf}{\special{language "Scientific
Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "FRAME";valid_file
"F";width 0.3494in;height 0.2992in;depth 0in;original-width
0.3226in;original-height 0.2811in;cropleft "0";croptop "0.9875";cropright
"1.0150";cropbottom "0";filename '../Graphics/swplogo.wmf';file-properties
"XNPEU";}}, iconified\FRAME{itbpF}{0.3494in}{0.2992in}{0in}{}{}{swplogo.wmf}{%
\special{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "ICON";valid_file "F";width 0.3494in;height 0.2992in;depth
0in;original-width 0.3226in;original-height 0.2811in;cropleft "0";croptop
"0.9875";cropright "1.0150";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}, using the default 
\FRAME{itbpF}{0.3494in}{0.2992in}{0in}{}{}{swplogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"FULL";valid_file "F";width 0.3494in;height 0.2992in;depth
0in;original-width 23.3125pt;original-height 20.3125pt;cropleft "0";croptop
"0.9875";cropright "1.0150";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}.

Different graphic types:

WMF :\FRAME{itbpF}{0.7507in}{0.2162in}{0in}{}{}{greeks.wmf}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.7507in;height 0.2162in;depth
0in;original-width 0.7187in;original-height 0.1877in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/greeks.wmf';file-properties "XNPEU";}} \ \ GIF:\FRAME{itbpF}{%
1.913in}{0.8553in}{0.2292in}{}{}{nb2.gif}{\special{language "Scientific
Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "PICT";valid_file
"F";width 1.913in;height 0.8553in;depth 0.2292in;original-width
1.8749in;original-height 0.8233in;cropleft "0";croptop "1";cropright
"1";cropbottom "0";filename '../Graphics/NB2.GIF';file-properties "XNPEU";}}
\ JPEG: \FRAME{itbpF}{0.6123in}{0.8475in}{0.2006in}{}{}{barry.jpg}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.6123in;height 0.8475in;depth
0.2006in;original-width 0.4566in;original-height 0.6434in;cropleft
"0";croptop "1";cropright "1";cropbottom "0";filename
'../Graphics/barry.jpg';file-properties "XNPEU";}}

AI: \FRAME{dtbpF}{2.3177in}{1.817in}{0pt}{}{}{020112.ai}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"PICT";valid_file "F";width 2.3177in;height 1.817in;depth 0pt;original-width
2.2779in;original-height 1.7798in;cropleft "0";croptop "1";cropright
"1";cropbottom "0";filename '../Graphics/020112.AI';file-properties "XNPEU";}%
}

Here is a floating graphic.

\FRAME{ftbpFU}{0.3632in}{0.3736in}{0pt}{\Qcb{This is the caption text. It's
below. It also contains a marker (\label{fig:key2})}}{\Qlb{fig:key1}}{%
nblogo.wmf}{\special{ language "Scientific Word"; type "GRAPHIC";
maintain-aspect-ratio TRUE; display "PICT"; valid_file "F"; width 0.3632in;
height 0.3736in; depth 0pt; original-width 0.3329in; original-height
0.3433in; cropleft "0"; croptop "1"; cropright "1"; cropbottom "0"; filename
'../Graphics/NBlogo.wmf';file-properties "XNPEU";}}

Reference to fig:key1 (\ref{fig:key1}) and to fig:key2 (\ref{fig:key2})

Here is a floating graphic with very long keys.

\FRAME{ftbpFU}{0.3632in}{0.3736in}{0pt}{\Qcb{This is the caption text. It's
below. It also contains a marker (\label{fig: This is a very long key that
can cause problems1})}}{\Qlb{fig: This is a very long key that can cause
problems2}}{nblogo.wmf}{\special{ language "Scientific Word"; type
"GRAPHIC"; maintain-aspect-ratio TRUE; display "PICT"; valid_file "F"; width
0.3632in; height 0.3736in; depth 0pt; original-width 0.3329in;
original-height 0.3433in; cropleft "0"; croptop "1"; cropright "1";
cropbottom "0"; filename '../Graphics/NBlogo.wmf';file-properties "XNPEU";}}

References to (\ref{fig: This is a very long key that can cause problems1})
and to (\ref{fig: This is a very long key that can cause problems2})\FRAME{%
ftbpFU}{0.3632in}{0.3736in}{0pt}{\Qcb{This is the caption text. It is a long
caption so that we can observe line wrap in this case of a long long long
caption longer than the line width.}}{}{nblogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"PICT";valid_file "F";width 0.3632in;height 0.3736in;depth
0pt;original-width 0.3329in;original-height 0.3433in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/NBlogo.wmf';file-properties "XNPEU";}}\FRAME{ftbpFU}{0.3632in}{%
0.3736in}{0pt}{\Qcb{This is a caption containing mathematics. $\protect\int_{%
\protect\alpha }^{\protect\beta }\ln udu$}}{}{nblogo.wmf}{\special{language
"Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display
"PICT";valid_file "F";width 0.3632in;height 0.3736in;depth
0pt;original-width 0.3329in;original-height 0.3433in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/NBlogo.wmf';file-properties "XNPEU";}}

\section{Standard \LaTeX{} Float Environments}

The standard \LaTeX{} float environments are figure and table. These are not
directly supported by the SW/SWP input and output filters. However, these
environments are preserved, and you can edit their contents using Edit
Properties. All label statements are also visible in SW/SWP for
cross-references.

\begin{figure}[ht]
\caption{Caption First}
\label{fig:in2}
\begin{center}
\fbox{\ldots{} figure body \ldots}
\par
\fbox{\ldots{} figure body \ldots}
\end{center}
\caption{Caption Second}
\label{fig:in4}
\end{figure}

\begin{table}[ht]
\caption{Caption First}
\label{tab:in2}
\begin{center}
\fbox{\ldots{} table body \ldots}
\par
\fbox{\ldots{} table body \ldots}
\end{center}
\caption{Caption Second}
\label{tab:in4}
\end{table}

\section{Scientific Notebook Items}

These constructs were introduced with the first version of Scientific
Notebook. They are now available in SW/SWP. They are provided here to test
the ability of SW/SWP to create a document containing these constructs that
can also be compiled with \LaTeX{}.

\subsection{Hypertext Links}

Hypertext link with text: 
%TCIMACRO{%
%\hyperref{MacKichan Software, Inc. home page}{}{}{http://www.mackichan.com}}%
%BeginExpansion
\msihyperref{MacKichan Software, Inc. home page}{}{}{http://www.mackichan.com}%
%EndExpansion

Hypertext link with graphic: 
%TCIMACRO{%
%\hyperref{\FRAME{itbpF}{0.499in}{0.2257in}{0in}{}{}{nb2.gif}{\special{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "PICT";valid_file "F";width 0.499in;height 0.2257in;depth 0in;original-width 1.8749in;original-height 0.8233in;cropleft "0";croptop "1";cropright "1";cropbottom "0";filename '../Graphics/Nb2.gif';file-properties "XNPEU";}}}{}{}{http://www.scinotebook.com}}%
%BeginExpansion
\msihyperref{\FRAME{itbpF}{0.499in}{0.2257in}{0in}{}{}{nb2.gif}{\special{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio TRUE;display "PICT";valid_file "F";width 0.499in;height 0.2257in;depth 0in;original-width 1.8749in;original-height 0.8233in;cropleft "0";croptop "1";cropright "1";cropbottom "0";filename '../Graphics/Nb2.gif';file-properties "XNPEU";}}}{}{}{http://www.scinotebook.com}%
%EndExpansion

Hypertext links can go to external documents specified by a URI as show
above, or to markers or Hypertext targets, as illustrated here: 
%TCIMACRO{\hyperref{go to target}{}{}{my target}}%
%BeginExpansion
\msihyperref{go to target}{}{}{my target}%
%EndExpansion

\subsection{Hypertext Targets}

Hypertext target at the end of this sentence.\label{my target} These become
visible by turning on markers.

\subsection{Formulas}

Formulas allow you to create elements which are recalculated every time they
are displayed on screen. If the expression uses defined quantities, then the
formula will change every time you redefine the quantity.

Formula: $%
%TCIMACRO{\FORMULA{\int ax^{2}dx}{\frac{1}{3}ax^{3}}{evaluate}}%
%BeginExpansion
\frac{1}{3}ax^{3}%
%EndExpansion
$

Now, define $a=\pi $ and see what happens.

\subsection{Units}

%TCIMACRO{\TeXButton{Reverse noindent}{\hspace{\parindent}}}%
%BeginExpansion
\hspace{\parindent}%
%EndExpansion
\begin{tabular}{lll}
\multicolumn{3}{c}{\textbf{Base SI Units}} \\ \hline
\textit{Physical quantity} &  & \textit{Symbol} \\ \hline
length &  & $\unit{m}$ \\ 
mass &  & $\unit{kg}$ \\ 
time &  & $\unit{s}$ \\ 
electric current &  & $\unit{A}$ \\ 
thermodynamic temperature &  & $\unit{K}$ \\ 
amount of substance &  & $\unit{mol}$ \\ 
luminous intensity &  & $\unit{cd}$ \\ \hline
\end{tabular}

\begin{tabular}{lll}
\multicolumn{3}{c}{\textbf{Supplementary SI Units}} \\ \hline
\textit{Physical quantity} & \textit{Name} & \textit{Symbol} \\ \hline
plane angle & radian & $\unit{rad}$ \\ 
solid angle & steradian & $\unit{sr}$ \\ \hline
\end{tabular}

\begin{tabular}{lll}
\multicolumn{3}{c}{\textbf{Derived SI Units with Special Names}} \\ \hline
\textit{Physical quantity} &  & \textit{Symbol} \\ \hline
frequency &  & $\unit{Hz}$ \\ 
energy &  & $\unit{J}$ \\ 
force &  & $\unit{N}$ \\ 
power &  & $\unit{W}$ \\ 
pressure &  & $\unit{Pa}$ \\ 
electric charge &  & $\unit{C}$ \\ 
electric potential difference &  & $\unit{V}$ \\ 
electric resistance &  & $\unit{%
%TCIMACRO{\U{3a9}}%
%BeginExpansion
\Omega%
%EndExpansion
}$ \\ 
electric conductance &  & $\unit{S}$ \\ 
electric capacitance &  & $\unit{F}$ \\ 
magnetic flux &  & $\unit{Wb}$ \\ 
inductance &  & $\unit{H}$ \\ 
magnetic flux density &  & $\unit{T}$ \\ 
luminous flux &  & $\unit{lm}$ \\ 
illumination &  & $\unit{lx}$ \\ \hline
\end{tabular}

The following examples use Unicode characters.

MicroFarad: $\unit{%
%TCIMACRO{\U{3bc}}%
%BeginExpansion
\mu%
%EndExpansion
F}$

Degree Celcius: $\unit{%
%TCIMACRO{\U{2103}}%
%BeginExpansion
{}^{\circ}{\rm C}%
%EndExpansion
}$

Angular Measure: $30\unit{%
%TCIMACRO{\U{b0}}%
%BeginExpansion
{{}^\circ}%
%EndExpansion
}10\unit{%
%TCIMACRO{\U{2032}}%
%BeginExpansion
{}^{\prime }%
%EndExpansion
}12\unit{%
%TCIMACRO{\U{2033}}%
%BeginExpansion
{}^{\prime \prime}%
%EndExpansion
}$

Ohm: $\unit{%
%TCIMACRO{\U{3a9}}%
%BeginExpansion
\Omega%
%EndExpansion
}$

\subsection{New Note Types}

Margin Hint with icon: 
\CustomNote{Margin Hint}{%
Margin Hint}

\vspace{1pt}Margin Hint with text: 
\CustomNote[Hint!]{Margin Hint}{%
Margin Hint}

Margin Hint with picture: 
\CustomNote[{\FRAME{itbpF}{0.3528in}{0.3105in}{0in}{}{}{swplogo.wmf}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.3528in;height 0.3105in;depth
0in;original-width 0.3226in;original-height 0.2811in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}}]{Margin Hint}{%
Margin Hint}

Solution Note with icon: 
\CustomNote{Solution Note}{%
Solution Note}

Solution Note with text: 
\CustomNote[Solution Note!]{Solution Note}{%
Solution Note} \

\vspace{1pt}Solution Note with picture: 
\CustomNote[{\FRAME{itbpF}{0.5405in}{0.2447in}{0in}{}{}{nb2.gif}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.5405in;height 0.2447in;depth
0in;original-width 1.8749in;original-height 0.8233in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/Nb2.gif';file-properties "XNPEU";}}}]{Solution Note}{%
Solution Note} \

Problem Solving Hint with icon: 
\CustomNote{Problem Solving Hint}{%
Problem Solving Hint}

Problem Solving Hint with text: 
\CustomNote[Problem Solving Hint!]{Problem Solving Hint}{%
Problem Solving Hint}

Problem Solving Hint with picture: 
\CustomNote[{\FRAME{itbpF}{0.5682in}{0.3822in}{0in}{}{}{triangle.wmf}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.5682in;height 0.3822in;depth
0in;original-width 2.3099in;original-height 1.5264in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/TRIANGLE.WMF';file-properties "XNPEU";}}}]{Problem Solving Hint}
{%
Problem Solving Hint}

Note with icon: 
\CustomNote{Note}{%
Note}

Note with text: 
\CustomNote[Note!]{Note}{%
Note} \

Note with picture: 
\CustomNote[{\FRAME{itbpF}{0.3892in}{0.5362in}{0in}{}{}{barry.jpg}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.3892in;height 0.5362in;depth
0in;original-width 0.4566in;original-height 0.6434in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/barry.jpg';file-properties "XNPEU";}}}]{Note}{%
Note}

Answer Note with icon: 
\CustomNote{AnswerNote}{%
Answer Note}.

Answer Note with text: 
\CustomNote[Answer Note!]{AnswerNote}{%
Answer Note}.

Answer Note with picture: 
\CustomNote[{\FRAME{itbpF}{0.5353in}{0.5353in}{0in}{}{}{sticker.gif}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.5353in;height 0.5353in;depth
0in;original-width 1.1459in;original-height 1.1459in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/STICKER.GIF';file-properties "XNPEU";}}}]{AnswerNote}{%
Answer Note}.

Here is a note containing a picture: 
\CustomNote[{\FRAME{itbpF}{0.5353in}{0.5353in}{0in}{}{}{sticker.gif}{\special%
{language "Scientific Word";type "GRAPHIC";maintain-aspect-ratio
TRUE;display "PICT";valid_file "F";width 0.5353in;height 0.5353in;depth
0in;original-width 1.1459in;original-height 1.1459in;cropleft "0";croptop
"1";cropright "1";cropbottom "0";filename
'../Graphics/Sticker.gif';file-properties "XNPEU";}}}]{AnswerNote}{%
This answer note contains a picture:\FRAME{dtbpF}{0.3528in}{0.3105in}{0pt}{}{%
}{swplogo.wmf}{\special{language "Scientific Word";type
"GRAPHIC";maintain-aspect-ratio TRUE;display "PICT";valid_file "F";width
0.3528in;height 0.3105in;depth 0pt;original-width 0.3226in;original-height
0.2811in;cropleft "0";croptop "1";cropright "1";cropbottom "0";filename
'../Graphics/swplogo.wmf';file-properties "XNPEU";}}}.

\subsection{HTML Fields}

These are analogous to TeX Fields, but are active when you Export to HTML.

%TCIMACRO{\HTMLButton{HTML Field}{<hr title="from an HTML field"/>}}%

\section{Conclusion}

We are now done with our sample article.

The following references automatically generate a References section heading.

\begin{thebibliography}{99}
\bibitem{black} D. Black, \emph{The Theory of Committees and Elections},
Cambridge: Cambridge University Press (1958).

\bibitem{blyth} C. Blyth, \emph{Some probability paradoxes in choice from
among random alternatives}, J. Amer. Statist. Assoc. \textbf{67} (1972),
366--373.

\bibitem{Chang} Chang Li-chien, \emph{On the maximin probability of cyclic
random inequalities}, Scientia Sinica \textbf{10} (1961), 499--504.

\bibitem{condorcet} Marquis de Condorcet, \emph{Essai sur l'application de
l'analyse \`{a} la probabilit\'{e} des d\'{e}cisions rendues \`{a} la
pluralit\'{e} des voix}, Paris (1785).

\bibitem{dunford} N. Dunford and J. Schwartz, \emph{Functional Analysis}, v.
2, John Wiley and Sons, New York, 1963.

\bibitem{funkenbusch} W. W. Funkenbusch, \emph{A gaming wheel based on
cyclic advantage in symbol choice}, The Gambling Papers, Vol. XIII (1982),
68--83 University of Nevada, Reno.

\bibitem{gardner} M. Gardner, \emph{The paradox of the nontransitive dice
and the elusive principle of indifference}, Scientific American \textbf{223}
(1970), 110--114.

\bibitem{gardnerb} M. Gardner, \emph{On the paradoxical situations that
arise from nontransitive relations}, Scientific American \textbf{231}
(1974), 120--125.

\bibitem{funkensaari} W. W. Funkenbusch and Saari, D. G., \emph{Preferences
among preferences or nested cyclic stochastic inequalities}, Congr. Numer. 
\textbf{39} (1983), 419--432.

\bibitem{struwe} M. Struwe, \emph{Semilinear wave equations}, Bull. Amer.
Math. Soc. \textbf{26} (1992), 53-85.

\bibitem{thurston} W.P. Thurston, \emph{Geometry and topology of three
manifolds}, Lecture notes, Princeton Univ., NJ, 1979.
\end{thebibliography}

\end{document}

### 2008-10-08 prince/TCITeX/TeX/LaTeX/SWmacros/maplems.tex
add parts of tcitex directory to prince

%% $Revision$
\documentstyle[maplems]{article}
{%
  \catcode`| = 0
  |catcode`\\ = 12
  |gdef|backslash{\}
}

\title{Export to Latex}
\author{Waterloo Maple Software}
\date{March, 1994}
\begin{document}
\maketitle

\section{Introduction}
Maple V Release 3 introduces the capability of exporting the 
contents of a Maple worksheet into a file suitable for processing 
by the \LaTeX{} document formatting system.

The text regions of the Maple worksheet and the various algebraic
output regions are automatically written to a file along with 
appropriate latex macros so that the contents of the worksheet 
can then be formatted and printed using \LaTeX{}.
Of particular interest is the fact that the math typeset
regions, including the multi-line displays, are reformatted
to the user specified column width using Maple's \LaTeX{} math formatting
capabilities\footnote{
This is an entirely new mechanism based on Maple's high resolution
math formatting technology. It is separate from Maple's library
level {\tt latex(~)} command which can still be used to format
individual expressions.}.  This feature automatically carries out
linebreaking of large mathematical formulae in \LaTeX{}.

The automatically generated \LaTeX{} source document (say ``worksht.tex'') 
has a structure similar to that shown below.

\begin{verbatim}
\documentstyle[maplems]{article}
\begin{document}
First paragraph of text.

Second paragraph of text. This is a test file.
\begin{mapleinput}
(a + b);
\end{mapleinput}
\begin{maplelatex}
\[
{a} + {b}
\]
\end{maplelatex}
We can display mathematics in a variety of forms.
\begin{mapleinput}
Int( 1/(1 + x^4),x);
\end{mapleinput}
\begin{maplelatex}
\[
{\displaystyle \int} {\displaystyle \frac {1}{1 + {x}^{4}}}\,{d}{
x}
\]
\end{maplelatex}
\begin{mapleinput}
value(");
\end{mapleinput}
\begin{maplelatex}
\begin{eqnarray*}
\lefteqn{{\displaystyle \frac {1}{8}}\,\sqrt {2}\,{\rm ln}
 \left( {\vrule height0.89em width0em depth0.89em} \right. \,
{\displaystyle \frac {{x}^{2} + {x}\,\sqrt {2} + 1}{{x}^{2} - {x}
\,\sqrt {2} + 1}}\, \left. {\vrule 
height0.89em width0em depth0.89em} \right)  + 
{\displaystyle \frac {1}{4}}\,\sqrt {2}\,{\rm arctan} \left( 
{\vrule height0.41em width0em depth0.41em} \right. \,{x}\,\sqrt {
2} + 1\, \left. {\vrule height0.41em width0em depth0.41em}
 \right) } \\
 & & \mbox{} + {\displaystyle \frac {1}{4}}\,\sqrt {2}\,{\rm 
arctan} \left( {\vrule height0.41em width0em depth0.41em}
 \right. \,{x}\,\sqrt {2} - 1\, \left. {\vrule 
height0.41em width0em depth0.41em} \right) \mbox{\hspace{88pt}}
\end{eqnarray*}
\end{maplelatex}
And more...   TTY based output is handled as
\begin{mapleinput}
Int((x+a)^3,x=a..b);
\end{mapleinput}
\begin{maplettyout}
                          b
                          /
                         |         3
                         |  (x + a)  dx
                         |
                        /
                        a
\begin{maplettyout}
We can even include a plot.
\mapleplot{worksht.ps1}
\maplesepline
\end{document}
%% End of Maple V Session Output
\end{verbatim}

Maple's text regions from the original worksheet become ordinary
\LaTeX{} paragraphs.  Except for embedded graphics, the other regions
(Maple input, Maple typeset mathematics output, 
and Maple character based mathematics output)
are formatted using an appropriate \LaTeX{} environment.

A default style is provided that tells \LaTeX how
to format each of these special environments.
Thus, the document can be printed as is.
The document can also be enhanced by editing
in standard \LaTeX constructs.
Experienced \LaTeX users can redefine these
style macros to achieve specific effects and
Most mathematics publishers have their own style macros
that can be modified to work in conjunction with these
macros.

\section{Printing or Viewing a Maple \LaTeX{} Document}
In order to format and print the document {\tt worksht.tex} 
you need a standard version of \LaTeX{} and the two 
\LaTeX{} style files {\tt maplems.sty} and {\tt mapleenv.sty}
that are provided with this document.  Documents which
are modified by hand to include plots also require access to
the \LaTeX{} style file {\tt psfig.sty}.  This macro package
is not commercially distributed, but can be obtained via
ftp from numerous archival sites.

If these style files are not installed in one of the locations
automatically searched by your installation of \LaTeX{} then they 
should appear in the same directory or folder as {\tt worksht.tex}.

To print or view this \LaTeX{} document we first 
produce a ``.dvi'' file.  
On a command based system you would normally type a 
command of the form

{\tt \hspace*{10ex} latex worksht.tex}

On an ``icon'' based system you would start the \LaTeX{} application
and then use its menus to ``open'' the file ``worksht.tex''.

Finally, the resulting file ``worksht.dvi'' is then processed by 
another application such as ``dvips'' to send the document 
to the printer or to preview it on your screen.

\section{How Maple's Export to \LaTeX{} Works}

The content of the original Maple worksheet is 
a sequence of regions.  These are either {\em plain text}
regions, {\em Maple input} regions, {\em Maple tty based output}
(such as error messages) or the 
{\em typeset mathematical output}.

In addition, each platform dependent user interface
permits the embedding of native graphics format files in the worksheet.  
These graphics may be generated by Maple, or by another application.

When a Maple worksheet is ``exported to \LaTeX{}'', the
text based regions, and the typeset mathematics are exported.
All the embedded graphics regions of the worksheet are ignored. 
PostScript graphics can be included directly into your document 
by hand editing the resulting file to include references to plot files
using the \LaTeX{} macro \verb|\mapleplot{}| that is provided
with these styles.

To create a \LaTeX{} version of your Maple worksheet proceed
as follows:

\begin{enumerate}
\item
Open the worksheet from within Maple and ensure that all
the Maple results are up-to-date.  If your worksheet is designed
to execute the Maple commands in sequence top to bottom
you can refresh your worksheet by selecting the {\em Execute
All} option.  (On the Macintosh version of Maple, simply select
the entire worksheet and press enter.)

\item
If your worksheet contains plot commands then re-executing 
the entire worksheet will regenerate those plots in 
separate windows.  You can use the {\tt plotsetup}
command to cause those plot commands to generate plots
to specific files.  Alternatively, in Windows 
or with the Motif interface, they can be saved from
the plot windows in PostScript to files of your choice.

\item
To add these plots to your \LaTeX{} document,
use a plain text editor to insert appropriate 
commands of the form

\begin{verbatim}
\mapleplot{filename.ps}
\end{verbatim}

where {\tt filename.ps} is the user chosen name of the
plot file.  Typically, such commands are added immediately
following the corresponding plot commands.

\item
Use a plain text editor to elaborate on the annotations
that are part of your document.  For example, a new section
heading ``An Example'' can be added directly to the worksheet simply
by inserting a \LaTeX{} command line of the form

\begin{verbatim}
\section{An Example}
\end{verbatim}

directly into the exported document.

\item
Process your \LaTeX{} document with \LaTeX{}.

\end{enumerate}

\section{\LaTeX{} Styles}
The style of your document can be changed simply by choosing
a different \LaTeX{} style.  There are many different available
styles, and most mathematics publishers can 
provide you with their own styles.

For example, to define an alternative document ``style'' 
you simply replace the existing style definition.

\begin{verbatim}
\documentstyle[maplems]{article}
\end{verbatim}

\noindent
by (for example)

\begin{verbatim}
\documentstyle[fullpage,mapleenv]{article}
\end{verbatim}

Here, the standard \LaTeX{} ``article'' style has been modified
by the contents of the two style files  {\tt fullpage.sty} and
{\tt mapleenv.sty}.  The style ``mapleenv'' is still 
necessary to provide the basic definitions for the 
special Maple environments.  However, it does not affect the
basic page layout.

\subsection{The Maple Style file {\tt maplems.sty}}

The ``Export to \LaTeX'' file is created with the ``article'' style
further modified by the style ``maplems''.  The effect of
using ``maplems'' is to define some special
commands needed by Maple, and to set the default
page layout settings.
They are defined by the contents of the file
\verb|maplems.sty|.  A copy of this file is found in
the Maple directory   {\tt maple/etc}, (or the equivalent
location on DOS and Macintosh platforms.)

This file has several sections, each setting a different group
of style parameters.  By changing these settings you can
change aspects of the overall style.  
These can be changed by editing a copy of
this file, or they can be reset directly in the ``preamble'' of your
document (i.e., the part between the line 
beginning {\tt \backslash documentstyle...}
and the line {\tt \backslash begin\{document\}})
by adding commands such as

\begin{verbatim}
\setlength{\LeftMapleSkip}{0in}
\end{verbatim}

\noindent
(This particular command would cause the indentation of Maple 
commands to be set to 0 inches.)

Portions of these style files are shown below.
The lines beginning with \% are comments to \TeX and \LaTeX.

\subsubsection{The Page Headings}
The page headings are set by the following commands.
Some possible alternative styles are listed as comments.

\begin{verbatim}
% \pagestyle{noheadings}
% \pagestyle{plain}
\pagestyle{myheadings}
\markright{\protect\rule[-5pt]{\linewidth}{1pt}\hspace{-\linewidth}%
{\protect\large Maple V\ \  Release 3}}%
\end{verbatim}

\noindent
For example, to change to the ``plain'' page style add the line
{\tt \backslash pagestyle\{plain\}} to the preamble of 
your document.

\subsubsection{Page Dimensions and spacing}
Next, some of the main page dimensions are reset.

\begin{verbatim}
% main document settings  
%
\topmargin=     -0.2in
\textheight=    8.75in
\textwidth=     6.0in
\headheight=    2.5ex
\headsep=       0.17in
\oddsidemargin= 0.25in
\evensidemargin=\oddsidemargin
\parsep=        2ex		  % space between item paragraphs
\parskip=       1.5ex  		  % space between paragraphs
\end{verbatim}

\noindent
To change these, again use {\tt \backslash setlength} in the
preamble of your document.

\subsubsection{Spacing and Sizes for the Maple Environments}
Finally the \LaTeX{} macros defining the special Maple environments
are read in and their user settable parameters are set to
default values.

\begin{verbatim}
% parameters controlling the special maple environments
%
\input mapleenv.sty
\MaplePrompttrue      % generate a prompt at start of each line?
\MaplePromptString =  {\raise 1pt \hbox{$\scriptstyle>$\space}}
\AboveMapleSkip =     1ex plus 2 pt minus 1 pt
\BelowMapleSkip =     \AboveMapleSkip
\LeftMapleSkip  =     5ex
\AboveMaplePlot =     2\AboveMapleSkip
\BelowMaplePlot =     2\AboveMapleSkip
\MaplePlotHeight =    25ex
\MaplePlotWidth =     1.3\MaplePlotHeight
\edef\MaplePlotAngle{270}
\let\MapleSepLineWidth\linewidth  % \let so that it will be redefined 
				  % properly for narrow environments.
\MapleSepLineHeight = 1pt
\let\MapleFont\tt     % font used for input and ttyout
\let\MapleSize\small  % font size for input and ttyout
\MapleFirstLinefalse  % hides first \cr of \mapleinput
\MapleTab = 8	      % spaces used by the tab character.
\end{verbatim}

\subsection{The Maple Style file {\tt mapleenv.sty}}
Use the style ``mapleenv'' in conjunction with
your chosen style when all that you need is the definitions
of the special regions. In this way, the special Maple environments
are defined, but the basic page style and layout remains
unmodified.

{ \parsep=.5ex
The special Maple environments and macros that are defined are:

\begin{verbatim}
\begin{mapleinput} ... \end{mapleinput}
\end{verbatim}

\begin{verbatim}
\begin{maplettyout} ... \end{maplettyout}
\end{verbatim}

\begin{verbatim}
\begin{maplelatex} ... \end{maplelatex}
\end{verbatim}

\begin{verbatim}
\maplesepline
\end{verbatim}

\noindent
and
\begin{verbatim}
\mapleplot{plotfile.ps}
\end{verbatim}
}

The definitions for these \LaTeX{} environments are parameterized.
By changing the parameters (in the same manner as done 
done in the file {\tt maplems.sty})
you can affect details such as the amount of space above or below
the environments, 
the amount of indentation used, 
the character used to identify prompts., etc.  
This can be done in the preamble of your document.

The two text based environments are special versions of 
\LaTeX{} ``verbatim'' environments while the {\tt maplelatex}
environment is used to permit control of page breaking 
and the spacing above and below the environment.

The {\tt \backslash maplesepline} command is used to create separator lines
such as found in the actual Maple worksheets. It has no arguments.

The {\tt \backslash mapleplot} macro is provided as an example of
how to include graphs.  It has one argument --- the name of the
file containing the PostScript description of the plot.

\section{Summary}
These style files are provided simply as samples of how to define
such \LaTeX{} environments.  You may use them or 
modify them, subject to the conditions outlined in each 
file.  Non-profit redistribution is also permitted.

\end{document}

### 2009-02-19 filters/mathml/ltex2mml.cpp
removed more assertions

@@ -5777,8 +5777,9 @@ TNODE* LaTeX2MMLTree::BindByOpPrecedence( TNODE* MML_list,
                 if ( MML_rover->next )
                   TCI_ASSERT(0);
 	    	  }
-            } else
-              TCI_ASSERT(0);
+			} else {
+              //TCI_ASSERT(0);
+			}
 
 		  } else if ( form==2 ) {		// infix
 
@@ -14070,7 +14071,7 @@ void LaTeX2MMLTree::GetAttribsFromGammarInfo( U8* zinfo,
 		    U16 ln  =  eptr - sptr;
 		    if ( ln > 0 ) {
 		      op_record.precedence  =  atoi( sptr );
-	        TCI_ASSERT( op_record.precedence );
+	        //TCI_ASSERT( op_record.precedence );
 		    }
 	    } else if ( state==3 ) {		// U0dddd,
 	  // currently not used
@@ -15485,7 +15486,7 @@ TCI_BOOL LaTeX2MMLTree::BucketContainsMath( TNODE* contents ) {
   if ( n_math_objects == 0
   &&   n_text_runs    == 0
   &&   n_tabulars     == 0 ) {	// Run contains no math!!
-	  TCI_ASSERT(0);
+	  //TCI_ASSERT(0);
 	  rv  =  FALSE;
   }
 
@@ -18045,8 +18046,9 @@ void LaTeX2MMLTree::UnicodesToSymbols( TNODE* LaTeX_list ) {
             DisposeTList( parts );
           } else
             TCI_ASSERT(0);
-        } else
-          TCI_ASSERT(0);
+		} else{
+          //TCI_ASSERT(0);
+		}
       } else    // if ( unicode )
         TCI_ASSERT(0);
 
@@ -18138,7 +18140,7 @@ TNODE* LaTeX2MMLTree::FixImpliedMRow( TNODE* mml_node ) {
           rv  =  mml_node->parts->contents;
           mml_node->parts->contents =  NULL;
         } else {
-          TCI_ASSERT(0);
+          //TCI_ASSERT(0);
           rv  =  NULL;
         }
         DisposeTList( mml_node );

### 2011-01-22 editor/libeditor/html/nsHTMLEditRules.cpp
Got successive returns to do almost the right thing is lists. I think whatever is left is a matter of fine-tuning the latexdefs file.

@@ -2272,7 +2272,7 @@ nsHTMLEditRules::WillDeleteSelection(nsISelection *aSelection,
         res = JoinBlocks(address_of(leftParent), address_of(rightParent), aCancel);
         *aHandled = PR_TRUE;
       }
-      aSelection->Collapse(selPointNode, selPointOffset);
+//      aSelection->Collapse(selPointNode, selPointOffset);
       return res;
     }
     else if (wsType==nsWSRunObject::eThisBlock)

### 2011-01-22 editor/libeditor/html/nsHTMLDataTransfer.cpp
Got successive returns to do almost the right thing is lists. I think whatever is left is a matter of fine-tuning the latexdefs file.

@@ -904,6 +904,7 @@ nsresult
 nsHTMLEditor::InsertReturnAt( nsIDOMNode * splitpointNode, PRInt32 splitpointOffset, PRBool fFancy)
 {
   nsresult res = NS_OK;
+  nsCOMPtr<nsISelection>selection;
   nsCOMPtr<nsIDOMNode> splitNode;
   nsCOMPtr<nsIDOMNode> outLeftNode;
   nsCOMPtr<nsIDOMNode> outRightNode;
@@ -1034,7 +1035,6 @@ nsHTMLEditor::InsertReturnAt( nsIDOMNode * splitpointNode, PRInt32 splitpointOff
       nsCOMPtr<nsIDOMNodeList> nodeList;
       nsCOMPtr<nsIDOMNode> node;
       PRUint32 nodeCount;
-      nsCOMPtr<nsISelection>selection;
       res = GetSelection(getter_AddRefs(selection));
       /// The following should be a procedure
       res = newElement->GetElementsByTagName(NS_LITERAL_STRING("cursor"), getter_AddRefs(nodeList));
@@ -1065,12 +1065,19 @@ nsHTMLEditor::InsertReturnAt( nsIDOMNode * splitpointNode, PRInt32 splitpointOff
       {
         nsAutoString tagClass;
         mtagListManager->GetClassOfTag(strTagName, nsAtom, tagClass);
-  		  fCanContain = (tagClass.EqualsLiteral("structtag")||tagClass.EqualsLiteral("envtag")||tagClass.EqualsLiteral("listtag"));
+  		  fCanContain = (tagClass.EqualsLiteral("structtag")||
+  		    tagClass.EqualsLiteral("listparenttag")||
+  		    tagClass.EqualsLiteral("envtag")||
+  		    tagClass.EqualsLiteral("listtag"));
       }
 	    if (fCanContain)
 	    {
+//        nsCOMPtr<nsIDOMNode> parent;
+//        PRInt32 offset;
+//        res = nsEditor::GetNodeLocation(splitNode, address_of(parent), &offset);
+        res = GetTagString(splitNode, strTagName);
 		    nsEditor::DeleteNode(splitNode);
-            res = mtagListManager->GetStringPropertyForTag(strTagName, atomNS, NS_LITERAL_STRING("inclusion"), s2);
+        res = mtagListManager->GetStringPropertyForTag(strTagName, atomNS, NS_LITERAL_STRING("inclusion"), s2);
[…]

### 2011-03-06 editor/libeditor/html/nsHTMLEditor.cpp
Big hand-merge to recover from train-wreck merge.

@@ -180,7 +180,7 @@ nsHTMLEditor::nsHTMLEditor()
   manager = new msiTagListManager;
   manager->SetEditor(this);
   mtagListManager = do_QueryInterface(manager);
-  nsresult result = CallGetService("@mackichan.com/keymap/keymap_service;1", NS_GET_IID(msiIKeyMap),
+  nsresult result = CallGetService("@mackichan.com/keymap;1", NS_GET_IID(msiIKeyMap),
                             (void**)&mKeyMap);
 } 
 

### 2011-03-06 prince/base/content/dialogs/cleanup.js

@@ -1,0 +1,25 @@
+var cleanupOptions = [];
+
+function startup()
+{
+  cleanupOptions= window.arguments[0].cleanupOptions;  
+  
+}
+
+function onAccept()
+{
+  var checkboxes = document.getElementsByTagName("checkbox");
+  cleanupOptions = [];
+  var i;
+  for (i = 0; i< checkboxes.length; i++)
+  {
+    if (checkboxes[i].checked) cleanupOptions.push(checkboxes[i].id);
+  }
+  window.arguments[0].cleanupOptions = cleanupOptions;
+  return true;
+}
+
+function onCancel()
+{
+  return true;
+}

### 2011-03-06 prince/base/content/dialogs/paragraphProperties.js

@@ -1,0 +1,276 @@
+
+var paragraphData = new Object();
+
+
+function initialize()
+{
+  paragraphData.node = window.arguments[0];
+  if (!paragraphData.node)
+    return;
+  assignDialogData(paragraphData.node);
+}
+
+
+function unitIndexFromVal(val)
+{
+  switch (val) {
+    case "pt": return 0;
+    case "cm": return 1;
+    case "mm": return 2;
+    case "in": return 3;
+    default: return -1;
+  }
+}
+  
+function alignmentIndexFromVal(val)
+{
+  switch (val) {
+    case "left": return 0;
+    case "right": return 1;
+    case "center": return 2;
+    case "normal": return 3;
+    default: return -1;
+  }
+}
+
+
+function assignDialogData(node)
+{
+  var val;
+  if (val = node.getAttribute("unit"))
+    document.getElementById("otfont.units").selectedIndex = unitIndexFromVal(val);
+  if (val = node.getAttribute("before"))
+    document.getElementById("beforetext").value = val;
+  if (val = node.getAttribute("after"))
+    document.getElementById("aftertext").value = val;
+  if (val = node.getAttribute("first"))
+    document.getElementById("firstline").value = val;
+  if (val = node.getAttribute("above"))
+    document.getElementById("aboveparagraph").value = val;
+  if (val = node.getAttribute("below"))
+    document.getElementById("belowparagraph").value = val;
+  if (val = node.getAttribute("spacing"))
+    document.getElementById("linespacing").value = val;
+  if (val = node.getAttribute("leading"))
+    document.getElementById("leadingval").value = val;
+  if (val = node.getAttribute("alignment"))
+    document.getElementById("alignment").selectIndex = alignmentIndexFromVal(val);
+  if (val = node.getAttribute("bwidth"))
+    document.getElementById("borderwidth").value = val;
+  if (val = node.getAttribute("sidep"))
+    document.getElementById("bordersidepad").value = val;
+  if (val = node.getAttribute("tpad"))
+    document.getElementById("bordertoppad").value = val;
+  if (val = node.getAttribute("bcolor"))
+    setColorWell("bordercolorWell",val);
+  if (val = node.getAttribute("bgcolor"))
+    setColorWell("backgroundcolorWell",val);
+  if (val = node.getAttribute("tcolor"))
+    setColorWell("textcolorWell",val);
+}
+
[…]

### 2011-03-06 prince/base/content/dialogs/passes.js

@@ -8,13 +8,16 @@ var timer = Components.classes["@mozilla.org/timer;1"]
                     .createInstance(Components.interfaces.nsITimer);
 
 var timerCallback = 
-{ notify: function(timer)
+{  
+  timercopy: timer,
+  notify: function(timer)
    { 
-//     Components.utils.reportError("exitValue = "+theProcess.exitValue+"\n");
-//     if (theProcess && theProcess.exitValue < 0) return;
-     // if we get here, the process is termination
-     // if (exitValue > 0) there was an error
-     //Components.utils.reportError("Exception: "+e.message);
+     if (timer) timercopy = timer;
+     if (!sentinel)
+     {
+        if (timercopy) timercopy.cancel();
+        return;
+     } 
      if (sentinel.exists())
      {
        if (++passData.passCounter < passData.passCount)
@@ -37,11 +40,13 @@ var timerCallback =
          }
        }
        else{
+         timer.cancel();
+         timer = null;
+         SaveWindowLocation();
          setProgressStatement(true);
-         //document.getElementById("passesDlg").cancelDialog();
-         if (timer) timer.cancel();
-         timer=null;
-         close();
+         document.getElementById("oktocontinue").hidden = false;
+         top.document.commandDispatcher.focusedWindow.focus();  
+         window.close();
        }
      }
    } 
@@ -86,7 +91,7 @@ function setProgressStatement(done)
   {
     progressStatement = document.getElementById("doneMessage").value;
     document.documentElement.setAttribute("buttonlabelcancel", document.documentElement.getAttribute("buttonlabelclose"));
-//    progressStatement="Done!";
+    progressStatement="Done!";
   }
   else
   {
@@ -104,10 +109,22 @@ function onCancel()
   timer=null;
   if (sentinel.exists()) sentinel.remove(false);
   theProcess = null;
-  Components.utils.reportError("in OnCancel\n");
+  Components.utils.reportError("in onCancel\n");
   SaveWindowLocation();
-  focus();
-//  window.close();
+  top.document.commandDispatcher.focusedWindow.focus();  
+  window.close();
+  return true;
+}
+
+
+function onAccept()
+{
+  if (timer) timer.cancel();
+  timer=null;
+  if (sentinel.exists()) sentinel.remove(false);
+  theProcess = null;a
+  Components.utils.reportError("in onAccept\n");
+  SaveWindowLocation();
   return true;
 }
 

### 2011-03-06 prince/base/content/dialogs/preferences.js

@@ -1,3 +1,31 @@
+
+
+function setIndex(item,idx) {
+  document.getElementById(item).selectedIndex = idx;
+}
+
+function setChecked(item,val) {
+  document.getElementById(item).setAttribute("checked", val == 1 ? "true" : "false");
+}
+
+function setValue(item,val) {
+  document.getElementById(item).value = val;
+}
+
+function getIndex(item) {
+  return document.getElementById(item).selectedIndex;
+}
+
+function getChecked(item) {
+  return document.getElementById(item).getAttribute("checked") == "true" ? 1 : 0;
+}
+
+function getValue(item) {
+  return document.getElementById(item).value;
+}
+
+
+
 function initialize()
 {
   var url;
@@ -49,28 +77,23 @@ function showShellsInDir(tree)
 
 
 
+
+
+
 var data;
-
-function setIndex(item,idx) {
-  document.getElementById(item).selectedIndex = idx;
-}
-
-function setChecked(item,val) {
-  document.getElementById(item).setAttribute("checked", val == 1 ? "true" : "false");
-}
-
-function setValue(item,val) {
-  document.getElementById(item).value = val;
-}
 
 function ComputeUserSettingsStartup(){
   data = window.arguments[0];
 
-  setValue("digits", data.digits.toString());
+  setValue("digitsUsed", data.digitsUsed.toString());
+  setValue("digitsRendered", data.digitsRendered.toString());
+  setValue("degree", data.degree.toString());
   setValue("lower", data.lower.toString());
   setValue("upper", data.upper.toString());
   setValue("primesasn", data.primesasn.toString());
-
+  
+  setChecked("principal", data.principal);
+  setChecked("special", data.special);
   setChecked("mixednum", data.mixednum);
   setChecked("trigargs", data.trigargs);
   setChecked("usearc", 1 - data.usearc);
@@ -88,19 +111,57 @@ function ComputeUserSettingsStartup(){
   setIndex("imagi", data.imaginaryi);
   setIndex("diffD", data.diffD);
   setIndex("diffd", data.diffd);
-  setIndex("expe", data.expe);
+  setIndex("expe", data.expe ? 1 : 0);
+
+  data.logSent     = msiComputeLogger.logMMLSent;
+  data.logReceived = msiComputeLogger.logMMLReceived;
+  data.engSent     = msiComputeLogger.logEngSent;
[…]

### 2011-03-06 prince/base/content/mathmlOverlay.js

@@ -2311,7 +2311,10 @@ function insertMathnameObject(mathNameObj, editorElement)
 function doInsertMathName(aName, editorElement)
 {
   var editor = msiGetEditor(editorElement);
-  editor.InsertMathname(aName);
+  var mathmlEditor = editor.QueryInterface(Components.interfaces.msiIMathMLEditor);
+  if (mathmlEditor){
+    mathmlEditor.InsertMathname(aName);
+  }
 }
 //  var mathNameObj = msiBaseMathNameList.getMathNameData(aName);
 //  if (mathNameObj == null)

### 2011-03-06 toolkit/components/Compute/Engines/Tree2StdMML.cpp

@@ -570,9 +570,10 @@ MNODE* Tree2StdMML::BindByOpPrecedence(MNODE* dMML_list, int high, int low)
               }
               break;
 
-            case OP_infix:
+            case OP_infix: {
+              MNODE * end = 0;
               if (rover->prev && rover->next) {
-                MNODE * end = rover->next;
+                end = rover->next;
                 // scan forward until we hit one of different precedence
                 MNODE * inner = end;
                 while (inner) {
@@ -592,14 +593,20 @@ MNODE* Tree2StdMML::BindByOpPrecedence(MNODE* dMML_list, int high, int low)
                   }
                 }
                 the_next = end;
-                MNODE* new_row = MakeMROW(rover->prev, end);
-                if (new_row != rover->prev) {
-                  the_next = new_row;
-                  if (rover->prev == rv)
-                    rv = the_next;
-                }
+              } else if (rover->prev){
+                end = rover;
+              } else {
+                  break;
               }
-              break;
+
+              MNODE* new_row = MakeMROW(rover->prev, end);
+              if (new_row != rover->prev) {
+                 the_next = new_row;
+                 if (rover->prev == rv)
+                   rv = the_next;
+              }
+            }
+            break;
 
 
             case OP_postfix:
@@ -1622,11 +1629,22 @@ bool Tree2StdMML::NodeIsFunction(MNODE* mml_node)
   // might be f^-1 or something, in which case the whole expr is the function
   if (HasScriptChildren(mml_node))
     return NodeIsFunction(mml_node->first_kid);
-  else if (ElementNameIs(mml_node, "mi"))
+  else if (ElementNameIs(mml_node, "mi")) {
     if (IsTrigArgFuncName(mml_entities,mml_node->p_chdata) ||
         IsReservedFuncName(mml_entities,mml_node->p_chdata) ||
         my_analyzer_data->IsDefinedFunction(mml_node))
       return true;
+  } else if (ElementNameIs(mml_node, "mo") && mml_node->attrib_list) {
+    const char* isMathname = GetATTRIBvalue(mml_node ->attrib_list, "msimathname");
[…]

### 2011-03-06 toolkit/components/Compute/Engines/Tree2StdMML.h

@@ -74,6 +74,7 @@ protected:
   void RemoveMSTYLEs(MNODE* MML_list);
   void RemoveMSTYLEnode(MNODE* mstyle);
   void RemoveHSPACEs(MNODE* MML_list);
+  void RemoveIT_and_AF(MNODE* MML_list);
 
 
   char *ChdataToString(const char *p_chdata);

### 2011-03-06 toolkit/components/keymap/src/msiKeyMap.h

@@ -47,11 +47,12 @@ public:
 static  msiKeyMap* GetInstance();
 static  void       ReleaseInstance();
 static msiKeyMap   *sInstance;
+keyNameAndCode virtKeyArray[80];
   
 PRUint32 VKeyStringToIndex( const nsString keyname);
 nsString VKeyIndexToString ( PRUint32 index );
 void keyArrayToString( nsTArray<PRUint32>& ka, nsString& sFile, nsClassHashtable<nsUint32HashKey, nsString>& table);
-keyNameAndCode virtKeyArray[80];
+
 
 private:
   ~msiKeyMap();

### 2011-03-06 layout/mathml/base/src/nsMathCursorUtils.cpp
Big hand-merge to recover from train-wreck merge.

@@ -6,11 +6,30 @@
 #include "nsMathMLCursorMover.h"
 
 PRBool IsMathFrame( nsIFrame * aFrame );
+PRBool IsDisplayFrame( nsIFrame * aFrame, PRInt32& count )
+{  
+  PRBool retval;
+  nsCOMPtr<nsIDOMElement> element = do_QueryInterface(aFrame->GetContent());
+  if (element)
+  {
+    nsAutoString stringTag;
+    element->GetLocalName(stringTag);
+    retval = (stringTag.EqualsLiteral("msidisplay"));
+    if (retval)
+    {
+  		aFrame = aFrame->GetParent();
+  		count = 0;
+      return PR_TRUE;
+    }
+  }
+  return PR_FALSE;
+}
 
 PRBool PlaceCursorAfter( nsIFrame * pFrame, PRBool fInside, nsIFrame** aOutFrame, PRInt32* aOutOffset, PRInt32& count)
 {
   nsIFrame * pChild;
   nsIFrame * pParent;
+  PRBool df = PR_FALSE;
   nsCOMPtr<nsIContent> pContent;
   pParent = pFrame->GetParent();
 
@@ -31,6 +50,12 @@ PRBool PlaceCursorAfter( nsIFrame * pFrame, PRBool fInside, nsIFrame** aOutFrame
       pContent = pParent->GetContent();
       *aOutOffset = 1+pContent->IndexOf(pFrame->GetContent());
       *aOutFrame = pParent;
+    }
+    else if (IsDisplayFrame(pParent, count))
+    {
+      *aOutFrame = GetFirstTextFramePastFrame(pParent);
+      *aOutOffset = count;
+      
     }
     else
     {
@@ -126,7 +151,7 @@ nsIFrame * GetFirstTextFramePastFrame( nsIFrame * pFrame )
     }
     if (pTemp) pTemp = pTemp->GetNextSibling();
     if (pTemp) pTextFrame = GetFirstTextFrame(pTemp);
-    else return nsnull;
+    else return nsnull;  // TODO: BBM can't return null without caller checking. Check this out.
   }
   return pTextFrame;
 }

### 2011-03-06 prince/base/content/computeOverlay.js

@@ -10,7 +10,8 @@ var msiEvaluateCommand =
             msiIsEditingRenderedHTML(theEditorElement) &&
             (isInMath(editorElement) || 
              aCommand == "cmd_MSIComputeFillMatrix" ||
-             aCommand == "cmd_MSIComputeRandomMatrix") );
+             aCommand == "cmd_MSIComputeRandomMatrix"||
+             aCommand == "cmd_MSIComputeRandomNumbers" ) );
   },
 
   getCommandStateParams: function(aCommand, aParams, editorElement) {},
@@ -32,9 +33,9 @@ var msiDefineCommand =
             msiIsEditingRenderedHTML(editorElement) &&
             ( isInMath(editorElement) || 
               aCommand == "cmd_MSIComputeShowDefs" ||
-              aCommand == "cmd_MSIComputeUserSettings" ||
+              //aCommand == "cmd_MSI/ComputeUserSettings" ||
               aCommand == "cmd_MSIComputeClearDefs" ||
-              aCommand == "cmd_MSIComputeSettings" ||
+              //aCommand == "cmd_MSIComputeSettings" ||
               aCommand == "cmd_MSIComputeSwitchEngines"  ) );
               
   },
@@ -56,6 +57,7 @@ function jsdump(str)
             .logEngineStringMessage(str);
 }
 /////////////////////////
+
 var msiComputeLogger = 
 {
   Sent: function(name,expr)
@@ -95,25 +97,25 @@ var msiComputeLogger =
   Init: function()
   {
     try {
-      this.logMMLSent = gPrefs.getBoolPref("swp.MuPAD.log_mathml_sent");
+      this.logMMLSent = GetPrefs().getBoolPref("swp.MuPAD.log_mathml_sent");
     }
     catch(ex) {
       jsdump("\nfailed to get MuPAD.log_mathml_sent pref!\n");
     }
     try {
-      this.logMMLReceived = gPrefs.getBoolPref("swp.MuPAD.log_mathml_received");
+      this.logMMLReceived = GetPrefs().getBoolPref("swp.MuPAD.log_mathml_received");
     }
     catch(ex) {
       jsdump("\nfailed to get MuPAD.log_mathml_received pref!\n");
     }
     try {
-      this.engMMLSent = gPrefs.getBoolPref("swp.MuPAD.log_engine_sent");
+      this.engMMLSent = GetPrefs().getBoolPref("swp.MuPAD.log_engine_sent");
     }
     catch(ex) {
[…]

### 2011-03-06 prince/base/content/dialogs/ComputeRandomNumbers.js

@@ -33,64 +33,98 @@ function Cancel(){
   data.Cancel = true;
 }
 
+function SetValue(p, str)
+// sets the value of p2 and hides or shows it depending on whether the value
+// is blank or not
+{
+  if (str.length > 0) p.parentNode.setAttribute("style", "visibility: visible;")
+  else p.parentNode.setAttribute("style", "visibility: hidden;");
+  p.value = str;
+  return str;
+}
+
+
+
 // sadly, this is all wrong because the strings can't be localized
 function doSelect(){
   var dist = document.getElementById("dist");
-  var p1   = document.getElementById("param1.text");
-  var p2   = document.getElementById("param2.text");
+  var p1   = document.getElementById("label1");
+  var p2   = document.getElementById("label2");
 
   switch (dist.selectedIndex) {
   case 0:  // Beta
-    p1.value = "Order";
-    p2.value = "Order";
+    p1.value = SetValue(p2,GetComputeString("Order"));
     break;
   case 1:  // Binomial
-    p1.value = "Number of Trials";
-    p2.value = "Probability of Success";
+    p1.value = GetComputeString("NumTrials");
+    SetValue(p2,GetComputeString("ProbSuccess"));
     break;
   case 2:  // Cauchy
-    p1.value = "Median";
-    p2.value = "Shape Parameter";
+    p1.value = GetComputeString("Median");
+    SetValue(p2,GetComputeString("Shape"));
     break;
   case 3:  // Chi-Square
-    p1.value = "Degrees of Freedom";
-    p2.value = "";
+    p1.value = GetComputeString("DegFreedom");
+    SetValue(p2,"");
     break;
   case 4:  // Exponential
-    p1.value = "Mean Time Between Arrivals";
-    p2.value = "";
+    p1.value = GetComputeString("MTBA");
+    SetValue(p2,"");
     break;
   case 5:  // F
-    p1.value = "Degrees of Freedom";
-    p2.value = "Degrees of Freedom";
+    p1.value = SetValue(p2,GetComputeString("DegFreedom"));
     break;
   case 6:  // Gamma
-    p1.value = "Shape Parameter";
-    p2.value = "Scale Parameter";
+    p1.value = GetComputeString("Shape");
+    SetValue(p2,GetComputeString("Scale"));
     break;
   case 7:  // Normal
-    p1.value = "Mean";
-    p2.value = "Standard Deviation";
+    p1.value = GetComputeString("Mean");
[…]

### 2011-03-06 prince/base/content/dialogs/autoSubstituteDialog.js

@@ -403,6 +403,11 @@ function getDataFromControl(whichType)
   return theValue;
 }
 
+function dataNonEmpty(whichtype)
+{
+  return getDataFromControl(whichtype).length > 0
+}
+
 function changeType(theType)
 {
   var currName = document.getElementById("keystrokesBox").value;
@@ -828,8 +833,11 @@ function dumpln(s)
   dump(s+"\n");
 }
 
-function onOK() {
+function onOK() 
+{
   dumpln("a");
+  var theType = document.getElementById("autosubTypeRadioGroup").value;
+  gDialog.bDataNonEmpty = dataNonEmpty(theType);
   var bActionEnabled = gDialog.bDataNonEmpty && gDialog.bNameOK;
   if (!gDialog.bIsNew)
     bActionEnabled = gDialog.bDataNonEmpty && gDialog.bNameOK && gDialog.bCurrentItemModified;

### 2011-03-06 prince/base/content/dialogs/typesetdocformat.js

@@ -94,7 +94,7 @@ function Startup()
   var node;
   if (!(docFormatNodeList && docFormatNodeList.length>=1)) node=null;
   else node = docFormatNodeList[0].getElementsByTagName('pagelayout')[0];
-  getPageLayout(node);
+  getPageLayout(node, doc);
   if (!(docFormatNodeList && docFormatNodeList.length>=1)) node=null;
   else node = docFormatNodeList[0].getElementsByTagName('crop')[0];
   getCropInfo(node);
@@ -320,7 +320,7 @@ function getNumberValue(numberwithunit)
 }
 
 
-function getPageLayout(node)
+function getPageLayout(node, document)
 {
   //node is the pageformat node, or null
   var subnode;
@@ -2480,8 +2480,10 @@ function saveClassOptionsEtc(docformatnode)
   // convention: default values are starred at the end.
   var widget;
   widget = document.getElementById("pgorient").selectedItem;
-  if (widget.hasAttribute("def")) optionNode.removeAttribute("pgorient")
-  else optionNode.setAttribute("pgorient", widget.value);
+  if (widget.hasAttribute("def")) 
+    optionNode.removeAttribute("pgorient")
+  else 
+    optionNode.setAttribute("pgorient", widget.value);
   
   widget = document.getElementById("papersize").selectedItem;
   if (widget.hasAttribute("def")) optionNode.removeAttribute("papersize")

### 2011-03-06 prince/base/content/msiEditorApplicationOverlay.js

@@ -51,6 +51,89 @@ function msiEditPageOrFrame()
   msiEditPage(url, window, false)
 }
 
+
+function msiPrefs()
+{
+  dump("\n ** msiPrefs\n");
+
+  var compsample = GetCurrentEngine();
+
+  msiComputeLogger.Sent("user settings","");
+
+  var o = new Object();
+
+  o.mfenced      = compsample.getUserPref(compsample.use_mfenced);
+  o.digitsRendered = compsample.getUserPref(compsample.Sig_digits_rendered);
+  o.lower        = compsample.getUserPref(compsample.SciNote_lower_thresh);
+  o.upper        = compsample.getUserPref(compsample.SciNote_upper_thresh);
+  o.trigargs     = compsample.getUserPref(compsample.Parens_on_trigargs);
+  o.imaginaryi   = compsample.getUserPref(compsample.Output_imaginaryi);
+  o.diffD        = compsample.getUserPref(compsample.Output_diffD_uppercase);
+  o.diffd        = compsample.getUserPref(compsample.Output_diffd_lowercase);
+  o.expe         = compsample.getUserPref(compsample.Output_Euler_e);
+  o.matrix_delim = compsample.getUserPref(compsample.Default_matrix_delims);
+  o.usearc       = compsample.getUserPref(compsample.Output_InvTrigFuncs_1);
+  o.mixednum     = compsample.getUserPref(compsample.Output_Mixed_Numbers);
+  o.derivformat  = compsample.getUserPref(compsample.Default_derivative_format);
+  o.primesasn    = compsample.getUserPref(compsample.Primes_as_n_thresh);
+  o.primederiv   = compsample.getUserPref(compsample.Prime_means_derivative);
+
+  o.loge         = compsample.getUserPref(compsample.log_is_base_e);
+  o.dotderiv     = compsample.getUserPref(compsample.Dot_derivative);
+  o.barconj      = compsample.getUserPref(compsample.Overbar_conjugate);
+  o.i_imaginary  = compsample.getUserPref(compsample.Input_i_Imaginary);
+  o.j_imaginary  = compsample.getUserPref(compsample.Input_j_Imaginary);
+  o.e_exp        = compsample.getUserPref(compsample.Input_e_Euler);
+
+
+  o.digitsUsed  = compsample.getEngineAttr(compsample.Digits);
+  o.degree      = compsample.getEngineAttr(compsample.MaxDegree);
[…]

### 2011-03-06 prince/base/content/prince.js

@@ -7,6 +7,22 @@ const NS_PROCESSINFO_CONTRACTID = "@mozilla.org/xpcom/process-info;1";
 Components.utils.import("resource://app/modules/macroArrays.jsm");
 var currPDFfileLeaf = "main.pdf"; // this is the leafname of the last pdf file generated.
 
+function princeStartUp()
+{
+  // take out parts of the UI not needed on the Mac
+  if ('Mac'==GetOS())
+  {
+    document.getElementById("printPreviewButton").hidden=true;
+    document.getElementById("printPreviewMenuItem").hidden=true;
+  }
+  else
+  {
+    document.getElementById("printPreviewButtonMac").hidden = true;
+    document.getElementById("printPreviewMenuItemMac").hidden=true;
+  }
+  msiEditorOnLoad();
+}
+
 function goAboutDialog() {
   window.openDialog("chrome://prince/content/aboutDialog.xul", "about", "modal,chrome,resizable=yes");
 }
@@ -2002,12 +2018,12 @@ function printTeX(preview )
             }
             else
             {
-              exefile = Components.classes["@mozilla.org/file/local;1"].
-                  createInstance(Components.interfaces.nsILocalFile);
-              exefile.initWithPath("/Applications/SWPPro.app/Contents/Resources/shell.bash");
-              arr = [pdffile.path];
+              extension = "bash";
+              exefile = dsprops.get("resource:app", Components.interfaces.nsILocalFile);
+              exefile.append("shell."+ extension);
               theProcess.init(exefile);
-              theProcess.run(false, arr, arr.length);             
+              arr = [pdffile.path];
+              theProcess.run(false, arr, arr.length);
             }
           }
           else // pdfAction == complete path to viewer

### 2011-03-06 toolkit/components/build/nsToolkitCompsCID.h

@@ -53,10 +53,6 @@
 #define NS_STRINGARRAYAUTOCOMPLETE_CONTRACTID \
   "@mozilla.org/autocomplete/search;1?name=stringarray"
 
-#define MSI_KEYMAP_CONTRACTID \
- "@mackichan.com/keymap/keymap_service;1"
-
-
 #define NS_DOWNLOADMANAGER_CONTRACTID \
   "@mozilla.org/download-manager;1"
 
@@ -93,7 +89,8 @@
 #define NS_URLCLASSIFIERHASHCOMPLETER_CONTRACTID \
     "@mozilla.org/url-classifier/hashcompleter;1"
 
-#define NS_SCRIPTABLEUNESCAPEHTML_CONTRACTID "@mozilla.org/feed-unescapehtml;1"
+#define NS_SCRIPTABLEUNESCAPEHTML_CONTRACTID \
+    "@mozilla.org/feed-unescapehtml;1"
 
 #define NS_NAVHISTORYSERVICE_CONTRACTID \
   "@mozilla.org/browser/nav-history-service;1"
@@ -117,7 +114,9 @@
     "@mozilla.org/autosubstitute;1"
 
 #define MSI_KEYMAP_CONTRACTID \
-    "@mozilla.org/keymap;1"
+    "@mackichan.com/keymap;1"
+
+
 
 
 
@@ -144,11 +143,6 @@
 //{F45EF03A-94FD-466c-97AC-ACCFCBB6AD5E}
 #define NS_STRINGARRAYAUTOCOMPLETE_CID \
 { 0xf45ef03a, 0x94fd, 0x466c, { 0x97, 0xac, 0xac, 0xcf, 0xcb, 0xb6, 0xad, 0x5e} }
-
-
-// {0176db9d-bae7-4b42-82af-6da0269bdd2f}
-#define MSI_KEYMAP_CID \
-{ 0x0176db9d, 0xbae7, 0x4b42, { 0x82, 0xaf, 0x6d, 0xa0, 0x26, 0x9b, 0xdd, 0x2f }}
 
 #define NS_DOWNLOADMANAGER_CID \
     { 0xedb0490e, 0x1dd1, 0x11b2, { 0x83, 0xb8, 0xdb, 0xf8, 0xd8, 0x59, 0x06, 0xa6 } }
@@ -218,6 +212,5 @@
 #define MSI_KEYMAP_CID \
[…]

### 2011-03-06 toolkit/components/build/nsToolkitCompsModule.cpp

@@ -134,7 +134,7 @@ NS_GENERIC_FACTORY_SINGLETON_CONSTRUCTOR(msiAutosub, msiAutosub::GetInstance)
 NS_GENERIC_FACTORY_SINGLETON_CONSTRUCTOR(msiSimpleComputeEngine2, msiSimpleComputeEngine2::GetInstance)
 NS_GENERIC_FACTORY_SINGLETON_CONSTRUCTOR(msiArrowStateService, msiArrowStateService::GetInstance)
 
-NS_GENERIC_FACTORY_CONSTRUCTOR(msiKeyMap)
+NS_GENERIC_FACTORY_SINGLETON_CONSTRUCTOR(msiKeyMap,msiKeyMap::GetInstance)
 /////////////////////////////////////////////////////////////////////////////
 
 static const nsModuleComponentInfo components[] =

### 2011-10-27 prince/TCITeX/TeX/LaTeX/SWmisc/opex/oestyle.tex
Sync with Version 5.5 SourceSafe projects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                   File: OEstyle.tex                 %
%                   VERSION: 1.08                     %
%                   Date: April 3, 1998               %
% LaTeX template file for use with OSA OPTICS EXPRESS %
% THIS FILE IS SHORTER, WITH FEWER DESCRIPTIONS OF    %
% TYPOGRAPHY (BOLD, ITALICS, POINT SIZES, ETC.)       %
%                                                     %
% This file requires a substyle file under the LaTeX  %
% Article style, opex.sty .                           %
%                   FOR LATEX 2E USE                  %
%         \documentclass[10pt]{article}               %
%         \usepackage{opex}                           %
%                                                     %
%                   FOR LATEX 2.09 USE                %
%         \documentstyle[opex]{article}               %
%                                                     %
%                   FOR REVTeX 3.0 or 3.1 USE         %
%         \documentstyle[osa,opex]{revtex}            %
%                                                     %
% Copyright 1997, The Optical Society of America      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%           FOR COLORED WWW LINKS USE                 %
%     \documentclass[10pt]{article}                   %
%     \usepackage{opex}                               %
%     \usepackage{color}%             (LATEX 2E)      %
%                                                     %
%           FOR COLOR WITH LATEX 2.09 BE              %
%           CERTAIN YOU HAVE color.sty AND USE        %
%     \documentstyle[opex,color]{article}             %
%                                                     %
%           FOR COLOR WITH REVTeX 3.0 or 3.1 BE       %
%           CERTAIN YOU HAVE color.sty AND USE        %
%     \documentstyle[osa,opex,color]{revtex}          %
%                                                     %
% Copyright 1997, The Optical Society of America      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentstyle[opex,color]{article}
%\documentstyle[osa,opex,color]{revtex}
\documentclass[10pt]{article}
\usepackage{opex}
%\usepackage{color}% DELETE THIS LINE IF YOU DO NOT HAVE color.sty
\begin{document}

\title{Instructions for the preparation of a LaTeX or 
REVTeX manuscript for Optics Express}

\author{Frank E. Harris}
\address{Optical Society of America, Washington, DC 20036-1023 USA}
\email{fharri@osa.org}

\begin{abstract}%
Explicit and detailed rules are given 
for preparing a compuscript 
(i.e., manuscript in electronic form) for 
Optics Express.  Specific commands 
are given for all major compuscript elements 
(such as abstract, headings, figures, 
tables, and references) to achieve optimal 
typographic quality.  Electronic submission
of a PostScript file, or of a tarred, gzipped archive 
containing a LaTeX file and PostScript or EPS 
figures, is described. 
\end{abstract}
\ocis{(000.0000) General}

% The commands, \begin{OEReferences} and \end{OEReferences}
% format the References section according to OpEx standard
% style, showing the title ``References''.
%
% The commands, \begin{OERefLinks} and \end{OERefLinks}
% format the References section according to OpEx standard
% style, if the references also include URLs or other
% unreviewed links.  In this case the title of the section
% is ``References and links''.
%

\begin{OERefLinks}
\item  P. J. Harshman,  T. K. Gustafson, and P. Kelley,
 ``Strong field theory of low loss optical switching and
  wave mixing in a semiconductor quantum well,''  \opex 
  {\bf 3}, 166-168  (1999).

\item  C. van Trigt, ``Visual system-response
 functions and estimating  reflectance,'' \josaa
 {\bf 14}, 741-755 (1997).

% DELETE THE FOLLOWING REFERENCE IF YOU DO NOT HAVE
% color.sty ON YOUR TeX SYSTEM.

\item  N. Gallagher, ``\underline{Chopper},'' 
OpticsNet, 4/23/97, %{\color{blue}
\underline{http://www.osa.org/video/qtime/chopper.mov}%}.

%\end{OEReferences}
\end{OERefLinks}

% The commands \color{blue} and \underline{} may be used 
% to indicate WWW links in the text.  For those who do not
% have the file color.sty on their systems, \underline{}
% alone may be used. color.sty may be downloaded from the
% CTAN archives at ftp://ftp.dante.de , ftp://ftp.SHSU.edu 
% , or ftp://ftp.cdrom.com .
%
% The set of style files released under the name, "hyperref,"
% also available from the CTAN ftp sites, may
% be used to create WWW links that will carry through to
% the PDF file generated from a .tex file.  This method of
% establishing links may be used to create links to online
% databases, cited articles, or software that cannot be
% served from OSA.  Hyperref is not part of the  
% standard LaTeX 2e package at this time.

\section{ Introduction}
Adherence to the style produced by the file 
opex.sty is essential for efficient 
review and publication of submissions. 
Optics Express takes advantage of 
some of the unique opportunities the electronic 
medium offers to allow authors to include 
3-D scenes and QuickTime sequences 
as illustrations within their papers.  
Instructions for submitting 3-D and video are 
included in Section 3. To take advantage 
of this new medium of publishing, compuscripts 
will be treated as camera-ready copy.  
{\it Authors should print out this style 
guide for use as a checklist for format.}

Note that the Optics Express rules as to style 
and layout are followed. This has been designed to 
be used in conjunction with the Instructions to 
Authors for Optics Express that can be found at 
(http://epubs.osa.org/opticsexpress/submission/).

\section{Software}
\subsection{TeX and LaTeX}
The current version of TeX software is 3.14159.  Virtually
all versions of TeX now available as freeware, shareware,
or commercially, are acceptable.  Opex.sty has been tested
extensively with LaTeX 2e and LaTeX 2.09.  Authors who
place WWW links in references are encouraged to 
underline the link.

Authors who wish to submit LaTeX files are encouraged to
create a tarred, gzipped archive of their LaTeX file and
all figures, in PostScript or EPS format.  Tar and gzip
archiving and compression software is available as 
shareware or freeware for Windows and Mac OS, and is part
of the Unix operating system.  Authors who submit a 
LaTeX file with no figures may submit an ASCII text file
without compression or archiving.

\subsection{Postscript drivers}
Authors who submit a PostScript file to {\it Optics Express} 
should use an appropriate PostScript printer 
driver to generate the compuscript file for submission.  
Almost all versions of dvips will generate 
proper output. The BaKoMa PostScript versions of the 
Computer Modern fonts must be used for submissions
of PostScript files.

\subsection{REVTeX and LaTeX support}
REVTeX and LaTeX commands for title, author, 
address, e-mail, and PACS are supported as aliases
of the OpEx commands listed below.  In limited testing,
REVTeX and LaTeX article style compuscripts have been
found to process with none to two LaTeX errors per
manuscript.  With very little effort a compuscript 
prepared in LaTeX or REVTeX can be converted to OpEx
style.

The OpEx style file, opex.sty, has been tested
under LaTeX 2e (both in native and 2.09 compatability 
mode) and under LaTeX 2.09.  Document styles 
\begin{verbatim}
  \documentclass[10pt]{article}
  \usepackage{opex}
\end{verbatim}
for LaTeX 2e and 
\begin{verbatim}
  \documentstyle[opex]{article}
\end{verbatim}
for LaTeX 2.09 have produced more consistent results in testing, than
\begin{verbatim}
  \documentstyle[osa,opex]{revtex},
\end{verbatim}
the appropriate style option for REVTeX.

Authors who want to place blue text indicating 
WWW links in an article may use the style file 
color.sty, with one of the following: 
\begin{verbatim}
  \documentclass[10pt]{article}% LaTeX 2e
  \usepackage{opex}
  \usepackage{color}
\end{verbatim}
\begin{verbatim}
  \documentstyle[opex,color]{article}% LaTeX 2.09
\end{verbatim}
\begin{verbatim}
  \documentstyle[osa,opex,color]{revtex}% REVTeX.
\end{verbatim}

%\pagebreak

\subsection{Title}
Authors should
place the title within the curly brackets of the 
\verb+\title{}+ command to achieve the correct 
format.

\subsection{Author name}
Author names should appear 
as used for conventional publication, 
with first and middle names or initials followed by 
surname.  Every effort should be made to keep 
author names consistent  from one paper to the next 
as they appear within OSA publications.  Authors should
place their names within the curly brackets of the 
\verb+\author{}+ command to achieve the correct 
format.

\subsection{Author affiliation}
Authors should place their affiliation 
within the curly brackets of the 
\verb+\address{}+ command to achieve the correct 
format. If several 
authors have the same affiliation, one listing of 
the affiliation should be used, preceded by the full 
list of those authors on the line above.

\subsection{E-Mail address}
Enter the e-mail address of the corresponding author 
directly below the corresponding author’s affiliation.  
Authors should place  
e-mail addresses within the curly brackets of the 
\verb+\email{}+ command to achieve the correct 
format.

Multiple use of the \verb+\author{}+, 
\verb+\address{}+, and \verb+\email{}+ commands 
are permitted and produce clear association of authors
with their institutions, as shown below.

\author{A. Gatti and L.A. Lugiato}
\address{Instituto Nazional di Fisica per la Materia, 
Dipartmento Di Fisica, Via  Celoria
 16, 20133 Milano, Italy}

\email{lugiato@mi.infi.it}
\author{S. K. Nash-Stevenson}
\address{NASA-Marshall Space Flight Center, EB22,
Huntsville, Alabama 35726}

\author{G-L. Oppo and R. Martin}
\address{Department of Physics, University, of Strathclyde, 
Rottenrow 107, Glasgow G4 ONG, Scotland}

\email{gianluca@phys.strath.ac.uk}

\subsection{Abstract}
Authors should place their abstract between 
\verb+\begin{abstract}+ and \verb+\end{abstract}+ 
commands to achieve the correct format.  The 
\verb+\begin{abstract}+ command will add the word 
{\bf Abstract:} to the front of the abstract.
The abstract should be limited to approximately 100 words. 
It should be an explicit summary of the paper that states 
the problem, the methods used, and the major results and 
conclusions.   A copyright statement will be added 
automatically, after the abstract.

\subsection{OCIS subject classification}
Optics Classification and Indexing Scheme (OCIS) subject classifications 
should be included after the abstract, on a 
separate line that begins with the words {\bf OCIS codes:} 
in bold.  Authors should
place their OCIS codes within the curly brackets of the 
\verb+\ocis{}+ command to achieve the correct 
format.  The OCIS codes should be placed after the abstract,
\verb+\end{abstract}+ command.  The REVTeX
command \verb+\pacs{}+ may be used in place of \verb+\ocis{}+.

\subsection{Main text}
The first line of the first paragraph of a section or 
subsection should start flush left.  The first line of 
subsequent paragraphs within the section or subsection 
should be indented.

\subsection{Equations}
Equations should be centered.  For long equations, the 
right side of the equation should be broken into 
approximately equal parts and aligned to the right of 
the equal sign.  The equation number should appear only 
at the righthand margin of the last line of the equation.

\begin{equation}
H = \frac{1}{2m}(p_x^2 + p_y^2) + \frac{1}{2} M{\Omega}^2
     (x^2 + y^2) + \omega (xp_y - yp_x)
\end{equation}
All equations should be numbered in the order in which 
they appear and should be referenced  from within the 
main text as Eq. (1), the Hamiltonian, Eq. (2), intensity 
distribution, etc.

%\newpage

\begin{eqnarray}
I_{(x,y,z,t)} & = & \frac{|E_{(x,y,z,t)}|^2}{2} \nonumber \\
     & = & \frac{1}{2}|A(t - \tau_+ z)|^2 \psi_+^2(x,y)
         + \frac{1}{2}|A(t - \tau_- z)|^2 \psi_-^2(x,y) \nonumber \\
     & &  + A(t - \tau_+ z) A(t - \tau_- z)
         \times \cos\left( \pi \frac{z}{L_c}\right) \psi_+(x,y) \psi_-(x,y)
\end{eqnarray}
where

\begin{eqnarray}
I_{(z, \tau)} & = & \frac{1}{2} \left[ \left| 
             A \left(\tau - \frac{\delta \tau}{2}z \right) \right|^2 
           + \frac{1}{2} \left| A \left( \tau + \frac{\delta \tau}{2}z \right) \right|^2 
           + 2A \left( \tau - \frac{\delta \tau}{2}z \right) 
             A \left( \tau + \frac{\delta \tau}{2}z \right) \right. \nonumber \\
     & & \left. \times \cos \left( \pi \frac{z}{L_c} \right) \right] 
             \int _{-\infty}^{+\infty}\int _{-\infty}^{+\infty}
             {\psi_1}^2(x,y){\rm d}x{\rm d}y  \nonumber \\
     & & + \frac{1}{2} \left[ \left| A \left( 
           \tau - \frac{\delta \tau}{2}z \right) \right| ^2 
           + \frac{1}{2} \left| A \left( \tau + \frac{\delta \tau}{2}z \right) \right| ^2 
           - 2A \left( \tau - \frac{\delta \tau}{2}z \right) 
              A \left( \tau + \frac{\delta \tau}{2}z \right) \right. \nonumber \\
     & & \left.  \times \cos \left( \pi \frac{z}{L_c} \right) \right] 
           \int _{-\infty}^{+\infty}\int _{-\infty}^{+\infty}
           {\psi_2}^2(x,y){\rm d}x{\rm d}y  
\end{eqnarray}

In-line math of simple fractions should use parentheses 
when necessary to avoid ambiguity, for example, to 
distinguish between $1/(n-1)$ and $1/n-1$.  Exceptions to 
this are the proper fractions such as $\frac{1}{2}$  
which are better left in this form.  
Summations and integrals that appear 
within text such as  $\frac{1}{2}{\Sigma }  _{n=1}^{n=\infty}
(n^2 - 2n)^{-1}$ 
should have limits placed to the 
right of the symbol to reduce white space.

\subsection{References and links}
References should appear at the top of the article, 
below the abstract, in the order in which they are 
referenced in the body text. 
Authors who use REVTeX may use the standard REVTeX 
commands for references and citations in place of the 
commands listed below. Bibtex may not be used, except as 
described in the OSA bibtex instruction accompanying 
REVTeX 3.1.  The {\bf References}
section must be delimited by horizontal rules above 
and below the section, which may be added manually
if the {\it Optics Express} commands are not used.

 The commands, \verb+\begin{OEReferences}+ 
 and \verb+\end{OEReferences}+ format the {\bf References} 
 section according to OpEx standard style, showing the
 title {\bf References}.  Use the \verb+\item+ command
 to start each reference.  If the references include 
 URLs or other WWW (World Wide Web) links, 
the commands, then \verb+\begin{OERefLinks}+ and 
 \verb+\end{OERefLinks}+ should be used.  If 
 \verb+\begin{OERefLinks}+ is used, the title of 
 the section will be {\bf References and links}.

Optics Express uses numerical notations in brackets 
for bibliographic citations, within square brackets[1] 
or as numerical superscripts.$^2$  When using the 
\verb+\ref{}+ command, labels must be placed in the references:
\begin{verbatim}
   \item\label{paper2}  C. van Trigt, ``Visual system-response 
   functions and estimating 
   reflectance,'' \josaa {\bf 14}, 741-755 (1997).
\end{verbatim}
Then the citation command should be of the form: 
\verb+[\ref{paper2}]+.

Optics Express follows the following citation style: For 
journal articles, authors are listed first, followed by 
the journal’s title abbreviation, the volume number in 
bold, inclusive page numbers and the year in parenthesis.  
This may be followed by a URL if one is available.
The number of a grant or contract should be omitted 
unless its inclusion is required by the agency supporting 
the research.

\vskip1pc

\noindent {\footnotesize
\begin{tabular}{lll}
 \hskip0.2in &2. &C. van Trigt, \josaa {\bf 14},
  741-755 (1997).
\end{tabular}}

\vskip1pc

For monographs in books, authors are listed first, followed 
by article’s full title in quotes, the word “in,” followed 
by the book title in italics, the editors of the book in 
parenthesis, the publisher, city, year.

\vskip1pc

\noindent {\footnotesize
\begin{tabular}{lll} 
 &3. &David F. Edwards, “Silicon (Si)” in 
  {\it Handbook of optical constants of solids}, E.D. Palik, 
   ed.  \\ & &(Academic, Orlando, Fla. 1985) \\
\end{tabular}}

\vskip1pc

For citation of a book as a whole or book chapter, authors or 
editors are listed first, followed by title in italics, and 
publisher, city, and year in parenthesis.  Chapter number may 
be added if applicable.

\vskip1pc

\noindent{\footnotesize 
\begin{tabular}{lll} 
 &4. &F. Ladouceur and J. D. Love,
   {\it Silica-based buried channel waveguides and devices}
    \\ & & (Chapman \& Hall, 1995), Chap.8. \\
\end{tabular}}

\vskip1pc

WWW links may be represented by a line in the references 
section of the compuscript. The URL of the referred item 
should be underlined.  WWW links should list the author, 
title (substitute file name, if needed), and the full URL 
(universal resource locator).

\vskip1pc

\noindent{\footnotesize
\begin{tabular}{lll} 
 &5. &QuickTime movie viewer plugins for web
 browsers, {\it Welcome to QuickTime}, \\ & & (Apple Computer, 
 1997),    \underline{http://quicktime.apple.com} \\
\end{tabular}}

\vskip1pc

To assist authors with journal abbreviations in references, 
standard abbreviations for 31 commonly cited journals 
have been included as macros within opex.sty.  These abbreviations 
are shown in Table 1.

\section{Tables, Figures, 3-D, and video}

\subsection{Figures}
Figures should be included directly in the document.  
All photographs must be in digital form and placed 
appropriately in the electronic document.  All  
illustrations must be numbered consecutively (i.e., 
not by section), with Arabic numbers. The size of a 
figure should be commensurate with the amount and 
value of the information conveyed by the figure.
Enclose figures within the \verb+\begin{figure}+
and \verb+\end{figure}+ commands.

All illustrations should be centered, except for 
small figures no wider than 6.6 cm (2.6 in), which may 
be placed side by side. Use the \verb+\centerline{}+
command. Place figures as close as possible to 
where they are mentioned in the text. No 
part of a figure should go beyond the typing area.
Authors should use PostScript or EPS figures. Place 
the file name of the figure within the 
curly brackets of the 
\verb+\epsfbox{}+ command. To resize figures, the 
\verb+\epsfxsize=+ command may be used, before 
the \verb+\epsfbox{}+ command, e.g.,
\verb+\epsfxsize=5in \epsfbox{OpExF1.EPS}+.  Figures 
created in the picture environment may be used if 
the submission system processes the figures with 
no errors. In general if a LaTeX file with PostScript 
(PS) or (EPS) figures is sent, the figures must also 
be included in the tarred, gzipped archive.

Short figure captions should be 
\verb+\footnotesize+ and centered beneath the figure.  
The abbreviation Fig. for figure should appear first 
followed by the figure number and a period.  Longer 
figure captions should be indented 1.27cm (0.5in) 
on both margins.  The \verb+\caption{}+ command
sets type size, margins, and numbers figures
automatically.   The text of captions
should follow normal full-sentence structure.

\subsection{Tables}
Tables should be centered and numbered consecutively. 
Short table headings should be centered above the 
table.  Longer headings should have margins that 
match the table width.  Tables should use horizontal 
lines to delimit the top and bottom of the table and 
column headings.  Detailed explanations or table 
footnotes should be typed directly beneath the table.  
Position tables as close as possible to where they 
are mentioned in the main text.

\begin{center}{\footnotesize Table 1. Standard abbreviations
 for 31 commonly cited journals}
\end{center}
\begin{table}
\begin{center}
\begin{tabular}{lp{1.7in}|lp{1.7in}}\hline 
Macro & Abbreviation & Macro & Abbreviation \\ \hline
\verb+\ao+ & Appl.\  Opt.\  & \verb+\nat+ & Nature (London)   \\
\verb+\ap+ & Appl.\  Phys.\  & \verb+\oc+ & Opt.\ Commun.\   \\
\verb+\apl+ & Appl.\ Phys.\ Lett.\
  & \verb+\opex+ & Opt.\ Express   \\
\verb+\apj+ & Astrophys.\ J.\  & \verb+\ol+ & Opt.\ Lett.\   \\
\verb+\bell+ & Bell Syst.\ Tech.\ J.\
  & \verb+\pl+ & Phys.\ Lett.\   \\
\verb+\jqe+ & IEEE J.\ Quantum Electron.\
  & \verb+\pra+ & Phys.\ Rev.\ A   \\
\verb+\assp+ & IEEE Trans.\ Acoust.\ Speech Signal Process.\
  & \verb+\prb+ & Phys.\ Rev.\ B   \\
\verb+\aprop+ & IEEE Trans.\  Antennas Propag.\ 
  & \verb+\prc+ & Phys.\ Rev.\ C   \\
\verb+\mtt+ & IEEE Trans.\ Microwave Theory Tech.\
  & \verb+\prd+ & Phys.\ Rev.\ D   \\
\verb+\iovs+ & Invest.\ Ophthalmol.\ Vis.\ Sci.\
  & \verb+\pre+ & Phys.\ Rev.\ E   \\
\verb+\jcp+ & J.\ Chem.\ Phys.\
  & \verb+\prl+ & Phys.\ Rev.\ Lett.\   \\
\verb+\jmo+ & J.\ Mod.\ Opt.\
  & \verb+\rmp+ & Rev.\ Mod.\ Phys.\   \\
\verb+\josa+ & J.\ Opt.\ Soc.\ Am.\  & 
  \verb+\pspie+ & Proc.\ Soc.\ Photo-Opt.\ Instrum.\ Eng.\   \\
\verb+\josaa+ & J.\ Opt.\ Soc.\ Am.\ A 
  & \verb+\sjqe+ & Sov.\ J.\ Quantum Electron.\   \\
\verb+\josab+ & J.\ Opt.\ Soc.\ Am.\ B
  & \verb+\vr+ & Vision Res.\   \\
\verb+\jpp+ & J.\ Phys.\ (Paris)  & &  \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsection{3-D and video}
Figures may be linked to video or 3-D multimedia.
The figure should be a representative frame of the 
animation.  QuickTime video and 3-D animation 
may be uploaded to OSA by following the instructions 
on the {\it Optics Express} submissions pages.
Include any special instructions concerning links 
in the cover message accompanying submission.

%  \pagebreak \epsfbox{filename.ps}
\noindent
\begin{figure}
\centerline{\epsfxsize=5in \epsfbox{OpExF1.EPS}}
\caption{Sample EPS figure showing Bose-Einstein 
condensate data. Use the caption command for longer 
figure captions. REVTeX or LaTeX will automatically 
number the figures.}
%\begin{center} 
%{\footnotesize Fig. 1. Short figure caption.}
%\end{center}
\end{figure}

Authors may submit the resulting PS 
file. Other authors who use LaTeX or REVTeX must make
a tarred, gzipped archive of their .TeX file and 
PS or EPS figures.

\section{Conclusion}
Conforming to the {\it Optics Express} style is of 
critical importance to the speedy publication of a 
compuscript. After proofreading the compuscript, 
authors who have the capability to make PS files 
with BaKoMa fonts, may print  
PostScript to a file using BaKoMa fonts and submit the 
PostScript file to the journal.  Authors who prefer to
submit LaTeX files must use tar and gzip compression
to archive the manuscript and figures.  If there is 
video or other multimedia, the associated 
files must be uploaded separately.

Enter the requested information into the OpEx online 
submission system at 
http://epubs.osa.org/opticsexpress/submission, and 
upload the file.  For instructions, please see the 
{\it Optics Express} help files.
\end{document}

### 2011-12-29 prince/base/content/prince.js
Fix 'launch' option for PDF display on Windows

@@ -840,24 +840,19 @@ function printTeX(preview )
           if (pdfAction == "launch")
           {
             var os = getOS(window);
-            if (os == "linux") 
+            if (os == "win")
+            {
+              extension = "cmd";
+            }
+            else 
             {
               extension = "bash";
-              exefile = dsprops.get("resource:app", Components.interfaces.nsILocalFile);
-              exefile.append("shell."+ extension);
-              theProcess.init(exefile);
-              arr = [pdffile.path];
-              theProcess.run(false, arr, arr.length);
             }
-            else
-            {
-              extension = "bash";
-              exefile = dsprops.get("resource:app", Components.interfaces.nsILocalFile);
-              exefile.append("shell."+ extension);
-              theProcess.init(exefile);
-              arr = [pdffile.path];
-              theProcess.run(false, arr, arr.length);
-            }
+            exefile = dsprops.get("resource:app", Components.interfaces.nsILocalFile);
+            exefile.append("shell."+ extension);
+            theProcess.init(exefile);
+            arr = [pdffile.path];
+            theProcess.run(false, arr, arr.length);
           }
           else // pdfAction == complete path to viewer
           {

### 2012-01-20 prince/base/content/GraphOverlay.js
Reworked the internal representation of plots so that we can support multiple plots better. I can't guarantee it works exactly as before, but I'll continue to work on this

@@ -9,36 +9,21 @@ function Graph () {
   // When adding to this list, you must also add to the MathServiceRequest in the compute engine
   // Compute/iCmpIDs.h and Compute/MRequest.cpp::NameToPID()
   // PlotStatus: UI use only. New/Inited/Deleted.
-  this.GRAPHATTRIBUTES  = new Array ("ImageFile", "XAxisLabel", "YAxisLabel", "ZAxisLabel", "Width",
-                                     "Height", "PrintAttribute", "Placement", "Offset", "Float",
-                                     "PrintFrame", "Key", "Name", "CaptionText", "CaptionPlace",
-                                     "Units", "AxesType", "EqualScaling", "EnableTicks",
-                                     "XTickCount", "YTickCount", "AxesTips", "GridLines", "BGColor",
-									 "Dimension", "AxisScale",
-                                     // added
-									 "CameraLocationX", "CameraLocationY", "CameraLocationZ",
-                                     "FocalPointX", "FocalPointY", "FocalPointZ",
-                                     "UpVectorX", "UpVectorY", "UpVectorZ",
-                                     "ViewingAngle", "OrthogonalProjection", "KeepUp",
-                                     " ");
-  this.PLOTATTRIBUTES   = new Array ("PlotStatus", "PlotType",
-                                     "LineStyle", "PointStyle", "LineThickness", "LineColor",
-                                     "DiscAdjust", "DirectionalShading", "BaseColor", "SecondaryColor",
-									 "PointSymbol", "SurfaceStyle", "IncludePoints",
-									 "SurfaceMesh", "CameraLocationX", "CameraLocationY",
-									 "CameraLocationZ",	"FontFamily", "IncludeLines",
-                                     "AISubIntervals", "AIMethod", "AIInfo", "FillPattern",
-                                     "Animate", "AnimateStart", "AnimateEnd", "AnimateFPS",
-                                     "AnimateVisBefore", "AnimateVisAfter",
-                                     "ConfHorizontalPts", "ConfVerticalPts");
-  this.PLOTELEMENTS     = new Array ("Expression", "XMax", "XMin", "YMax", "YMin", "ZMax", "ZMin",
-                                     "XVar", "YVar", "ZVar", "XPts", "YPts", "ZPts", "TubeRadius");
-  this.modFlag          = new Object ();
-  this.plotCount        = 0;
[…]

### 2012-02-08 prince/prince-prefs.js
Capitalization problem

@@ -97,7 +97,7 @@ pref("swp.graph.Dimension",  "2");
 pref("swp.graph.HSize", "3.0");          
 pref("swp.graph.VSize", "4.5");         
 pref("swp.graph.defaultUnits", "cm");   
-pref("swp.graph.Placement", "display"); 
+pref("swp.graph.placement", "display"); 
 pref("swp.graph.floatLocation.forceHere", false);
 pref("swp.graph.floatLocation.here", true);
 pref("swp.graph.floatLocation.pageFloats", false);

### 2012-02-08 prince/base/content/dialogs/msiEdImageProps.js
Continuing work on plots, adding msiframe object.

@@ -1839,7 +1839,7 @@ function onAccept()
   dump("in onAccept\n");
   if (ValidateData())
   {
-//    var editorElement = msiGetParentEditorElementForDialog(window);
+    var editorElement = msiGetParentEditorElementForDialog(window);
     var editor = msiGetEditor(gEditorElement);
 
     editor.beginTransaction();
@@ -1847,8 +1847,9 @@ function onAccept()
     {
       var tagname="object";
 //      var frameElement = null;
-      gCaptionData.m_captionStr = getCaptionEditContents();
-      var bHasCaption = (gCaptionData.m_captionStr && gCaptionData.m_captionStr.length);
+//BBM      gCaptionData.m_captionStr = getCaptionEditContents();
+//BBM      var bHasCaption = (gCaptionData.m_captionStr && gCaptionData.m_captionStr.length);
+      var bHasCaption = true;
       var posInParent;
       if (imageElement)
       {
@@ -1899,11 +1900,11 @@ function onAccept()
 //        frameElement.appendChild(imageElement);
       }
 
-      var capData = findCaptionNodes(wrapperElement);
-      var capPosition = gDialog.captionPlacementGroup.value;
-      if (!capPosition || !capPosition.length)
-        capPosition = "below";
-//      syncCaptionAndExisting(gCaptionData.m_captionStr.below, capData.belowCaption, editor, wrapperElement, "below");
+//BBM      var capData = findCaptionNodes(wrapperElement);
+//BBM      var capPosition = gDialog.captionPlacementGroup.value;
+//BBM      if (!capPosition || !capPosition.length)
+//BBM        capPosition = "below";
+//BBM//      syncCaptionAndExisting(gCaptionData.m_captionStr.below, capData.belowCaption, editor, wrapperElement, "below");
 //      var capAttrStr = "";
 //      if (capData.aboveCaption && capData.aboveCaption.length)
 //        capAttrStr = "above";
@@ -1926,7 +1927,7 @@ function onAccept()
 //        wrapperElement = imageElement = msiEditorFindJustInsertedElement("object", editor);
 //      dump("In msiEdImageProps.onAccept(), oldWrapper is [" + ((wrapperElement == oldWrapper) ? "same as" : "different from") + "] one in document.\n");
 //      dump("In msiEdImageProps.onAccept(), oldImage is [" + ((imageElement == oldImage) ? "same as" : "different from") + "] one in document.\n");
[…]

### 2012-02-08 prince/base/content/GraphOverlay.js
Continuing work on plots, adding msiframe object.

@@ -1,407 +1,366 @@
-Components.utils.import("resource://app/modules/os.jsm");
 #include productname.inc
 #ifndef PROD_SW
+Components.utils.import("resource://app/modules/os.jsm");
 //----------------------------------------------------------------------------------
-// an array of DOM <graph> elements currently being reformatted
-var currentDOMGs = new Array();
-
 // ************ Graph section ******
-function Graph () {
+
+function Graph() {
   // these arrays enumerate the data for a graph. PLOTELEMENTS are in mathml
   // When adding to this list, you must also add to the MathServiceRequest in the compute engine
   // Compute/iCmpIDs.h and Compute/MRequest.cpp::NameToPID()
   // PlotStatus: UI use only. New/Inited/Deleted.
-  this.plots            = [];  //an array of plots, see below
-  this.modFlag          = {};  //a Boolean for each attribute in GRAPHATTRIBUTES
-  this.errStr           = "";
+  var i, list, lengtj;
+  this.plots = []; //an array of plots, see below
+  this.modFlag = {}; //a Boolean for each attribute in GRAPHATTRIBUTES
+  this.errStr = "";
   this.currentDisplayedPlot = -1;
-  for (var i = 0; i < this.GRAPHATTRIBUTES.length; i++) {
-    this[this.GRAPHATTRIBUTES[i]] = this.getDefaultValue(this.GRAPHATTRIBUTES[i]);
+  list = this.graphAttributeList();
+  length = list.length;
+  for (i = 0; i < length; i++) {
+    this[list[i]] = this.getDefaultValue(list[i]);
   }
   this.frame = new Frame(this);
 }
+Graph.prototype = {
+  COMPATTRIBUTES: ["ImageFile", "XAxisLabel", "YAxisLabel", "ZAxisLabel", "Width", "Height",
+                              "Units", "AxesType", "EqualScaling", "EnableTicks", "XTickCount",
+                              "YTickCount", "AxesTips", "GridLines", "BGColor", "Dimension",
+                              "AxisScale", "CameraLocationX", "CameraLocationY", "CameraLocationZ",
+                              "FocalPointX", "FocalPointX", "FocalPointZ", "UpVectorX", "UpVectorY",
+                              "UpVectorZ", "ViewingAngle", "OrthogonalProjection", "KeepUp", 
+                              "OrientationTiltTurn"],
+  GRAPHATTRIBUTES: ["Key", "Name", "CaptionPlace"],
+  constructor: Graph,
+  ser: new XMLSerializer(),
[…]

### 2012-02-08 prince/base/content/dialogs/ComputeGraphSettings.js

@@ -17,20 +17,29 @@ var plotArray = [];
 //   extract the value of the attribute and put it in the document
 function Startup(){ 
 
+  msidump("1");
   var graphnode = window.arguments[1];
   graph = new Graph();
   graph.extractGraphAttributes(graphnode);
+  msidump("2");
+  var frame = graphnode.getElementsByTagName("msiframe");
+  if (frame.length > 0) frame = frame[0];
+  msidump("3");
+  var plotwrapper = graphnode.getElementsByTagName("plotwrapper");
+  if (plotwrapper.length>0) plotwrapper = plotwrapper[0];
   var units = graph["Units"];
   if (!units || units.length === 0) 
   {
     units = "cm";
     graph["Units"] = units;
   }
-  gd = new Object();
+  var gd = new Object();
+  msidump("4");
   setHasNaturalSize(false);
   setCanRotate(false);
   document.getElementById("role-image").setAttribute("hidden",gFrameModeImage?"false":"true");
   plotwrapper = graphnode.getElementsByTagName("plotwrapper")[0];
+  msidump("5");
   gd = initFrameTab(gd, plotwrapper, false, null);
   var alist = graph.graphAttributeList(); 
   var id;                   
@@ -41,15 +50,6 @@ function Startup(){
     }                                                       
   } 
    
-  // some plotwrapper attributes override the GraphSpec attributes
-  var value;
-  if (value = plotwrapper.getAttribute("height"))                                                     
-    graph["Height"] = value;
-  if (value = plotwrapper.getAttribute("width"))                                                     
-    graph["Width"] = value;
-  if (value = plotwrapper.getAttribute("units"))                                                     
-    graph["Units"] = value;
-
   var plotNumControl    = document.getElementById('plotnumber');
   var numPlots = graph.getNumPlots();
   if (numPlots ===  0){ 
@@ -58,6 +58,7 @@ function Startup(){
   }
   plotNumControl.max = numPlots;
   plotNumControl.valueNumber = 1;
+  msidump("6");
   var firstActivePlot = 0;
   graph["plotnumber"] = firstActivePlot.toString();
   var plot = graph["plots"][0];
@@ -67,6 +68,7 @@ function Startup(){
   setColorWell("lineColorWell", plot.attributes["LineColor"]);  
   
   initKeyList();
+  msidump("7");
   
   var editorControl = document.getElementById("plotDlg-content-frame");
[…]

### 2012-02-14 prince/base/content/dialogs/ComputeGraphSettings.js
Checking in changes to plotting; the layout especially has been improved.

@@ -1,79 +1,83 @@
- // Copyright (c) 2005 MacKichan Software, Inc.  All Rights Reserved.
+// Copyright (c) 2005 MacKichan Software, Inc.  All Rights Reserved.
 // Three data items are passed into this dialog: 
-// window.arguments[0]: the graph object 
-// window.arguments[1]: DOMGraph, the DOM element that should be replaced
+// window.arguments[0]: editorElement 
+// window.arguments[1]: commandStr
+// window.arguments[2]: DOMGraph, the DOM element that should be replaced
 
 Components.utils.import("resource://app/modules/unitHandler.jsm"); 
 var gFrameModeImage = true;
 var gFrameModeTextFrame = false;
 var plotUnitsHandler = new UnitHandler();
 var graph;
+var graphnode;
 var plotwrapper;
 var plotArray = [];
+
 
 // Populate the dialog with the current values stored in the Graph object.
 // The element ids in ComputeGraphSettings.xul match the Graph attributes
 // if the document has an element matching an attribute name, 
 //   extract the value of the attribute and put it in the document
 function Startup(){ 
-
-  msidump("1");
-  var graphnode = window.arguments[1];
+  var plotwrapper, units, alist, id, i, plotNumControl, numPlots, firstActivePlot, 
+    plot, editorControl, theStringSource, oldval;
+  var gd = {};
+  graphnode = window.arguments[2];
+  var editorElement = window.arguments[0];
   graph = new Graph();
   graph.extractGraphAttributes(graphnode);
-  msidump("2");
   var frame = graphnode.getElementsByTagName("msiframe");
-  if (frame.length > 0) frame = frame[0];
-  msidump("3");
-  var plotwrapper = graphnode.getElementsByTagName("plotwrapper");
-  if (plotwrapper.length>0) plotwrapper = plotwrapper[0];
-  var units = graph["Units"];
+  if (frame.length > 0) 
+  {
+    frame = frame[0];
+  }
+  plotwrapper = graphnode.getElementsByTagName("plotwrapper");
+  if (plotwrapper.length>0) 
+  {
+    plotwrapper = plotwrapper[0];
+  }
+  units = graph["Units"];
   if (!units || units.length === 0) 
   {
     units = "cm";
     graph["Units"] = units;
   }
-  var gd = new Object();
-  msidump("4");
   setHasNaturalSize(false);
   setCanRotate(false);
[…]

### 2012-02-14 prince/base/content/msiEditor.js

@@ -10745,14 +10745,10 @@ function openOTFontDialog(tagname, node)
 
 function openGraphDialog(tagname, node, editorElement)
 {
-  if (DOMGListMemberP (node, currentDOMGs)) {
-    return;
-  }
-  DOMGListAdd (node, currentDOMGs);
   // non-modal dialog, the return is immediate
-  var dlgWindow = msiDoModelessPropertiesDialog("chrome://prince/content/ComputeGraphSettings.xul", "Plot Dialog", "chrome,close,titlebar,dependent",
-     editorElement, "cmd_objectProperties", node, null, node, currentDOMGs);
-  var editorElement = msiGetActiveEditorElement();
+  var dlgWindow = openDialog("chrome://prince/content/ComputeGraphSettings.xul", "Plot Dialog", "chrome,close,titlebar,dependent",
+     editorElement, "cmd_objectProperties", node);
+// why find it again???  var editorElement = msiGetActiveEditorElement();
 	msiGetEditor(editorElement).incrementModificationCount(1);
 
 }

### 2012-02-14 prince/base/content/GraphOverlay.js
Checking in changes to plotting; the layout especially has been improved.

@@ -9,7 +9,7 @@ function Graph() {
   // When adding to this list, you must also add to the MathServiceRequest in the compute engine
   // Compute/iCmpIDs.h and Compute/MRequest.cpp::NameToPID()
   // PlotStatus: UI use only. New/Inited/Deleted.
-  var i, list, lengtj;
+  var i, list, length;
   this.plots = []; //an array of plots, see below
   this.modFlag = {}; //a Boolean for each attribute in GRAPHATTRIBUTES
   this.errStr = "";
@@ -32,7 +32,6 @@ Graph.prototype = {
   GRAPHATTRIBUTES: ["Key", "Name", "CaptionPlace"],
   constructor: Graph,
   ser: new XMLSerializer(),
-  prompt: Components.classes["@mozilla.org/embedcomp/prompt-service;1"].getService(Components.interfaces.nsIPromptService),
   addPlot: function (plot) {
     // Add a plot to a graph. Conceptually, a plot is a collection of attribute/value pairs
     this.plots.push(plot);
@@ -62,7 +61,6 @@ Graph.prototype = {
       try {
         var topWin = msiGetTopLevelWindow();
         topWin.msiComputeLogger.Sent4("plotfuncCmd", filename, str, "");
-        //msiComputeLogger.Sent4 ("plotfuncCmd", filename, "", "");
         var out = GetCurrentEngine().plotfuncCmd(str);
         msiComputeLogger.Received(out);
       }
@@ -71,7 +69,7 @@ Graph.prototype = {
         msiComputeLogger.Exception(e);
       }
     } else {
-      dump(this.errStr);
+      msidump(this.errStr);
     }
     RestoreCursor(editorElement);
   },
@@ -93,7 +91,6 @@ Graph.prototype = {
     }
     catch (e) {
       status = "ERROR";
-      //this.prompt.alert (null, "Computation Error", "Query Graph: " + eng.getEngineErrors());
       dump("Computation Error", "Query Graph: " + eng.getEngineErrors() + "\n");
       msiComputeLogger.Exception(e);
     }
@@ -138,10 +135,12 @@ Graph.prototype = {
     var DOMFrame = document.createElementNS(htmlns, "msiframe");
     var DOMPw = document.createElementNS(htmlns, "plotwrapper");
     var DOMObj = document.createElementNS(htmlns, "object");
+    var DOMCaption = document.createElementNS(htmlns,"imagecaption");
     var editorElement = msiGetActiveEditorElement();
[…]

### 2012-02-14 prince/base/content/dialogs/msiFrameOverlay.js

@@ -828,7 +828,6 @@ function isValid()
   return true;
 }
 
-
 function setFrameAttributes(frameNode, contentsNode)
 {
   var rot;
@@ -842,9 +841,9 @@ function setFrameAttributes(frameNode, contentsNode)
     metrics.unit = "pt";
   }
   msiEditorEnsureElementAttribute(frameNode, "units",metrics.unit, editor);
-  if (contentsNode)
+  if (contentsNode) {
     msiEditorEnsureElementAttribute(contentsNode, "units",metrics.unit, editor);
-  
+  }
   if (!contentsNode)
     contentsNode = frameNode;
 
@@ -866,7 +865,7 @@ function setFrameAttributes(frameNode, contentsNode)
     var topmargin = getSingleMeasurement("margin", "Top", metrics.unit, false);
     msiEditorEnsureElementAttribute(frameNode, "topmargin", topmargin, editor);
     var overhang = getSingleMeasurement("margin", "Right", metrics.unit, false);
-    msiEditorEnsureElementAttribute(frameNode, "overhang", overhang, editor);
+     msiEditorEnsureElementAttribute(frameNode, "overhang", overhang, editor);
 		var marginArray = [];
 		marginArray[0] = frameUnitHandler.getValueAs(topmargin,"px");
 		marginArray[2] = marginArray[0];
@@ -904,32 +903,42 @@ function setFrameAttributes(frameNode, contentsNode)
     var borderwidth = getSingleMeasurement(borderAtt, "Left", metrics.unit, false);
     msiEditorEnsureElementAttribute(contentsNode, "borderw", borderwidth, editor);
   }
-  else
+  else {
     msiEditorEnsureElementAttribute(contentsNode, "borderw", getCompositeMeasurement("border",metrics.unit, false), editor);
+  }
   if (gFrameModeImage) {
     var padding = getSingleMeasurement("padding", "Left", metrics.unit, false);
     msiEditorEnsureElementAttribute(contentsNode, "padding", padding, editor);
   }
-  else
+  else{
     msiEditorEnsureElementAttribute(contentsNode, "padding", getCompositeMeasurement("padding",metrics.unit, false), editor);
+  }
   if (gFrameTab.autoHeightCheck.checked)
   {
-    if (gFrameModeImage)
+    if (gFrameModeImage){
       msiEditorEnsureElementAttribute(contentsNode, heightAtt, null, editor);
-    else
+    }
+    else{
[…]

### 2012-02-14 prince/base/content/msiEditorUtilities.js

@@ -11641,7 +11641,7 @@ function newline(output, currentline, indent)
 }
 
 var nonInlineTags=".math.html.head.requirespackage.newtheorem.definitionslist.documentclass.preamble.usepackage.preambleTeX."+
-  "msidisplay.pagelayout.page.textregion.columns.header.footer."+
+  "msidisplay.pagelayout.page.textregion.columns.header.footer.plot."+
   "titleprototype.docformat.numberstyles.sectitleformat.docformat.numberstyles.texprogram.";
 function isInlineElement(editor, element)
 {

### 2012-02-16 toolkit/components/Compute/Engines/STree2MML.cpp
Experiment with a unicode differential d. I think it works better

@@ -6208,7 +6208,8 @@ void STree2MML::SetUserPref(U32 which_one, const char *new_value)
     if (new_value && *new_value && strlen(new_value) < 16) {
       strcpy(up_differentiald, new_value);
     } else
-      up_differentiald[0] = 'd';
+      strcpy(up_differentiald, "&#x2146;");
+      //up_differentiald[0] = 'd';
     break;
   case CLPF_Output_Euler_e:    // e
     if (new_value && *new_value && strlen(new_value) < 16) {

### 2012-06-10 editor/libeditor/html/nsHTMLDataTransfer.cpp
Merging with pulled changes (forgot to update before committing local changes...)

@@ -303,6 +303,36 @@ NS_IMETHODIMP nsHTMLEditor::InsertHTML(const nsAString & aInString)
                                nsnull,  nsnull, 0, PR_TRUE);
 }
 
+nsresult nsHTMLEditor::NodeContainsOnlyMn(nsIDOMNode * curNode, nsIDOMNode ** textNode)
+{
+  nsCOMPtr<nsIDOMNode> node = curNode;
+  nsCOMPtr<nsIDOMNode> retNode;
+  node->Normalize();
+  PRUint32 childCount;
+  nsAutoString nodeName;
+  nsresult res;
+  nsCOMPtr<nsIDOMNodeList> nodeList;
+  while (node)
+  {
+    res = GetTagString(node, nodeName);
+    node->GetChildNodes(getter_AddRefs(nodeList));
+    res = nodeList->GetLength(&childCount);
+    if (childCount != 1)
+    {
+      *textNode = nsnull;
+      return NS_OK;
+    }
+    if (nodeName.EqualsLiteral("mn"))
+    {
+      node->GetFirstChild(getter_AddRefs(retNode));
+      *textNode = retNode;
+      return NS_OK;
+    }
+    node->GetFirstChild(getter_AddRefs(node));
+  }
+  *textNode = retNode;
+  return NS_OK;
+}
 
 nsresult
 nsHTMLEditor::InsertHTMLWithContext(const nsAString & aInputString,
@@ -716,7 +746,22 @@ nsHTMLEditor::InsertHTMLWithContext(const nsAString & aInputString,
             {
             }
           }
-          if (!(tagName.EqualsLiteral("math") || tagName.EqualsLiteral("mrow")))
+          if (tagName.EqualsLiteral("mn"))
+          {
+            nsCOMPtr<nsIDOMNode> textNode;
+            res = NodeContainsOnlyMn(curNode, getter_AddRefs(textNode));
+            if (textNode)
+            {
+              curNode = textNode;
+              parentNode->Normalize();
+              res = parentNode->GetFirstChild(getter_AddRefs(parentNode));
+              NS_ENSURE_SUCCESS(res, res);
+              GetTagString(parentNode, tagName);
+              // don't put mn into an mn, but put the contents into the contents
+            }
+          }
+          if (!(tagName.EqualsLiteral("math") || tagName.EqualsLiteral("mrow")
+            || tagName.EqualsLiteral("#text")))
           {
[…]

### 2012-06-10 layout/base/nsDisplayList.h

@@ -101,12 +101,20 @@ class nsIDeviceContext;
  * tree containing FRAME/IFRAME elements can include frames from the subdocuments.
  */
 
+#if 0
 #ifdef NS_DEBUG
-#define NS_DISPLAY_DECL_NAME(n) virtual const char* Name() { return n; }
+#define NS_DISPLAY_DECL_NAME(n, e) \
+   virtual const char* Name() { return n; } \
+   virtual Type GetType() { return e; }
 #else
-#define NS_DISPLAY_DECL_NAME(n) 
+#define NS_DISPLAY_DECL_NAME(n, e) \
+  virtual Type GetType() { return e; }
 #endif
+#endif
+#define NS_DISPLAY_DECL_NAME(n) \
+  virtual const char* Name() { return n; }
 
+  
 /**
  * This manages a display list and is passed as a parameter to
  * nsIFrame::BuildDisplayList.
@@ -837,7 +845,9 @@ public:
      const nsRect& aDirtyRect) {
     mPaint(mFrame, aCtx, aDirtyRect, aBuilder->ToReferenceFrame(mFrame));
   }
+#ifdef DEBUG
   NS_DISPLAY_DECL_NAME(mName)
+#endif
 protected:
   PaintCallback mPaint;
 #ifdef DEBUG

### 2012-06-10 layout/generic/nsIFrame.h

@@ -799,10 +799,18 @@ public:
    * Child frames are linked together in a singly-linked list
    */
   nsIFrame* GetNextSibling() const { return mNextSibling; }
-  void SetNextSibling(nsIFrame* aNextSibling) {
-    NS_ASSERTION(this != aNextSibling, "Creating a circular frame list, this is very bad."); 
-    mNextSibling = aNextSibling;
-  }
+   void SetNextSibling(nsIFrame* aNextSibling) {
+     NS_ASSERTION(this != aNextSibling, "Creating a circular frame list, this is very bad.");
+     if (mNextSibling && mNextSibling->GetPrevSibling() == this) {
+       mNextSibling->mPrevSibling = nsnull;
+     }
+     mNextSibling = aNextSibling;
+     if (mNextSibling) {
+       mNextSibling->mPrevSibling = this;
+     }
+   }
+
+   nsIFrame* GetPrevSibling() const { return mPrevSibling; }
 
   /**
    * Builds the display lists for the content represented by this frame
@@ -2135,6 +2143,7 @@ protected:
   nsStyleContext*  mStyleContext;
   nsIFrame*        mParent;
   nsIFrame*        mNextSibling;  // singly-linked list of frames
+  nsIFrame*        mPrevSibling;  // Do not touch outside SetNextSibling!
   nsFrameState     mState;
   
   // Helpers

### 2012-06-10 layout/mathml/base/src/nsMathMLmfracFrame.cpp

@@ -326,8 +326,8 @@ nsMathMLmfracFrame::Place(nsIRenderingContext& aRenderingContext,
   // our last visit there)
   nsEmbellishData coreData;
   GetEmbellishDataFrom(mEmbellishData.coreFrame, coreData);
-  nscoord leftSpace = PR_MAX(onePixel, coreData.leftSpace);
-  nscoord rightSpace = PR_MAX(onePixel, coreData.rightSpace);
+  nscoord leftSpace = PR_MAX(onePixel, coreData.leadingSpace);
+  nscoord rightSpace = PR_MAX(onePixel, coreData.trailingSpace);
 
   // see if the linethickness attribute is there 
   nsAutoString value;

### 2012-06-10 layout/mathml/base/src/nsMathMLmoFrame.cpp

@@ -24,6 +24,7 @@
  *   David J. Fiddes <D.J.Fiddes@hw.ac.uk>
  *   Shyjan Mahamud <mahamud@cs.cmu.edu>
  *   Pierre Phaneuf <pp@ludusdesign.com>
+ *   Frederic Wang <fred.wang@free.fr>
  *
  * Alternatively, the contents of this file may be used under the terms of
  * either of the GNU General Public License Version 2 or later (the "GPL"),
@@ -45,7 +46,6 @@
 #include "nsStyleContext.h"
 #include "nsStyleConsts.h"
 #include "nsIRenderingContext.h"
-#include "nsIFontMetrics.h"
 #include "nsContentUtils.h"
 #include "nsMathCursorUtils.h"
 #include "nsIDOMText.h"
@@ -65,6 +65,8 @@ NS_NewMathMLmoFrame(nsIPresShell* aPresShell, nsStyleContext *aContext)
 {
   return new (aPresShell) nsMathMLmoFrame(aContext);
 }
+
+//NS_IMPL_FRAMEARENA_HELPERS(nsMathMLmoFrame)
 
 nsMathMLmoFrame::~nsMathMLmoFrame()
 {
@@ -86,31 +88,36 @@ nsMathMLmoFrame::GetMathMLFrameType()
 // since a mouse click implies selection, we cannot just rely on the
 // frame's state bit in our child text frame. So we will first check
 // its selected state bit, and use this little helper to double check.
-PRBool
+bool
 nsMathMLmoFrame::IsFrameInSelection(nsIFrame* aFrame)
 {
   NS_ASSERTION(aFrame, "null arg");
-  if (!aFrame)
-    return PR_FALSE;
-
   PRBool isSelected = PR_FALSE;
   aFrame->GetSelected(&isSelected);
   if (!isSelected)
     return PR_FALSE;
-
   const nsFrameSelection* frameSelection = aFrame->GetConstFrameSelection();
   SelectionDetails* details =
-    frameSelection->LookUpSelection(aFrame->GetContent(), 0, 1, PR_TRUE);
+    frameSelection->LookUpSelection(aFrame->GetContent(), 0, 1, true);
 
   if (!details)
-    return PR_FALSE;
+    return false;
 
   while (details) {
     SelectionDetails* next = details->mNext;
     delete details;
     details = next;
   }
-  return PR_TRUE;
+  return true;
+}
+
+bool
+nsMathMLmoFrame::UseMathMLChar()
+{
[…]

### 2012-06-10 layout/mathml/content/src/nsMathMLOperators.cpp

@@ -106,12 +106,39 @@ static const char* const kMathVariant_name[] = {
   "double-struck"
 };
 
-void
+static void
+SetBooleanProperty(OperatorData* aOperatorData,
+                   nsString      aName)
+{
+  if (aName.IsEmpty())
+    return;
+
+  if (aName.EqualsLiteral("stretchy") && (1 == aOperatorData->mStr.Length()))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_STRETCHY;
+  else if (aName.EqualsLiteral("fence"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_FENCE;
+  else if (aName.EqualsLiteral("accent"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_ACCENT;
+  else if (aName.EqualsLiteral("largeop"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_LARGEOP;
+  else if (aName.EqualsLiteral("separator"))
+    aOperatorData->mFlags |=  NS_MATHML_OPERATOR_SEPARATOR;
+  else if (aName.EqualsLiteral("movablelimits"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_MOVABLELIMITS;
+  else if (aName.EqualsLiteral("symmetric"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_SYMMETRIC;
+  else if (aName.EqualsLiteral("integral"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_INTEGRAL;
+  else if (aName.EqualsLiteral("mirrorable"))
+    aOperatorData->mFlags |= NS_MATHML_OPERATOR_MIRRORABLE;
+}
+
+static void
 SetProperty(OperatorData* aOperatorData,
             nsString      aName,
             nsString      aValue)
 {
-  if (!aName.Length() || !aValue.Length())
+  if (aName.IsEmpty() || aValue.IsEmpty())
     return;
 
   // XXX These ones are not kept in the dictionary
@@ -119,71 +146,33 @@ SetProperty(OperatorData* aOperatorData,
   // maxsize (default: infinity)
   // minsize (default: 1)
 
-  if (aValue.EqualsLiteral("true")) {
-    // see if we should enable flags with default value=false
-    if (aName.EqualsLiteral("fence"))
-      aOperatorData->mFlags |= NS_MATHML_OPERATOR_FENCE;
-    else if (aName.EqualsLiteral("accent"))
[…]

### 2012-06-10 layout/mathml/content/src/nsMathMLOperators.h

@@ -5,7 +5,7 @@
  * The contents of this file are subject to the Mozilla Public License Version
  * 1.1 (the "License"); you may not use this file except in compliance with
  * the License. You may obtain a copy of the License at
- * http://www.mozilla.org/MPL/
+ * http://www.mozilla.or©g/MPL/
  *
  * Software distributed under the License is distributed on an "AS IS" basis,
  * WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License
@@ -65,23 +65,28 @@ enum {
   NS_MATHML_OPERATOR_FORM_INFIX           = 1,
   NS_MATHML_OPERATOR_FORM_PREFIX          = 2,
   NS_MATHML_OPERATOR_FORM_POSTFIX         = 3,
+  NS_MATHML_OPERATOR_DIRECTION            = 0x3<<2,
+  NS_MATHML_OPERATOR_DIRECTION_HORIZONTAL = 1<<2,
+  NS_MATHML_OPERATOR_DIRECTION_VERTICAL   = 2<<2,
   // the next 2 bits tell us the stretchiness
-  NS_MATHML_OPERATOR_STRETCHY           = 0xC,
-  NS_MATHML_OPERATOR_STRETCHY_VERT        = 1<<2,
-  NS_MATHML_OPERATOR_STRETCHY_HORIZ       = 1<<3,
+  NS_MATHML_OPERATOR_STRETCHY           = 1<<4,
   // other bits used in the Operator Dictionary
-  NS_MATHML_OPERATOR_FENCE              = 1<<4,
-  NS_MATHML_OPERATOR_ACCENT             = 1<<5,
-  NS_MATHML_OPERATOR_LARGEOP            = 1<<6,
-  NS_MATHML_OPERATOR_SEPARATOR          = 1<<7,
-  NS_MATHML_OPERATOR_MOVABLELIMITS      = 1<<8,
-  NS_MATHML_OPERATOR_SYMMETRIC          = 1<<9,
+  NS_MATHML_OPERATOR_FENCE              = 1<<5,
+  NS_MATHML_OPERATOR_ACCENT             = 1<<6,
+  NS_MATHML_OPERATOR_LARGEOP            = 1<<7,
[…]

### 2012-06-10 editor/libeditor/html/nsHTMLEditRules.cpp
Merging with pulled changes (forgot to update before committing local changes...)

@@ -3070,8 +3070,10 @@ PRInt32 FindCursorIndex(nsHTMLEditor* editor,
           mathmltype = msiUtils::GetMathmlNodeType(editingBC);
         }
 
-        if (mathmltype == msiIMathMLEditingBC::MATHML_MFRAC && i == 1){
-          // Passing into a denominator
+        if (( mathmltype == msiIMathMLEditingBC::MATHML_MFRAC || 
+              mathmltype == msiIMathMLEditingBC::MATHML_MSUB  ||
+              mathmltype == msiIMathMLEditingBC::MATHML_MSUP     )  && i == 1) {
+          // Passing into a denominator, subscript, ...
           count += 1;  
         }
         
@@ -3082,9 +3084,24 @@ PRInt32 FindCursorIndex(nsHTMLEditor* editor,
           break;
         
       }
+
       if (node == caretNode) {    
          done = true;
       }
+
+      if (!done){
+        msiUtils::GetMathMLEditingBC(editor, node, dontcare, false, editingBC);
+        
+        if (editingBC) {
+          mathmltype = msiUtils::GetMathmlNodeType(editingBC);
+        }
+
+        if ( mathmltype == msiIMathMLEditingBC::MATHML_MFRAC) {
+            // Passing out of denominator ...
+            count += 1;  
+        }
+      }
+
       printf("\nReturn sum %d", count);
       return count;
 
@@ -3119,8 +3136,8 @@ void FindCursorNodeAndOffset(nsHTMLEditor* editor, nsIDOMNode* node, PRInt32& ch
          }
 
      }  else {
-         theNode = node;
-         theOffset = 0;
+         //theNode = node;
+         //theOffset = 0;
 
          nsCOMPtr<msiIMathMLEditingBC> editingBC; 
          PRUint32 dontcare(0);
@@ -3138,26 +3155,45 @@ void FindCursorNodeAndOffset(nsHTMLEditor* editor, nsIDOMNode* node, PRInt32& ch
          node->GetChildNodes(getter_AddRefs(children));
          msiUtils::GetNumberofChildren(node, number);
 
+         //nsCOMPtr<nsIDOMNode>& saveNode = theNode;
+
          for (PRUint32 i = 0; i < number; ++i) {
             printf("\nGet child %d\n", i);
             msiUtils::GetChildNode(node, i, child);
 
             //printf("\nCharLength is %d\n", CharLength(child));
[…]

### 2012-06-10 layout/generic/nsFrame.cpp

@@ -485,8 +485,8 @@ nsFrame::Destroy()
   nsIPresShell *shell = presContext->GetPresShell();
   NS_ASSERTION(!(mState & NS_FRAME_OUT_OF_FLOW) ||
                !shell->FrameManager()->GetPlaceholderFrameFor(this),
-               "Deleting out of flow without tearing down placeholder "
-               "relationship; see comments in nsFrame.h");
+"Deleting out of flow without tearing down placeholder relationship; see comments in nsFrame.h"
+               );
 
   shell->NotifyDestroyingFrame(this);
 

### 2012-06-10 layout/mathml/base/src/nsMathMLChar.cpp

@@ -23,6 +23,7 @@
  *   Roger B. Sidje <rbs@maths.uq.edu.au>
  *   Shyjan Mahamud <mahamud@cs.cmu.edu>
  *   Karl Tomlinson <karlt+@karlt.net>, Mozilla Corporation
+ *   Frederic Wang <fred.wang@free.fr>
  *
  * Alternatively, the contents of this file may be used under the terms of
  * either of the GNU General Public License Version 2 or later (the "GPL"),
@@ -47,7 +48,8 @@
 #include "nsUnicharUtils.h"
 #include "nsIRenderingContext.h"
 #include "gfxPlatform.h"
-#include "nsIFontMetrics.h"
+#include "nsIThebesFontMetrics.h"
+#include "gfxFont.h"
 
 #include "nsIPrefBranch.h"
 #include "nsIPrefService.h"
@@ -60,16 +62,9 @@
 #include "nsNetUtil.h"
 
 #include "nsILookAndFeel.h"
-#include "nsIDeviceContext.h"
 #include "nsCSSRendering.h"
 #include "prprf.h"         // For PR_snprintf()
 
-#if ALERT_MISSING_FONTS
-#include "nsIDOMWindow.h"
-#include "nsINonBlockingAlertService.h"
-#include "nsIWindowWatcher.h"
-#include "nsIStringBundle.h"
-#endif
 #include "nsDisplayList.h"
 
 #include "nsMathMLOperators.h"
@@ -77,12 +72,19 @@
 
 //#define SHOW_BORDERS 1
 //#define NOISY_SEARCH 1
+#ifndef M_SQRT2
+#define M_SQRT2         1.41421356237309504880
+#endif
 
 // -----------------------------------------------------------------------------------
 static const PRUnichar   kSpaceCh   = PRUnichar(' ');
-static const nsGlyphCode kNullGlyph = {0, 0};
+static const nsGlyphCode kNullGlyph = {{0, 0}, 0};
 typedef enum {eExtension_base, eExtension_variants, eExtension_parts}
   nsMathfontPrefExtension;
+enum {
+  // Number of bits needed to represent all types
+  TYPE_BITS = 8
+};
 
 // -----------------------------------------------------------------------------------
 // nsGlyphTable is a class that provides an interface for accessing glyphs
@@ -134,57 +136,6 @@ typedef enum {eExtension_base, eExtension_variants, eExtension_parts}
 #define NS_TABLE_STATE_EMPTY        0
[…]

### 2012-06-10 layout/mathml/base/src/nsMathMLChar.h

@@ -23,6 +23,7 @@
  *   Roger B. Sidje <rbs@maths.uq.edu.au>
  *   Shyjan Mahamud <mahamud@cs.cmu.edu>
  *   Karl Tomlinson <karlt+@karlt.net>, Mozilla Corporation
+ *   Frederic Wang <fred.wang@free.fr>
  *
  * Alternatively, the contents of this file may be used under the terms of
  * either of the GNU General Public License Version 2 or later (the "GPL"),
@@ -58,9 +59,11 @@ enum {
   NS_STRETCH_LARGER   = 0x08, // don't stretch less than requested size
   // A largeop in displaystyle
   NS_STRETCH_LARGEOP  = 0x10,
+  NS_STRETCH_INTEGRAL  = 0x20,
+
   // Intended for internal use:
   // Find the widest metrics that might be returned from a vertical stretch
-  NS_STRETCH_MAXWIDTH = 0x20
+  NS_STRETCH_MAXWIDTH = 0x40
 };
 
 // A single glyph in our internal representation is characterized by a 'code@font' 
@@ -68,18 +71,20 @@ enum {
 // (depending on the type of nsGlyphTable where this comes from). The 'font' is a
 // numeric identifier given to the font to which the glyph belongs.
 struct nsGlyphCode {
-  PRUnichar code; 
+  PRUnichar code[2]; 
   PRInt32   font;
 
-  PRBool Exists() const
+  PRInt32 Length() { return (code[1] == PRUnichar('\0') ? 1 : 2); }
+  bool Exists() const
   {
-    return (code != 0);
+    return (code[0] != 0);
   }
-  PRBool operator==(const nsGlyphCode& other) const
+  bool operator==(const nsGlyphCode& other) const
   {
-    return other.code == code && other.font == font;
+    return (other.code[0] == code[0] && other.code[1] == code[1] && 
+            other.font == font);
   }
-  PRBool operator!=(const nsGlyphCode& other) const
+  bool operator!=(const nsGlyphCode& other) const
   {
     return ! operator==(other);
   }
@@ -104,6 +109,11 @@ public:
     mStyleContext = nsnull;
     mSibling = nsnull;
     mParent = aParent;
+    mUnscaledAscent = 0;
+    mScaleX = mScaleY = 1.0;
+    mDrawNormal = true;
+    mMirrored = false;
+    mGlyphFound = false;
   }
 
[…]

### 2012-06-10 layout/mathml/base/src/nsMathMLFrame.cpp

@@ -113,8 +113,8 @@ nsMathMLFrame::InheritAutomaticData(nsIFrame* aParent)
   mEmbellishData.flags = 0;
   mEmbellishData.coreFrame = nsnull;
   mEmbellishData.direction = NS_STRETCH_DIRECTION_UNSUPPORTED;
-  mEmbellishData.leftSpace = 0;
-  mEmbellishData.rightSpace = 0;
+  mEmbellishData.leadingSpace = 0;
+  mEmbellishData.trailingSpace = 0;
 
   mPresentationData.flags = 0;
   mPresentationData.baseFrame = nsnull;
@@ -191,8 +191,8 @@ nsMathMLFrame::GetEmbellishDataFrom(nsIFrame*        aFrame,
   aEmbellishData.flags = 0;
   aEmbellishData.coreFrame = nsnull;
   aEmbellishData.direction = NS_STRETCH_DIRECTION_UNSUPPORTED;
-  aEmbellishData.leftSpace = 0;
-  aEmbellishData.rightSpace = 0;
+  aEmbellishData.leadingSpace = 0;
+  aEmbellishData.trailingSpace = 0;
 
   if (aFrame && aFrame->IsFrameOfType(nsIFrame::eMathML)) {
     nsIMathMLFrame* mathMLFrame;
@@ -332,10 +332,10 @@ nsMathMLFrame::GetAxisHeight(nsIRenderingContext& aRenderingContext,
   // get the bounding metrics of the minus sign, the rendering context
   // is assumed to have been set with the font of the current style context
 #ifdef NS_DEBUG
-  nsCOMPtr<nsIFontMetrics> currFontMetrics;
-  aRenderingContext.GetFontMetrics(*getter_AddRefs(currFontMetrics));
-  NS_ASSERTION(currFontMetrics->Font().Equals(aFontMetrics->Font()),
-	"unexpected state");
+//  nsCOMPtr<nsIFontMetrics> currFontMetrics;
+//  aRenderingContext.GetFontMetrics(*getter_AddRefs(currFontMetrics));
+//  NS_ASSERTION(currFontMetrics->Font().Equals(aFontMetrics->Font()),
+//	"unexpected state");
 #endif
   nscoord xHeight;
   aFontMetrics->GetXHeight(xHeight);

### 2012-07-19 editor/libeditor/html/nsHTMLEditRules.cpp
Changes in InsertStructure to fix bugs in inserting a section inside of a section

@@ -8821,7 +8821,8 @@ nsHTMLEditRules::InsertStructure(nsIDOMNode *inNode,
   }
   if (topSplitNode != sourceNode) {
     NS_ASSERTION(topSplitNode,"no node can hold the section. Not even body?");
-    mHTMLEditor->SplitNodeDeep(topSplitNode, sourceNode, sourceOffset, &destOffset, PR_TRUE, 
+    res = nsEditor::GetNodeLocation(sourceNode, address_of(parent), &sourceOffset);
+    mHTMLEditor->SplitNodeDeep(topSplitNode, parent, sourceOffset, &destOffset, PR_TRUE, 
       address_of(outLeftNode), address_of(outRightNode)); 
     res = nsEditor::GetNodeLocation(outRightNode, address_of(destParentNode), &destOffset);
   } else
@@ -8844,35 +8845,37 @@ nsHTMLEditRules::InsertStructure(nsIDOMNode *inNode,
     newStructureNode = do_QueryInterface(elem);
   }
   *outNode = newStructureNode; 
-  NS_ADDREF(*outNode);
-  // Hold off on inserting this node until it is fully populated. This makes counter update more
-  // reliable
+    NS_ADDREF(*outNode);
+if (false)
+{
+// Hold off on inserting this node until it is fully populated. This makes counter update more
+// reliable
   
-  // now march up the tree while the new tagtype (aStructureType, atomNamespace) is *not*
-  // allowed as a contained item. As we go, we collect children to the right of our chain
-  // in the new outNode. 
+// now march up the tree while the new tagtype (aStructureType, atomNamespace) is *not*
+// allowed as a contained item. As we go, we collect children to the right of our chain
+// in the new outNode. 
   
-  offset = 0;
-  MoveNodesFromRight(mHTMLEditor, sourceNode, newStructureNode, offset);  
-  // Now move the source paragraph node to the new section node
-  PRInt32 zeroOffset = 0;
-  mHTMLEditor->MoveNode( sourceNode, newStructureNode, zeroOffset);
-  offset++;
-  parent = sourceParentNode;
-  while (parent)
-  {
-    res = mtagListManager->NodeCanContainTag(parent, aStructureType, atomNamespace, &fCanContain);
+offset = 0;
+MoveNodesFromRight(mHTMLEditor, sourceNode, newStructureNode, offset);  
+// Now move the source paragraph node to the new section node
[…]

### 2012-07-19 editor/libeditor/html/nsHTMLEditor.cpp

@@ -2399,6 +2399,7 @@ nsHTMLEditor::SetCaretAfterElement(nsIDOMElement* aElement)
 NS_IMETHODIMP 
 nsHTMLEditor::SetStructureTag(const nsAString& aSectionTag)
 {
+  nsresult res;
   nsAutoString strStruct; strStruct.Assign(aSectionTag);
   TagKey tag(strStruct);
   if (tag.localName().EqualsLiteral("dd") || tag.localName().EqualsLiteral("dt"))
@@ -2407,8 +2408,11 @@ nsHTMLEditor::SetStructureTag(const nsAString& aSectionTag)
   else
   {
     nsCOMPtr<nsIAtom> nsAtom;
+    BeginTransaction();
     mtagListManager->NameSpaceAtomOfTagKey(tag.key, (nsIAtom**)address_of(nsAtom));
-    return InsertStructureNS(tag.localName(), nsAtom);
+    res = InsertStructureNS(tag.localName(), nsAtom);
+    EndTransaction();
+    return res;
   }
 }
 

### 2012-07-19 editor/libeditor/base/msiTagListManager.cpp
Changes in InsertStructure to fix bugs in inserting a section inside of a section

@@ -1175,7 +1175,7 @@ NS_IMETHODIMP msiTagListManager::GetNewInstanceOfNode(const nsAString & strTag, 
   PRBool fInHash = msiTagHashtable.Get(strKey, (TagData **)&data);
   if (fInHash)
   {
-    retNode = data->initialContents;
+    res = data->initialContents->CloneNode( PR_TRUE, getter_AddRefs(retNode));
     res = doc->ImportNode(retNode, PR_TRUE, _retval);
     NS_ADDREF(retNode.get());
   }

### 2012-10-31 prince/TCITeX/TeX/LaTeX/SWmisc/latex209/jeep/jeep.tex
Add typesetting specification files from Version 5.5 located in TCITeX\TeX\latex209 (killing the contrib level).

\documentstyle[11pt,jeep]{article}
%\headheight 14pt
\lhead{\large\tt jeep.sty}\rhead{April 29, 1991}
\cfoot{\thepage}
\underhead
\tighttoc
\thispagestyle{plain}
\numberbysection
\begin{document}
\begin{center}
\large\sc {\tt JEEP}\smallskip\\
A Customization of the \LaTeX\\
Article and Report Styles
\smallskip\\
G.  W.  Stewart\symbolnote{1}{Department of Computer Science and
Institute for Advanced Computer Studies, University of Maryland,
College Park, MD 20742 (stewart@cs.umd.edu).}
\bigskip
\end{center}

\tableofcontents

\section{Introduction}

This note describes a style file to accompany the \LaTeX\ document
styles article and report.  It is not a systematic revision of these
styles; rather it consists of modifications I found necessary or
desirable in the course of my work.  Although I have used the
modifications for some time in a variety of applications, they no
doubt still contain some bugs.  Please send any comments to the
address below.

The name \verb|jeep| is a continuation of Leslie Lamport's analogy,
in which he compares \TeX\ to a racing car and \LaTeX\ to a family
sedan.  The modifications here convert the sedan to a general purpose
vehicle\,---\,a jeep.  The modifications, like a jeep, are not
pretty, but the casual \LaTeX er can cover a lot of territory with
them.

\section{Page Size}

The default page size is changed to take full advantage of the
default North American paper size of $8\frac{1}{2}\times 11$ in.  It
looks OK in eleven or twelve point type.  I find no virtues in ten
point type on pages of this size.

\section{Chapter, Section, and Theorem Heads}

Even among well printed books, there is great variation in the format
of section heads.  The font may be bold, sans serif, or small caps,
in sizes ranging from normal to rather large.  If a section number is
present, it may be followed by a period or by a long space.  The
changes here give the casual \LaTeX er more control over the style of
his headings.

\subsection{Chapter heads}

The format of chapter heads may be controlled by the command
\begin{quote}
\begin{verbatim}
\mychapter{<head1>}{<head2>}
\end{verbatim}
\end{quote}
Here \verb|<head1>| is the chapter heading to use when the chapter is
numbered and \verb|<head2>| is the heading to use with the
\verb|\chapter*| command.  The text of the \verb|\chapter| command is
referenced in \verb|<head1>| and \verb|<head2>| by writing \verb|#1|.
For example, the default chapter head is defined by
\begin{quote}
\begin{verbatim}
\mychapter{\LARGE \sc \thechapter. #1}{\LARGE \sc #1}
\end{verbatim}
\end{quote}

Chapters always begin on a new page.  The style parameter
\verb|\chaptopsep| is the amount of blank space placed at the top of
the page before the chapter head, and \verb|\chapaftersep| is
the amount of blank space placed between the chapter head and
the text.  They are initially \verb|.5in|.  They may be changed
by the \verb|\setlength| command.

The default head does not have the word ``Chapter'' preceding
the chapter number, which is fine with me, but may not please you.
To get back something approximating the original \LaTeX\ heads
try
\begin{quote}
\begin{verbatim}
\mychapter{\huge \bf \chapapp\ \thechapter\\[20pt]\Huge\bf #1}
{\Huge \bf #1}
\end{verbatim}
\end{quote}
The command \verb|\chapapp| is ordinarily defined to be
``Chapter'' but the \LaTeX\ command \verb|\appendix| changes it
to ``Appendix''.  If you want more flexibility in your appendix
heads, use \verb|\mychapter| to define them anew.

\subsection{Section heads}
The format of section heads may be controlled by the command
\begin{quote}
\begin{verbatim}
\mysection{<sec>}{<style>}{<preface>}
\end{verbatim}
\end{quote}
Here {\tt <sec>} is the section level\,---\,{\tt section}, {\tt
subsection}, etc.  The style in which the section is to be set is
specified by \verb|<style>|; e.g., \verb|\large\sf|.  The argument
{\tt <preface>} is the text to be set before the text of the section
head\,---\,usually \verb|\thesection| and some punctuation.  For example
the section heads in this document were produced by the commands.
\begin{quote}
\begin{verbatim}
\mysection{section}{\large\bf}{\thesection.~}
\mysection{subsection}{\normalsize\bf}{\thesubsection.~}
\mysection{subsubsection}{\normalsize\bf}{\thesubsubsection.~}
\mysection{paragraph}{\normalsize\bf}{\theparagraph.}
\mysection{subparagraph}{\normalsize\bf}{\thesubparagraph.}
\end{verbatim}
\end{quote}
These are the default for {\tt jeep.sty}.

\subsection{Theorem heads}
One already has considerable flexibility in controlling the
theorem environment.  For example, the definition
\begin{quote}
\begin{verbatim}
\newtheorem{theorem}{\sf Theorem}
\end{verbatim}
\end{quote}
will cause theorem headings to be printed in sans serif type.
However, it is not easy to slip a punctuation mark after
the theorem number.  This can now be done by the statement
\begin{quote}
\begin{verbatim}
\renewcommand{\thmcounterend}{<punctuation>}
\end{verbatim}
\end{quote}
where {\tt <punctuation>} is the desired punctuation.  The
default is a period.  This command affects all user defined
theorem environments.

The default typestyle within the theorem environment has been
changed to \verb|\sl|.  This can easily be overridden.

\section{Numbering}

A new command, \verb|\numberbysection|, which should appear only in
the preamble, places the equation, figure, table, and theorem counters
within the section counter and redefines \verb|\the<counter>| to be
\verb|\thesection.\arabic{<counter>}|.  The change is inherited by all
theorem environments that are defined to be numbered with
\verb|theorem| (however, be sure to create the \verb|theorem|
environments {\it before} invoking \verb|\numberbysection|).

In the article style, \verb|\numberbysection| is the natural way to
write a paper.  In the report style, the user of
\verb|\numberbysection| must provide explicit chapter numbers
when referencing equations, theorems, etc, outside the
current chapter.

An analogous command, \verb|\numberbysubsection|, causes the
counters to be reset when subsections change.  This option is
especially useful for a style of writing in which the work is
broken up into short subsections of one or two paragraphs, each
with its own heading.  Try writing this way if you have
temporary writer's block.  At its best the technique produces a
lively work that moves quickly from topic to topic.  At its
worst it produces a rambling, ill-organized mish-mash.

\section{Headers}

\subsection{Three part headers and footers}

A finished article or report should have a limited number of simple,
informative headers and footers\,---\,perhaps a title or section head
and a page number.  Work in progress requires additional information;
e.g., the author's name or initials, the date, and a statement that
this is a draft.  To help with this, I have made Lance
Berc's\footnote{Ollivetti Research Center, 2882 Sand Hill Road,
Menlo Park, CA 94025} three part headers and footers the default page
style.  The commands
\begin{quote}
\begin{verbatim}
\lhead{<item>}
\chead{<item>}
\rhead{<item>}
\end{verbatim}
\end{quote}
sets the left, center, and right parts of the headers.  The
corresponding commands for footers are
\begin{quote}
\begin{verbatim}
\lfoot{<item>}
\cfoot{<item>}
\rfoot{<item>}
\end{verbatim}
\end{quote}
The \verb|\pagestyle| command
overrides the three part option.

If the \verb|twoside| style option is invoked before jeep, the macros
switch the right and left items on even numbered pages.  If you
require different headers and footers for even numbered pages, as
often with books, use the commands
\begin{quote}
\begin{verbatim}
\elhead{<item>}
\echead{<item>}
\erhead{<item>}
\elfoot{<item>}
\ecfoot{<item>}
\erfoot{<item>}
\end{verbatim}
\end{quote}
to define them.  They should follow the commands, \verb|\lhead|,
\verb|chead|, etc.

\subsection{Underlined headers}

The preamble command \verb|\underhead| places a
rule of length \verb|\textwidth| a distance of
\verb|\underheadsep| under the header text.  The value
of \verb|\underheadsep| can be changed in the preamble by
\verb|\settolength|.  This length is added
to the style parameter \verb|\headhight|, so that the top of the text
is moved down by \verb|\underheadsep|.  To keep the top of the text
in the original position execute the command
\begin{quote}
\begin{verbatim}
\addtolength{\headsep}{-\underheadsep}
\end{verbatim}
\end{quote}

In preparing assignments and classroom notes, I find it convenient to
use the header line as a title, in which case I do not want it
underlined on the first page.  Underlining on the current page can be
suppressed by the command \verb|\nounderhead|.

\section{Enumerated Lists}

\subsection{The {\tt enumerate} environment}

As a matter of personal taste, I prefer my lists enumerated by simple
arabic numbers.  Consequently, I have changed the numbering
conventions on the {\tt enumerate} environment to use arabic numbers
at all levels.

\subsection{The {\tt outline} environment}

Many people who use the {\tt enumerate} environment to produce a
syllabus or other long nested lists of short items are dismayed
by the amount of space between the items.  The {\tt outline}
environment, which is essentially the same as {\tt enumerate},
suppresses some of this space.  It leaves space, however, at the
beginning and end of a list, but not a sublist.  For example
\begin{outline}
\item Rome and Carthage
   \begin{outline}
   \item The first Punic war
   \item The second Punic war
      \begin{outline}
      \item Hannibal in Spain
      \item Hannibal in Italy
      \item Hannibal in flight
      \end{outline}
   \item {\it Carthago delenda est}
   \end{outline}
\item Rome in the Adriatic
\end{outline}
You should use the {\tt outline} environment sparingly.  For
most purposes, even for a list of a few short items, the {\tt
enumerate} environment produces more pleasing results.

\section{The {\tt literatim} environment}
One of the frustrations of the verbatim environment is that it does
not permit commands to be executed.  This means that you cannot
change fonts or insert equations.  For example, the verbatim
environment cannot be used to produce an annotated program like the
following.
\begin{quote}
\begin{literatim}{}
x = exp(y);                 {\rm: Initialize \$x\$.}

p = a[n];                   {\rm: Evaluate the polynomial}
for (i=n-1; i>=0; i--)      {\rm: \$a\_nx\^n+\cdots+a\_0\$.} 
   p = x*p + a[i];
\end{literatim}
\end{quote}

To circumvent this difficulty, \verb|jeep| provides a
\verb|literatim| environment\,---\,an extension of Lamport's
\verb|alltt| environment\,---\,in which \verb|\|, \verb|{|, and
\verb|}| retain their original functions,  so that we can
invoke commands and delimit their arguments.  For example,
the above program listing was produced by the statements
\begin{quote}
\small
\begin{verbatim}
\begin{literatim}{}
x = exp(y);                 {\rm: Initialize \$x\$.}

p = a[n];                   {\rm: Evaluate the polynomial}
for (i=n-1; i>=0; i--)      {\rm: \$a\_nx\^n+\cdots+a\_0\$.} 
   p = x*p + a[i];
\end{literatim}
\end{verbatim}
\end{quote}

One difficulty with the \verb|literatim| environment is that you loose
the special commands that are not preceded by a backslash.  For
example, we cannot delimit an equation by dollar signs, since they
are now interpreted literally.  One solution would be to use the
\TeX\ delimiters \verb|\(| and \verb|\)|  
(as well as the commands \verb|\sp{}|
and \verb|\sb{}| for \verb|^{}| and \verb|_{}|).  But this is a
bother, especially for people who do not have a powerful editor.
Instead \verb|literatim| defines the commands \verb|\$|, \verb|\^|,
\verb|\_|, and \verb|\&| to be the equivalent of the special
commands \verb|$|, \verb|^|, \verb|_|, and \verb|&|.  (Unfortunately, the
definition of \verb|\^| redefines the command that produces a
circumflex over a letter.  To get a circumflex in the
\verb|literatim| environment use the command \verb|\circumflex{<letter>}|.)
In addition \verb|\@|, which is not needed in the literatim environment,
produces a backslash.

Even a short equation can have a long definition, so that it is
necessary to break it across lines.  Unfortunately, we cannot use a
line break (\verb|^M|) for this purpose in the \verb|literatim|
environment, and the character \verb|%| is no longer available as an
escape.  To handle this difficulty, \verb|literatim| has a
(nonoptional) argument to specify the comment character, which must
be preceeded by a backslash in the argument.  If the argument is
empty, there will be no comment characters.  Thus if we wish to name
our polynomial and include another term, we might enter
\begin{quote}
\small
\begin{verbatim}
\begin{literatim}{\`}
x = exp(y);                 {\rm: Initialize \$x\$.}

p = a[n];                   {\rm: Evaluate the polynomial}
for (i=n-1; i>=0; i--)`
      {\rm: \$p(x)=a\_nx\^n+a\_{n-1}x\^{n-1}+\cdots+a\_0\$.} 
   p = x*p + a[i];
\end{literatim}
\end{verbatim}
\end{quote}
which will give
\begin{quote}
\begin{literatim}{\`}
x = exp(y);                 {\rm: Initialize \$x\$.}

p = a[n];                   {\rm: Evaluate the polynomial}
for (i=n-1; i>=0; i--)`
      {\rm: \$p(x)=a\_nx\^n+a\_{n-1}x\^{n-1}+\cdots+a\_0\$.} 
   p = x*p + a[i];
\end{literatim}
\end{quote}

In using the \verb|literatim| environment, you should keep in
mind that the space character is active.  This means, among
other things, that spaces following a command are not removed
and that spaces in equations will actually appear in the text.
For example the statements
\begin{quote}
\begin{verbatim}
\begin{literatim}{}
{\rm Let \$c = (a + b)/2\$ be the {\it mean value}\ldots.} 
\end{literatim}
\end{verbatim}
\end{quote}
produce
\begin{quote}
\begin{literatim}{}
{\rm Let \$c = (a + b)/2\$ be the {\it mean value}\ldots.}
\end{literatim}
\end{quote}
What we really want is
\begin{quote}
\begin{literatim}{}
{\rm{}Let \$c=(a+b)/2\$ be the {\it{}mean value}\ldots.}
\end{literatim}
\end{quote}
which is produced by
\begin{quote}
\begin{verbatim}
\begin{literatim}{}
{\rm{}Let \$c=(a+b)/2\$ be the {\it{}mean value}\ldots.}
\end{literatim}
\end{verbatim}
\end{quote}

\section{Table of Contents}

In technical articles it is sometimes convenient to place a
table of contents on the first page, right after the title and
abstract.  I find the section entries in the default table of
contents for the article style to be too assertive and too
widely spaced for this purpose.  The command
\begin{quote}
\begin{verbatim}
\tighttoc
\end{verbatim}
\end{quote}
produces a tighter table of contents.  It was used to generate
the table of contents on the first page.

\section{Miscellaneous}

\subsection{Symbolic footnote marks}
Since there is no standard place to cut windows in technical
report covers, most people are reduced to hacking their own
title pages.  This creates the problem of producing footnotes
using the symbols $*$, \dag, \ddag, etc.  The command
\begin{quote}
\begin{verbatim}
\symbolnote{<num>}{<text>}
\end{verbatim}
\end{quote}
produces a footnote with footnote symbol \verb|<num>|, where
\verb|<num>| is a number between 1 and 9 (for a list of the
symbols see \S C.7.4 in the \LaTeX\ manual).  This command does
not alter the usual sequencing of numbered footnotes, so that it
can be used to produce auxiliary footnotes anywhere in the
manuscript.  The following sequence generated the footnote at
the beginning of this note.
\begin{quote}
\begin{verbatim}
G. W. Stewart\symbolnote{1}{Department of ... }
\end{verbatim}
\end{quote}

The commands \verb|\symbolmark{<num>}| and
\verb|\symboltext{<num>}{<text>}| are analogues of
\verb|\footnotemark[<num>]| and \verb|\footnotetext[<num>]{<text>}|.
Observe that the argument \verb|<num>|, which is optional in the
\LaTeX\ commands, is mandatory in the \verb|jeep| commands.

\subsection{Symbolic equation labels} In short notes, classroom
assignment, and tests it is often convenient to label an
equation by a symbol; e.g.
\begin{symboleqn}{(*)}
x^n + y^n = z^n.
\end{symboleqn}
This can be accomplished by the sequence
\begin{quote}
\begin{verbatim}
\begin{symboleqn}{(*)}
x^n + y^n = z^n.
\end{symboleqn}
\end{verbatim}
\end{quote}
Any text can replace the $(*)$, but keep in mind that it will be set in
math mode.  Equations generated by \verb|symboleqn| cannot be labeled;
any references must be constructed explicitly.

Since asterisks are a favorite symbol in this connection, let me note
some of the pitfalls.  Always set $(*)$ in math mode thus:
\verb|$(*)$|.  If you enter \verb|(*)|, you will get (*), with the
asterisk too high.  To get $(*{*}*)$ enter \verb|$(*{*}*)$|.  The
braces keep \TeX\ from treating the inner asterisk as an operator.

\subsection{The \TeX\ delimiters {\tt bigl}, {\tt bigr}, etc.}
\TeX\ has a series of delimiters of increasing size.  For example
\begin{quote}
\begin{verbatim}
$x\bigl(x(xa+b)+c\bigr)+e$
\end{verbatim}
\end{quote}
should produce $x\bigl(x(xa+b)+c\bigr)+e$.  As they were originally
defined, these delimiters do not do not scale along with the type
size commands of \LaTeX.  I have included definitions by John Hobby
that cure this problem.
\end{document}

### 2012-10-31 prince/TCITeX/TeX/LaTeX/SWmisc/latex209/deproc/deproc-doc.tex
Add typesetting specification files from Version 5.5 located in TCITeX\TeX\latex209 (killing the contrib level).

%               DEPROCLDC.TeX
%
%  This file is the preliminary version of a talk given at the Spring '86
%  DECUS in Dallas by Barbara Beeton, American Mathematical Society.
%  It describes the method by which an author of an article for the DECUS
%  Proceedings can prepare his camera copy using LaTeX.
%
%  This file, when run through LaTeX, will be formatted as described below.
%  It uses the macro package DEPROC.STY and the LaTeX ARTICLE.STY files,
%  plus a few locally defined macros, which are given at the top of this file.
%
%  One page in the output will be blank, reserved for a table.  The
%  contents of the table are in the file DEPROCDEV.TeX, which is to be
%  run through TeX as a separate job.
%
%  Although essentially complete, and to the best of my knowledge correct,
%  some details can be expected to change prior to publication.
%
%  Barbara Beeton
%  American Mathematical Society
%  P O Box 6248
%  Providence, RI 02940
%    (401)272-9500
%
%  20 Apr 86

%  If TeX is the program being run, this \input statement is required.
%\input latex
\documentstyle [draft]{deproc}

%       try to force a blank page in the middle for the floating figure

\def\dblfloatpagefraction{.5}
\def\textfraction{0}
\def\floatpagefraction{.5}

%       macros needed for this article

\newcommand{\AMS}{American Mathematical Society}
\newcommand{\Proc}{Proceedings}
\newcommand{\DP}{\mbox{\tt DEPROC}}
\newcommand{\DProc}{{\sl DECUS \Proc}}
\newcommand{\POBox}{P.\thinspace O.~Box }
\newcommand{\TB}{{\sl The \TeX book}}
\newcommand{\tub}{TUGboat}
\newcommand{\TUG}{\TeX\ Users Group}
\newcommand{\VAX}{\leavevmode\hbox{V\kern-.12em A\kern-.1em X}}

%\def{\<#1>{$\langle${#1}$\rangle$}
%\newcommand{\cs}{\<cs>}
%\newcommand{\css}{\cs es}
\newcommand{\cs}{{\tt cs}}
\newcommand{\css}{\cs-es}
\newcommand{\CR}{$\langle${\sc cr}$\rangle$}
\newcommand{\tab}{$\langle${\sc tab}$\rangle$}
\newcommand{\ttvert}{{\tt\char'174 }\ignorespaces}
\newcommand{\allowhbreak}{\penalty0\hskip0pt}

\makeatletter
\newlength{\n@rmal@labelwidth}\setlength{\n@rmal@labelwidth}{\labelwidth}
\newlength{\n@rmal@labelsep}\setlength{\n@rmal@labelsep}{\labelsep}
\def\pseudobibliography#1{\setbox0=\hbox{#1}\list
  {\ifomit@biblabels \else [\arabic{enumi}]\fi}{\ifomit@biblabels
  \setlength{\labelwidth}{0pt}\setlength{\labelsep}{0pt}\else
  \settowidth\labelwidth{[#1]}\fi\leftmargin\labelwidth
  \advance\leftmargin\labelsep
  \ifomit@biblabels\else\usecounter{enumi}\fi}}
\def\endpseudobibliography{\endlist \global\omit@biblabelsfalse
  \setlength{\labelwidth}{\n@rmal@labelwidth}%
  \setlength{\labelsep}{\n@rmal@labelsep}}
\makeatother
\def\pseudocite#1{[#1]}

\begin{document}

\title{Typesetting Articles for the DECUS
    Proceedings with \LaTeX}
\author{Barbara N. Beeton\\
    \AMS\\
    Providence, Rhode Island}

\begin{abstract}
The \DProc\/ have traditionally been published from copy supplied by
the authors, prepared according to rules devised for typewritten
material.  The power of the computer typesetting language
\TeX,\footnotemark\ through the macro package \LaTeX, has
now been applied to this task, and a formatting package, named \DP,
has been submitted to the DECUS Program Library for use by authors who
have access to a working \TeX\ system.  (The \TeX\ program and related
software, created by Donald Knuth of Stanford, are in the public domain.)

This paper presents the important features of the \LaTeX\ implementation
of \DP\ and, through
examples, shows how it is to be used.  Use of \DP, which is
encouraged, will produce the author's work, nicely typeset, in the
standard {\sl\Proc\/} format.  There is a general description
of how the package works and of the mechanical requirements for camera
copy of {\sl\Proc\/} articles, which will be created on the
author's local output device.

No prior knowledge of \TeX\ or \LaTeX\ is required, but authors using \DP\ will
be expected to learn some rudiments, especially if their papers
contain special notation or formats such as tables.
\end{abstract}

%\begin{document}

\maketitle

\footnotetext[1]{\TeX\ is a trademark of the \AMS.}

The \DProc, like the conference proceedings of many other organizations,
is rushed to publication as quickly as possible so that the material
will reach the conference participants and other interested readers
before its value is diminished by time.  Reproducing author-prepared
copy eliminates the considerable bother and expense of typesetting,
proofreading and corrections.  The published document should be
compact, uniform in appearance, and readable, regardless of the kind
or quality of printing device available to the author.  For these
reasons, instructions to authors have heretofore assumed that nothing
more elaborate is available than an ordinary typewriter or dot matrix
printer.

To enforce uniformity, the author is provided with ``model paper'', on
which are printed (in non-reproducing ink) column and page borders,
alignment marks, and instructions for placement of title, author, and
the other parts of a proceedings article.  The dimensions of the model
paper are almost always larger than those of the published \Proc\Dash
this permits more text to be packed onto each page, and also improves
its appearance or ``quality'' when photographically reduced, smoothing
out the rough edges of letters and symbols generated by a typewriter,
dot-matrix printer or other ``low-resolution'' device.

Within the past few years, advances in laser-printer technology have
made good-quality output accessible to a growing number of users,
through a widening selection of low-cost output systems based on print
engines with 300 dot-per-inch resolution and (relatively) easy-to-use
interfaces.  Such devices have been attached to most kinds of DEC
computers, and drivers now exist to print the output from such programs
as Scribe,\footnote{Scribe is a trademark of Unilogic Ltd.}
\TeX\ and Troff.  Most low-end laser printers cannot use paper wider
than $8\sfrac1/2''$, however, so even if both a good composition
program and output printer had been available, until now an author
would have been discouraged from using them for mechanical reasons.

The editor of the \DProc\/ has now agreed to accept typeset copy
printed on such a system at 100\% on $8\sfrac1/2\times11''$ paper,
provided it conforms to the published format.  This article (which has
itself been produced by the technique it describes) introduces a
package, \DP, designed to prepare {\sl\Proc\/} articles using \LaTeX.

\newcommand{\Dag}{$^{\thinspace\dagger}$}
\newcommand{\1}[1]{{\let\\=\newline\parbox[t]{.177\hsize}{\raggedright#1}}}
\newcommand{\8}{\vrule height .9\baselineskip depth 0pt width 0pt\ignorespaces}
\newcommand{\9}{\vrule height 0pt depth .4\baselineskip width 0pt}
\newcommand{\KnS}{Kellerman\thinspace\&\thinspace Smith}
\begin{figure*}[p]
\begin{tabular}{|l|l|l|l|l|}                    \hline
\1{\8\9}& \multicolumn{1}{c}{DECSystem-10}
                & \multicolumn{1}{c}{DECSYSTEM-20}
                        & \multicolumn{1}{c}{VAX (Unix)}
                                & \multicolumn{1}{c}{VAX (VMS)} \\ \hline
\1{\8 Allied Linotronic\\L100, L300P\9}
        &       &       & \1{Textset}
                                & \1{Textset} \\ \hline
\1{\8 Apple LaserWriter\\ \9}
        &       &       & \1{Carleton University\\Textset\Dag}
                                & \1{Textset\Dag} \\ \hline
\1{\8 Autologic\\APS-5, Micro-5\9}
        &       & \1{Textset}
                        & \1{Textset}
                                & \1{Intergraph\Dag\\Textset} \\ \hline
\1{\8 Canon\\ \9}
        &       &       & \1{Canon} &   \\ \hline
\1{\8 Compugraphic\\8400, 8600\9}
        &       &       &       & \1{\KnS}      \\ \hline
\1{\8 DEC LN01\\ \9}
        &       &       & \1{Univ of Washington}
                                & \1{Louisiana State U} \\ \hline
\1{\8 DEC LN03\\ \9}
        &       &       &       & \1{DEC\\ \KnS} \\ \hline
\1{\8 Imagen\\ \9}
        & \1{Stanford\\Vanderbilt}
                & \1{SRI\\Columbia}
                        & \1{Univ of Maryland}
                                & \1{\KnS\Dag} \\ \hline
\1{\8 QMS Lasergrafix\\ \9}
        &       &       & \1{Textset\\Univ of Washington}
                        & \1{GA Technologies\\Texas A\&M\\Textset\9} \\ \hline
\1{\8 Symbolics\\ \9}
        &       & \1{Univ of Washington}
                        & \1{Univ of Washington}
                                & \1{UMass} \\ \hline
\1{\8 Talaris\\ \9}
        & \1{Talaris\Dag}
                & \1{Talaris\Dag}
                        & \1{Talaris\Dag}
                                & \1{Talaris\Dag} \\ \hline
\1{\8 Xerox Dover\\ \9}
        &       & \1{Carnegie-Mellon U}
                        & \1{Stanford}  & \\ \hline
\1{\8 Xerox 2700\\ \9}
        &       & \1{Ohio State U}
                        & \1{Ohio State U}      & \\ \hline
\1{\8 Xerox 9700\\ \9}
        & \1{Univ of Delaware}
                &       & \1{Univ of Delaware}
                                & \1{ACC\\Textset} \\ \hline
\end{tabular}
\par\vspace{2pt}
\mbox{\Dag\thinspace Graphics supported}
\vspace{-.5\baselineskip}
\caption[outdev]{Computer/output device combinations with \TeX\ interfaces}
\vspace{.5\baselineskip}
\label{outdev}
\end{figure*}
\newcommand{\site}[1]{\par \noindent \hangindent 20pt
                {\bf #1}\quad\ignorespaces}
\begin{table*}[p]
\hbox to\textwidth{%
\parbox[t]{.47\textwidth}{%
  Information regarding the interfaces shown here can be obtained
  from the individual listed below for the site.  This table and
  the names of the site contacts were provided by the \TeX\ Users Group.

\raggedright \hyphenpenalty=10000 \exhyphenpenalty=10000
\medskip
\site{ACC {\rm(Advanced Computer Communications)}} Diane~Cast, 805-963-9431

\site{Canon {\rm (Tokyo)}} Masaaki Nagashima, (03) 758-2111

\site{Carleton University} Neil Holtz, 613-231-7145

\site{Carnegie-Mellon University} Howard Gayle, 412-578-3042

\site{Columbia University} Frank da Cruz, 212-280-5126

\site{DEC {\rm(Digital Equipment Corp)}} John Sauter, 603-881-2301

\site{GA Technologies} Phil Andrews, 619-455-4583

\site{Intergraph} Mike Cunningham, 205-772-2000

\site{\KnS} Barry Smith, 503-222-4234

}%              end \parbox
\hfill
\parbox[t]{.47\textwidth}{%
\raggedright \hyphenpenalty=10000 \exhyphenpenalty=10000
\site{Louisiana State University} Neil Stoltzfus, 504-388-1570

\site{Ohio State University} John Gourlay, 614-422-6653

\site{SRI}

\site{Stanford}

\site{Talaris} Sonny Burkett, 619-587-0787

\site{Texas A\&M} Bart Childs, 409-845-5470

\site{Textset} Bruce Baker, 313-996-3566

\site{University of Delaware} Daniel Grim, 302-451-1990

\site{University of Maryland} Chris Torek, 301-454-7690

\site{University of Massachusetts} Gary Wallace, 413-545-4296

\site{University of Washington} Pierre MacKay, 206-543-2386

\site{Vanderbilt University} H. Denson Burnum, 615-322-2357

}%              end \parbox
}%              end \line
\end{table*}

\section{What is \TeX? What is \LaTeX?}

\TeX\ is a public-domain typesetting language created by Donald Knuth
of Stanford University.  His original aim was to typeset his own books,
in particular {\sl The Art of Computer Programming\/} \cite{ACP}, with
a quality equal to that produced by the best traditional composition
methods.  The technical content of these books assured that full
attention was given to the niceties of formatting mathematical
expressions, as well as to the structures of documents commonly
encountered in technical publishing.

\TeX\ deals with low-level concepts familiar to typesetters\Dash type
size, leading, interword spacing and kerning.  It does not incorporate
directly the structures an author encounters when writing a paper\Dash
title, figure references, bibliographic entries.  However, \TeX\ is
essentially a macro compiler, and provides a full vocabulary of low-level
functions that can be manipulated by knowledgeable users to create
higher-level packages to support the casual user.

One such macro package is \LaTeX.  \LaTeX\ \cite{LT} is
a powerful document formatter, providing the capability to format
books and reports, with functionality similar to that provided by
Scribe.

\section{The \DP\ macro package}

In order to use this implementation of the \DP\ macro package, the
author of a \DProc\/ article must have available a working \LaTeX\ system,
which presupposes a working \TeX\ system.
\TeX\ has been implemented on \VAX es and DECsystem-10s and -20s
under the standard operating systems.
There is also a good selection of output devices available, capable
of production output of quality suitable for the {\sl\Proc\/};
Table~\ref{outdev}
shows the computer/output device combinations known to the \TUG.
(\TeX\ has not, however, been implemented on PDP-11s, since
it requires a larger address space than is supported on those machines.)

\LaTeX\ may not be available to all \TeX\ users.  (\TeX\ is a very large
program by itself, and routinely adding a large macro package can put
unwelcome strain on an already overloaded machine.  Some system
administrators prefer not to give their users that opportunity.)
An earlier implementation of \DP\ does not require \LaTeX, but only
\TeX\ itself; it was
described in \cite{DP}, and the supporting files are on the Fall~'85
DECUS Program Library tapes for Languages \& Tools, Large Systems, and \VAX.

The present \LaTeX-based version of this macro package
is called \verb|DEPROC.STY|, for ``\DProc\/ style file''.  It is
an ordinary ASCII file, and has been submitted to the Spring~86 DECUS
Program Library for the same systems listed above.

\section{Some preliminary \TeX nical information}

An author who intends to use the \LaTeX\ version of \DP\ should
preferably have used \LaTeX\ already.  Nonetheless, a few basic
concepts are worth repeating.  (\LaTeX\ is identical to \TeX\ in
many ways.  The following discussion will specify \LaTeX\ only when
there is a difference.)

\subsection{Spacing}

\TeX\ uses different spacing rules in text (paragraphs) and math.
Paragraphs are set so that interword spacing is as uniform as possible.
Wider spaces are set after punctuation that indicates the ends of
sentences (period, !\ and ?).  Within math, the best traditions for
arranging symbols in two dimensions, including proper spacing, are
observed.  Thus input spacing is largely ignored, except
for its functions of separating words and marking the boundaries of
certain kinds of expressions.  \TeX\ considers
multiple spaces in an input file to be equivalent to a single space.
The carriage return \CR\ and the tab character \tab\ are equivalent
to ordinary spaces, except in special environments (noted below).
And all spaces at the beginning of any line are ignored.

\subsection{Paragraph breaks}

A blank line in the input file indicates a paragraph break.  A line is
blank if it contains only a \CR\ or spaces and a \CR.  Multiple blank
lines are equivalent to a single blank line.  (A paragraph can also be
indicated by \verb|\par|; terms beginning with \verb|\| are described below.)

\subsection{Comments}

A comment may be entered on any line; a comment begins with a \verb|%| sign:
\begin{verbatim}
%  This line contains nothing but a comment.
\newcommand{\cs}{...}%  explanatory comment
... Smythe % ***** check spelling *****
\end{verbatim}
\TeX\ will ignore the \verb|%| and everything following it, including the \CR.
Thus, the space ordinarily indicated by the \CR\ will be suppressed,
and if a space is really wanted between the last item before a comment
and the first item on the next line, it must be input before the \verb|%|.
Conversely, if no space is wanted between the last item on a line and
the first item on the next, a \verb|%| can be used to suppress it
intentionally.

\subsection{Control sequences, also called macros}

A ``control sequence'' \cs\ is an instruction for \TeX\ to perform
some action or to produce a particular symbol.  A \cs\ begins with a
backslash, \verb|\|.  There are two types of \css:
\begin{itemize}
\item[--] A ``control word'' consists of \verb|\| followed by one or more
        letters.  It is terminated by any non-letter, including a space;
        multiple spaces follow the usual compression rule, so a
        special technique (see next paragraph) is required to create an
        output space after a control word.  \verb|\TeX| is an example of
        a control word; it produces the \TeX\ logo.
\item[--] A ``control symbol'' consists of \verb|\| followed by exactly one
        non-letter.  Since its length is known, no special terminator
        is required.  \verb|\&| is a control symbol to produce an \&.
        \verb*|\ | (\verb|\| followed by a space) is an explicit space, to
        be used where an output space should follow an element
        input as a control word.
\end{itemize}

\noindent
New \css\ can be defined within a document to make input easier or clearer.
A few principles governing \cs\ names should be observed carefully.
\begin{itemize}
\item[--] Case matters; \verb|\csname| is not the same as
        \verb|\Csname| or \verb|\CSName|.
        Try to pick a name that means something to you, and is easy to type.
\item[--] Don't try to redefine an existing \cs\ name unless you really
        know what you're doing; results, as they say, ``may be unpredictable''.
\item[--] Never define or redefine any \cs\ whose name begins with
        `\verb|\end|'.
\end{itemize}

\noindent
To define a new command,
\begin{verbatim}
\newcommand{\csname}{...something...}
\end{verbatim}
If the name has been used before, \LaTeX\ will stop and report an
error.  If you are really adamant about re-using this name,
\begin{verbatim}
\renewcommand{\csname}{...something...}
\end{verbatim}
will assign it the new meaning.

The control symbols \verb|\0,...,\9| always start out undefined, so they are
available for transient use without checking.

A \cs\ with arguments is defined by
\begin{verbatim}
\newcommand{\csname}[2]{...#1...{#2}...}
\end{verbatim}
with the number of arguments given in brackets as shown; for details,
see \cite{LT}.

\subsection{Math}

Mathematical expressions are input between \verb|\(...\)|.  Display
math is begun and ended with \verb|\[...\]|.  For details of math
input, see \cite{LT}.
%(Math input is also described in \cite{FG} and \cite{TB}, in
%increasing order of complexity of expressions handled.)

\section{Starting a \DProc\/ article}

The first step in preparing an article is to create a file.
The first two lines in this file should be
\begin{verbatim}
\documentstyle{deproc}
\begin{document}
\end{verbatim}
This will cause the formatting definitions to be loaded when the file
is input to \LaTeX.

Next, enter the ``top matter''.  This consists of such
things as the title of the article, the author(s) and their addresses,
and the abstract.

\subsection{Title and authors}

For an article with a short title and one author, the input looks like this:
\begin{verbatim}
\title{A One-Line Title}
\author{Author Name\\
    Author's Organization\\
    City, State}
\end{verbatim}
The double backslashes \verb"\\" indicate line breaks.  This technique is
also used to break up long titles:
\begin{verbatim}
\title{Here We Have a Particularly
    Long Title\\That Can't Possibly
    Fit on a Single Line}
\end{verbatim}
This will be set (in a boldface font slightly larger than text size) as\strut
\begin{center}
        \bf Here We Have a Particularly Long Title\\
        That Can't Possibly Fit on a Single Line
\end{center}
Notice that the way the lines are broken in the input file is not how
they appear in the output\Dash only \verb"\\" matters to \TeX.
Actually, \TeX\ will break long titles into lines short enough to fit
on the page, but a multi-line title usually makes more sense to the reader
if the author decides where the line breaks should occur.

For multiple authors, the same \verb"\author" tag is used with
\verb"\and" or \verb"\And":
\begin{verbatim}
\author{First Author
  \and
    Second Author\\
    Common Organization\\
    City, State}
\end{verbatim}
or
\begin{verbatim}
\author{First Author\\
    First Organization\\
    City, State
  \And
    Second Author\\
    Second Organization\\
    City, State}
\end{verbatim}
and so forth, which will appear thus in the output:\strut
\begin{center}
        {\bf First Author\enspace{\rm and}\enspace Second Author}\\
        Common Organization\\
        City, State
\end{center}
\par\noindent
or\strut
\begin{center}
        \interlinepenalty=10000
        {\bf First Author}\\
        First Organization\\
        City, State\\
        \hspace{10pt}\\
        {\bf Second Author}\\
        Second Organization\\
        City, State\endgraf
\end{center}
%\noindent
Authors' names (the first line, and the first line after \verb"\And") are
printed in boldface; if an author name is to appear on any other line,
begin that line with \verb"\bf" (the \TeX\ instruction for boldface type).

The title and author of the present paper look like this in the file:
\begin{verbatim}
\title{Typesetting Articles for the DECUS
    Proceedings with \LaTeX}
\author{Barbara N. Beeton\\
    \AMS\\
    Providence, Rhode Island}
\end{verbatim}
One item to look at here is \verb"\AMS", which becomes \AMS\ in the output.
This is an example of a ``local definition'', something that is not likely
to be useful to anyone else, but can save the author a lot of time correcting
typing errors.  Local definitions that are used throughout an article are
best input right after specifying the document style:
\begin{verbatim}
\documentstyle{deproc}
\newcommand{\AMS}{American
           Mathematical Society}
...
\begin{document}
\end{verbatim}

\subsection{Abstract}

The abstract is the final part of the top matter.
\begin{verbatim}
\begin{abstract}
This is a short summary of what
the article is about.
\end{abstract}
\end{verbatim}
\par\noindent
The heading ``{\bf Abstract}'' is provided automatically; don't input it.
The abstract may contain more than one paragraph.  Paragraphs are
separated by a blank line or by \verb"\par", as usual.

The top matter is now complete.  The body of the article follows.
\begin{itemize} \parskip=0pt \itemsep=0pt
\item[] \verb"\maketitle"
\item[] (\it{Text of footnotes to the top matter is given here\/})
\item[] {}
\item[] \verb"This is the first sentence of article text."
\item[] \verb"..."
\item[] \verb"\end{document}"
\end{itemize}

\section{The body of the article}

An article can start out with text or with a heading.
Three levels of headings are provided by \DP:
\begin{verbatim}
\section{Section heading}
\subsection{Subsection heading}
\subsubsection{Subsubsection heading}
\end{verbatim}
These produce headings (with extra space above and below, not shown here)
in the following styles:
$$\vbox{\advance\baselineskip by 2pt
\centerline{\bf Section heading}
\leftline{\bf Subsection heading}
\leftline{\it Subsubsection heading}}
$$

The first paragraph following a heading will not be indented in the
default style.  Other paragraphs will be indented a standard amount.
To suppress indentation on a single paragraph, precede it by \verb"\noindent".

\subsection{Footnotes}

A footnote consists of two parts, the mark and the text.  These
are usually entered as a unit\footnote{Like this.}:
\begin{verbatim}
... as a unit\footnote{Like this.}:
\end{verbatim}
This is equivalent to the two statements\footnotemark
\footnotetext{Or this.}
\begin{verbatim}
... two statements\footnotemark
\footnotetext{Or this.}
\end{verbatim}
The two-statement form must be used for footnotes in the title or
abstract and in ``boxed'' environments
 (which will not be explained here; see
\cite{LT} for details).  In such cases, the \verb"\footnotetext" should
be specified as soon as possible after completion of the special
environment.

Footnotes are automatically numbered sequentially starting with 1.
Numbers may also be given explicitly, between \verb"[...]"
following the \verb"\footnote..." command.  In most contexts, this is
optional, but for footnotes in abstracts or in ``boxed'' environments,
the number {\sl must\/} be given for the \verb"\footnotetext"; the
first footnote in this article was produced by the following:
\begin{verbatim}
\maketitle
\footnotetext[1]{\TeX\ is a trademark
       of the \AMS.}
\end{verbatim}

Footnote numbers can be reset if necessary by
\begin{itemize}
\item[] \verb"\resetcounter{footnote}{"{\it integer\/}\verb"}"
\end{itemize}

\subsection{Quotations}

Short quotations, of less than a paragraph, are set with
\begin{verbatim}
\begin{quote}
If you can't fix it, ... {\em Button}
\end{quote}
\end{verbatim}
and look like this:
\begin{quote}
If you can't fix it, call it a feature. \ {\em Button}
\end{quote}

\noindent
For longer quotations, use
\begin{verbatim}
\begin{quotation}
...
\end{quotation}
\end{verbatim}
in a similar manner, separating paragraphs with blank lines as usual.

\subsection{Lists}

Itemized and enumerated lists occur in many \DProc\/ articles.
\LaTeX\ provides automatic counters and up to four levels of nesting.
Here is a short example of a two-level itemized list.
\begin{verbatim}
\begin{itemize}
  \item first item
  \item second item
 \begin{itemize}
   \item new level
   \item one more
 \end{itemize}
  \item back a level
\end{itemize}
\end{verbatim}
\par\noindent
Here's what the output looks like, after padding out the text a bit to show
how longer items look.
\begin{itemize}
\item The first item in this list isn't particularly interesting,
        but it has to be long enough to make two lines.
\item The second item isn't either.
\begin{itemize}
\item Even going to a new level doesn't add very much
        excitement to this exercise.
\item We'll do one more at this level.
\end{itemize}
\item Then we'll go back a level to finish things off.
\end{itemize}
%\noindent
If \verb"{enumerate}" is specified instead of \verb"{itemize}", the
items will be numbered\Dash 1, 2,\dots\ at the first level,
a, b,\dots\ at the second level.  If the default labels aren't what
you want, an overriding label may be specified, for example,
\mbox{\verb"[--]"} (used in Figure~\ref{figtype}).  Each item
comprises one paragraph; an unlabeled paragraph can be produced by
specifying an empty label.  Extra space above and below a list is
provided automatically.

\begin{figure}[t,b]
\hrule
\begin{itemize}
\item[--] Small figures which can be set in place, i.e., in the same
        relative position where they occur in the input file
\item[--] One-column figures to be set at the top or bottom of the
        first available column
\item[--] Double-column figures to be set at the top or bottom of the
        first available page
\item[--] Full-page figures
\end{itemize}
\vspace{-.5\baselineskip}
\caption[figtype]{Possible figure formats}
\vspace{.5\baselineskip}
\hrule
\label{figtype}
\end{figure}

\subsection{Figures}

Figures come in the sizes, shapes and page locations listed in
Figure \ref{figtype}.  Not all these formats are supported yet by \DP\@.
In particular, two-column figures cannot be placed at the
bottom of text pages.

\subsubsection{One-column figures}

To get a single-column figure, enter
\begin{itemize} \parskip=0pt \itemsep=0pt
\item[] \verb"\begin{figure}["{\it loc\/}\verb"]"
\item[] {\it content of figure}
\item[] \verb"\caption{Caption text}"
\item[] \verb"\label{"{\it label\/}\verb"}"
\item[] \verb"\end{figure}"
\end{itemize}
\par\noindent
{\it loc\/} is the location where the figure is to be placed, specified
by one to four letters (in the order in which you find the possible
locations suitable), as follows:
\begin{itemize}
\item[\verb"h"] here, at the position in the text where the figure is input.
\item[\verb"t"] at the top of a text page.
\item[\verb"b"] at the bottom of a text page.
\item[\verb"p"] on a page of ``floats''.
\end{itemize}
\par\noindent
The default {\it loc\/} is \verb"tbp"; note that figures will not be
placed in-line unless \verb"h" is indicated explicitly.  For
additional details, see \cite{LT}.

Figures are numbered automatically.  The optional {\it label\/} is
provided to permit references in the text to the figure:
\begin{itemize}
\item[] \verb"... shown in Figure~\ref{"{\it label\/}\verb"}"
\end{itemize}

To reserve space for figures which will be prepared separately,
use the command \verb"\vspace{"{\it dimension\/}\verb"}".
Some space is automatically skipped above and below a figure, and also
between the figure and the caption, so the dimension given with
\verb"\vspace" should be precisely the height of the item to be pasted in.

\subsubsection{Two-column figures}

Double-column figures can be placed either at the top of a text
page or on a separate page of ``floats''.  The command syntax is the same
as for one-column figures, except that the ``star'' notation
\verb"\begin{figure*}...\end{figure*}" is used.

\subsubsection{Full-page figures}

Full-page figures are a special case of two-column figures,
specified by \verb"\begin{figure*}[p]...\end{figure*}".  A full-page
figure will be placed on the first available page.  If space is to
be reserved for insertion of a separately-prepared figure, use the
\verb"\vspace" command with a suitably large dimension; \verb"8.5in"
should be sufficient.

\subsection{Tables}

\LaTeX\ contains powerful table-formatting capabilities.  However, since
their use is specialized and the rules somewhat complex, specifics
are not presented here; see \cite{LT} for details.

\subsection{Verbatim}

Verbatim items are printed in so-called ``typewriter'' style, using \TeX's
\verb"\tt" font.  In-text verbatim items are preceded by the command
\verb"\verb" and enclosed within a pair of identical characters which
do not occur within the verbatim string (except a space, a letter,
or \verb"*"), for example, vertical bars \verb"|...|" or ditto marks
\verb|"..."|.  Blocks of verbatim code are delimited by
\begin{itemize} \parskip=0pt \itemsep=0pt
\item[] \verb"\begin{verbatim}"
\item[] \verb"..."
\item[] \verb"\end{verbatim}"
\end{itemize}
\verb"\begin{verbatim}" and \verb"\end{verbatim}" should be on lines
by themselves.  Within verbatim
mode, \CR s are obeyed as line breaks, not spaces.  An input line that is too
long for the current column width will be broken at a space if possible,
and the remainder of the line hanging indented on the next output line;
since this may change the meaning of the verbatim passage, such passages
should be checked with special care in the output.  Overlong lines also
frequently result in overfull \verb"\hbox"es, which are listed in the
transcript file.  To mark overfull \verb"\hbox"es clearly on the printed
output (with black boxes: \rule{5pt}{\ht\strutbox}\thinspace), specify
\begin{verbatim}
\documentstyle [draft]{deproc}
\end{verbatim}
at the beginning of your input file.
%{\vrule height\ht\strutbox depth\dp\strutbox width 5pt }\thinspace.
The \verb"draft" option can easily be removed when you are ready to
prepare the final copy.

A passage occurring between \verb"\begin{verbatim}..."\allowhbreak
\verb"\end{verbatim}"
is treated as a unit by \LaTeX\Dash if it is too long for the vertical
space available, it either will be carried over as a unit to the next
column or page, or will result in an overfull \verb"\vbox", which will
be noted only in the transcript of the \LaTeX\ run.  In such a case,
the best remedy is to break the passage in two, by inserting another
\verb"\end{verbatim} \begin{verbatim}".

Verbatim mode is suitable for program listings, indicating keyboarding
instructions, file names, and similar uses.

\subsection{References, bibliography}

References in text to items in the bibliography are input as
\begin{itemize}
\item[] \verb"\cite{"{\it label\/}\verb"}"
\item[] \verb"\cite["{\it text\/}\verb"]{"{\it label\/}\verb"}"
\end{itemize}
where the label is the same as that specified for the item in the bibliography.
For a label ``ABC'', the reference will be rendered \pseudocite{ABC}.
See \cite[pp.~73, 189]{LT} for further details.

References may also be made to figures, tables, or anything else for which
you have established a label:
\begin{itemize}
\item[] \verb"\ref{"{\it label\/}\verb"}"
\item[] \verb"\pageref{"{\it label\/}\verb"}"
\end{itemize}
\verb"\pageref" is not immediately useful\Dash the page numbers
generated by \TeX\ will not be the same as those assigned when the
collection is put together in the editorial office.  This feature would
become useful if it ever becomes possible to submit articles electronically,
as \LaTeX\ input files.

Before you start to input the reference list, some housekeeping is
required\Dash you must decide what you want the list to look like.
This is what the input looks like for one of the items in the reference
list at the end of this article:
\begin{verbatim}
\bibitem[TB]{TB} Knuth, Donald E., \TB,
    Addison-Wesley and \AMS, 1984.
\end{verbatim}
(\verb"\TB" and \verb"\AMS" are among the local definitions for this article.)
Default output looks like this:
\smallskip
{\begin{pseudobibliography}{ACP}
\bibitem[TB]{TB} Knuth, Donald E., \TB, Addison-Wesley and \AMS, 1984.\endgraf
\end{pseudobibliography}
}
\smallskip

Labels may also be omitted, or numbered sequentially.  Begin the
reference list with this command:
\begin{itemize}
\item[] \verb"\begin{thebibliography}{"{\it widest label\/}\verb"}"
\end{itemize}
This will generate the {\bf References} section heading, and establish
the item indentation, using the width of the specified label.

If you do not wish to use labels, substitute \verb"\omit" for the widest
label.  (The \verb"{...}" are still required in the context of
\verb"\bibitem".)
\begin{verbatim}
\bibitem{} Knuth, Donald E., ...
\end{verbatim}
will result in
\par\nobreak\smallskip
{\begin{pseudobibliography}{\omit}
\bibitem{} Knuth, Donald E., \TB, Addison-Wesley and \AMS, 1984.\endgraf
\end{pseudobibliography}
}
\smallskip
\noindent Note that \verb"\cite" cannot be used if references are unlabeled.

If your labels are numeric, no labels need be entered\Dash items will
automatically be numbered sequentially.  However, the widest label
must be specified at the beginning of \verb"thebibliography" environment.
The input
\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{TB} Knuth, Donald E., ...
\end{verbatim}
will now look like this:
\par\nobreak\smallskip
{\begin{pseudobibliography}{99}
\bibitem[2]{TB} Knuth, Donald E., \TB, Addison-Wesley and \AMS, 1984.\endgraf
\end{pseudobibliography}
}

\section{Caveats}

\DP\ and this article were created on a DECSYSTEM-20 at the
\AMS, running \LaTeX\ version~2.08 under
\TeX\ version~1.3.  The AMS installation is standard in all ways.

With one exception, none of the changes to the \TeX\ program since
version~1.0 should have any noticeable effect on an article produced
with \DP.  The exception is large, complex tables\Dash
tables incorporating many boxes and rules require large amounts of
\TeX\ memory.  Memory management was radically changed in version~1.3
to make more memory available to the user without actually changing
the physical memory allotment.  (Otherwise, if you run out of memory,
the most likely cause is an input error.)

Although thorough testing has been attempted, no one outside the AMS has
tried to use \DP\ yet, so bugs are sure to be found.  In fact,
the version of \DP\ first placed in the Program Library should best
be considered a beta test version.  If you find a bug, please
communicate it to the author, accompanied by an example which
demonstrates the bug as simply as possible.  Suggestions for
improvements are also welcome.  Send everything to\break
{\obeylines %
        \indent Barbara Beeton
        \AMS
        \POBox 6248
        Providence, RI 02940
}

%\Bibliography{ACP}
\begin{thebibliography}{ACP}

\bibitem[DP]{DP} Beeton, Barbara, Typesetting articles for the DECUS
        Proceedings with \TeX, {\sl Proceedings of the Digital Equipment
        Computer Users Society}, USA Spring 1985, 349--356.

\bibitem[ACP]{ACP} Knuth, Donald E., {\sl The Art of Computer Programming},
        Addison-Wesley, Vol.~2, second edition, 1981.

\bibitem[TB]{TB} Knuth, Donald E., \TB, Addison-Wesley and \AMS, 1984.

\bibitem[LT]{LT} Lamport, Leslie, {\sl L\kern-.36em\raise.3ex\hbox{\small A}%
        \kern-.15em\TeX, A document preparation system}, Addison-Wesley,
        1985.

\bibitem[TD]{TD} Southall, Richard, First principles of typographic design
        for document production, {\sl\tub\/} Vol.~5 (1984), No.~2, 79--90;
        Corrigenda, Vol.~6 (1985), No.~1, p.~6.

\bibitem[TUB]{TUB} {\sl\tub, the Newsletter of the \TUG}, \TUG, \careof\AMS,
        \POBox 9506, Providence, RI, 02940.

\end{thebibliography}

\end{document}

### 2013-06-18 prince/base/content/dialogs/EdDialogCommon.js
Interim commit so I can do a merge

@@ -361,7 +361,7 @@ function getColor(ColorPickerID)
     if (color && color == "")
       return null;
     // Clear color so next if it's called again before
-    //  color picker is actually used, we dedect the "don't set color" state
+    //  color picker is actually used, we detect the "don't set color" state
     colorPicker.setAttribute("color","");
   }
 
@@ -386,6 +386,7 @@ function setColorWell(ColorWellID, color)
     {
       colorWell.removeAttribute("default");
       // Use setAttribute so colorwell can be a XUL element, such as button
+      colorWell.setAttribute("color", color);
       colorWell.setAttribute("style", "background-color:"+color);
     }
   }

### 2013-06-18 prince/base/content/dialogs/msiEdDialogCommon.js

@@ -332,7 +332,7 @@ function getColor(ColorPickerID)
     if (color && color == "")
       return null;
     // Clear color so next if it's called again before
-    //  color picker is actually used, we dedect the "don't set color" state
+    //  color picker is actually used, we detect the "don't set color" state
     colorPicker.setAttribute("color","");
   }
 
@@ -362,6 +362,7 @@ function setColorWellControl(colorWell, color)
     {
       colorWell.removeAttribute("default");
       // Use setAttribute so colorwell can be a XUL element, such as button
+      colorWell.setAttribute("color", color);
       colorWell.setAttribute("style", "background-color:"+color);
     }
   }

### 2013-06-18 prince/base/content/dialogs/EdInsertTable.js
Interim commit so I can do a merge

@@ -42,6 +42,7 @@ var gTableColor;
 var gTableCaptionPlacement;
 var gTableBaseline = "baseline";
 var gBorderCollapse = "collapse";  //This should be the default???
+var gTableCaptionElement;
 
 var gCollatedCellData;
 var gCellChangeData;
@@ -52,6 +53,53 @@ var gSelectionTypeStr = "Cell";
 var gApplyUsed = false;
 var gIsMatrix = false; //We have to set this in the initialization code.
 var data = null;
+
+function initGDialogObject()
+{
+  gDialog.rowsInput      = document.getElementById("rowsInput");
+  gDialog.columnsInput   = document.getElementById("columnsInput");
+  gDialog.widthInput     = document.getElementById("widthInput");
+  gDialog.autoCheckbox   = document.getElementById("autoWidthCheckbox");
+  gDialog.CellHeightInput= document.getElementById("CellHeightInput");
+  gDialog.CellWidthInput = document.getElementById("CellWidthInput");
+  gDialog.currentunits   = document.getElementById("currentunits");
+  gDialog.unitMenulist   = document.getElementById("unitMenulist");
+  gDialog.wrapping       = document.getElementById("TextWrapCheckbox");
+  gDialog.vAlignChoices  = document.getElementById("vAlignChoices");
+  gDialog.hAlignChoices  = document.getElementById("hAlignChoices");
+  gDialog.BordersPreviewCenterCell = document.getElementById("BordersPreviewCenterCell");
+  gDialog.BorderSideSelectionList = document.getElementById("BorderSideSelectionList");
+  gDialog.CellBorderStyleList = document.getElementById("cellBorderStyleList");
+  gDialog.CellBorderWidthList = document.getElementById("cellBorderWidthList");
+  gDialog.borderCW = document.getElementById("borderCW");
+
+  gDialog.OkButton = document.documentElement.getButton("accept");
+  gDialog.sizeLabel = document.getElementById("sizeLabel");
+  gRows = gDialog.rowsInput.value;
+  gColumns = gDialog.columnsInput.value;
+}
+
+function initUnitHandler()
+{
+  unitHandler = new UnitHandler();
+  var fieldList = [];
+  fieldList.push(gDialog.CellHeightInput);
+  fieldList.push(gDialog.CellWidthInput);
+  fieldList.push(gDialog.widthInput);
+  unitHandler.setEditFieldList(fieldList);
+  if (gPrefs)
[…]

### 2013-06-18 prince/base/content/dialogs/msiEdTableProps.js

@@ -1,6 +1,8 @@
 /* ***** BEGIN LICENSE BLOCK *****
  Copyright 2009 MacKichan Software, Inc. *
  * ***** END LICENSE BLOCK ***** */
+"use strict";
+
 Components.utils.import("resource://app/modules/unitHandler.jsm"); 
 
 
@@ -31,6 +33,8 @@ var gColCount = 1;
 var gLastRowIndex;
 var gLastColIndex;
 var gNewRowCount;
+var unitHandler;
+var newTable;
 //var gNewColCount;
 //var gCurRowIndex;
 //var gCurColIndex;
@@ -57,8 +61,22 @@ From C++:
                           Note: This is the value if all rows (thus all cells) are selected
  3 TABLESELECTION_COLUMN All cells are in 1 or more columns
 */
+var gCellID = 12;
 
 //var gSelectedCellCount = 0;
+var gOurCellData;
+var gInitialCellData;
+var gCollatedCellData = {};  //This starts out as the same as the previous, but changes as the user makes selections in the dialog.
+var gColElementArray;
+var gRowElementArray;
+
+var gTableColor;
+var gTableCaptionPlacement;
+var gTableBaseline = "baseline";
+var gBorderCollapse = "collapse";  //This should be the default???
+
+var gCellChangeData;
+var gTableChangeData;
 var gCurrentSide = "";
 var gBorderSides = ["top", "right", "bottom", "left"];
 
@@ -83,6 +101,112 @@ var data;
 
 // dialog initialization code
 
+function MakePersistsValue(elt)
+{
+  elt.setAttribute("value", elt.value);
+}
+
+function SelectSize(cell)
+{
+  gColumns  = (gCellID % 10);
+  gRows     = Math.ceil(gCellID / 10);
+
+  gDialog.rowsInput.value    = gRows;
+  gDialog.columnsInput.value = gColumns;
+
+  DisplaySize();
+}
+
+
+function DisplaySize()
+{
+  var i, anyCell;
+  for (i = 1; i < 80; i += 10)
+  {
+    anyCell = document.getElementById("c"+i);
+    while (anyCell)
+    {
+      anyCell.removeAttribute("mark");
+      anyCell = anyCell.nextSibling;
+    }
+  }
+
+  var numCellID;
+  numCellID = Math.min(gRows-1,7)*10 + Math.min(gColumns,8);
+  for (i = numCellID; i > 0; i -= 10)
+  {
[…]

### 2013-08-26 toolkit/components/Compute/computelib/SNode.cpp
Fix 2873

@@ -334,7 +334,7 @@ void FenceToMatrix(SEMANTICS_NODE * operand)
       brover = brover->next;
     }
 
-    if (n_cols > 1) {
+    if (n_cols > 1){
       operand->semantic_type = SEM_TYP_TABULATION;
       operand->nrows = n_rows;
       operand->ncols = n_cols;

### 2014-03-11 editor/libeditor/base/nsEditorUtils.cpp
Fix 3104

@@ -217,6 +217,7 @@ nsEditorUtils::IsDescendantOf(nsIDOMNode *aNode, nsIDOMNode *aParent, PRInt32 *a
   
   do
   {
+    if (!node) return PR_FALSE; // jcs
     res = node->GetParentNode(getter_AddRefs(parent));
     if (NS_FAILED(res)) return PR_FALSE;
     if (parent == aParent) 

### 2014-04-05 prince/base/content/prince.js
Commented out latex post-processing. Not sure we need it anymore.

@@ -1289,17 +1289,17 @@ function documentToTeXString(document, xslPath)
     xsltProcessor.importStylesheet(doc);
     var newDoc = xsltProcessor.transformToDocument(document);
     strResult = newDoc.documentElement.textContent || "";
-    while (strResult.search(/\n[ \t]+/) >= 0)
-		  strResult = strResult.replace(/\n[ \t]+/,"\n","g");
-    while (strResult.search(/\n\n/) >= 0)
-      strResult = strResult.replace(/\n\n/,"\n","g");
-	  while (strResult.search(/\\par[ \t]*\n/) >= 0)
-		  strResult = strResult.replace(/\\par[ \t]*\n/,"\n\n", "g");
-
-    while (strResult.search(/\\par[ \t\n]+/) >= 0)
-		  strResult = strResult.replace(/\\par[ \t\n]+/,"\n\n", "g");
-    while (strResult.search(/\\msipar[ \t\n]+/) >= 0)
-		  strResult = strResult.replace(/\\msipar([ \t\n]+)/,"\\par$1", "g");  
+//     while (strResult.search(/\n[ \t]+/) >= 0)
+// 		  strResult = strResult.replace(/\n[ \t]+/,"\n","g");
+//     while (strResult.search(/\n\n/) >= 0)
+//       strResult = strResult.replace(/\n\n/,"\n","g");
+// 	  while (strResult.search(/\\par[ \t]*\n/) >= 0)
+// 		  strResult = strResult.replace(/\\par[ \t]*\n/,"\n\n", "g");
+// 
+//     while (strResult.search(/\\par[ \t\n]+/) >= 0)
+// 		  strResult = strResult.replace(/\\par[ \t\n]+/,"\n\n", "g");
+//     while (strResult.search(/\\msipar[ \t\n]+/) >= 0)
+// 		  strResult = strResult.replace(/\\msipar([ \t\n]+)/,"\\par$1", "g");  
 		//while (strResult.search(/\\par/) >= 0)
 		//  strResult = strResult.replace(/\\par/,"\n\n", "g");
     if (compiler === "pdflatex")  //convert utf-8 characters to tex strings

### 2014-05-13 widget/src/xpwidgets/nsPrintOptionsImpl.cpp
Fixing direct print preview on Windows

@@ -173,7 +173,7 @@ nsPrintOptions::ShowPrintSetupDialog(nsIPrintSettings *aPS)
 
   return wwatch->OpenWindow(parent,
                             "chrome://global/content/printPageSetup.xul",
-                            "_blank","chrome,modal,centerscreen", array,
+                            "_blank","chrome, resizable, centerscreen", array,
                             getter_AddRefs(newWindow));
 }
 

### 2014-08-19 prince/base/content/prince.js
Add possibility of xslt post-pretex

@@ -440,14 +440,54 @@ function openTeX()
 		     dump("\nexe  = "  + exefile);
          dump("\narg paths = " + dataDir.path + "\n   " + fp.file.path + "\n    " + outfile.path + "\n     " + outdir.path);
          dump(ex+"\n");
-    }      
+    }
+      
 //  TODO BBM todo: we may need to run a merge program to bring in processing instructions for specifying tag property files
     if ((outfile) && (outfile.path.length > 0))
-    {      
-      msiEditPage(msiFileURLFromFile(outfile), window, false, false);
+    { 
+      var xsltProcessor = setupInputXSLTproc();
+      var parser = new DOMParser();
+      var xmlDoc = document.implementation.createDocument("", "", null);
+      xmlDoc.async = false;
+      var url = msiFileURLFromFile(outfile);
+      var request = Components.classes["@mozilla.org/xmlextras/xmlhttprequest;1"].createInstance();
+      request.QueryInterface(Components.interfaces.nsIXMLHttpRequest);
+      request.open("GET", url.spec, false);
+      request.send(null);
+      var res = request.responseXML;
+      var newDoc = xsltProcessor.transformToDocument(res);
+      
+      var outputStream = Components.classes["@mozilla.org/network/file-output-stream;1"].createInstance(Components.interfaces.nsIFileOutputStream);
+      var fileMode = 0x22;  //MODE_WRONLY|MODE_TRUNCATE - rewrite the file
+      var permissions = 0x777; //all permissions for everybody?
+      outputStream.init(outfile, fileMode, permissions, 0);
+      var serializer = new XMLSerializer();
+      serializer.serializeToStream(newDoc, outputStream, "utf-8");
+      outputStream.close(); 
+      
+      msiEditPage(url, window, false, false);
     }
   }                  
 }
+
+function setupInputXSLTproc()
+{
+  var xslFileURL = "chrome://ptprince/content/ptprince.xsl";
+  var xsltStr = getXSLAsString(xslFileURL);
+  var xsltProcessor = new XSLTProcessor();
+
+  try
+  {
+    var parser = new DOMParser();
+    var xslDoc = parser.parseFromString(xsltStr, "text/xml");
+    xsltProcessor.importStylesheet(xslDoc);
+  }
+  catch(e)
+  { dump("error: " + e + "\n"); }
+
+  return xsltProcessor;
+}
+
 
 #define INTERNAL_XSLT
 

### 2014-09-22 prince/base/content/dialogs/ComputeGraphSettings.js
Working on editing plots

@@ -7,11 +7,21 @@
 Components.utils.import("resource://app/modules/unitHandler.jsm"); 
 var gFrameModeImage = true;
 var gFrameModeTextFrame = false;
-var plotUnitsHandler = new UnitHandler();
 var graph;
 var graphnode;
 var plotwrapper;
 var plotArray = [];
+var gDefaultWidth = 200;
+var gDefaultHeight = 100;
+var gDefaultUnit = "pt";
+var gInitialSrc = "";
+var gHaveDocumentUrl = false;
+var gOriginalSrcUrl = "";
+var gSrcUrl;
+var gPreviewImageWidth = 80;
+var gPreviewImageHeight = 50;
+var gDialog;
+var gInsertNewObject = true;
 
 function getFirstElementByTagName(node, name) {
   var  element = node.getElementsByTagName(name);
@@ -27,34 +37,40 @@ function getFirstElementByTagName(node, name) {
 // if the document has an element matching an attribute name, 
 //   extract the value of the attribute and put it in the document
 function Startup(){ 
+  debugger;
   var plotwrapper, units, alist, id, i, plotNumControl, numPlots, firstActivePlot, 
     plot, theStringSource, oldval, captionnode, placeLocation, obj, frame, topWindow;
   var graphEditorControl, radiusEditorControl;
   try {
-    var gd = {};
+    gDialog = {};
     graphnode = window.arguments[2];
     var editorElement = window.arguments[0];
     graph = new Graph();
+
+    // get graph attributes
     graph.extractGraphAttributes(graphnode);
     frame = getFirstElementByTagName(graphnode,"msiframe");
     plotwrapper = getFirstElementByTagName(graphnode,"plotwrapper");
     obj = getFirstElementByTagName(graphnode, "object");
+    if (obj && obj.hasAttribute("data")) gInsertNewObject = false;
+
+    // get frame attributes
+    initFrameTab(gDialog, frame, gInsertNewObject, obj);
+
     topWindow = msiGetTopLevelWindow();
     if (topWindow && topWindow.document && topWindow.document.getElementById("vcamactive") 
          && (topWindow.document.getElementById("vcamactive").getAttribute("hidden")=="false"))
       queryVCamValues(obj, graph, graphnode, true);
 
-    units = graph["Units"];
+    units = frame["units"];
     if (!units || units.length === 0) 
     {
-      units = "cm";
-      graph["Units"] = units;
+      units = "pt";
[…]

### 2014-09-22 prince/base/content/GraphOverlay.js
Working on editing plots

@@ -74,6 +74,9 @@ function Graph() {
   this.frame = new Frame(this);
 }
 Graph.prototype = {
+  //  BBM: Some of the following attributes below really belong on the msiframe object or the VCam object
+  // Namely: ImageFile===obj.data, Width, Height, Units, BGColor. Some of these probably should appear *only*
+  // elsewhere: width, height, units
   COMPATTRIBUTES: ["ImageFile", "XAxisLabel", "YAxisLabel", "ZAxisLabel", "Width", "Height",
                               "Units", "AxesType", "EqualScaling", "EnableTicks", "XTickCount",
                               "YTickCount", "ZTickCount", "AxesTips", "GridLines", "BGColor", "Dimension",

### 2014-09-22 prince/base/content/dialogs/msiEdImageProps.js

@@ -193,7 +193,7 @@ function Startup()
     window.close();
     return;
   }
-  gDialog = new Object();
+  gDialog = {};
   gDialog.isImport          = true;
   gDialog.tabBox            = document.getElementById( "TabBox" );
   gDialog.tabPicture        = document.getElementById( "imagePictureTab" );

### 2014-09-24 filters/mathml/ltex2mml.cpp
Fix rest of 3109

@@ -3366,18 +3366,18 @@ _LISTOFCELLS_LIST(5.35.11,_MTCELL_,5.35.12,,/mtr|/mtable,)
 _MTCELL_IF(MATH,?mtd?,5.35.14)ifEND
 */
 
-      TNODE* mtr  =  CreateElemWithBucketAndContents( 5,35,13,11,NULL );
+    TNODE* mtr  =  CreateElemWithBucketAndContents( 5,35,13,11,NULL );
 	  mtr->parts->parts =  mtd_head;
 	  mtd_head->sublist_owner =  mtr->parts;
 
-  // Put the current row under a node in the row list
+    // Put the current row under a node in the row list
 
 	  U8 zlistID[32];
-      UidsTozuID( 5,35,9,(U8*)zlistID );
+    UidsTozuID( 5,35,9,(U8*)zlistID );
 	  U16 zln =  strlen( (char*)zlistID );
 	  zlistID[zln]  =  ':';
-          // JCS non-standard: itoa( row_count,(char*)zlistID+zln+1,10 );
-          sprintf((char*)zlistID+zln+1, "%d", row_count);
+    // JCS non-standard: itoa( row_count,(char*)zlistID+zln+1,10 );
+    sprintf((char*)zlistID+zln+1, "%d", row_count);
 	  TNODE* row_list_node  =  MakeTNode( 0,0,0,(U8*)zlistID );
 	  row_list_node->parts  =  mtr;
 	  mtr->sublist_owner  =  row_list_node;

### 2014-12-22 prince/base/content/msiComposerCommands.js
Progress on various fronts

@@ -1386,7 +1386,7 @@ var msiExportToTexCommand =
     if (okToPrint())
     {
       try {
-        return exportTex();
+        return exportTeX();
       }
       catch (e) {
         finalThrow(cmdFailString('exporttex'), e.message);
@@ -4166,9 +4166,12 @@ var msiCopyTeX =
 {
   isCommandEnabled: function(aCommand, aRefCon)
   {
-    var editor = aRefCon.QueryInterface(Components.interfaces.nsIEditor);
-    if (editor)
-      return editor.canCut();
+    //var editor = aRefCon.QueryInterface(Components.interfaces.nsIEditor);
+    var editorElement = msiGetActiveEditorElement();
+    var editor = msiGetEditor(editorElement);
+    var nsed = editor.QueryInterface(Components.interfaces.nsIEditor);
+    if (nsed)
+      return nsed.canCut();
     return false;
   },
 

### 2014-12-30 editor/ui/dialogs/content/EdSpellCheck.js
Fixed the spell check dialog starting out with what seems to be a blank misspelled word.

@@ -229,19 +229,23 @@ function InitLanguageMenu(aCurLang)
   );
 
   // Remove any languages from the list.
-  var languageMenuPopup = gDialog.LanguageMenulist.firstChild;
-  while (languageMenuPopup.firstChild.localName != "menuseparator")
-    languageMenuPopup.removeChild(languageMenuPopup.firstChild);
+  var languageMenuPopup = null;
+  var defaultItem = null; 
+  if (gDialog.LanguageMenulist) {
+    languageMenuPopup = gDialog.LanguageMenulist.firstChild;
+    while (languageMenuPopup && anguageMenuPopup.firstChild.localName != "menuseparator")
+      languageMenuPopup.removeChild(languageMenuPopup.firstChild);
 
-  var defaultItem = null;
+  
 
-  for (i = 0; i < count; i++)
-  {
-    var item = gDialog.LanguageMenulist.insertItemAt(i, dictList[i][0], dictList[i][1]);
-    if (aCurLang && dictList[i][1] == aCurLang)
-      defaultItem = item;
+    for (i = 0; i < count; i++)
+    {
+      var item = gDialog.LanguageMenulist.insertItemAt(i, dictList[i][0], dictList[i][1]);
+      if (aCurLang && dictList[i][1] == aCurLang)
+        defaultItem = item;
+    }
   }
-
+ 
   // Now make sure the correct item in the menu list is selected.
   if (defaultItem)
   {

### 2015-04-22 editor/libeditor/msi/msiEditor.cpp
Changed the UnitHandler constructor to take an editor parameter so it can get to the system-defined pixelsPerInch value. This is now available in an editor function.

@@ -113,6 +113,27 @@ msiEditor::Init(nsIDOMDocument *aDoc, nsIPresShell *aPresShell,  nsIContent *aRo
   return res;
 }
 
+/* double CSSPixelsPerInch (); */
+NS_IMETHODIMP msiEditor::CSSPixelsPerInch(double *_retval)
+{
+  nsCOMPtr<nsIPresShell> presShell;
+  nsPresContext* context;
+  nsresult rv;
+  rv = GetPresShell(getter_AddRefs(presShell));
+  if (NS_SUCCEEDED(rv)) {
+     context = presShell->GetPresContext();
+  }
+  PRInt32 auPerCSSPixel = context->AppUnitsPerDevPixel();
+  // PRInt32 AppUnitsPerDevPixel() const  { return mDeviceContext->AppUnitsPerDevPixel(); }
+  PRInt32 auPerInch = context->AppUnitsPerInch();
+  if (auPerCSSPixel > 0) {
+    *_retval = (double)auPerInch / (double)auPerCSSPixel;
+    return NS_OK;
+  }
+  else
+    return NS_ERROR_ILLEGAL_VALUE;
+}
+
 /* attribute boolean AutoSubEnabled; */
 NS_IMETHODIMP msiEditor::GetAutoSubEnabled(PRBool *aAutoSubEnabled)
 {

### 2015-04-22 prince/base/content/GraphOverlay.js

@@ -348,7 +348,7 @@ Graph.prototype = {
     var DOMCaption = DOMFrame.getElementsByTagName("caption")[0];
     var attr, value, alist, i, domPlots, plot, domPlotLabels, status, caption, captionloc, child, optnum;
     var graphData = new graphVarData(this);
-    var unitHandler = new UnitHandler();
+    var unitHandler = new UnitHandler(editor);
     var units = this.getValue("Units");
     unitHandler.initCurrentUnit(units);
     this.frame.reviseFrameDOMElement(DOMFrame, forComp, editorElement);
@@ -1898,7 +1898,7 @@ Frame.prototype = {
     var editor = msiGetEditor(editorElement);
     var attributes, i, j, att, graph, units, height, width, heightinpx, widthinpx, pos, placeLocation, captionlocation, x;
     var DOMObj = DOMFrame.getElementsByTagName("object")[0];
-    var unitHandler = new UnitHandler();
+    var unitHandler = new UnitHandler(editor);
     var needsWrapfig = false;
     try {
       graph = this.parent;

### 2015-04-22 prince/base/content/dialogs/msiFrameOverlay.js

@@ -24,6 +24,9 @@ var gDefaultPlacement = "center";
 var gDefaultInlineOffset = "";
 var hasNaturalSize;
 var gCaptionLoc;
+var editorElement = msiGetActiveEditorElement();
+var editor = msiGetEditor(editorElement);
+
 
 var sizeState = null;
 
@@ -56,8 +59,8 @@ SizeState.prototype = {
   sizeUnit: null,
 
   selectActualSize: function() {
-    var unitHandler = new UnitHandler();
-    unitHandler.initCurrentUnit('px');
+    var unitHandler = new UnitHandler(editor);
+    unitHandler.initCurrentUnit(this.actualSize.unit);
     this.isCustomSize = false;
     this.preserveAspectRatio = false;
     this.width = unitHandler.getValueAs(this.actualSize.width, this.sizeUnit);
@@ -135,13 +138,13 @@ SizeState.prototype = {
   },
 
   computeInferredDimensions: function() {
-    var unitHandler = new UnitHandler();
+    var unitHandler = new UnitHandler(editor);
     if (!this.isCustomSize &&
       this.actualSize.width != null && this.actualSize.height != null)
     {
       unitHandler.initCurrentUnit(this.actualSize.unit);
-      this.width = unitHandler.getValueAs(this.actualSize.width, this.sizeUnit);
-      this.height = unitHandler.getValueAs(this.actualSize.height, this.sizeUnit);
+      if (this.width == 0) this.width = unitHandler.getValueAs(this.actualSize.width, this.sizeUnit);
+      if (this.height == 0) this.height = unitHandler.getValueAs(this.actualSize.height, this.sizeUnit);
       this.enabledState.height = this.enabledState.width = false;
     }
     if (this.preserveAspectRatio && this.isCustomSize) {
@@ -186,7 +189,7 @@ function setHasNaturalSize()
     return;
   }
   hasNaturalSize = (sizeState.actualSize.width != null) && (sizeState.actualSize.height != null);
-  if (istrue)
+  if (hasNaturalSize)
   {
     bcaster.removeAttribute("hidden");
   }
@@ -199,13 +202,13 @@ function setHasNaturalSize()
 function setCanRotate(istrue)
 {
   var rotationbox = document.getElementById("rotate");
-  if (!istrue)
+  if (istrue)
   {
-    rotationbox.setAttribute("hidden", "true");
[…]

### 2015-04-22 prince/base/content/dialogs/otfont.js

@@ -1,6 +1,6 @@
 #include ../productname.inc
-Components.utils.import("resource://app/modules/fontlist.jsm"); 
-//Components.utils.import("resource://app/modules/pathutils.jsm"); 
+Components.utils.import("resource://app/modules/fontlist.jsm");
+//Components.utils.import("resource://app/modules/pathutils.jsm");
 Components.utils.import("resource://app/modules/unitHandler.jsm");
 
 var texnode;
@@ -17,11 +17,11 @@ function startup()
   {
     throw("No editor in otfont.OnAccept!");
   }
-  var editor = msiGetEditor(editorElement);  
+  var editor = msiGetEditor(editorElement);
   var name;
   var count = 0;
   var item;
-	unitHandler = new UnitHandler();
+	unitHandler = new UnitHandler(editor);
 	initializeUnitHandler(unitHandler);
   var menuObject = { menulist: []};
   menuObject.menulist = document.getElementById("otfontlist");
@@ -92,7 +92,7 @@ function getColorAndUpdate()
   if (colorObj.Cancel)
     return;
   color = colorObj.TextColor;
-  setColorWell("colorWell", color); 
+  setColorWell("colorWell", color);
   colorWell.setAttribute("color",color);
 }
 
@@ -105,7 +105,7 @@ function onAccept()
      throw("No editor in otfont.OnAccept!");
    }
 	var editor = msiGetEditor(editorElement);
-  
+
   var fontname = getFontName();
 	var leading = unitHandler.getValueAs(getLeading(), "pt");
 	var color = getColorFromColorPicker();
@@ -114,7 +114,7 @@ function onAccept()
 #ifndef PROD_SNB
   rawtex = getRawTeX();
 #endif
-	
+
   var theWindow = window.opener;
   if (!theWindow || !("msiEditorSetTextProperty" in theWindow))
   {
@@ -126,7 +126,7 @@ function onAccept()
 		editor.beginTransaction();
 		if (fontname) theWindow.msiEditorSetTextProperty(editorElement, "otfont", "fontname", fontname);
 		if (color) theWindow.msiEditorSetTextProperty(editorElement, "fontcolor", "color", color);
-		if (fontsize) 
+		if (fontsize)
 		{
 			var fontsizedata;
 			if (leading) fontsizedata = fontsize+"/"+leading+" pt";
@@ -157,7 +157,7 @@ function getFontName()
   return null;
 }
 
-function getFontSize() 
+function getFontSize()
 {
[…]

### 2015-04-22 prince/base/content/msiComposerCommands.js

@@ -634,7 +634,7 @@ function msiPokeMultiStateUI(uiID, cmdParams)
     else
       try {
         desiredAttrib = cmdParams.getStringValue("state_attribute");
-      } 
+      }
       catch( e ) {
         return;
       }
@@ -704,7 +704,7 @@ function msiPokeMultiStateUI(uiID, cmdParams)
 //        }
 //      }
 //    }
-//  } 
+//  }
 //  catch(e) {}
 //}
 //
@@ -792,7 +792,7 @@ function msiDoStatefulCommand(commandID, newState, editorElement)
         msiPokeMultiStateUI(commandID, cmdParams);
     }
     msiResetStructToolbar(editorElement);
-    if (newState === 'bibitem') 
+    if (newState === 'bibitem')
     {
       msiGoDoCommand("cmd_reviseManualBibItemCmd");
     }
@@ -967,7 +967,7 @@ function updateViewMenuFromEditor(editorElement)
                       ["viewInputBoxes","showInputBoxes"], ["viewIndexEntries","showIndexEntries"],
                       ["viewMarkers","showMarkers"]];
 
-  // I don't know what Ron intended here, but this can't work because command is not set.                      
+  // I don't know what Ron intended here, but this can't work because command is not set.
 
   // var docList = msiGetUpdatableItemContainers(command, editorElement);
   // var menuItem;
@@ -998,7 +998,7 @@ function updateViewMenuFromEditor(editorElement)
       else
         menuItem.setAttribute("checked", "false");
     }
-  }  
+  }
 }
 
 ////-----------------------------------------------------------------------------------
@@ -1113,7 +1113,7 @@ function openDocument()
       dump("Ready to edit page: " + fp.fileURL.spec +"\n");
       var newdocumentfile;
       newdocumentfile = createWorkingDirectory(fp.file);
-      
+
       msiEditPage(msiFileURLFromFile(newdocumentfile), window, false, false);
       msiSaveFilePickerDirectoryEx(fp, fp.file.parent.path, MSI_EXTENSION);
     }
@@ -1245,7 +1245,7 @@ var msiSaveCommand =
       return result;
     }
     else {
-      finalThrow(cmdFailString("save"), "Saving is not allowed. This program is not licensed."); 
+      finalThrow(cmdFailString("save"), "Saving is not allowed. This program is not licensed.");
     }
   }
 }
@@ -1290,7 +1290,7 @@ var msiSoftSaveCommand =
[…]

### 2015-04-22 prince/base/content/msiEditor.js

@@ -504,40 +504,56 @@ var msiResizeListener =
 
   resizeGraphic : function(anElement, oldWidth, oldHeight, newWidth, newHeight)
   {
-    var theUnits = anElement.getAttribute("units");
-    // var style = "";
-    var elemWidth = anElement.getAttribute("imageWidth");
-    var elemHeight = anElement.getAttribute("imageHeight");
-    var bSetWidth = elemWidth && (Number(elemWidth) != 0);
-    var bSetHeight = elemHeight && (Number(elemHeight) != 0);
-    if (bSetWidth && !bSetHeight)  //only set height if no longer preserves aspect ratio
-    {
-      var ratio = Number(anElement.getAttribute("naturalHeight"))/Number(anElement.getAttribute("naturalWidth"));
-      if (!ratio || (ratio == Number.POSITIVE_INFINITY) || (ratio == Number.NEGATIVE_INFINITY) || (ratio == Number.NaN))
-        bSetHeight = true;
-      else
-        bSetHeight = (Math.abs(ratio * newWidth - newHeight) > 2.0);
+    // When this is called, the height and width style attributes for anElement have already been set.
+    // We take care of a possible surrounding msiframe, and attributes other than style,such as ltx_width and
+    // ltx_height
+    var editorElement = msiGetActiveEditorElement();
+    var editor = msiGetEditor(editorElement);
+
+    var unitHandler = new UnitHandler(editor);
+    var frame = anElement.parentNode;
+    var dHeight = newHeight - oldHeight;
+    var dWidth = newWidth - oldWidth;
+    var frameWidth, frameHeight;
+;
+    var theUnits = anElement.getAttribute("units") || frame.getAttribute("units");
+    var pixelsPerUnit;
+    var elemWidth = anElement.getAttribute("ltx_width");
+    var elemHeight = anElement.getAttribute("ltx_height");
+
+    unitHandler.initCurrentUnit('px'); //the unit for resize callbacks
+    if (!(theUnits || elemWidth || elemHeight)) return;
+    pixelsPerUnit = unitHandler.getValueOf(1, theUnits);
+    anElement.setAttribute('ltx_width', newWidth/pixelsPerUnit);
+    anElement.setAttribute('ltx_height', newHeight/pixelsPerUnit);
+
+    // Do we also set width and height attributes, or imageWidth and imageHeight attributes
+
+    if (frame.nodeName === 'msiframe') {
[…]

### 2015-04-22 prince/base/content/dialogs/addruleforsection.js
Changed the UnitHandler constructor to take an editor parameter so it can get to the system-defined pixelsPerInch value. This is now available in an editor function.

@@ -1,13 +1,16 @@
-Components.utils.import("resource://app/modules/unitHandler.jsm"); 
+Components.utils.import("resource://app/modules/unitHandler.jsm");
 
 var color;
 var ruleElement;
 var ruleUnits;
-var unitHandler = new UnitHandler();
+var unitHandler;
 
 
 function startUp()
 {
+  var editorElement = msiGetActiveEditorElement();
+  var editor = msiGetEditor(editorElement);
+  unitHandler = new UnitHandler(editor);
   ruleElement= window.arguments[0];
   if (!ruleElement) return;
 //  color = window.arguments[1];
@@ -18,7 +21,7 @@ function startUp()
   unitHandler.initCurrentUnit(ruleUnits);
   document.getElementById("ruleUnits").setAttribute("value",unitHandler.currentUnit);
   var numberAndUnit;
-  var tlheight = ruleElement.getAttribute("tlheight"); 
+  var tlheight = ruleElement.getAttribute("tlheight");
   var ht;
   numberAndUnit = unitHandler.getNumberAndUnitFromString(tlheight);
   if (numberAndUnit)
@@ -72,7 +75,7 @@ function getColorAndUpdate()
 		msiGetEditor(editorElement).incrementModificationCount(1);
 	}
   color = colorObj.TextColor;
-  setColorWell("colorWell", color); 
+  setColorWell("colorWell", color);
 }
 
 
@@ -90,7 +93,7 @@ function onAccept()
     var style= "background-color:"+color +"; height:"+ nInPixels + "px; ";
     var tlwidth = document.getElementById("rulelength").value;
     switch (tlwidth) {
-      case "other": 
+      case "other":
       {
         tlwidth = document.getElementById("ruleWidth").value+ruleUnits;
         break;

### 2015-04-22 prince/base/content/dialogs/msiEdTableProps.js

@@ -3,7 +3,7 @@
  * ***** END LICENSE BLOCK ***** */
 "use strict";
 
-Components.utils.import("resource://app/modules/unitHandler.jsm"); 
+Components.utils.import("resource://app/modules/unitHandler.jsm");
 
 
 //Cancel() is in msiEdDialogCommon.js
@@ -188,16 +188,16 @@ function ChangeRowOrColumn(id)
   forceInteger(id);
 
   // Enable OK only if both rows and columns have a value > 0
-  var enable = gDialog.rowsInput.value.length > 0 && 
+  var enable = gDialog.rowsInput.value.length > 0 &&
                               gDialog.rowsInput.value > 0 &&
                               gDialog.columnsInput.value.length > 0 &&
                               gDialog.columnsInput.value > 0;
 
   SetElementEnabled(gDialog.OkButton, enable);
   SetElementEnabledById("AdvancedEditButton1", enable);
-  if (enable) 
-  {  
-    gRows = gDialog.rowsInput.value;  
+  if (enable)
+  {
+    gRows = gDialog.rowsInput.value;
     gColumns = gDialog.columnsInput.value;
     gCellID = 10*(gColumns) - - gRows;  //forces gRows to a number
     DisplaySize();
@@ -227,7 +227,7 @@ function setVariablesForControls()
   gDialog.autoWidthCheckbox = document.getElementById("autoWidthCheckbox");
 
   // gDialog.tableBackgroundCW =  document.getElementById("tableBackgroundCW");
-  
+
   // Cells Panel
   gDialog.CellHeightInput = document.getElementById("CellHeightInput");
   gDialog.CellHeightUnits = document.getElementById("CellHeightUnits");
@@ -298,14 +298,14 @@ function setDataFromReviseData(reviseData, commandStr)
 
 function setUpChangeData()
 {
-  gCellChangeData = 
+  gCellChangeData =
   {
     border : { style : [], width : [], color : []},
     size : { width : false, height : false },
     align : { halign : false, valign : false },
     wrap : false, background : false, cellType : false
   };
-  gTableChangeData = 
+  gTableChangeData =
   {
     size : { width : false, height : false },
     baseline : false, background : false, caption : false, borderCollapse : false
@@ -458,11 +458,11 @@ function translateSelectionTypeString(selTypeStr)
 
 function Startup()
 {
-  
-  frameUnitHandler = new UnitHandler();
+
 
[…]

### 2015-04-22 prince/base/content/dialogs/typesetDocFormat.js

@@ -2,8 +2,8 @@ Components.utils.import("resource://app/modules/fontlist.jsm");
 Components.utils.import("resource://app/modules/pathutils.jsm");
 Components.utils.import("resource://app/modules/unitHandler.jsm");
 
-var unitHandler = new UnitHandler();
-var secUnitHandler = new UnitHandler();
+var unitHandler;
+var secUnitHandler;
 var gNumStyles={};
 var widthElements;
 var heightElements;
@@ -95,6 +95,8 @@ function startup()
     window.close();
     return;
   }
+  unitHandler = new UnitHandler(editor);
+  secUnitHandler = new UnitHandler(editor);
   widthElements=["lmargin","bodywidth","colsep", "mnsep","mnwidth","computedrmargin",
       /*"sectrightheadingmargin", "sectleftheadingmargin",*/ "pagewidth", "paperwidth"];
   heightElements=["tmargin","hedd","heddsep",

### 2015-04-22 prince/base/content/msiEditorUtilities.js

@@ -61,6 +61,8 @@ function FixJS() {
 function isLicensed() {
   var editorElement = msiGetActiveEditorElement();
   var editor = msiGetEditor(editorElement);
+  if (editor) {
+
   var licensedApp = editor.mAppUtils.licensedApp;
 #ifdef PROD_SWP
     return (licensedApp == 3);
@@ -71,6 +73,8 @@ function isLicensed() {
 #ifdef PROD_SNB
     return (licensedApp == 1);
 #endif
+  }
+  else return false;
 }
 
 function okToPrint()
@@ -148,6 +152,15 @@ function setStyleAttributeOnNode(node, att, value, editor) {
     msiEditorEnsureElementAttribute(node, 'style', style, editor);
   else
     node.setAttribute('style', style);
+}
+function getStyleAttributeOnNode(node, att, editor) {
+  var style = node.getAttribute('style');
+  var regexp = new RegExp('\\b' + att + ':\\s*([a-zA-Z0-9])');
+  var value = regexp.exec(style);
+  if (value && value.length > 1) {
+    return value[1];
+  }
+  return null;
 }
 function removeStyleAttributeFamilyOnNode(node, att, editor) {
   if (!node) {

### 2015-04-22 editor/libeditor/html/nsHTMLObjectResizer.cpp
Get whether to preserve aspect ratio when resizing with widgets from the 'aspect' object attribute.

@@ -77,7 +77,7 @@ static NS_DEFINE_CID(kLookAndFeelCID, NS_LOOKANDFEEL_CID);
 // ==================================================================
 NS_IMPL_ISUPPORTS1(DocumentResizeEventListener, nsIDOMEventListener)
 
-DocumentResizeEventListener::DocumentResizeEventListener(nsIHTMLEditor * aEditor) 
+DocumentResizeEventListener::DocumentResizeEventListener(nsIHTMLEditor * aEditor)
 {
   mEditor = do_GetWeakReference(aEditor);
 }
@@ -115,7 +115,7 @@ ResizerSelectionListener::NotifySelectionChanged(nsIDOMDocument *, nsISelection 
 {
   if ((aReason & (nsISelectionListener::MOUSEDOWN_REASON |
                   nsISelectionListener::KEYPRESS_REASON |
-                  nsISelectionListener::SELECTALL_REASON)) && aSelection) 
+                  nsISelectionListener::SELECTALL_REASON)) && aSelection)
   {
     // the selection changed and we need to check if we have to
     // hide and/or redisplay resizing handles
@@ -138,7 +138,7 @@ ResizerMouseMotionListener::ResizerMouseMotionListener(nsIHTMLEditor * aEditor)
   mEditor = do_GetWeakReference(aEditor);
 }
 
-ResizerMouseMotionListener::~ResizerMouseMotionListener() 
+ResizerMouseMotionListener::~ResizerMouseMotionListener()
 {
 }
 
@@ -332,7 +332,7 @@ nsHTMLEditor::RefreshResizers()
                            mResizedObjectX, mResizedObjectY);
 }
 
-NS_IMETHODIMP 
+NS_IMETHODIMP
 nsHTMLEditor::ShowResizers(nsIDOMElement *aResizedElement)
 {
   NS_ENSURE_ARG_POINTER(aResizedElement);
@@ -386,7 +386,7 @@ nsHTMLEditor::ShowResizers(nsIDOMElement *aResizedElement)
   res = SetAllResizersPosition();
   if (NS_FAILED(res)) return res;
 
-// BBM: Disable shadows, since they were producing a second image out of place 
+// BBM: Disable shadows, since they were producing a second image out of place
[…]

### 2015-05-04 prince/base/content/msiEditor.js
Fixed problem that caused swpwelcome.tex to not import. Fixed a javascript crash.

@@ -138,7 +138,9 @@ function initMetaData( doc ) {
     node = doc.createElement("sw-meta");
     node.setAttribute("id", "sw-meta");
     // put in the head
-    headnode.insertBefore(node, headnode.firstChild);
+    if (headnode){
+      headnode.insertBefore(node, headnode.firstChild);
+    }
   }
   // Initial data are version, created, lastrevised
   var product = "Scientific WorkPlace";

### 2015-10-12 prince/base/content/about.js
Tuesday?

@@ -3,7 +3,7 @@
 function onLoad() {
   var versionField = document.getElementById("versionField");
   var brandShortNameEl = document.getElementById("brandShortName");
-  versionField.value = brandShortNameEl.firstChild.nodeValue + ' ' + navigator.vendorSub + ' (6.0.7 10/09/2015)';
+  versionField.value = brandShortNameEl.firstChild.nodeValue + ' ' + navigator.vendorSub + ' (6.0.7 10/13/2015)';
   var CopyRight = document.getElementById("CopyRight");
   var currentTime = new Date();
   var year = currentTime.getFullYear();

### 2016-06-16 editor/libeditor/html/nsHTMLEditor.cpp
Added processing for Unicode combining long bar. We already had it for the short bar, but the decorations dialog generates the long bar.

@@ -7379,6 +7379,7 @@ void handleCombiningChars( const PRUnichar** pCur, PRUnichar combiningChar, nsAS
       thisChar = NS_LITERAL_STRING("\\k{") + thisChar + cbrace;
       break;
     case 0x0331 :
+    case 0x0332 :
       thisChar = NS_LITERAL_STRING("\\b{") + thisChar + cbrace;
       break;
     case 0x0338 :

### 2016-08-10 prince/samples/CalculusMadeEasyChapXV.tex
Add titlepage environment and an additional final page with .bmp and .png sample graphics.  Now five different graphics types referenced.

%2multibyte Version: 5.50.0.2960 CodePage: 1252
\documentclass[12pt,openany]{book}%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}%
\setcounter{MaxMatrixCols}{30}
%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{Codepage=1252}
%TCIDATA{LastRevised=Wednesday, August 10, 2016 12:02:22}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%BeginMSIPreambleData
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
%EndMSIPreambleData
\def\tb{\begin{center}\rule{1.5in}{0.5pt}\end{center}}
\renewcommand{\thechapter}{\Roman{chapter}}
\setcounter{chapter}{14}
\geometry{margin=1in}
\begin{document}
%
%TCIMACRO{\TeXButton{B titlepage}{\begin{titlepage}}}%
%BeginExpansion
\begin{titlepage}%
%EndExpansion

\begin{center}
(excerpted from)

\bigskip

\textbf{{}{\Huge CALCULUS MADE EASY:}{}}\vspace*{0.67in}

{\large BEING A VERY-SIMPLEST INTRODUCTION TO}\medskip

{\large THOSE BEAUTIFUL METHODS OF RECKONING}\medskip

{\large WHICH ARE GENERALLY CALLED BY THE}\medskip

{\large TERRIFYING NAMES OF THE}\vspace*{0.5in}

{\Large DIFFERENTIAL CALCULUS}\bigskip

{\large AND THE}\bigskip

{\Large INTEGRAL CALCULUS.}\vspace*{0.33in}

{\large BY}\bigskip

{\LARGE F. R. S.}\vspace*{0.5in}

{\Large SECOND EDITION, ENLARGED}%

%TCIMACRO{\FRAME{itbpF}{5.0548in}{1.8334in}{0in}{}{}{mcmillianlogo.png}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 5.0548in;  height 1.8334in;  depth 0in;  original-width 5.028in;
%original-height 1.8057in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";  filename 'McMillianLogo.png';file-properties "XNPEU";}} }%
%BeginExpansion
{\includegraphics[
natheight=1.805700in,
natwidth=5.028000in,
height=1.8334in,
width=5.0548in
]%
{C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__1.jpg}%
}
%EndExpansion

{\large MACMILLAN AND CO., LIMITED}\medskip

{\large ST. MARTIN'S STREET, LONDON}\medskip

{\large 1914}
\end{center}%

%TCIMACRO{\TeXButton{E titlepage}{\end{titlepage}}}%
%BeginExpansion
\end{titlepage}%
%EndExpansion

\chapter[SINES AND COSINES]{How to deal with Sines and Cosines}

\setcounter{page}{162}

GREEK letters being usual to denote angles, we will take as the usual letter
for any variable angle the letter~$\theta$ (``theta'').

Let us consider the function
\[
y= \sin\theta.
\]
%

%TCIMACRO{\FRAME{dtbpF}{2.7233in}{2.5278in}{0pt}{}{}{calculusmadeeasyfig43.jpg}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.7233in;  height 2.5278in;  depth 0pt;  original-width 2.6809in;
%original-height 2.4863in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";
%filename 'CalculusMadeEasyFig43.jpg';file-properties "XNPEU";}}}%
%BeginExpansion
\begin{center}
\includegraphics[
natheight=2.486300in,
natwidth=2.680900in,
height=2.5278in,
width=2.7233in
]%
{CalculusMadeEasyFig43.jpg}%
\end{center}
%EndExpansion

What we have to investigate is the value of $\dfrac{d(\sin\theta)}{d \theta}$;
or, in other words, if the angle~$\theta$ varies, we have to find the relation
between the increment of the sine and the increment of the angle, both
increments being indefinitely small in themselves. Examine Fig 43, wherein, if
the radius of the circle is unity, the height of~$y$ is the sine, and $\theta$
is the angle. Now, if $\theta$ is supposed to increase by the addition to it
of the small angle $d \theta$---an element of angle---the height of~$y$, the
sine, will be increased by a small element~$dy$. The new height~$y + dy$ will
be the sine of the new angle $\theta+ d \theta$, or, stating it as an
equation,
\[
y+dy = \sin(\theta+ d \theta);
\]
and subtracting from this the first equation gives
\[
dy = \sin(\theta+ d \theta)- \sin\theta.
\]

The quantity on the right-hand side is the difference between two sines, and
books on trigonometry tell us how to work this out. For they tell us that if
$M$ and~$N$ are two different angles,
\[
\sin M - \sin N = 2 \cos\frac{M+N}{2}\cdot\sin\frac{M-N}{2}.
\]

If, then, we put $M= \theta+ d \theta$ for one angle, and $N= \theta$ for the
other, we may write
\begin{align*}
dy  &  =2\cos\frac{\theta+d\theta+\theta}{2}\textperiodcentered\sin
\frac{\theta+d\theta-\theta}{2},\\
\text{or,\qquad\qquad}dy  &  =2\cos(\theta+\tfrac{1}{2}d\theta
)\textperiodcentered\sin\tfrac{1}{2}d\theta.
\end{align*}

But if we regard $d \theta$ as indefinitely small, then in the limit we may
neglect~$\frac{1}{2} d \theta$ by comparison with~$\theta$, and may also take
$\sin\frac{1}{2} d \theta$ as being the same as~$\frac{1}{2} d \theta$. The
equation then becomes:
\begin{align*}
dy  &  = 2 \cos\theta\times\tfrac{1}{2} d \theta;\\
dy  &  = \cos\theta\cdot d \theta,\\
\text{and, finally,\qquad\qquad}\dfrac{dy}{d \theta}  &  = \cos\theta.
\end{align*}

The accompanying curves, Figs 44 and 45, show, plotted to scale, the values of
$y=\sin\theta$, and $\dfrac{dy}{d\theta}=\cos\theta$, for the corresponding
values of~$\theta$.%

%TCIMACRO{\FRAME{dtbpF}{4.6207in}{2.5261in}{0pt}{}{}{calculusmadeeasyfig44.wmf}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 4.6207in;  height 2.5261in;  depth 0pt;  original-width 4.5688in;
%original-height 2.4855in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";
%filename 'CalculusMadeEasyFig44.wmf';file-properties "XNPEU";}}}%
%BeginExpansion
\begin{center}
\includegraphics[
natheight=2.485500in,
natwidth=4.568800in,
height=2.5261in,
width=4.6207in
]%
{C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__2.pdf}%
\end{center}
%EndExpansion
%

%TCIMACRO{\FRAME{dtbpF}{4.619in}{2.5175in}{0pt}{}{}{calculusmadeeasyfig45.eps}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 4.619in;  height 2.5175in;  depth 0pt;  original-width 4.5671in;
%original-height 2.4768in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";
%filename 'CalculusMadeEasyFig45.eps';file-properties "XNPEU";}}}%
%BeginExpansion
\begin{center}
\includegraphics[
height=2.5175in,
width=4.619in
]%
{CalculusMadeEasyFig45.eps}%
\end{center}
%EndExpansion

\begin{center}
\rule{1.5in}{0.5pt}
\end{center}

Take next the cosine.

Let $y=\cos\theta$.

Now $\cos\theta=\sin\left(  \dfrac{\pi}{2}-\theta\right)  $.

Therefore%
\begin{align*}
&
\begin{array}
[c]{r}%
dy=d\left(  \sin\left(  \frac{\pi}{2}-\theta\right)  \right)  =\cos\left(
\frac{\pi}{2}-\theta\right)  \times d(-\theta),\\
=\cos\left(  \frac{\pi}{2}-\theta\right)  \times(-d\theta),
\end{array}
\\
&  \frac{dy}{d\theta}=-\cos\left(  \frac{\pi}{2}-\theta\right)  .
\end{align*}

And it follows that%
\[
\frac{dy}{d\theta}=-\sin\theta.
\]

\begin{center}
\rule{1.5in}{0.5pt}
\end{center}

Lastly, take the tangent.
\begin{align*}
\text{Let\qquad\qquad\qquad\qquad\qquad}y  &  =\tan\theta,\\
dy  &  =\tan(\theta+d\theta)-\tan\theta.
\end{align*}

Expanding, as shown in books on trigonometry%

\begin{align*}
\tan(\theta+d\theta)  &  =\frac{\tan\theta+\tan d\theta}{1-\tan\theta\cdot\tan
d\theta};\\
\text{whence\qquad\qquad\qquad}dy  &  =\frac{\tan\theta+\tan d\theta}%
{1-\tan\theta\cdot\tan d\theta}-\tan\theta\\
&  =\frac{(1+\tan^{2}\theta)\tan d\theta}{1-\tan\theta\cdot\tan d\theta}.
\end{align*}

Now remember that if $d\theta$ is indefinitely diminished, the value of~$\tan
d\theta$ becomes identical with~$d\theta$, and $\tan\theta\cdot d\theta$ is
negligibly small compared with~$1$, so that the expression reduces to
\begin{align*}
dy  &  = \frac{(1+\tan^{2} \theta)\, d\theta}{1},\\
\text{so that\qquad\qquad} \frac{dy}{d\theta}  &  = 1 + \tan^{2}\theta,\\
\text{or\qquad\qquad} \frac{dy}{d\theta}  &  = \sec^{2} \theta.
\end{align*}

Collecting these results, we have:

\begin{center}%
\begin{tabular}
[c]{|c|c|}\hline
$\rule[-12pt]{0pt}{32pt}y$ & $\dfrac{dy}{d\theta}$\\\hline
$\sin\theta$ & $\cos\theta$\\
$\cos\theta$ & $-\sin\theta$\\
$\tan\theta$ & $\sec^{2}\theta$\\\hline
\end{tabular}

\end{center}

Sometimes, in mechanical and physical questions, as, for example, in simple
harmonic motion and in wave-motions, we have to deal with angles that increase
in proportion to the time. Thus, if $T$ be the time of one complete
\emph{period}, or movement round the circle, then, since the angle all round
the circle is $2\pi$~radians, or~$360%
%TCIMACRO{\U{b0}}%
%BeginExpansion
{{}^\circ}%
%EndExpansion
$, the amount of angle moved through in time~$t$, will be
\begin{align*}
\theta &  = 2\pi\frac{t}{T},\quad\text{in radians,}\\
\text{or\qquad\qquad} \theta &  = 360\frac{t}{T},\quad\text{in degrees.}%
\end{align*}

If the \emph{frequency}, or number of periods per second, be denoted by~$n$,
then $n = \dfrac{1}{T}$, and we may then write:
\[
\theta=2\pi nt.
\]
Then we shall have
\[
y = \sin2\pi nt.
\]

If, now, we wish to know how the sine varies with respect to time, we must
differentiate with respect, not to~$\theta$, but to~$t$. For this we must
resort to the artifice explained in Chapter~IX., and put
\[
\frac{dy}{dt} = \frac{dy}{d\theta} \cdot\frac{d\theta}{dt}.
\]

Now $\dfrac{d\theta}{dt}$ will obviously be~$2\pi n$; so that
\begin{align*}
\frac{dy}{dt}  &  =\cos\theta\times2\pi n\\
&  =2\pi n\cdot\cos2\pi nt.
\end{align*}
Similarly, it follows that%
\[
\frac{d(\cos2\pi nt)}{dt}=-2\pi n\cdot\sin2\pi nt.
\]

\section*{Second Differential Coefficient of Sine or Cosine.}

We have seen that when $\sin\theta$ is differentiated with respect to~$\theta$
it becomes $\cos\theta$; and that when $\cos\theta$ is differentiated with
respect to~$\theta$ it becomes $-\sin\theta$; or, in symbols,
\[
\frac{d^{2}(\sin\theta)}{d\theta^{2}} = -\sin\theta.
\]

So we have this curious result that we have found a function such that if we
differentiate it twice over, we get the same thing from which we started, but
with the sign changed from $+$~to~$-$.

The same thing is true for the cosine; for differentiating $\cos\theta$ gives
us $-\sin\theta$, and differentiating $-\sin\theta$ gives us $-\cos\theta$; or
thus:
\[
\frac{d^{2}(\cos\theta)}{d\theta^{2}} = -\cos\theta.
\]

\emph{Sines and cosines are the only functions of which the second
differential coefficient is equal \emph{(and of opposite sign to)} the
original function.}

\begin{center}
\rule{1.5in}{0.5pt}
\end{center}

\subsection*{Examples.}

With what we have so far learned we can now differentiate expressions of a
more complex nature.

(1) $y=\arcsin x$.

If $y$ is the arc whose sine is~$x$, then $x = \sin y$.
\[
\frac{dx}{dy}=\cos y.
\]

Passing now from the inverse function to the original one, we get
\begin{align*}
\frac{dy}{dx}  &  = \frac{1}{\;\dfrac{dx}{dy}\;} = \frac{1}{\cos y}.\\
\text{Now\qquad\qquad} \cos y  &  = \sqrt{1-\sin^{2} y}=\sqrt{1-x^{2}};\\
\text{hence\qquad\qquad\qquad\qquad} \frac{dy}{dx}  &  = \frac{1}%
{\sqrt{1-x^{2}}},
\end{align*}
a rather unexpected result.

(2) $y=\cos^{3} \theta$.

This is the same thing as $y=(\cos\theta)^{3}$.

Let $\cos\theta=v$;\quad then $y=v^{3}$;\quad$\dfrac{dy}{dv}=3v^{2}$.
\begin{align*}
\frac{dv}{d\theta}  &  = -\sin\theta.\\
\frac{dy}{d\theta}  &  = \frac{dy}{dv} \times\frac{dv}{d\theta} = -3 \cos^{2}
\theta\sin\theta.
\end{align*}

(3) $y=\sin(x+a)$.

Let $x+a=v$;\quad then $y=\sin v$.
\[
\frac{dy}{dv}=\cos v;\qquad\frac{dv}{dx}=1 \quad\text{and}\quad\frac{dy}%
{dx}=\cos(x+a).
\]

(4) $y=\log_{\epsilon}\sin\theta$.

Let $\sin\theta=v$;\quad$y=\log_{\epsilon}v$.
\begin{align*}
\frac{dy}{dv}  &  = \frac{1}{v};\quad\frac{dv}{d\theta}=\cos\theta;\\
\frac{dy}{d\theta}  &  = \frac{1}{\sin\theta} \times\cos\theta= \cot\theta.
\end{align*}

(5) $y=\cot\theta=\dfrac{\cos\theta}{\sin\theta}$.
\begin{align*}
\frac{dy}{d\theta}  &  = \frac{-\sin^{2}\theta- \cos^{2} \theta}{\sin^{2}
\theta}\\
&  = -(1+\cot^{2} \theta) = -\csc^{2} \theta.
\end{align*}

(6) $y=\tan3\theta$.

Let $3\theta=v$;\quad$y=\tan v$;\quad$\dfrac{dy}{dv}=\sec^{2} v$.
\[
\frac{dv}{d\theta}=3;\quad\frac{dy}{d\theta}=3 \sec^{2} 3\theta.
\]

(7) $y = \sqrt{1+3\tan^{2}\theta}$;\quad$y=(1+3 \tan^{2} \theta)^{\frac{1}{2}%
}$.

Let $3\tan^{2}\theta=v$.
\begin{align*}
y  &  = (1+v)^{\frac{1}{2}};\quad\frac{dy}{dv} = \frac{1}{2\sqrt{1+v}}\\
\frac{dv}{d\theta}  &  = 6\tan\theta\sec^{2} \theta\\
\text{(for, if $\tan\theta= u$,\qquad\qquad} v  &  = 3u^{2};\quad\frac{dv}{du}
= 6u;\quad\frac{du}{d\theta} = \sec^{2} \theta;\\
\text{hence\qquad\qquad} \frac{dv}{d\theta}  &  = 6 (\tan\theta\sec^{2}
\theta)\\
\text{hence\qquad\qquad} \frac{dy}{d\theta}  &  = \frac{6\tan\theta\sec
^{2}\theta}{2\sqrt{1 + 3\tan^{2}\theta}}.
\end{align*}

(8) $y=\sin x\cos x$.
\begin{align*}
\frac{dy}{dx} &  =\sin x(-\sin x)+\cos x\times\cos x\\
&  =\cos^{2}x-\sin^{2}x.
\end{align*}

\newpage%

%TCIMACRO{\FRAME{dtbpF}{2.8202in}{2.2623in}{0pt}{}{}{project_gutenberg-1.bmp}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.8202in;  height 2.2623in;  depth 0pt;  original-width 2.7778in;
%original-height 2.2226in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";  filename 'project_gutenberg-1.bmp';file-properties "XNPEU";}%
%}}%
%BeginExpansion
\begin{center}
\includegraphics[
natheight=2.222600in,
natwidth=2.777800in,
height=2.2623in,
width=2.8202in
]%
{C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__3.jpg}%
\end{center}
%EndExpansion
This sample document was derived from
\textit{\href{http://www.gutenberg.org/3/3/2/8/33283/}{\textit{Calculus Made
Easy, 2nd Edition} by Silvanus Thompson}}, from
\href{http://www.gutenberg.org/}{Project Gutenberg}. See the Project Gutenberg
licnesing information
\href{http://www.gutenberg.org/wiki/Gutenberg:The_Project_Gutenberg_License}{*here*}%
.

This document demonstrates typical mathematical text, plus shows graphics
using five different formats:

\begin{enumerate}
\item .png, the logo on the first page

\item .jpg, Fig. 43

\item .wmf, Fig. 44

\item .eps, Fig 45

\item .bmp, the logo on the last page
\end{enumerate}

\end{document}

### 2017-05-11 prince/samples/CalculusMadeEasyChapXV.tex

@@
 %TCIDATA{Codepage=1252}
-%TCIDATA{LastRevised=Wednesday, August 10, 2016 12:02:22}
+%TCIDATA{LastRevised=Wednesday, May 10, 2017 14:52:02}
 %TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
@@
 {\large 1914}
-\end{center}%
+\end{center}
+
+%
 
@@
 
-%TCIMACRO{\FRAME{dtbpF}{2.7233in}{2.5278in}{0pt}{}{}{calculusmadeeasyfig43.jpg}%
+%TCIMACRO{\FRAME{fhF}{2.7233in}{2.5278in}{0pt}{}{}{calculusmadeeasyfig43.jpg}%
 %{\special{ language "Scientific Word";  type "GRAPHIC";
@@
 %cropbottom "0";
-%filename 'CalculusMadeEasyFig43.jpg';file-properties "XNPEU";}}}%
+%filename 'CalculusMadeEasyFig43.jpg';file-properties "XNPEU";}} }%
 %BeginExpansion
-\begin{center}
+\begin{figure}[h]%
+\centering
 \includegraphics[
@@
 {CalculusMadeEasyFig43.jpg}%
-\end{center}
+\end{figure}
 %EndExpansion
 
-What we have to investigate is the value of $\dfrac{d(\sin\theta)}{d \theta}$;
+What we have to investigate is the value of $\dfrac{d(\sin\theta)}{d\theta}$;
 or, in other words, if the angle~$\theta$ varies, we have to find the relation
@@
 is the angle. Now, if $\theta$ is supposed to increase by the addition to it
-of the small angle $d \theta$---an element of angle---the height of~$y$, the
-sine, will be increased by a small element~$dy$. The new height~$y + dy$ will
-be the sine of the new angle $\theta+ d \theta$, or, stating it as an
-equation,
+of the small angle $d\theta$---an element of angle---the height of~$y$, the
+sine, will be increased by a small element~$dy$. The new height~$y+dy$ will be
+the sine of the new angle $\theta+d\theta$, or, stating it as an equation,
 \[
-y+dy = \sin(\theta+ d \theta);
+y+dy=\sin(\theta+d\theta);
 \]
@@
 \[
-dy = \sin(\theta+ d \theta)- \sin\theta.
+dy=\sin(\theta+d\theta)-\sin\theta.
 \]
@@
 
-%TCIMACRO{\FRAME{dtbpF}{2.8202in}{2.2623in}{0pt}{}{}{project_gutenberg-1.bmp}%
+%TCIMACRO{\FRAME{dtbpFX}{2.8202in}{2.2623in}{0pt}{}{}{project_gutenberg-1.bmp}%
 %{\special{ language "Scientific Word";  type "GRAPHIC";
@@
 \begin{center}
-\includegraphics[
+\fbox{\includegraphics[
 natheight=2.222600in,
@@
 {C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__3.jpg}%
+}
 \end{center}
@@
 \begin{enumerate}
-\item .png, the logo on the first page
+\item .png, the logo on the first page using in line placement
 
-\item .jpg, Fig. 43
+\item .jpg, Fig. 43 using floating placement with only the here placement option
 
-\item .wmf, Fig. 44
+\item .wmf, Fig. 44 using displayed placement
 
-\item .eps, Fig 45
+\item .eps, Fig 45 using displayed placement
 
-\item .bmp, the logo on the last page
+\item .bmp, the logo on the last page using displayed placement with a frame
+around the graphic
 \end{enumerate}

### 2017-07-18 prince/base/content/GraphOverlay.js
Fixed a problem where <math> was being wrapped in <math>

@@ -1150,9 +1150,10 @@ Plot.prototype =
             textval = this.adjustExpressionForComputation(plotData);
           if ((textval !== "") && (textval !== "unspecified")) {
               // textval = runFixup(textval); // runFixup(runFixup(textval));
-            tNode = (new DOMParser()).parseFromString (textval, "text/xml");
-            removeInvisibles(tNode);
-            textval = GetFixedMath(tNode);
+              tNode = (new DOMParser()).parseFromString (textval, "text/xml");
+	      tNode = tNode.documentElement;
+              removeInvisibles(tNode);
+              textval =  GetFixedMath(tNode);
             tNode = (new DOMParser()).parseFromString (textval, "text/xml");
             DOMEnode.appendChild (tNode.documentElement);
             DOMPlot.appendChild (DOMEnode);
@@ -2320,7 +2321,7 @@ function insertNewGraph(math, dimension, plottype, optionalAnimate, editorElemen
   if (!editorElement) editorElement = msiGetActiveEditorElement();
   var editor = msiGetEditor(editorElement);
   var checkedExpr = preParsePlotExpression(math, plottype, selection, editorElement);
-  var expr = GetFixedMath(checkedExpr); //runFixup(GetFixedMath(checkedExpr));
+    var expr = GetMathAsString(checkedExpr); //GetFixedMath(checkedExpr); //runFixup(GetFixedMath(checkedExpr));
 
   var graph = new Graph();
   var frame = graph.frame;

### 2017-07-18 prince/base/content/ComputeUtils.js
Fixed a problem where <math> was being wrapped in <math>

@@ -5,10 +5,13 @@
 
 function GetMathAsString(math)
 {
-  var ser = new XMLSerializer();
-  var mathstr = ser.serializeToString(math);
-  if (math.localName !== "math")
-    mathstr = "<math>" + mathstr + "</math>";
+    var ser = new XMLSerializer();
+    var mathstr = ser.serializeToString(math);
+    var localname = math.localName;  
+    if (localname !== "math"){
+	//dump("###" + math.localName + " !== \"math\"");
+	mathstr = "<math>" + mathstr + "</math>";
+    }
   // risky string surgery, but it works in simple cases
   mathstr = mathstr.replace(/ _moz_dirty=\"\"/g,"");
   mathstr = mathstr.replace(/<mi\/\>/g,"");

### 2017-10-16 prince/base/content/dialogs/Minipage.js
Miscellaneous changes

@@ -1,12 +1,13 @@
 var frmElement = {};
 var newElement = true;
 var gd;
-var gDialog;
 var editor;
 var msiframe;
 var isNewNode;
 var gFrameModeTextFrame = true ;
 var gFrameModeImage = false ;
+
+Components.utils.import("resource://app/modules/unitHandler.jsm");
 
 var msiframe;
 var scale= .25; /*scale of reduced diagram*/
@@ -14,11 +15,6 @@ var editor;
 
 function startUp()
 {
-  var widthregexp = /width\s*\:\s*([0-9]+)([a-z]*)\s*;/;
-  var heightregexp = /height\s*\:\s*([0-9]+)([a-z]*)\s*;/;
-  var match;
-  var width, height;
-  var style;
   try {
     var editorElement = msiGetParentEditorElementForDialog(window);
     editor = msiGetEditor(editorElement);
@@ -28,23 +24,12 @@ function startUp()
       return;
     }
     msiframe = null;
-    var i = 0;
-    while (i < window.arguments.length) {
-      msiframe = window.arguments[i];
-      if (msiframe !== null  && msiframe.nodeName === 'msiframe') break;
-      i ++ ;
-    }
-    isNewNode = !(msiframe) || msiframe.nodeName !== 'msiframe';
-    if (isNewNode) {
-      msiframe = editor.createFrameWithDefaults('textframe', false, null, 0);
-      editor.getFrameStyleFromAttributes(msiframe);
-    } 
-    gDialog = {};
-
-    gd = initFrameTab(gDialog, msiframe, false, null);
-    gSizeState.selectCustomSize();
-    gSizeState.setPreserveAspectRatio(false);
-    document.getElementById('sizeRadio').hidden = true;
+    if (window.arguments.length > 0) msiframe = window.arguments[0];
+    isNewNode = !(msiframe);
+    gd = new Object();
+    
+    gd = initFrameTab(gd, msiframe, isNewNode, null);
+//    setHasNaturalSize(false);
   // we don't want heavy-weight frames inline
     document.getElementById('inline').hidden=true;
   //  initFrameSizePanel(); // needed when the user can set the size
@@ -56,7 +41,7 @@ function startUp()
 
 
 function onOK() {
-  if (!isValid()) return false; // isValid is in msiFrameOverlay.js
+  if (!isValid()) return false; // isValid is in msiFrameOverlay.j s 
   editor.beginTransaction();
 	if (isNewNode) 
 	{
[…]

### 2017-10-16 prince/base/content/dialogs/msiFrameOverlay.js

@@ -388,6 +388,7 @@ function initFrameTab(dg, element, newElement,  contentsElement)
   dg.custom               = document.getElementById( "custom" );
   dg.constrainCheckbox    = document.getElementById( "constrainCheckbox" );
   dg.sizeRadio            = document.getElementById( "sizeRadio" );
+  dg.keyInput             = document.getElementById( "keyInput" );
   gSizeState.sizeUnit = currUnit;
 
   var fieldList = [];

### 2017-10-16 prince/base/content/msiEditorUtilities.js

@@ -11497,7 +11497,7 @@ function xmlFragToTeX(intermediateString) {
 }
 function getChildByTagName(anElement, tagName) {
   var elements;
-  if (!anElement || !(anElement.getElementsByTagName))
+  if (anElement && anElement.getElementsByTagName)
     elements = anElement.getElementsByTagName(tagName);
   if (elements && elements.length > 0)
     return elements[0];
@@ -11724,7 +11724,7 @@ function readTextOnClipboard() {
   }
   catch (e)
   {
-    dump("text/unicode not supported\n\n");
+    return retval;
   }
   trans.removeDataFlavor("text/unicode");
   return retval;

### 2017-10-16 editor/msiediting/src/msiEditingManager.cpp
Miscellaneous changes

@@ -922,10 +922,8 @@ msiEditingManager::InsertSymbol(nsIEditor * editor,
   nsresult res(NS_ERROR_FAILURE);
   nsCOMPtr<nsIDOMNode> selStartNode;
   PRInt32 selStartOffset;
-  // BBM: force collapsed selection for first version
   res = selection->GetFocusNode(getter_AddRefs(selStartNode));
   res = selection->GetFocusOffset(&selStartOffset);
-//  selection->Collapse(selStartNode, selStartOffset);
 
   NS_ASSERTION(editor && selection && node, "Null editor, selection or node passed to msiEditingManager::InsertSymbol");
   nsCOMPtr<nsIHTMLEditor> htmleditor = do_QueryInterface(editor);

### 2017-10-16 prince/base/content/dialogs/ComputeGraphSettings.js

@@ -73,7 +73,7 @@ function Startup(){
       units = "pt";
       frame.setAttribute("units") = units;
     }
-    // setHasNaturalSize(false);
+//    setHasNaturalSize(false);
 #ifndef PROD_SNB
     setCanRotate(false);
 #endif
@@ -234,7 +234,39 @@ function OK() {
   graph.setGraphAttribute("returnvalue", "true");
   graph.recomputeVCamImage(editorElement, graphnode);
   initVCamObjects(editor.document);
-return true;
+  //  var editor = msiGetEditor(editorElement);
+//   changed = true;
+//   if (changed) {
+//     graph.recomputeVCamImage(editorElement);
+//   }
+//   theWindow = window.opener;
+//   if (!theWindow || !(theWindow.hasOwnProperty("nonmodalRecreateGraph"))) {
+//     theWindow = msiGetTopLevelWindow();
+//   }
+//   try {
+//     theWindow.nonmodalRecreateGraph(graph, window.arguments[2], editorElement);
+//   }
+//   catch (e) {}
+//   var parentWindow = window.opener;
+//   var data;
+//   var obj = graphnode.getElementsByTagName("object");
+//   if (obj && obj.length)
+//   {
+//     obj = obj[0];
+//   }
+// //     if (obj) {
+// //       if (obj.wrappedJSObject) obj = obj.wrappedJSObject;
+// //       try {
+// //         data = graphnode.getElementsByTagName('graphSpec')[0].getAttribute('ImageFile');
+// //         obj.setAttribute('data', data);
+// // //        parentWindow.doVCamInitialize(obj);
+// //       }
+// //       catch(e)
+// //       {}
+// //     }
+// //  }
+// //  graph.setGraphAttribute("returnvalue", "true");
+  return true;
 }
 
 // Extract the values from the dialog and store them in the data structure
@@ -821,12 +853,12 @@ function hideShowControls(dim, ptype, graphAnimated, aiMethod)
 function openVariablesAndIntervalsDlg()
 {
   var graphData = new graphVarData(graph);
-  openDialog('chrome://prince/content/intervalsAndAnimation.xul', 'plotintervalsandanimation', 'chrome,close,titlebar,modal,resizable', graphData);
+  openDialog('chrome://prince/content/intervalsAndAnimation.xul', 'Plot Intervals and Animation', 'chrome,close,titlebar,modal,resizable', graphData);
 }
 
[…]

### 2018-11-16 filters/mathml/xfltutil.cpp
Added code to import more types of fenced matrices. Still needs to add some mrows. To get PDF to work, you must include the mathtools package in some cases. I haven't done cases and rcases yet.

@@ -1253,7 +1253,9 @@ TNODE* MATRIXtoExternalFormat( TNODE* MATRIX_node ) {
           TCI_ASSERT(0);
         break;
       }
-
+      if (rv_subtype >= 712 && cont->var_value[1]=='s') {
+        rv_subtype += 10;
+      } // these are psmallmatrix ... Bsmallmatrix
     } else
       TCI_ASSERT(0);
   }

### 2018-11-16 filters/mathml/ltex2mml.cpp
These belonged in the previous commit

@@ -2463,7 +2463,7 @@ TNODE* LaTeX2MMLTree::MathStructureToMML( TNODE* obj_node,
 
         if        ( usub == 140 ) {
           mml_rv  =  LaTeXCases2MML( array,out_of_flow_list );
-        } else if ( usub >= 710 && usub <= 716 ) {
+        } else if ( (usub >= 710 && usub <= 716 || (usub >= 722 && usub <= 726)) ) {
           HLinesToBucket( array,FALSE );
         // These LaTeX schemata don't have a {cols} arg
           mml_rv  =  Matrix2MML( array,out_of_flow_list,usub );
@@ -2937,7 +2937,12 @@ TNODE* LaTeX2MMLTree::MathStructureToMML( TNODE* obj_node,
       case 713  :       // \bmatrix
       case 714  :       // \vmatrix
       case 715  :       // \Vmatrix
-      case 716  : {     // \Bmatrix
+      case 716  :       // \Bmatrix
+      case 722  :       // \psmallmatrix
+      case 723  :       // \bsmallmatrix
+      case 724  :       // \vsmallmatrix
+      case 725  :       // \Vsmallmatrix
+      case 726  : {     // \Bsmallmatrix
         HLinesToBucket( obj_node,FALSE );
     // These LaTeX schemata don't have a {cols} arg
         mml_rv  =  Matrix2MML( obj_node,out_of_flow_list,subclass );
@@ -15492,7 +15497,7 @@ TNODE* LaTeX2MMLTree::Matrix2MML( TNODE* tex_matrix_node,
 
 // All except matrix and smallmatrix have built-in delimiters
 
-  if ( subtype >= 712 && subtype <= 716 ) {
+  if ( (subtype >= 712 && subtype <= 719 && subtype != 717) || subtype >= 721 && subtype <=726 ) {
 
 /* from MathML.gmr, context MATH
 (<uID5.712.0,l>U0xxxx,form="prefix"   fence="true" stretchy="true" symmetric="true" lspace="0em" rspace="0em"
@@ -15501,6 +15506,8 @@ TNODE* LaTeX2MMLTree::Matrix2MML( TNODE* tex_matrix_node,
 .
 {<uID5.716.0,l>U0xxxx,form="prefix"   fence="true" stretchy="true" symmetric="true" lspace="0em" rspace="0em"
[…]

### 2020-06-09 prince/base/content/dialogs/ComputeGraphSettings.js
Working on upgrading mathml editors in dialog

@@ -187,7 +187,7 @@ function initializeAxisLabelEditors() {
     editorElement = document.getElementById(id);
     if (editorElement) {
       editorElement.mbSinglePara = true;
-      theStringSource = 'get me from graph data';
+      theStringSource = GetComputeString("Math.emptyForInput");
       editorInitializer.addEditorInfo(editorElement, theStringSource, true);
     }
   }
@@ -213,13 +213,13 @@ function initializeViewIntervalEditors() {
     editorElement = document.getElementById(id + 'rangelow');
     if (editorElement) {
       editorElement.mbSinglePara = true;
-      theStringSource = 'get me from graph data';
+      theStringSource = GetComputeString("Math.emptyForInput");
       editorInitializer.addEditorInfo(editorElement, theStringSource, true);
     }
     editorElement = document.getElementById(id + 'rangehigh');
     if (editorElement) {
       editorElement.mbSinglePara = true;
-      theStringSource = 'get me from graph data';
+      theStringSource = GetComputeString("Math.emptyForInput");
       editorInitializer.addEditorInfo(editorElement, theStringSource, true);
     }
   }

### 2020-12-30 editor/libeditor/html/nsHTMLDataTransfer.cpp
I've done the hard part of tuning selections for inserting fences, fractions, roots, etc.

@@ -406,7 +406,7 @@ nsHTMLEditor::InsertMathNode
     // We can't insert plain text, only an mi, an mn, an mo or a mtext. This should happen only when pasting, so insertThisNode should
     // have a parent
     res = insertThisNode->GetParentNode(getter_AddRefs(nodeToInsert));
-    if (!nodeToInsert) return NS_ERROR_INVALID_ARG;
+if (!nodeToInsert) return NS_ERROR_INVALID_ARG;
   }
   else {
     nodeToInsert = insertThisNode;
@@ -560,7 +560,7 @@ PRBool TrimDocFragment( nsIDOMNode * fragmentAsNode) {
   // children (such as msub, msup and mfrac) which require 2 children) actually have that many in the
   // fragment. If not, we replace the offending tag with an mrow.
 
-  res = ValidateMathSyntax( fragmentAsNode); */
+  res = z( fragmentAsNode); */
 
 PRUint32 MathChildCount( nsIDOMElement * aElement) {
   nsCOMPtr<nsIDOMNodeList> children;

### 2020-12-30 editor/libeditor/html/nsHTMLEditRules.cpp

@@ -1,3 +1,4 @@
+
 /* -*- Mode: C++; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
 /* ***** BEGIN LICENSE BLOCK *****
  * Version: MPL 1.1/GPL 2.0/LGPL 2.1
@@ -747,8 +748,8 @@ nsHTMLEditRules::WillDoAction(nsISelection *aSelection,
       return WillMakeStructure(aSelection, info->blockType, aCancel, aHandled);
     case kRemoveStructure:
       return WillRemoveStructure(aSelection, aCancel, aHandled);
-	    case kRemoveEnv:
-	      return WillRemoveEnv(aSelection, aCancel, aHandled);
+      case kRemoveEnv:
+        return WillRemoveEnv(aSelection, aCancel, aHandled);
   }
   return nsTextEditRules::WillDoAction(aSelection, aInfo, aCancel, aHandled);
 }
@@ -2878,7 +2879,7 @@ nsHTMLEditRules::InsertBRIfNeeded(nsISelection *aSelection)
   if (NS_FAILED(res)) return res;
   if (!node) return NS_ERROR_FAILURE;
 
-	  // examine selection
+    // examine selection
   nsWSRunObject wsObj(mHTMLEditor, node, offset);
   if (((wsObj.mStartReason & nsWSRunObject::eBlock)|| (wsObj.mStartReason & nsWSRunObject::eBreak)) &&
       (wsObj.mEndReason & nsWSRunObject::eBlock))
@@ -2912,7 +2913,7 @@ nsHTMLEditRules::InsertBRIfNeeded(nsISelection *aSelection)
         res = mHTMLEditor->CreateBR(node, offset, address_of(brNode), nsIEditor::ePrevious);
       }
     }
-	}
+  }
   return res;
 }
 
@@ -3329,7 +3330,7 @@ PRInt32 FindCursorIndex(nsHTMLEditor* editor,
           return str.Length();
       }
 
-  }	else {
+  } else {
     nsCOMPtr<nsIDOMElement> element = do_QueryInterface(node);
 
     nsCOMPtr<nsIDOMNodeList> childList;
@@ -4160,9 +4161,9 @@ void   hackSelectionCorrection(nsHTMLEditor * ed,
   //       ||name.EqualsLiteral("mn")
   //       ||name.EqualsLiteral("mo"))
   //     {
[…]

### 2020-12-30 editor/libeditor/html/nsIHTMLEditRules.h

@@ -63,6 +63,7 @@ public:
   NS_IMETHOD InsertStructure(nsIDOMNode *inNode, nsIDOMNode **outNode,
                            const nsAString &aStructureType, nsIAtom * atomNamespace )=0;
   NS_IMETHOD InsertBRIfNeeded(nsISelection *aSelection)=0;
+  NS_IMETHOD PromoteMathRange(nsIDOMRange *domRange)=0;
   NS_IMETHOD CanonicalizeMathSelection(nsIDOMRange * domRange) = 0;
   
 };

### 2020-12-30 prince/base/content/msiComposerCommands.js

@@ -394,6 +394,10 @@ function msiGoUpdateCommandState(command, editorElement)
     break;
 
     case "cmd_MSImathtext":
+    case "cmd_MSIinlineMathCmd":
+    case "cmd_MSItextModeCmd":
+    case "cmd_MSItextmath":
+    case "cmd_MSImathtextButton":  
       updateMathText(editorElement);
     break;
 

### 2020-12-30 prince/base/content/msiEditor.js

@@ -4710,20 +4710,21 @@ function msiRewriteHideInvisibles(editor) {
       parentNode.insertBefore(newNode, nextNode);
     else
       parentNode.appendChild(newNode);
-  }
+  } 
 
-  var rootElement = editor.document.documentElement;
-  var treeWalker = editor.document.createTreeWalker(rootElement, NodeFilter.SHOW_ELEMENT,
-    findInvisNodes, true);
-  if (treeWalker) {
-    for (var currNode = treeWalker.nextNode(); currNode != null;) {
-      var nextNode = treeWalker.nextNode();
-      replaceByTextNode(currNode);
-      currNode = nextNode;
+   // continue msiRewriteHideInvisibles
+    var rootElement = editor.document.documentElement;
+    var treeWalker = editor.document.createTreeWalker(rootElement, NodeFilter.SHOW_ELEMENT,
+      findInvisNodes, true);
+    if (treeWalker) {
+      for (var currNode = treeWalker.nextNode(); currNode != null;) {
+        var nextNode = treeWalker.nextNode();
+        replaceByTextNode(currNode);
+        currNode = nextNode;
+      }
+      rootElement.normalize();
     }
-    rootElement.normalize();
   }
-}
 
 function msiInitPasteAsMenu(editorElement) {
   if (!editorElement)

### 2020-12-30 prince/base/content/vcamoverlay.js

@@ -551,9 +551,9 @@ VCamObject.prototype = {
           else this.obj.startAnimation();
           isRunning = !isRunning;
           break;
-		case "cmd_vcReset":
-		  this.obj.resetViewpoint();
-		  break;
+    case "cmd_vcReset":
+      this.obj.resetViewpoint();
+      break;
         case "cmd_vcFitContents":
           this.obj.fitContents();
           break;

### 2020-12-30 python/lldbutils/lldbutils/content.py

@@ -93,6 +93,12 @@ def mnodetree(debugger, command, result, dict):
    if len(newcommand) > 0:
        debugger.HandleCommand("exp nsString outputString; DumpNode(" + newcommand + ", 0, 1, outputString), outputString;")
 
+def mrange(debugger, command, result, dict):
+   """Displays name and attributes for a range and all its descendents"""
+   newcommand = modcommand(debugger, command, result, dict)
+   if len(newcommand) > 0:
+       debugger.HandleCommand("exp nsString outputString; DumpRange(" + newcommand + ", 0, outputString), outputString;")
+
 
 
 
@@ -104,6 +110,7 @@ def init(debugger):
     debugger.HandleCommand("command script add -f lldbutils.content.ptag ptag")
     debugger.HandleCommand("command script add -f lldbutils.content.mnode mnode")
     debugger.HandleCommand("command script add -f lldbutils.content.mnodetree mnodetree")
+    debugger.HandleCommand("command script add -f lldbutils.content.mrange mrange")
     debugger.HandleCommand("command script add -f lldbutils.content.mparent mparent")
     debugger.HandleCommand("command script add -f lldbutils.content.mfirstchild mfirstchild")
     debugger.HandleCommand("command script add -f lldbutils.content.mnext mnext")

### 2020-12-30 editor/libeditor/base/nsEditor.cpp
I've done the hard part of tuning selections for inserting fences, fractions, roots, etc.

@@ -208,6 +208,24 @@ void DumpNode(nsIDOMNode *aNode, PRInt32 indent, bool recurse, nsAString& output
 #endif
 }
 
+void DumpRange( nsIDOMRange * range, PRInt32 indent, nsAString& output) {
+#ifdef DEBUG
+  nsCOMPtr<nsIDOMNode> anchorNode, focusNode;
+  PRInt32 anchorOffset, focusOffset;
+  range->GetStartContainer(getter_AddRefs(anchorNode));
+  range->GetStartOffset(&anchorOffset);
+  range->GetEndContainer(getter_AddRefs(focusNode));
+  range->GetEndOffset(&focusOffset);
+  printf("Anchor: offset=%d\n", anchorOffset);
+  output.Append(NS_LITERAL_STRING("ANCHOR: OFFSET=  "));
+  DumpNode(anchorNode, indent, PR_TRUE, output);
+  printf("Focus: offset=%d\n", focusOffset);
+  output.Append(NS_LITERAL_STRING("FOCUS: OFFSET=  "));
+  DumpNode(focusNode, indent, PR_TRUE, output);
+  output.Append(NS_LITERAL_STRING("\n"));
+#endif //Debug
+}
+
 } // extern C
 
 #ifdef DEBUG_Barry

### 2020-12-30 editor/libeditor/html/nsHTMLEditRules.h

@@ -134,21 +134,26 @@ public:
   NS_IMETHOD DidDeleteSelection(nsISelection *aSelection);
   NS_IMETHOD AdvanceCursorToEditableText(nsIDOMNode *aStartNode, PRUint32 aOffset,
                                          nsIDOMNode **aOutNode, PRUint32 *aOutOffset);
-  NS_IMETHOD CanonicalizeMathSelection(nsIDOMRange* domRange);
-  
-protected:
-
-  enum RulesEndpoint
+ enum RulesEndpoint
   {
     kStart,
     kEnd
   };
+  
+  NS_IMETHOD GetPromotedMathPoint(RulesEndpoint aWhere, nsIDOMNode *aNode, PRInt32 aOffset, nsIDOMNode *ancestor,
+                                  nsCOMPtr<nsIDOMNode> *outNode, PRInt32 *outOffset);
+  NS_IMETHOD PromoteMathRange(nsIDOMRange *aRange);
+  NS_IMETHOD CanonicalizeMathSelection(nsIDOMRange* domRange);
+  
 
+ 
   enum BRLocation
   {
     kBeforeBlock,
     kBlockEnd
   };
+
+protected:
 
   // nsHTMLEditRules implementation methods
   nsresult WillInsert(nsISelection *aSelection, PRBool *aCancel);

### 2020-12-30 editor/libeditor/msi/msiEditor.cpp

@@ -530,35 +530,29 @@ msiEditor::InsertBinomial(const nsAString& opening, const nsAString& closing,
 NS_IMETHODIMP
 msiEditor::InsertSqRoot()
 {
-  nsresult res(NS_ERROR_FAILURE);
+  nsresult res(NS_OK);
   nsAutoEditBatch beginBatching(this);
   if (!(mFlags & eEditorPlaintextMask)) // copied from nsHTMLEditor -- I don't know if this is an issue
   {
-    nsCOMPtr<nsISelection> selection;
     nsCOMPtr<nsIDOMNode> startNode, endNode;
     PRInt32 startOffset(0), endOffset(0);
     PRBool bCollapsed(PR_FALSE);
     nsCOMPtr<nsIHTMLEditRules> htmlRules = do_QueryInterface(mRules);
-    if (htmlRules) {
-      nsCOMPtr<nsISelection> sel;
-      GetSelection(getter_AddRefs(sel));
-      nsCOMPtr<nsIDOMRange> domRange;
-      sel->GetRangeAt(0, getter_AddRefs(domRange));
-      htmlRules->CanonicalizeMathSelection(domRange); // BBM 2016-08-16
-    }
-    res = GetNSSelectionData(selection, startNode, startOffset, endNode,
-                           endOffset, bCollapsed);
+    nsCOMPtr<nsISelection> sel;
+    GetSelection(getter_AddRefs(sel));
+    
+
     if (NS_SUCCEEDED(res))
     {
       nsCOMPtr<nsIDOMNode> theNode;
       PRInt32 theOffset(0);
       theNode = startNode;
-      theOffset = startOffset;
+        
       if (NS_SUCCEEDED(res))
       {
         nsCOMPtr<nsIEditor> editor;
         QueryInterface(NS_GET_IID(nsIEditor), getter_AddRefs(editor));
-        res = m_msiEditingMan->InsertSqRoot(editor, selection, theNode, theOffset);
+        res = m_msiEditingMan->InsertSqRoot(editor, sel, theNode, theOffset);
       }
     }
   }
@@ -568,24 +562,26 @@ msiEditor::InsertSqRoot()
 NS_IMETHODIMP
 msiEditor::InsertRoot()
 {
-  nsresult res(NS_ERROR_FAILURE);
+  nsresult res(NS_OK);
   nsAutoEditBatch beginBatching(this);
[…]

### 2020-12-30 editor/msiediting/src/msiEditingManager.cpp

@@ -993,6 +993,36 @@ msiEditingManager::InsertSymbol(nsIEditor * editor,
   return res;
 }
 
+// This is a utility routine to help those math insertion commands where the selection gets copied into the new structure/\.
+// Examples include fences, raditcals, and fractions (where the selection is copied into the numberator)
+
+NS_IMETHODIMP
+msiEditingManager::PrepareSelectionForCopying(msiIMathMLEditor* mathmlEditor, nsIDOMRange* range, nsIDOMDocumentFragment ** copiedContent) {
+  nsresult res(NS_OK);
+  PRBool isCollapsed(0);
+    range->GetCollapsed(&isCollapsed);
+  mathmlEditor->CanonicalizeMathSelection(range);
+  if (!isCollapsed) range->CloneContents(copiedContent);
+  mathmlEditor->PromoteMathRange(range);
+  return res;
+}
+
+NS_IMETHODIMP
+msiEditingManager::SetSelectionFromRange(nsIDOMRange * range, nsISelection* selection) {
+  nsresult res(NS_OK);
+  nsCOMPtr<nsIDOMNode> startNode, endNode;
+  PRInt32 startOffset, endOffset;
+  res = range->GetStartContainer(getter_AddRefs(startNode));
+  res = range->GetEndContainer(getter_AddRefs(endNode));
+  res = range->GetStartOffset(&startOffset);
+  res = range->GetEndOffset(&endOffset);
+  selection->Collapse(startNode, startOffset);
+  selection->Extend(endNode, endOffset);
+  return res;
+}
+
+
+
 NS_IMETHODIMP
 msiEditingManager::InsertFraction(nsIEditor * editor,
                                   nsISelection * selection,
@@ -1001,54 +1031,59 @@ msiEditingManager::InsertFraction(nsIEditor * editor,
                                   const nsAString & lineThickness,
                                   PRUint32 attrFlags)
 {
-   nsresult res(NS_OK);
-//   nsCOMPtr<nsIDOMRange> range;
-//   nsCOMPtr<nsIDOMDocumentFragment> content;
+  nsresult res(NS_OK);
+  nsCOMPtr<nsIDOMRange> range;
+  nsCOMPtr<nsIDOMDocumentFragment> content;
+  selection->GetRangeAt(0, getter_AddRefs(range));
[…]

### 2021-03-24 prince/base/content/dialogs/indexentry.js
Do not make varioref a required package for an index item.  Varioref does nothing with the index.

@@ -227,7 +227,6 @@ function onAccept()
 
   // activeEditor.beginTransaction();
   if (!node) return 0;
-  node.setAttribute("req", "varioref");
   var v = primary.value;
   node.setAttribute("pri", v);
   v = secondary.value;
